### 2011-10-20 bylaws.tex
Initial files from Dumont's latex conversion project a while back.

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc. 
%  However, if a sub part is moved to a different part, its references must be 
%  changed.
% -This document must be ratified by the House (as per the Constitution), 
%  then printed, signed, notarized, and placed in the House filing cabinet
%  if changes are to be officialized.

\documentclass{article}
% The xr package allows external references
\usepackage{xr}

% This package is useful for debugging label problems
% Comment out in final revision
%\usepackage{showkeys}

% Define the external document to be constitution for cross referencing purposes
\externaldocument{constitution}

% Title page information
\title{Computer Science House By-Laws}
\author{Computer Science House Executive Board}
% Last Modified Date
\newcommand{\datechanged}{Monday, April 5, 2004}
\date{\datechanged}

% Fix margins
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}

% Use \article for articles and \asection for sections of articles.
% Automatically provide labels with the same article or section title.
\newcommand{\bylaw}[1]{\section{#1} \label{#1}}
\newcommand{\bsection}[1]{\subsection{#1} \label{#1}}
\newcommand{\bsubsection}[1]{\subsubsection{#1} \label{#1}}
\renewcommand{\thesection}{By-Law \Roman{section}}
\renewcommand{\thesubsection}{Section \arabic{section}.\Alph{subsection}}
\renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill  As of \datechanged \hfill Page }}
% Reference example:
%Test reference \ref{House Objectives} House Objectives.

\begin{document}
% Title
\maketitle

% By-Laws
\bylaw{By-Law Structure}
By-Laws define the more flexible aspects of the House. Any semantic change to a by-law requires the change to be proposed at a House Meeting, discussed, followed by a House vote as described in \ref{Voting}, Voting. A by-law may be overridden by an immediate House vote with a quorum of sixty-six percent of the number of all House members privileged to vote. A vote equaling or exceeding sixty-six percent of all House members present during the vote is required for the override to go through. The By-Laws are arranged by section with each section of By-Laws pertain to a particular governing aspect of the House

\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the ten weeks of Fall, Winter, and Spring Academic Quarters.  The Summer Academic Quarter, all between Quarter Interim, and all end of Quarter Exam Weeks are considered Non-Standard Operating Session.  Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.

\bylaw{Operations of the Executive Board}
\bsection{Weekly Notes}
The Executive Board members are expected to submit to the House, notes for their meetings each week.
\bsection{The House Rules}
The House Rules shall contain the following information:
\begin{itemize}
\item The Section of \ref{Membership} Membership that corresponds to the membership status of the signing member.
\item The explanatory paragraph from \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process} describing the Evaluation Process
\item The Computer Science House Code of Conduct Sheets pertaining to responsible utilization of the Computer Science House and Rochester Institute of Technology facilities.
\end{itemize}
\bsection{Closed Executive Board}
\newcommand{\writeoutref}{\ref{Executive Board}, \ref{Voting Members},}
\bsubsection{Closed Executive Board Meetings are open only two the Chairman and Voting Members of the Executive Board as deﬁned in Article 6, Section A, Subsection 3, and those with express permission of the Executive Board. }

\bsubsection{A closed Executive Board meeting may be called at any time by any member of the Executive Board.  However, the Chairman and at least two-thirds of the Voting Members as defined in Article 6, Section A, Subsection 3 must be present for a meeting to be called.}

\bylaw{Operations of the Financial Committee}
\bsection{Amount of House Dues}
The amount of dues for Resident Members is thirty dollars (\$35.00) per Academic Quarter.  The amount of dues for Non-Resident Members is twenty-five dollars (\$30.00) per Academic Quarter.
\bsection{Collection of House Dues}
The Financial Director is responsible for ensuring the House is notified of the due date for the payment of House dues at least two weeks in advance of the actual due date. If a member is unable to pay House dues by the due date, he or she should contact the Financial Director prior to the due date or his or her payment will be considered delinquent.
\\* \\*
If the Financial Director determines that the member's reason for inability to pay House dues is sufficient, an extended due date will be set for that member. If the Financial Director determines the reason to be insufficient, the member may appeal the Executive Board. If the Executive Board upholds the Financial Director's ruling, then the member's payment is considered delinquent. If the Executive Board overrides the Financial Director's ruling, the Executive Board will set an extended due date for that member.
\\* \\*
If the member again finds himself or herself unable to pay dues at the time of the extended due date, he or she may follow the same procedure for the first extension.
\\* \\*
If a member's payment goes delinquent for any of the above reasons, his or her case is brought before the Executive Board, and action may be taken at the discretion of the Executive Board. The Financial Director should be present at this hearing. If the initial House judicial board feels it is unable to adequately resolve the case, or the member wishes to appeal any ruling by the initial House judicial board, the case may be presented to the Executive Board as the final House judicial board.
\\* \\*
The Executive Board has the authority to enforce House sanctions up to and including revocation of House privileges and/or the removal of membership status. Once the dues have been paid, the judicial board has the option of dropping all current sanctions or continuing the current sanctions until they have been completed. The Executive Board may not continue to render new sanctions once the dues have been paid.
\bsection{Breakdown of Dues for Committee Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Committee or Budget Name & Percentage of Dues \\
\hline
\hline
Operational Communications &	19\% \\
\hline
Evaluations \& Selections & 4\% \\
\hline
House History & 9\% \\
\hline
House Improvements & 9\% \\
\hline
Research and Development & 19\% \\
\hline
Miscellaneous & 5\% \\
\hline
House Accum. & 10\% \\
\hline
Social & 25\% \\
\hline
\end{tabular}
\end{center}
\bsection{Expenditure Approval}
All House expenditures must be approved by the financial director and the director responsible for the budget from which the funds will be drawn. If any single expenditure exceeds fifty dollars (\$50.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated. If any total expenditure exceeds seventy-five dollars (\$75.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated. A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
Any project requiring more than \$300 in total funding from CSH must include a Complete Project proposal, including a Project Budget, Timeline and Resources needed. The person requesting the funds must then report to executive board once per week on the progress of the project.

\bylaw{Operations of the Evaluations Committee}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for an applicant or new member to meet existing House members, learn House history, demonstrate their involvement potential in the House, and allow existing House members to meet and evaluate the applicant or new member.
\\* \\*
The Evaluations Committee chooses between 1 and 3 House members to be Introductory Process Advisors. The advisors organize the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.  All participants will receive an Intro. Packet minimally containing the following information:
\begin{itemize}
\item A description of the History of Computer Science House
\item A list of all Resident members, as defined in Article V, Membership.
\item The Computer Science House Constitution and By-Laws.
\item The Computer Science House Dictionary
\end{itemize}
The Introductory Process lasts for a minimum of six weeks from the initiation of the process, until the participant has completed all of the following requirements. The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process based on requirements listed in the Introductory Process Proposal. However, the Introductory Project must be complete before the Introductory Evaluation occurs.
\\* \\*
The participant is given 2 weeks complete the following lists, termed the Intro. Sheets:
\begin{itemize}
\item For each Resident member, Executive Board member, and for Fifteen Non-Resident and Alumni members (in addition to Non-Resident Executive Board Members), list:
\begin{itemize}
\item The member's home town
\item The members local room and phone, or address as applicable
\item The member's major and year
\item The House committee(s) the member is interested in
\item A question of your own to get to know the member
\item The member's signature.
\end{itemize}
\item For each House committee, list:
\begin{itemize}
\item The full name of the committee
\item Some of the responsibilities of the committee
\item The name of the committee's director
\item The weekly meeting time and place
\end{itemize}
\item Seven annual Computer Science House social events
\item Seven major Computer Science House technical achievements
\end{itemize}
The participant is also expected to be involved in the following:
\begin{itemize}
\item  Attend all House meetings during the process
\item  Attend at least one House committee meeting each week of the process
\item  Attend at least one House social event during the process
\item  Show an acceptable amount of participation in at least one Technical Project.  Acceptable participation is determined by the project leader and the Introductory Evaluation Process described in By-Law V, Section F, Subsection 5.  This project is in addition to the Technical Project required for all Resident and Non-Resident members as stated in By-Law V, Section G.
\end{itemize}
The participant is also expected to be involved in the Introductory Project. The Introductory Project is an annual fundraiser that takes place during the Fall Quarter Introductory Process. It is organized and carried out by all Introductory Process participants. All of the proceeds go to a charity chosen in advance by the participants. The participants must elect a non-voting Executive Board Representative, termed the Freshman President who is required to represent the Introductory Process participants on the Executive Board. The Freshman President is responsible for any internal Introductory Project duties as well as for bringing a written Introductory Project Proposal to the Executive Board. The Executive board will hold discussion followed by a closed ballot Simple Majority Vote according to \ref{Voting} Voting, \ref{Simple Majority Vote} Simple Majority Vote, to determine if the proposed project fulfills the Introductory Project requirements.
\\* \\*
At the end of the Introductory Period, there will be an Introductory Evaluation, described in By-Law V, Section F, Subsection 5, to determine which members will be extended offers of full membership.

\bsection{Selection Process for Students Attending RIT for at Least One Quarter}
\bsubsection{The applicant submits an application to the Evaluations Committee for review.}
\bsubsection{The applicant participates in an informal interview with exactly three current Resident, Non-Resident, Alumni, or Honorary Members.}
\bsubsection{The Evaluations Committee then meets and reviews all of the application materials and decides whether to accept the person as a special introductory member.}
\bsubsection{The applicant is interviewed again, no less than 10 weeks after acceptance to the introductory process, by three different persons meeting the same requirements as for the first interview. The purpose of this interview is to determine if the applicant has shown sufficient interest and work to merit becoming a full Resident or Non-Resident Member.}
\bsubsection{The Evaluations Committee reviews all information regarding the applicant and if the applicant is found to be a positive influence on House objectives or morale; accepts the applicant to either full Resident or Non-Resident membership, rejects the applicant, or extends the introductory process for the applicant until the next fall quarter, during which time the applicant must participate in the introductory process used by introductory members during fall quarter.}
Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues. 
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\bsection{Selection Process for First Quarter and Entering RIT Students}
\bsubsection{The applicant submits an application to the Evaluations Committee for review. The preferred application time is during the previous academic year up to one week prior to the Department of Residence Life's Deadline for Acceptance of Entering Students into Special Interest Houses.}
\bsubsection{The applicant participates in an informal interview with exactly three current Resident, Non-Resident, or Alumni members.}
\bsubsection{The application and interview is reviewed by the Evaluations Committee to make a decision on either the granting or denial of membership in the House. The applicant is notified of the committee's decision within three weeks after the Department of Residence Life's Deadline for Acceptance of Entering Students into Special Interest Houses.}
\bsubsection{The applicant moves onto the House Fall Quarter and is granted full membership privileges and responsibilities including House dues, combinations, and accounts. In addition to these privileges and responsibilities, the new member must participate in the Introductory Process.}
\bsubsection{During the Introductory Evaluation Process, the new member's Introductory Process will be used to aid in evaluating their membership. If the new member has unsuccessfully completed the Introductory Process or has been found to be a detriment to House objectives or morale, the person's membership may be revoked pursuant to the Membership Revocation Process and the person would be asked to find alternative housing as soon as possible in accordance with all applicable Residence Life Policies regarding room changes. If the new member has completed the Introductory Process, passes the Introductory Evaluation Process and is not found to be a detriment to House objectives or morale, it is announced at the following House meeting and appropriate traditions are upheld.}
Note: Most membership privileges do not initiate until successful completion of the introductory process. This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum. The member does, however, have the right to use Computer Science House's facilities. The member must also pay dues. 
\\* \\*
Additional Note: Any member who has not been subject to at least one Objective Evaluation (Spring Evaluations) cannot become an Alumni. Instead, if the member moves off floor, the member becomes a Non-Resident member. This is only true of persons who have not gone through the Objective Evaluation Process at some point during their Computer Science House membership.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\bsection{Selection Process for Honorary Members}
\bsubsection{A House Member submits to the Evaluations Committee, a nomination for a person they feel is deserving of Honorary Membership.}
\bsubsection{The Evaluations Committee performs some preliminary research on the candidate and presents the finding.}
\bsubsection{The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote. If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.}
\bsubsection{The nomination is presented at a House meeting for discussion. Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period. A quorum of two-thirds the number of all House members eligible to vote is required for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is required for the candidate to be granted Honorary Membership.}
\bsubsection{The candidate is notified of their selection as an Honorary Member and presented with the honor.}

\bsection{Selection Process for Advisory Members}
\bsubsection{A House Member submits to the Executive Board, a nomination for a person who they feel would benefit the House as an advisor during the period of time provided for by Article V, Section F, Subsection 2 Advisory Membership Selection.}
\bsubsection{After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.}
\bsubsection{A discussion of the candidates will be held at the following House meeting.}
\bsubsection{Ballots will then be distributed for a secret ballot House vote. The vote is a fifty-percent vote meaning a quorum of fifty percent of the number of all House members eligible to vote is required for the selections to be official. A vote for the selection of a specific candidate equaling or exceeding fifty percent of the number of ballots cast is required for the respective advisor candidate to be selected. If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level. If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated. This recast process may not be repeated a second time.}
\bsubsection{All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection. If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors. Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level. If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.}

\bsection{Evaluations Process}
During the academic year, a House member is evaluated by two different processes. The first process, known as the Subjective Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House. The second process, known as the Objective Evaluation, is responsible for determining those individuals who will be offered residence on the House for the next academic year. These processes are separate from each other and should not interfere with one another, with the exception that the Subjective Evaluation is used to provide information for the Objective Evaluation.
\\* \\*
At the beginning of any Evaluation Process listed herein, the director of the Evaluation Committee must read the sections of the Computer Science House Constitution and By Laws used during the respective Evaluation Process.
\bsubsection{Subjective Evaluation}
The subjective evaluation process occurs during the academic year. It is performed mid Winter Quarter. The members of the Evaluations Committee, on a member by member basis, review the project logs for projects on which the member was involved, along with the member's activity worksheet and any other information the member chooses to provide. Each active House member will receive two Housing Points (see By-Law V, Section F). The Evaluation Committee may also award one bonus point if it decides that this house member has performed a large or exceptional amount of work for the house. The committee may also deduct one housing point from any House member who has not performed an acceptable amount of work for the house. The guidelines of the committees will be used as a guide in determining bonus and deducted points. No housing points will be awarded to members who do not return the Evaluation Activity Sheets.
\\* \\*
Any house member not living on-floor, for example, because a leave of absence for CO-OP, during the quarter of Subjective Evaluations will be evaluated by these criteria and awarded their share of housing points near the end of the quarter in which they return.
\\* \\*
A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
\\* \\*
All votes during the Subjective Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in Article VIII, Section C, Subsection 4. The votes will be counted by the Evaluations Director and two randomly chosen vote counters from the Evaluation Process Participants.
\bsubsection{Objective Evaluation}
The objective evaluation process occurs once per academic year. It is performed as part of the Evaluation Process that takes place during the middle of spring quarter. The Evaluation Committee, on a member by member basis, ensures that each member has met the minimum requirements in order to be placed on the housing list for the following year. These requirements are detailed in Article V under expectations for each category of membership. These requirements must be completed by the seventh week of Spring Quarter when objective evaluations will occur.
\\* \\*
A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
\\* \\*
All votes during the Objective Evaluation Process must be Closed Ballot, Simple Majority Vote as defined in Article VIII, Section C, Subsection 1. The votes will be counted by the Evaluations Director and two randomly chosen vote counters from the Evaluation Process Participants.
\bsubsection{Responsibilities of Members and Directors}
Each member will be required to complete a form known as the activity worksheet for each Subjective Evaluation. This form is a list of what projects the member participated in since the last evaluation period, and should detail the level of involvement in each project. After being verified by the appropriate directors, the Evaluation Committee will include this list in its review of the member.
\\* \\*
\textbf{It is incumbent upon each House member to provide the Evaluation Committee with whatever information he or she feels is necessary to ensure an accurate evaluation.}
\\* \\*
For every House project there will be created a project log. It minimally contains information describing the project as well as the project leaders and participants, and should detail the participants involvement with the project. The project log is to be submitted to the appropriate director. If an appropriate director does not exist, the project log is to be submitted to the chairman. It is the director's responsibility to ensure that a project log is created and submitted for every House project that falls under that director's jurisdiction.
\bsubsection{Appeals Process}
If a member disagrees with the outcome of any evaluation, (e.g. is not asked to return to the House for the following year) and wishes to appeal the decision, he or she should immediately contact the Evaluations Director, the House Manager, or the Chairman. At the following Executive Board meeting, the member will present his appeal to the Board. The Executive Board can uphold, overturn or conditionally overturn the Evaluation Committee's decision with a secret ballot Two Thirds Vote as described in Article VIII, Section C, Subsection 3. If the decision is overturned or conditionally overturned, the member is to be added to the housing list immediately.
\\* \\*
If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the Area Coordinator.
\bsubsection{Introductory Evaluation}
The Introductory Evaluation process occurs once per academic year. It is performed as part of the Introductory Process that takes place during Fall Quarter, immediately after completion of the Introductory Process. On a member by member basis, this evaluation process decides if each member has successfully completed the Introductory Process Requirements. These requirements are listed in By-Law V, Section A. If the person has met the requirements, he is asked to become a Resident or Non-Resident member. Otherwise the person is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life Policies regarding room changes.
\\* \\*
A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

\bsection{Expectations of House Members}
Each Member is required to pay House dues as stated in By-Law IV, Section A, attend all House Meetings, be an active participant in at least one committee, and attend at least twenty-five (25) committee meetings of which ten (10) are for the committee in which the member is an active participant. Each director will establish guidelines at the start of Fall Quarter, outlining explicit expectations of active participants. Members are also required to actively participate in a majority of House activities.
\\* \\*
The member must lead one major House project during the academic year. The member is required to submit a proposal for this major project to the Executive Board for approval. As an option to this requirement, the member may instead assist on a large number of House activities and projects without actually assuming a leadership role in the activity or project. However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year. This participation will be evaluated by the Executive Board.
\bsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment, the Assignment of Available Housing, or the changing of status membership status to Resident Member. The member with top priority is the member with the most Housing Priority Points. Housing points are accumulated during the Subjective Evaluation described in By Law-IV, Section1.13, Subsection1.13.1.
\\* \\*
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
\bsection{Single Room Assignments}
When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H, regardless of the member's current housing status. If that House member declines the option, it will be offered to the member with the next highest Housing Priority. This process continues until a member selects to move into the single room. Once in a single room, a House member retains the assignment until voluntarily giving it up. It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
\bsection{Double Rooms as Single Rooms}
During the third week of each quarter, if there is no waiting list for resident membership to the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in By-Law V, Section I. It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single. This only applies if there is a totally vacant room.
\end{document}

### 2011-10-20 constitution.tex
Initial files from Dumont's latex conversion project a while back.

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc. 
%  However, if a sub part is moved to a different part, its references must be 
%  changed.
% -This document must be ratified by the House (as per the Constitution), 
%  then printed, signed, notarized, and placed in the House filing cabinet
%  if changes are to be officialized.

\documentclass{article}
% The xr package allows external references
\usepackage{xr}

% This package is useful for debugging label problems 
% Comment out in final revision
%\usepackage{showkeys}

% Define the external document to be bylaws for cross referencing purposes
\externaldocument{bylaws}

% Title page information
\title{Computer Science House Constitution}
\author{Computer Science House Executive Board}
% Last Modified Date
\newcommand{\datechanged}{Proposed: \today}
\date{\datechanged}

% Fix margins
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}

% Use \article for articles and \asection for sections of articles.
% Automatically provide labels with the same article or section title.
\newcommand{\article}[1]{\section{#1} \label{#1}}
\newcommand{\asection}[1]{\subsection{#1} \label{#1}}
\newcommand{\asubsection}[1]{\subsubsection{#1} \label{#1}}
\renewcommand{\thesection}{Article \Roman{section}}
\renewcommand{\thesubsection}{Section \arabic{section}.\Alph{subsection}}
\renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}

% Headings
\pagestyle{myheadings}
\markright{{\rm CSH Constitution \hfill  As of \datechanged \hfill Page }}

% Reference example:
%Test reference \ref{House Objectives} House Objectives.

\begin{document}
% Title
\maketitle

% Articles
\article{Name}
The name of this Special Interest House shall be Computer Science House.

\article{Derivation of Authority}
The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Department of Residence Life in conjunction with the Residence Halls Association.

\article{House Objectives}
The objectives of Computer Science House are:
	\begin{enumerate}
	\item To enhance the education experience of its members.
	\item To offer students educational programming with an emphasis in computers.
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community.
	\item To provide a friendly and comfortable living environment in the residence halls.
\end{enumerate}

\article{Constitutional Structure}
\asection{House Charter}
The House Charter is a document drafted by the department of Residence Life, setting down the guidelines within which this House operates and from which it derives its authority.

\asection{Constitution}
The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.  It is reviewed annually by the Department of Residence Life.  The House Constitution is comprised of three sections:  articles, by-laws, and guidelines.  Any non-semantic change to an article or by-law should be presented to the House by the Evaluations Committee for discussion.  After the discussion an immediate House vote is taken.  A quorum of fifty percent of the number of all House members eligible to vote must be present in order for the vote to be official.  A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.  Non-semantic changes to the guidelines and semantic changes to articles, by-laws, or guidelines are described in detail below.

\asubsection{Articles}
Articles define the major aspects of the House. Any semantic change to an article requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week. The final proposal is presented the following week and ballots are distributed for a secret ballot House vote as described in \ref{Voting}, Voting. The ballots are collected for a minimum of a forty-eight hour period. A quorum of two-thirds of the number of all House members eligible to vote must cast ballots for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. An article may be overridden by an immediate House vote as described in \ref{Voting}, Voting. There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official. A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

\asubsection{By-Laws}
By-Laws define the more flexible aspects of the House. A by-law may expand on rules outlined in an article, but they must never contradict an article. Any semantic change to a by-law requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is re-read prior to voting. The vote may be taken immediately or tabled one week at the discretion of the Executive Board. When the final proposal is ready to be voted upon, an immediate House vote will be taken as described in \ref{Voting}, Voting. A quorum of two-thirds of the number of all House members eligible to vote must cast a vote for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. A by-law may be overridden by an immediate House vote as described in \ref{Voting}, Voting. There must be a quorum of two-thirds of the number of all House members eligible to vote for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the override to take effect.

\asubsection{Guidelines}
Guidelines define the standard operating procedure of the Committees of the House. Guidelines must never contradict any rule defined in either the articles or by-laws. They are drafted during the Executive Board Training Process by the Director of the respective Committee. Directors and Committees are expected to adhere to them, but if necessary, may deviate from a stated guideline. The guidelines will include:
\begin{itemize}
\item An explicit definition of what it means to be a member of the respective committee
\item Expectations of members in the committee
\item Goals of the committee for the operating year
\end{itemize}
The House must be notified of any deviation from a stated guideline. Any semantic or non-semantic change to a guideline is presented in writing to the Committee the guideline pertains to. The change must pass a simple majority vote within the members of the committee for it to be accepted. It is then presented to the Executive Board for review prior to placing it in the Constitution. The House is notified of the change at the following House meeting.

\asubsection{House Rules}
The House Rules capsulate a House Member's responsibilities and expectations. Members are required to sign the document signifying their acceptance of the membership requirements and expectations. All Resident and Non-Resident are required to sign the House Rules annually. Because the House Rules are extracted from the Constitution, any modifications to the contents of the House Rules must first be made to the Constitution. \ref{Operations of the Executive Board}, \ref{The House Rules}, describes which information is extracted from the Constitution and placed into the House Rules.

\article{Membership}
There are six major types of membership available to Computer Science House.  Each carries different qualifications, expectations, and privileges.  When describing the different memberships available, the following terms are used:
\begin{description}
\item[Qualifications:] What qualifications an applicant needs to apply.
\item[Selection:] The process by which an applicant gains membership.
\item[Expectations:] What expectations the House has on its members.
\item[Privileges:] What privileges the member can expect from the House.
\item[Evaluations:] The process by which a member is reviewed and evaluated.
\item[Resignations:] The process by which a member resigns membership.
\item[Term:] The length of time the membership lasts.
\end{description}
\asection{Introductory Membership}
\asubsection{Introductory Membership Qualifications}
Introductory Membership is open to all RIT students.
\asubsection{Introductory Membership Selection}
Applicants notify the House of their interest in membership by submitting an application to the Evaluations Committee.  They must then undergo the selection process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
\asubsection{Introductory Membership Expectations}
Introductory members are expected to be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}. If an Introductory member fails to  obtain 60\% (rounded up to the nearest whole person) of the Resident  Members signatures in the Introductory packet, discussed in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}, said member will not receive use of Computer Science House  facilities, as described in \ref{Introductory Membership Privileges}, until successful completion  of Introductory Evaluations.
\asubsection{Introductory Membership Privileges}
Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
\asubsection{Introductory Membership Evaluations}
Introductory members are evaluated on their performance during the introductory period.  The introductory process is described in \ref{Operations of the Evaluations Committee}, \ref{The Introductory Process}.
\asubsection{Introductory Membership Resignations}
An introductory member may resign by submitting the request for termination of membership to the House Chairman, or Evaluations Director in writing before the completion of the introductory process.
\asubsection{Introductory Membership Term}
The introductory membership shall last until the end of the introductory process, at which time they will either have their membership revoked or have their membership status changed to Resident member or Non-Resident member.

\asection{Resident Membership}
\asubsection{Resident Membership Qualifications}
Resident Membership is open to all RIT students who comply with the Residence Life policies regarding residence in the Residence Halls.
\asubsection{Resident Membership Selection}
Applicants notify the House of their interest in Resident Membership by submitting an application to the Evaluations Committee and must then undergo the Selection Process as described in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
\asubsection{Resident Membership Expectations}
Resident members are expected to live on the house and be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
\asubsection{Resident Membership Privileges}
Resident Members receive the right: to vote on all issues brought before the House, to have residency on the House, to hold an Executive Board office on the House, to use the Computer Science House facilities, to attend Computer Science House functions, to have priority for available housing on the House when returning from cooperative education as stated in \ref{Operations of the Evaluations Committee}, \ref{Housing Priority System}, to have guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process.
\asubsection{Resident Membership Evaluations}
Resident Members are evaluated semi-annually through the Evaluation Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Resident Membership Resignations}
A Resident member may resign by submitting in writing the reason for resignation to the House Chairman, or Evaluations Director.  The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Resident Membership Term}
Resident Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Non-Resident Membership}
\asubsection{Non-Resident Membership Qualifications}
Non-Resident membership is open to all RIT students.
\asubsection{Non-Resident Membership Selection}
Applicants notify the House of their interest in Non-Resident membership by submitting an application to the Evaluations Committee and must then undergo the Selection Process as described in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.  Any house Alumni may become a Non-Resident member by notifying the Evaluations Committee of their intent to participate, at which point they are reinstated as Non-Resident members of the house.
\asubsection{Non-Resident Membership Expectations}
Non-Resident members are expected to be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
\asubsection{Non-Resident Membership Privileges}
Non-Resident Members receive the right: to vote on all issues brought before the House, to use the Computer Science House facilities, to attend Computer Science House functions, to have priority for available housing on the House as stated in \ref{Operations of the Evaluations Committee}, \ref{Housing Priority System}.
\asubsection{Non-Resident Membership Evaluations}
Non-Resident Members are evaluated semi-annually through the Evaluation Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
\asubsection{Non-Resident Membership Resignations}
A Non-Resident Member may resign by submitting in writing the reason for resignation to the House Chairman, or Evaluations Director.  The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Non-Resident Membership Term}
Non-Resident Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status according to \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all prior members of Computer Science House who departed for reasons other than revocation of House Membership or failing the Objective Evaluation. 
\asubsection{Alumni Membership Selection}
Alumni Membership is the status of all prior members of Computer Science House who departed the house for any reasons other than failure of the Evaluations Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status, however those who are able are encouraged to adhere to \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
\asubsection{Alumni Membership Privileges}
Alumni Members, at the discretion of the Executive Board, shall receive the right: to the use of Computer Science House facilities and to attend Computer Science House functions.
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject to the Evaluations Process.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last until the member changes their membership status as described in the Qualifications and Selections sections of either Resident or Non-Resident Membership.

\asection{Honorary Membership}
\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
\asubsection{Honorary Membership Selection}
Any House member may nominate a candidate for Honorary Membership by submitting the name in writing to the Evaluations Committee. The Evaluation Committee then begins the Honorary Membership Selection Process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Honorary Members}.
\asubsection{Honorary Membership Expectations}
Honorary Members are encouraged to remain in contact with the House.
\asubsection{Honorary Membership Privileges}
Honorary Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Honorary Membership Evaluations}
Honorary Members are not subject to formal evaluations.
\asubsection{Honorary Membership Resignations}
An Honorary Member may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Honorary Membership Term}
Honorary Membership shall last until the member resigns.

\asection{Advisory Membership}
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Advisory Membership Selection}
Advisors are selected during the start of the academic year. Any House member may nominate a candidate for Advisory Membership by submitting the name in writing to the Executive Board. The candidates then participate in the Advisor Selection Process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Advisory Members}.
\asubsection{Advisory Membership Expectations}
Advisors are encouraged to offer advise and assistance to the House in any capacity the Advisor is able to help. Advisors are also encouraged to meet the House members and occasionally attend House activities.
\asubsection{Advisory Membership Privileges}
Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
\asubsection{Advisory Membership Evaluations}
Advisors are not subject to formal evaluations.
\asubsection{Advisory Membership Resignations}
An Advisor may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become effective at that time.
\asubsection{Advisory Membership Term}
Advisory Membership shall last for one academic year or until the member resigns.

\article{Executive Board}
The Executive Board is the main governing body of the House.  Its purpose if to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
\asection{Members of the Executive Board}
\asubsection{Chairman}
\asubsection{Voting Members}
\begin{itemize}
    \item Evaluations Director
    \item Social Director(s)
    \item Financial Director
    \item Research and Development Director
    \item House Improvements Director
    \item Root Type Persons Representative
    \item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
    \item House Secretary
\end{itemize}

\asection{Responsibilities}
% For this section, we want items to use letters
\renewcommand{\theenumi}{\alph{enumi}}
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
\item To fulfill the responsibilities pertaining to its purpose as stated in the description of the Executive Board in the header paragraph for \ref{Executive Board} (Executive Board).
\item To meet at least weekly during the standard operating session, as defined in \ref{General Operations of the House}, \ref{Standard Operating Session}, to discuss and report the operations of the House.
\item To report pertinent information to House members at the following House Meeting.
\item To establish goals and expectations for the House for the upcoming year.
\item To submit a yearly statement of goals and accomplishments of the present year to House members and to the Department of Residence Life.
\item To act as a judicial board for any final ruling on the interpretation of the House Constitution, House document, or action taken by the House.
\end{enumerate}

\asubsection{Responsibilities of the Chairman}
\begin{enumerate}
\item To preside over Executive Board and House Meetings.
\item To exercise general supervision over the operations of the Executive Board.
\item To exercise general supervision over regular House activities.
\item To act as a liaison to the academic and administrative departments at RIT.
\item To act in collaboration with the Evaluations Director and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House. 
\item To cast tie-breaking vote in a split decision in an Executive Board vote.
\end{enumerate}

\asubsection{Responsibilities of the Evaluations Director}
\begin{enumerate}
\item To preside over Evaluations Committee Meetings
\item To exercise general supervision over the operations of the Evaluations Committee.
\item To oversee the selection of new House members.
\item To oversee the evaluations of current House members.
\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership status to Resident Membership.
\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House. 
\item To prepare the House for Open Houses, tours, and special events.
\end{enumerate}

\asubsection{Responsibilities of the Social Director}
\begin{enumerate}
\item To preside over Social Committee Meetings
\item To exercise general supervision over the operations of the Social Committee.
\item To oversee the organization, initiation, and execution of House activities and events.
\end{enumerate}
\asubsection{Responsibilities of the Financial Director}
\begin{enumerate}
\item To oversee the Financial Committee.
\item To supervise financial administrators and transactions involving house projects.
\item To maintain financial and inventory records of House capital and assets.
\item To plan and enforce a House budget.
\item To supervise House expenditures and financial transactions.
\item To publish a quarterly House financial statement.
\item To supervise the collection of quarterly House dues.
\item To oversee the planning and execution of fundraising events.
\end{enumerate}

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
\item To preside over Research and Development Committee Meetings
\item To exercise general supervision over the operations of the Research and Development Committee.
\item To oversee the organization and construction of technical projects for the House's benefit.
\item To collaborate with the Operational Communications Committee in an attempt to fulfill the House's need for technical equipment.
\item To provide seminars and tutorials to educate House members in technical areas.
\end{enumerate}

\asubsection{Responsibilities of the House Improvements Director}
\begin{enumerate}
\item To preside over House Improvements Committee Meetings.
\item To exercise general supervision over the operations of the House Improvements Committee.
\item To oversee the organization and construction of physical improvements to the House.
\item To oversee the general maintenance of the appearance of the House.
\end{enumerate}

\asubsection{Responsibilities of the Root Type Persons Representative}
\begin{enumerate}
\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings.
\item To report the status of the House computer systems and network to the Executive Board and House members.
\item To oversee the implementation of maintenance and upgrades to the House Computer Systems and Network.
\end{enumerate}

\asubsection{Responsibilities of the Root Type Persons}
\begin{enumerate}
\item The Root Type Persons are responsible for improvement, maintenance, and management of the House's computer systems and networking equipment.
\item There must always be at least two Root Type Persons at all times.
\end{enumerate}

\asubsection{Responsibilities of the House History Director}
\begin{enumerate}
\item To preside over House History Committee Meetings
\item To exercise general supervision over the operations of the House History Committee.
\item To oversee the upkeep of House Members records.
\item To oversee the celebration of all House Member's birthdays.
\item To oversee the production of a quarterly newsletter highlighting Computer Science House happenings and a yearly Alumni Directory.
\item To maintain, uphold, and promote house traditions.
\item To collaborate with the Social Director(s) to ensure that all the Non-Resident, Alumni, and Advisory Members are informed of upcoming events.
\end{enumerate}

\asubsection{Responsibilities of the House Secretary}
\begin{enumerate}
\item To ensure that minutes are recorded and posted for Executive Board Meetings.
\item To ensure that minutes are recorded and posted for House Meetings.
\item To oversee the maintenance of Executive Board records and documents.
\item To provide administrative assistance to the Executive Board.
\item To oversee the maintenance of the Activities Information Centers.
\item To record all votes cast during House Meetings and Open Executive Board Meetings.
\end{enumerate}

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director, House Improvements Director, House History Director}
\begin{enumerate}
\item Candidates must be Resident Members or Non-Resident Members during the term of office.
\item Candidates must have at least two prior quarters House membership as either Resident or Non-Resident Membership.
\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
\end{enumerate}
\asubsection{Qualifications to be the Root Type Persons Representative}
\begin{enumerate}
\item Candidates must be a current Root Type Person.
\item Candidates must be a currently Resident or Non-Resident House Member.
\item A Root Type Person cannot be the representative if they currently hold any other Executive Board Position.
\end{enumerate}
\asubsection{Qualifications to be a Root Type Person}
\begin{enumerate}
\item Candidates must be a Resident Member in good standing, or be a Non-Resident Member and have been a Resident member within the last twelve months.
\item Candidates may be granted an exemption by current Root Type Persons.  Such an exemption may be withdrawn at any time by the current Root Type Persons.
\item Prior Root Type Persons are those members who are no longer current Resident or Non-Resident House members and have not been granted an extension by the current Root Type Persons.  Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
\end{enumerate}

\asubsection{Qualifications to be the House Secretary}
\begin{enumerate}
\item Candidates must be Resident Members on the House during the term of office.
\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
\end{enumerate}

\asection{Selection}
\asubsection{Dual Directorship}
Social Director is the only Executive Board position that allows for Dual Directorship. If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot. If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative. Each different nomination must be a separate entry on the election ballot.
\\The following special cases cover the operation of a dual directorship:
\begin{itemize}
\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated. The vacated office is then handled like any other vacated office; see \ref{Executive Board}, \ref{Resignations}.
\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes. The members of the dual directorship need not vote the same way in a vote.
\item A member of a dual directorship may not hold any other Executive Board position.
\item When attendance requirements call for the Social Directors to be present, both dual directorship members are to fulfill the requirements.
\end{itemize}
\asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director}
\begin{enumerate}
\item The opening of the Executive Board position is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.  Any House member may nominate any House member or members for a Dual Directorship if it is permitted for the respective office.
\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.  Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.  A list of all nominees who have accepted their nominations will be posted shortly thereafter.
\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.
\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.  The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.  In addition, an area will be provided to indicate a write-in selection of a candidate.
\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Voting}, Voting.
\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Voting}, Voting.  A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official.  All winners are notified and asked to accept or decline their election.  Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.
\end{enumerate}
\asubsection{Selection of the Research and Development Director, House Secretary}
\begin{enumerate}
\item The opening of the Executive Board position is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.  A House member may nominate any House member.
\item The candidates meeting the qualifications of the office that were nominated for, will be notified of their nomination.  Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.  A list of all nominees who have accepted their nominations will be posted shortly thereafter.
\item Each candidate will be given an equal amount of time before the Executive Board to present their platforms of candidacy.  This Executive Board Meeting is closed to the Executive Board Members and House members with explicit invitation from the Executive Board.
\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.  After each candidate for an office has been presented and discussed, a simple majority Executive Board vote, as described in \ref{Voting}, Voting, is taken to determine the selection of candidates.
\item All winners are notified and asked to accept or decline their selection.  Any office whose winner declines the selection shall remain vacant and a new selection process shall begin for that office.
\end{enumerate}
\asubsection{Selection of the Root Type Persons Representative}
\begin{enumerate}
\item Root Type Persons Representative shall be chose by the current Root Type Persons.  The representative may change on a daily basis.
\end{enumerate}
\asubsection{Selection of Root Type Persons}
\begin{enumerate}
\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Executive Board}, \ref{Qualifications to be a Root Type Person}.
\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.  
\item A list of all nominees who have accepted is presented to the Executive Board for approval.  This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.  A simple majority Executive Board vote, as described in \ref{Voting}, is taken to determine whether the nominations of the Root Type Persons are accepted.
\end{enumerate}

\asection{Evaluations}
\begin{enumerate}
\item All members of the Executive Board are subject to the Evaluation Process as stated in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
\end{enumerate}

\asection{Resignations}
An Executive Board Member may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become e?ective at that time. The o?ce will become vacant and the selection process for a new member will begin at that time. The duties and responsibilities of a vacated o?ce are assumed by the Chairman or by a member of the Executive Board that is appointed at the Chairman’s discretion until the new member takes o?ce. The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast. 
\asection{Impeachment}
\begin{enumerate}
\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Voting}, \ref{Total Number of Possible Votes}.
\item The impeachment petition is then presented at an Executive Board Meeting.  The member(s) initiating the petition present their case to the Executive Board.  The Executive Board then questions the accused member of the allegations.
\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment. If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed. This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office. Votes shall be collected and counted as described in \ref{Voting}, \ref{Secret Ballot}.
\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office. If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
\item If the percentage of a?rmative votes equals or exceeds the minimum the impeached o?cer is relinquished of their position and any beneﬁts thereof and this position is treated like any other vacated position. A new selection and interim duty fulﬁllment procedure is followed similar to that of a resignation; see Article VI, Section 6.F.
\end{enumerate}

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin no later than the third week of the Spring Quarter.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 30 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, failure of the evaluation process, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\end{enumerate}

\article{House Committees}
House Committees are the major work force of the House. There are two major types of committees: permanent and ad-hoc. There is one permanent committee for each major aspect of the government of the House, and each permanent committee is chaired by an Executive Board member. The ad-hoc committees are created on an as-needed basis. They are generally very task oriented and are chaired by a House member. A committee has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest. Any large expenditures or large effect decisions must be brought before the entire House.
\asection{Evaluations Committee}
\begin{enumerate}
\item The Evaluations Committee is responsible for the screening, interviewing, and acceptance or rejection of prospective members to the House.  The committee is also responsible for Semi-Annual Evaluations of current House members.
\item Membership in the Evaluations Committee is open to any member of the house.  Evaluations Committee meetings are open to any member of the House.
\item Semi-Annual Evaluations Meetings are open only to all current Resident and Non-Resident Members.  These members must have attended the Criteria Definition Meeting held prior to the actual Semi-Annual Evaluations.  All committee directors are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
\end{enumerate}
\asection{Social Committee}
\begin{enumerate}
\item The Social Committee is responsible for organizing and planning many of the House activities and social events.  The committee is expected to ensure that there is a variety of activities for House members to participate in throughout the academic year.
\item Membership in the Social Committee is open to any member of the House.  House members with ideas for social events are encourages to approach the Social Director(s), discuss their ideas, and present them at a committee meeting.
\end{enumerate}
\asection{Research and Development Committee}
\begin{enumerate}
\item The Research and Development Committee is responsible for researching and planning House’s technical projects and activities. It is the responsibility of the committee to promote technical projects and seminars on ﬂoor and help develop the learning aspect of Computer Science House. 
\item  Membership in the Research and Development Committee is open to any member of the House. House members are encourage to work on technical projects or bring ideas for projects to the Research and Development Director for discussion and to present them at the committee meeting. 
\end{enumerate}
\asection{House Improvements Committee}
\begin{enumerate}
\item The House Improvements Committee is responsible for the maintenance and upkeep of the House facilities, along with physical improvements to the living environment.
\item Membership in the House Improvements Committee is open to any member of the House.  Members are encouraged to participate in some of the House Improvement projects.
\end{enumerate}
\asection{House History Committee}
\begin{enumerate}
\item The House History Committee is responsible for the maintenance and upkeep of House records of members and the production and distribution of a quarterly newsletter and a yearly Alumni Directory.
\item The House History Committee is also responsible for the promotion of all Computer Science House traditions and leading the celebration of Computer Science House member's birthdays.  The House History Committee will also present a yearbook outlining House events for the year to the House.
\item Membership in the House History Committee is open to any member of the House.  House members are encouraged to participate in Committee activities.
\end{enumerate}
\asection{Operational Communications Committee}
\begin{enumerate}
\item The Operational Communications Committee is responsible for the improvement, maintenance, and management of the House's computer systems and networking equipment.
\item Membership in the Operational Communications Committee is defined as any member who has been selected as a Root Type Person as defined in \ref{Executive Board}, \ref{Qualifications to be a Root Type Person}.
\item The Operational Communications Committee is a self-governing committee making decisions by a simply majority vote.
\end{enumerate}
\asection{Financial Committee}
\begin{enumerate}
\item The Financial Committee is responsible for the generation of House funds.
\item Membership in the Financial Committee is open to any member of the House.  House members with ideas for fund-raising activities are encouraged to approach the Financial Director, discuss their ideas, and present them at a committee meeting.
\item Included in the Financial Committee are those administrators responsible for overseeing those House privileges which require monetary commitment, for example: Drink Administrators.
\end{enumerate}
\asection{Ad-Hoc Committees}
\begin{enumerate}
\item Ad-Hoc Committees are responsible for the task for which they were created.  When the task is completed, the committee dissolves.  When the Executive Board or a group of House members feels an Ad-hoc Committee is necessary, they present their plans to the Executive Board and the Executive Board decides whether committee status is granted.
\item When the Ad-Hoc Committee is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
\item Any responsibilities for budgets or finances for the Ad-Hoc Committee are placed upon the assigned director.
\item When an Ad-Hoc Committee Director resigns his duties, the committee dissolves and committee status must be reinstated with a new director.
\end{enumerate}

\article{Voting}
There are two major ways to describe a vote: type of balloting and number of ballots required. A vote may be any combination of one type of balloting and one number of ballots required. There are also a number of definitions that need to be defined before the procedures can be defined.
\asection{Definitions}
\asubsection{Total Number of Possible Votes}
The Total Number of Possible Votes is defined as the number of possible ballots that can be cast in a vote. In a House vote, it is the sum of the number of all Resident and Non-Resident members. In a formal Executive Board vote, it is defined as the number of all voting Executive Board members. In a committee vote, it is defined as the number of members present at the current committee meeting.
\asubsection{Quorum}
A Quorum is defined as the minimum number of votes cast required for a vote to be official. It is usually defined as a fraction or a percentage of the total number of possible votes. A Quorum is reached if the number of votes cast, counting abstentions, is equal to or exceeding the minimum number of votes.
\asubsection{Absent Ballot}
An Absent Ballot is defined as any ballot that was not entered into the vote because a member eligible to vote did not vote or provide a means to indicate his or her vote. Absent Ballots are not counted towards a Quorum, but they are counted toward the total number of possible votes cast.
\asubsection{Proxy Ballot}
A Proxy Ballot is defined as any ballot that was cast by one member on behalf of another member. Any member may cast Proxy Ballots for another member who is unable to actually participate in the vote and only by written permission for the specific vote. Proxy votes are only permissible where explicitly stated.
\asubsection{Abstention}
An Abstention is defined as a vote indicating a neutral position in the vote. A means to abstain must always be provided in a vote. Abstentions are counted towards a quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
\asubsection{Total Number of Votes Cast}
The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.

\asection{Type of Balloting}
\asubsection{Secret Ballot}
When a Secret Ballot is called for, the person chairing the vote will see that ballots are made with a means to indicate every possible choice in the vote. They are then distributed to each House member eligible to cast a ballot in the vote, and collected in the indicated ballot box for a pre-specified period of time, the length time depending on the nature of the vote. This time period must be a minimum of forty-eight hours in length for any constitutional modification vote, candidate selection vote, or officer removal vote, and twenty-four hours in length for any other vote. The minimum length of the time period may be explicitly lengthened, but never shortened, in the text describing the actual vote. At the end of the voting period, the person chairing the vote collects the ballot box thus closing the voting. The votes are to be counted by person chairing the vote, and two House Members randomly selected, none of whom are directly involved in the vote. Being directly involved is defined as being a candidate in an election, or the accused or accuser in an impeachment. If every Executive Board member is directly involved in the vote, then a third House member is selected at random to count votes in place of the person chairing the vote. Any additional requirements to the voting procedure are described in the section pertaining to the actual vote.
\asubsection{Immediate Vote}
When an Immediate Vote is called for, the person chairing the vote will state all of the possible ways to vote and then call out each possibility one at a time. The chairing member will count the number of members casting their immediate vote for that possibility. When all of the possibilities have been voted upon, the totals will be tallied. Any additional requirements to the voting procedure are also described in the section pertaining to the actual vote.
\asection{Number of Ballots Required}
The Number of Ballots Required refers to the numbers required to achieve a quorum and for a vote to pass.  Below are listed three standard votes.  Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority Vote}
In a Simple Majority Vote a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes. A selection in the vote passes if the number of votes cast for that selection is larger than the number of votes cast for every other selection individually.
\asubsection{Fifty Percent Vote}
In a Fifty Percent Vote a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds fifty percent of the Total Number of Possible Votes. A selection in the vote passes if the number of votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-thirds Vote}
In a Two-thirds Vote a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes. A selection in the vote passes if the number of votes cast for the selection equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three Tiered Vote}
When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest of highest option will only pass is the votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast.  If neither the highest or lowest selection reaches fifty percent, the middle option will then be passed.  In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes. 
\asection{Ties Between Vote Selections}
The action to take on a tie depends on whether or not the vote was a pass/fail vote or a multiple choice vote. In a pass/fail vote, if the number of votes cast for the pass selection equals the number of votes cast for the fail selection, then the vote failed. In a multiple choice vote, if multiple selections may pass, then a tie does not present a problem, however, if only one selection may pass, then the vote must either be recast or tabled according to the discretion of the person chairing the vote. In the event of a tie in an Executive Board vote, the Chairman may cast the tie-breaking vote. 
\end{document}

### 2011-10-20 bylaws.tex
Clockfort's modification to increase commitee money-voting powers. Succesful house vote on 10/19/2011.

@@
 % Last Modified Date
-\newcommand{\datechanged}{Monday, April 5, 2004}
+\newcommand{\datechanged}{Wednesday, October 19, 2010}
 \date{\datechanged}
@@
 All House expenditures must be approved by the financial director and the director responsible for the budget from which the funds will be drawn.
-If any single expenditure exceeds fifty dollars (\$50.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated.
-If any total expenditure exceeds seventy-five dollars (\$75.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated.
+If any single expenditure exceeds seventy-five dollars (\$75.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated.
+If any total expenditure exceeds one-hundred dollars (\$100.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated.
 A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.

### 2013-05-24 bylaws.tex
Fixed date, and allowed for cross-document hyperlinking

--- 2011-10-20 bylaws.tex
@@
 % The xr package allows external references
-\usepackage{xr}
+\usepackage{xr-hyper}
+\usepackage{hyperref}
 
@@
 % Define the external document to be constitution for cross referencing purposes
-\externaldocument{constitution}
+\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]
 
@@
 \title{Computer Science House By-Laws}
-\author{Computer Science House Executive Board}
+\author{Computer Science House Constitution Committee}
 % Last Modified Date
-\newcommand{\datechanged}{Monday, April 5, 2004}
+\newcommand{\datechanged}{Last Updated \today}
 \date{\datechanged}
@@
 
+% Adding a \bsubsubsection -- I feel dirty
+\setcounter{secnumdepth}{5}
+\newcommand{\bsubsubsection}[1]{\paragraph{#1} \label{#1}}
+\renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}
+
 % Headings
 \pagestyle{myheadings}
-\markright{{\rm CSH Constitution \hfill  As of \datechanged \hfill Page }}
+\markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}
 % Reference example:
@@
 
-% By-Laws
-\bylaw{By-Law Structure}
-By-Laws define the more flexible aspects of the House.
-Any semantic change to a by-law requires the change to be proposed at a House Meeting, discussed, followed by a House vote as described in \ref{Voting}, Voting.
-A by-law may be overridden by an immediate House vote with a quorum of sixty-six percent of the number of all House members privileged to vote.
-A vote equaling or exceeding sixty-six percent of all House members present during the vote is required for the override to go through.
-The By-Laws are arranged by section with each section of By-Laws pertain to a particular governing aspect of the House
+% BY-LAW I - INTRODUCTION
+\bylaw{Introduction}
+By-Laws will expand upon, while not redefining, Articles laid out in the Constitution. By-Laws provide additional depth and definition to the processes and operations of House.
 
+% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
 \bylaw{General Operations of the House}
 \bsection{Standard Operating Session}
-The Standard Operating Session for Computer Science House is during the ten weeks of Fall, Winter, and Spring Academic Quarters.
-The Summer Academic Quarter, all between Quarter Interim, and all end of Quarter Exam Weeks are considered Non-Standard Operating Session.
-Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.
+The Standard Operating Session for Computer Science House is during the fifteen weeks of Fall and Spring semesters.
+The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
+Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.
 
-\bylaw{Operations of the Executive Board}
-\bsection{Weekly Notes}
-The Executive Board members are expected to submit to the House, notes for their meetings each week.
-\bsection{The House Rules}
-The House Rules shall contain the following information:
-\begin{itemize}
-\item The Section of \ref{Membership} Membership that corresponds to the membership status of the signing member.
-\item The explanatory paragraph from \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process} describing the Evaluation Process
-\item The Computer Science House Code of Conduct Sheets pertaining to responsible utilization of the Computer Science House and Rochester Institute of Technology facilities.
-\end{itemize}
-\bsection{Closed Executive Board}
-\newcommand{\writeoutref}{\ref{Executive Board}, \ref{Voting Members},}
-\bsubsection{Closed Executive Board Meetings are open only two the Chairman and Voting Members of the Executive Board as deﬁned in Article 6, Section A, Subsection 3, and those with express permission of the Executive Board.
-}
-
-\bsubsection{A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairman and at least two-thirds of the Voting Members as defined in Article 6, Section A, Subsection 3 must be present for a meeting to be called.}
-
-\bylaw{Operations of the Financial Committee}
+% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
+\bylaw{Operations of the Financial Directorship}
 \bsection{Amount of House Dues}
-The amount of dues for Resident Members is thirty dollars (\$35.00) per Academic Quarter.  The amount of dues for Non-Resident Members is twenty-five dollars (\$30.00) per Academic Quarter.
+The amount of dues for Active Members living on floor will be fifty-five dollars (\$55.00) per Academic Semester.
+The amount of dues for Active Members living off floor twill be fifty dollars (\$50.00) per Academic Semester.
 \bsection{Collection of House Dues}
-The Financial Director is responsible for ensuring the House is notified of the due date for the payment of House dues at least two weeks in advance of the actual due date.
-If a member is unable to pay House dues by the due date, he or she should contact the Financial Director prior to the due date or his or her payment will be considered delinquent.
-\\* \\*
-If the Financial Director determines that the member's reason for inability to pay House dues is sufficient, an extended due date will be set for that member.
-If the Financial Director determines the reason to be insufficient, the member may appeal the Executive Board.
-If the Executive Board upholds the Financial Director's ruling, then the member's payment is considered delinquent.
-If the Executive Board overrides the Financial Director's ruling, the Executive Board will set an extended due date for that member.
-\\* \\*
-If the member again finds himself or herself unable to pay dues at the time of the extended due date, he or she may follow the same procedure for the first extension.
-\\* \\*
-If a member's payment goes delinquent for any of the above reasons, his or her case is brought before the Executive Board, and action may be taken at the discretion of the Executive Board.
-The Financial Director should be present at this hearing.
-If the initial House judicial board feels it is unable to adequately resolve the case, or the member wishes to appeal any ruling by the initial House judicial board, the case may be presented to the Executive Board as the final House judicial board.
-\\* \\*
-The Executive Board has the authority to enforce House sanctions up to and including revocation of House privileges and/or the removal of membership status.
-Once the dues have been paid, the judicial board has the option of dropping all current sanctions or continuing the current sanctions until they have been completed.
-The Executive Board may not continue to render new sanctions once the dues have been paid.
-\bsection{Breakdown of Dues for Committee Budgets}
+At the start of the academic year, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected at the start of each semester by the Financial Director.
+For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+\\*\\*
+If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
+If the Financial Director deems their situation appropriate, they may grant an extension for payment.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
+If the Executive board disagrees with the Financial Director, the Executive board may grant an extension.
+If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
+\bsection{Breakdown of Dues for Directorship Budgets}
 \begin{center}
 \begin{tabular}[c]{l c}
-Committee or Budget Name & Percentage of Dues \\
+Directorship Name & Percentage of Dues \\
 \hline
 \hline
-Operational Communications &	19\% \\
+Operational Communications & 20\% \\
 \hline
-Evaluations \& Selections & 4\% \\
+Evaluations \& Selections & 5\% \\
 \hline
-House History & 9\% \\
+House History & 10\% \\
 \hline
-House Improvements & 9\% \\
+House Improvements & 15\% \\
 \hline
-Research and Development & 19\% \\
+Research and Development & 20\% \\
 \hline
-Miscellaneous & 5\% \\
+Social & 20\% \\
 \hline
-House Accum. & 10\% \\
-\hline
-Social & 25\% \\
+Accumulated & 10\% \\
 \hline
@@
 \end{center}
+
+The suggested total operational budget is \$5544.
+This figure is based on yearly estimated on-floor member dues (\$110 x 56 members = \$6160) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues are deposited into the CSH Account and saved.
+
 \bsection{Expenditure Approval}
-All House expenditures must be approved by the financial director and the director responsible for the budget from which the funds will be drawn.
-If any single expenditure exceeds fifty dollars (\$50.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated.
-If any total expenditure exceeds seventy-five dollars (\$75.00) in amount, it must be approved by a simple majority House vote at a House meeting before the funds may be appropriated.
+All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
 A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
 \\* \\*
-Any project requiring more than \$300 in total funding from CSH must include a Complete Project proposal, including a Project Budget, Timeline and Resources needed.
-The person requesting the funds must then report to executive board once per week on the progress of the project.
+If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
+It is required that, for expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+It is also recommended that all expenditure approvals done at House meeting, regardless of amount, provide such a proposal.
+\\* \\*
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+Miscellaneous purchases are deducted directly from the CSH Account, and therefore must have final approval of the Financial Director.
+\\* \\*
+Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
 
-\bylaw{Operations of the Evaluations Committee}
+% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
+\bylaw{Operations of the Evaluations Directorship}
 \bsection{The Introductory Process}
-The Introductory Process is designed to provide an easy means for an applicant or new member to meet existing House members, learn House history, demonstrate their involvement potential in the House, and allow existing House members to meet and evaluate the applicant or new member.
-\\* \\*
-The Evaluations Committee chooses between 1 and 3 House members to be Introductory Process Advisors.
-The advisors organize the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
-All participants will receive an Intro.
-Packet minimally containing the following information:
+The Introductory Process is designed to provide an easy means for introductory members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+\bsubsection{The Evaluation Period}
+The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
+\bsubsection{The Introductory Project}
+Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
+\bsubsection{Introductory Executive Board}
+An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
+The Introductory Executive Board consists of three members:
 \begin{itemize}
-\item A description of the History of Computer Science House
-\item A list of all Resident members, as defined in Article V, Membership.
-\item The Computer Science House Constitution and By-Laws.
-\item The Computer Science House Dictionary
+	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
+	\item A Vice President, who assists the President in leadership and representation.
+	\item A Treasurer, who manages the finances for the project.
 \end{itemize}
-The Introductory Process lasts for a minimum of six weeks from the initiation of the process, until the participant has completed all of the following requirements.
-The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process based on requirements listed in the Introductory Process Proposal.
-However, the Introductory Project must be complete before the Introductory Evaluation occurs.
-\\* \\*
-The participant is given 2 weeks complete the following lists, termed the Intro. Sheets:
+Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
+\bsubsubsection{The Project} 
+The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
+All of the proceeds go to a charity chosen in advance by the participants.
+The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
+\bsubsubsection{Introductory Project Advisors} 
+The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
+The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
+\bsubsection{The Introductory Packet}
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
 \begin{itemize}
-\item For each Resident member, Executive Board member, and for Fifteen Non-Resident and Alumni members (in addition to Non-Resident Executive Board Members), list:
+	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A description of each Executive board position, including:
 	\begin{itemize}
-\item The member's home town
-\item The members local room and phone, or address as applicable
-\item The member's major and year
-\item The House committee(s) the member is interested in
-\item A question of your own to get to know the member
-\item The member's signature.
+		\item The responsibilities of the position
+		\item The name(s) of the position’s member(s)
+		\item The position’s weekly meeting time
 	\end{itemize}
-\item For each House committee, list:
-\begin{itemize}
-\item The full name of the committee
-\item Some of the responsibilities of the committee
-\item The name of the committee's director
-\item The weekly meeting time and place
+	\item A list of seven (7) annual House social events
+	\item A list of seven (7) major House technical achievements
 \end{itemize}
-\item Seven annual Computer Science House social events
-\item Seven major Computer Science House technical achievements
-\end{itemize}
-The participant is also expected to be involved in the following:
+\bsubsection{Expectations of an Introductory Member}
+Before the end of the Process, an Introductory Member is expected to:
 \begin{itemize}
 \item Attend all House meetings during the process
-\item  Attend at least one House committee meeting each week of the process
+\item Complete the Introductory Packet
+\item Be an active participant in an the Introductory Project
+\item Attend at least one House directorship meeting for each week of the process
 \item Attend at least one House social event during the process
-\item  Show an acceptable amount of participation in at least one Technical Project.
-Acceptable participation is determined by the project leader and the Introductory Evaluation Process described in By-Law V, Section F, Subsection 5.
-This project is in addition to the Technical Project required for all Resident and Non-Resident members as stated in By-Law V, Section G.
+\item Attend at least two seminars relating to computing or electronics
+\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations.
 \end{itemize}
-The participant is also expected to be involved in the Introductory Project.
-The Introductory Project is an annual fundraiser that takes place during the Fall Quarter Introductory Process.
-It is organized and carried out by all Introductory Process participants.
-All of the proceeds go to a charity chosen in advance by the participants.
-The participants must elect a non-voting Executive Board Representative, termed the Freshman President who is required to represent the Introductory Process participants on the Executive Board.
-The Freshman President is responsible for any internal Introductory Project duties as well as for bringing a written Introductory Project Proposal to the Executive Board.
-The Executive board will hold discussion followed by a closed ballot Simple Majority Vote according to \ref{Voting} Voting, \ref{Simple Majority Vote} Simple Majority Vote, to determine if the proposed project fulfills the Introductory Project requirements.
-\\* \\*
-At the end of the Introductory Period, there will be an Introductory Evaluation, described in By-Law V, Section F, Subsection 5, to determine which members will be extended offers of full membership.
 
-\bsection{Selection Process for Students Attending RIT for at Least One Quarter}
-\bsubsection{The applicant submits an application to the Evaluations Committee for review.}
-\bsubsection{The applicant participates in an informal interview with exactly three current Resident, Non-Resident, Alumni, or Honorary Members.}
-\bsubsection{The Evaluations Committee then meets and reviews all of the application materials and decides whether to accept the person as a special introductory member.}
-\bsubsection{The applicant is interviewed again, no less than 10 weeks after acceptance to the introductory process, by three different persons meeting the same requirements as for the first interview.
-The purpose of this interview is to determine if the applicant has shown sufficient interest and work to merit becoming a full Resident or Non-Resident Member.}
-\bsubsection{The Evaluations Committee reviews all information regarding the applicant and if the applicant is found to be a positive influence on House objectives or morale; accepts the applicant to either full Resident or Non-Resident membership, rejects the applicant, or extends the introductory process for the applicant until the next fall quarter, during which time the applicant must participate in the introductory process used by introductory members during fall quarter.}
+\bsubsection{Introductory Evaluation}
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
+Occurs once per academic year as part of the Introductory Process.
+\bsubsubsection{Voting} 
+On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+A Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\bsubsubsection{Outcomes} 
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Introductory Member fails to meet the requirements, his membership will be revoked.
+In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
+A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+Each conditional consists of a set of additional requirements a deadline for completing them.
+When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+A conditional member who does not meet these additional requirements forfeits membership.
+\end{enumerate}
+\bsection{Selection Processes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\bsubsection{Selection Process for Students Attending RIT for at Least One Semester}
+\begin{enumerate}
+	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
+	\item The application materials are then reviewed at an Evaluations meeting and the members present vote on whether to accept the person as an introductory member.
+\end{enumerate}
 Note: Most membership privileges do not initiate until successful completion of the introductory process.
@@
 Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
-
-\bsection{Selection Process for First Quarter and Entering RIT Students}
-\bsubsection{The applicant submits an application to the Evaluations Committee for review.
-The preferred application time is during the previous academic year up to one week prior to the Department of Residence Life's Deadline for Acceptance of Entering Students into Special Interest Houses.}
-\bsubsection{The applicant participates in an informal interview with exactly three current Resident, Non-Resident, or Alumni members.}
-\bsubsection{The application and interview is reviewed by the Evaluations Committee to make a decision on either the granting or denial of membership in the House.
-The applicant is notified of the committee's decision within three weeks after the Department of Residence Life's Deadline for Acceptance of Entering Students into Special Interest Houses.}
-\bsubsection{The applicant moves onto the House Fall Quarter and is granted full membership privileges and responsibilities including House dues, combinations, and accounts.
-In addition to these privileges and responsibilities, the new member must participate in the Introductory Process.}
-\bsubsection{During the Introductory Evaluation Process, the new member's Introductory Process will be used to aid in evaluating their membership.
-If the new member has unsuccessfully completed the Introductory Process or has been found to be a detriment to House objectives or morale, the person's membership may be revoked pursuant to the Membership Revocation Process and the person would be asked to find alternative housing as soon as possible in accordance with all applicable Residence Life Policies regarding room changes.
-If the new member has completed the Introductory Process, passes the Introductory Evaluation Process and is not found to be a detriment to House objectives or morale, it is announced at the following House meeting and appropriate traditions are upheld.}
+\bsubsection{Selection Process for First Semester and Entering RIT Students}
+\begin{enumerate}
+	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
+The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
+	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
+An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.
+\end{enumerate}
 Note: Most membership privileges do not initiate until successful completion of the introductory process.
@@
 \\* \\*
-Additional Note: Any member who has not been subject to at least one Objective Evaluation (Spring Evaluations) cannot become an Alumni.
-Instead, if the member moves off floor, the member becomes a Non-Resident member.
-This is only true of persons who have not gone through the Objective Evaluation Process at some point during their Computer Science House membership.
-\\* \\*
 Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
-
-\bsection{Selection Process for Honorary Members}
-\bsubsection{A House Member submits to the Evaluations Committee, a nomination for a person they feel is deserving of Honorary Membership.}
-\bsubsection{The Evaluations Committee performs some preliminary research on the candidate and presents the finding.}
-\bsubsection{The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
-If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.}
-\bsubsection{The nomination is presented at a House meeting for discussion.
-Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
-A quorum of two-thirds the number of all House members eligible to vote is required for the vote to be official.
-A vote equaling or exceeding two-thirds the number of all ballots cast is required for the candidate to be granted Honorary Membership.}
-\bsubsection{The candidate is notified of their selection as an Honorary Member and presented with the honor.}
-
-\bsection{Selection Process for Advisory Members}
-\bsubsection{A House Member submits to the Executive Board, a nomination for a person who they feel would benefit the House as an advisor during the period of time provided for by Article V, Section F, Subsection 2 Advisory Membership Selection.}
-\bsubsection{After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.}
-\bsubsection{A discussion of the candidates will be held at the following House meeting.}
-\bsubsection{Ballots will then be distributed for a secret ballot House vote.
-The vote is a fifty-percent vote meaning a quorum of fifty percent of the number of all House members eligible to vote is required for the selections to be official.
-A vote for the selection of a specific candidate equaling or exceeding fifty percent of the number of ballots cast is required for the respective advisor candidate to be selected.
+\bsubsection{Selection Process for Honorary Members}
+\begin{enumerate}
+	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
+	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
+	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
+	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
+Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
+	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
+\end{enumerate}
+\bsubsection{Selection Process for Advisory Members}
+\begin{enumerate}
+	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members.
+After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
+	\item After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.
+	\item A discussion of the candidates will be held at the following House meeting.
+	\item Ballots will then be distributed for a secret ballot, fifty-percent House vote, as defined in \ref{Fifty Percent}.
 If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level.
 If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated.
-This recast process may not be repeated a second time.}
-\bsubsection{All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
+This recast process may not be repeated a second time.
+	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
 If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors.
 Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level.
-If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.}
+If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.
+\end{enumerate}
 
-\bsection{Evaluations Process}
+\bsection{Evaluations Processes}
 During the academic year, a House member is evaluated by two different processes.
-The first process, known as the Subjective Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House.
-The second process, known as the Objective Evaluation, is responsible for determining those individuals who will be offered residence on the House for the next academic year.
-These processes are separate from each other and should not interfere with one another, with the exception that the Subjective Evaluation is used to provide information for the Objective Evaluation.
+The first process, known as the Housing Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House.
+The second process, known as the Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+These processes are separate from each other and should not interfere with one another.
+Semi-Annual Evaluations Meetings are open only to all current Active Members.
+All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
 \\* \\*
-At the beginning of any Evaluation Process listed herein, the director of the Evaluation Committee must read the sections of the Computer Science House Constitution and By Laws used during the respective Evaluation Process.
-\bsubsection{Subjective Evaluation}
-The subjective evaluation process occurs during the academic year.
-It is performed mid Winter Quarter.
-The members of the Evaluations Committee, on a member by member basis, review the project logs for projects on which the member was involved, along with the member's activity worksheet and any other information the member chooses to provide.
-Each active House member will receive two Housing Points (see By-Law V, Section F).
-The Evaluation Committee may also award one bonus point if it decides that this house member has performed a large or exceptional amount of work for the house.
-The committee may also deduct one housing point from any House member who has not performed an acceptable amount of work for the house.
-The guidelines of the committees will be used as a guide in determining bonus and deducted points.
-No housing points will be awarded to members who do not return the Evaluation Activity Sheets.
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
+It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.
+\bsubsection{Housing Evaluation}
+The Housing Evaluation process occurs during the academic year.
+It is performed late Fall Semester after the Introductory Evaluation and is led by the Evaluations Director.
+The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).
 \\* \\*
-Any house member not living on-floor, for example, because a leave of absence for CO-OP, during the quarter of Subjective Evaluations will be evaluated by these criteria and awarded their share of housing points near the end of the quarter in which they return.
+All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant.
+A member’s failure to submit the activity report will result in that member receiving no housing points.
+Attendance is also required for a member to be evaluated, else they will receive no housing points.
+Any member unable to attend because of outstanding circumstances (e.g.
+away on co-op) may also submit an activity report and be voted on, though they may not vote.
+Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.
 \\* \\*
-A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
+The participating members, on a member by member basis, review the activity report provided by each member.
+The participating members may then choose to award one, two, or three housing points to each member.
+Points are awarded on the basis of contributions to House.
+Above average members receive three points, average members two points, and below average members one point.
 \\* \\*
-All votes during the Subjective Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in Article VIII, Section C, Subsection 4.
-The votes will be counted by the Evaluations Director and two randomly chosen vote counters from the Evaluation Process Participants.
-\bsubsection{Objective Evaluation}
-The objective evaluation process occurs once per academic year.
-It is performed as part of the Evaluation Process that takes place during the middle of spring quarter.
-The Evaluation Committee, on a member by member basis, ensures that each member has met the minimum requirements in order to be placed on the housing list for the following year.
-These requirements are detailed in Article V under expectations for each category of membership.
-These requirements must be completed by the seventh week of Spring Quarter when objective evaluations will occur.
+A quorum of two-thirds of all Active (excluding Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
 \\* \\*
-A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
+All votes during the Housing Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in \ref{Three Tiered}.
+\bsubsection{Membership Evaluation}
+The Membership Evaluation process occurs once per academic year. It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+\bsubsubsection{Voting} 
+A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year.
+All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.These requirements are detailed in Article V under expectations for each category of membership.
+These requirements must be completed before the Membership Evaluation occurs.
+A secret Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\bsubsubsection{Outcomes}
+Members who receive a pass have the option participate as an Active Member in the following the year and remain on the upcoming roster if applicable.
 \\* \\*
-All votes during the Objective Evaluation Process must be Closed Ballot, Simple Majority Vote as defined in Article VIII, Section C, Subsection 1.
-The votes will be counted by the Evaluations Director and two randomly chosen vote counters from the Evaluation Process Participants.
-\bsubsection{Responsibilities of Members and Directors}
-Each member will be required to complete a form known as the activity worksheet for each Subjective Evaluation.
-This form is a list of what projects the member participated in since the last evaluation period, and should detail the level of involvement in each project.
-After being verified by the appropriate directors, the Evaluation Committee will include this list in its review of the member.
+If a member fails and has never passed an Membership Evaluation in the past, his membership will be revoked at the end of the year.
+If the member has previously passed an Membership Evaluation he will move to Alumni Membership status.
+In either case, the member forfeits his ability to be included on the following year’s roster.
 \\* \\*
-\textbf{It is incumbent upon each House member to provide the Evaluation Committee with whatever information he or she feels is necessary to ensure an accurate evaluation.}
-\\* \\*
-For every House project there will be created a project log.
-It minimally contains information describing the project as well as the project leaders and participants, and should detail the participants involvement with the project.
-The project log is to be submitted to the appropriate director.
-If an appropriate director does not exist, the project log is to be submitted to the chairman.
-It is the director's responsibility to ensure that a project log is created and submitted for every House project that falls under that director's jurisdiction.
+A member may be given a conditional to complete as a means of making up for missing requirements.
+A conditional may be proposed by any member present at the Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+Each conditional consists of a set of additional requirements a deadline for completing them.
+When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+A conditional member who does not meet these additional requirements will have failed the evaluation.
 \bsubsection{Appeals Process}
 If a member disagrees with the outcome of any evaluation, (e.g.
-is not asked to return to the House for the following year) and wishes to appeal the decision, he or she should immediately contact the Evaluations Director, the House Manager, or the Chairman.
+is not asked to return to the House for the following year) and wishes to appeal the decision, he or she should immediately contact the Evaluations Director or the Chairman.
 At the following Executive Board meeting, the member will present his appeal to the Board.
-The Executive Board can uphold, overturn or conditionally overturn the Evaluation Committee's decision with a secret ballot Two Thirds Vote as described in Article VIII, Section C, Subsection 3.
-If the decision is overturned or conditionally overturned, the member is to be added to the housing list immediately.
+The Executive Board can uphold, overturn or conditionally overturn the Evaluation decision with a Simple Majority Vote as described in \ref{Simple Majority}.
 \\* \\*
-If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the Area Coordinator.
-\bsubsection{Introductory Evaluation}
-The Introductory Evaluation process occurs once per academic year.
-It is performed as part of the Introductory Process that takes place during Fall Quarter, immediately after completion of the Introductory Process.
-On a member by member basis, this evaluation process decides if each member has successfully completed the Introductory Process Requirements.
-These requirements are listed in By-Law V, Section A.
-If the person has met the requirements, he is asked to become a Resident or Non-Resident member.
-Otherwise the person is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life Policies regarding room changes.
-\\* \\*
-A quorum of two-thirds of all Resident and Non-Resident (except for Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the Area Coordinator
 
 \bsection{Expectations of House Members}
-Each Member is required to pay House dues as stated in By-Law IV, Section A, attend all House Meetings, be an active participant in at least one committee, and attend at least twenty-five (25) committee meetings of which ten (10) are for the committee in which the member is an active participant.
-Each director will establish guidelines at the start of Fall Quarter, outlining explicit expectations of active participants.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
 Members are also required to actively participate in a majority of House activities.
 \\* \\*
-The member must lead one major House project during the academic year.
-The member is required to submit a proposal for this major project to the Executive Board for approval.
-As an option to this requirement, the member may instead assist on a large number of House activities and projects without actually assuming a leadership role in the activity or project.
+The member must participate significantly in at least one major House project during the academic year.
+The member is required to submit a description for this major project to the Executive Board for approval.
+As an option to this requirement, the member may instead assist on a large number of House activities and projects.
 However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
 This participation will be evaluated by the Executive Board.
+
+\bsection{Housing Status}
+All Active and Introductory Members have a housing status.
+This status indicates their right to priority housing on the floor.
+Any Alumni Member in good standing will maintain their previous On Floor status upon a return to Active membership.
+\bsubsection{On-Floor Status}
+Members with On-Floor status are eligible to live on the floor.
+To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
+The Evaluations Director will then bring them up for vote at the next meeting.
+\bsubsection{Off-Floor Status}
+Members with Off-Floor status do not have the right to live on the floor. They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
+
 \bsection{Housing Priority System}
-The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment, the Assignment of Available Housing, or the changing of status membership status to Resident Member.
-The member with top priority is the member with the most Housing Priority Points.
-Housing points are accumulated during the Subjective Evaluation described in By Law-IV, Section1.13, Subsection1.13.1.
+The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
+The member with top priority is the member with on-floor status and the most Housing Priority Points.
+Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
 \\* \\*
 In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
-\bsection{Single Room Assignments}
-When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H, regardless of the member's current housing status.
+\bsubsection{Single Room Assignments}
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
 If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
@@
 It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
-\bsection{Double Rooms as Single Rooms}
-During the third week of each quarter, if there is no waiting list for resident membership to the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in By-Law V, Section I.
+\bsubsection{Double Rooms as Single rooms}
+During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
 It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
 This only applies if there is a totally vacant room.
+
+% BY-LAW V - OPERATIONS OF THE OPERATIONAL COMMUNICATIONS DIRECTORSHIP
+\bylaw{Operations of the Operational Communications Directorship}
+The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+It  is a self-governing committee making decisions by a simply majority vote.
+Membership is composed of all Root Type Persons.
+
+\bsection{Selection of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
+This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.
+A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
+\end{enumerate}
+
+\bsection{Qualifications of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
+	\item Candidates may be granted an exemption by current Root Type Persons. Such an exemption may be withdrawn at any time by the current Root Type Persons.
+	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
+Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
+	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+\end{enumerate}
+
+\bsection{Creation of Accounts}
+Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
+	\item Obtain 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+\end{enumerate}
+
 \end{document}

### 2013-05-24 constitution.tex
Fixed date, and allowed for cross-document hyperlinking

@@
 % Define the external document to be bylaws for cross referencing purposes
-\externaldocument{bylaws}
+\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
 
@@
 \title{Computer Science House Constitution}
-\author{Computer Science House Executive Board}
+\author{Computer Science House Constitution Committee}
 % Last Modified Date
@@
 
+% % Adding an \asubsubsection -- I feel dirty
+\setcounter{secnumdepth}{5}
+\newcommand{\asubsubsection}[1]{\paragraph{#1} \label{#1}}
+\renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}
+
 % Headings
 \pagestyle{myheadings}
-\markright{{\rm CSH Constitution \hfill  As of \datechanged \hfill Page }}
+\markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}
 
@@
 
-% Articles
-\article{Name}
+% ARTICLE I - INTRODUCTION
+\article{Introduction}
+
+\asection{Name}
 The name of this Special Interest House shall be Computer Science House.
 
-\article{Derivation of Authority}
+\asection{Derivation of Authority}
 The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Department of Residence Life in conjunction with the Residence Halls Association.
 
-\article{House Objectives}
+\asection{House Objectives}
 The objectives of Computer Science House are:
@@
 
+% ARTICLE II - CONSTITUTIONAL STRUCTURE
 \article{Constitutional Structure}
+
 \asection{House Charter}
@@
 It is reviewed annually by the Department of Residence Life.
-The House Constitution is comprised of three sections:  articles, by-laws, and guidelines.
-Any non-semantic change to an article or by-law should be presented to the House by the Evaluations Committee for discussion.
+The House Constitution is comprised of two sections: articles and by-laws.
+Articles define the major aspects of the House.
+A by-law may expand on rules outlined in an article, but they must never contradict a Constitutional article.
+
+\asubsection{ Non-Semantic Changes}
+Any non-semantic change to the Constitution should be presented to the House for discussion.
 After the discussion an immediate House vote is taken.
@@
 A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.
-Non-semantic changes to the guidelines and semantic changes to articles, by-laws, or guidelines are described in detail below.
 
-\asubsection{Articles}
-Articles define the major aspects of the House.
-Any semantic change to an article requires the change to be proposed in writing for discussion at a House Meeting.
+\asubsection{Semantic Changes}
+Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a secret ballot House vote as described in \ref{Voting}, Voting.
+The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
-An article may be overridden by an immediate House vote as described in \ref{Voting}, Voting.
+The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
 There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official.
@@
 
-\asubsection{By-Laws}
-By-Laws define the more flexible aspects of the House.
-A by-law may expand on rules outlined in an article, but they must never contradict an article.
-Any semantic change to a by-law requires the change to be proposed in writing for discussion at a House Meeting.
-Any modifications made due to the discussion are added to the written proposal and the modified proposal is re-read prior to voting.
-The vote may be taken immediately or tabled one week at the discretion of the Executive Board.
-When the final proposal is ready to be voted upon, an immediate House vote will be taken as described in \ref{Voting}, Voting.
-A quorum of two-thirds of the number of all House members eligible to vote must cast a vote for the vote to be official.
-A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
-A by-law may be overridden by an immediate House vote as described in \ref{Voting}, Voting.
-There must be a quorum of two-thirds of the number of all House members eligible to vote for the vote to be official.
-A vote equaling or exceeding two-thirds of the number of votes cast is required for the override to take effect.
-
-\asubsection{Guidelines}
-Guidelines define the standard operating procedure of the Committees of the House.
-Guidelines must never contradict any rule defined in either the articles or by-laws.
-They are drafted during the Executive Board Training Process by the Director of the respective Committee.
-Directors and Committees are expected to adhere to them, but if necessary, may deviate from a stated guideline.
-The guidelines will include:
-\begin{itemize}
-\item An explicit definition of what it means to be a member of the respective committee
-\item Expectations of members in the committee
-\item Goals of the committee for the operating year
-\end{itemize}
-The House must be notified of any deviation from a stated guideline.
-Any semantic or non-semantic change to a guideline is presented in writing to the Committee the guideline pertains to.
-The change must pass a simple majority vote within the members of the committee for it to be accepted.
-It is then presented to the Executive Board for review prior to placing it in the Constitution.
-The House is notified of the change at the following House meeting.
-
-\asubsection{House Rules}
-The House Rules capsulate a House Member's responsibilities and expectations.
-Members are required to sign the document signifying their acceptance of the membership requirements and expectations.
-All Resident and Non-Resident are required to sign the House Rules annually.
-Because the House Rules are extracted from the Constitution, any modifications to the contents of the House Rules must first be made to the Constitution.
-\ref{Operations of the Executive Board}, \ref{The House Rules}, describes which information is extracted from the Constitution and placed into the House Rules.
-
+% ARTICLE III - MEMBERSHIP
 \article{Membership}
-There are six major types of membership available to Computer Science House.
+There are five major types of membership available to Computer Science House.
 Each carries different qualifications, expectations, and privileges.
@@
 	\item[Selection:] The process by which an applicant gains membership.
-\item[Expectations:] What expectations the House has on its members.
-\item[Privileges:] What privileges the member can expect from the House.
-\item[Evaluations:] The process by which a member is reviewed and evaluated.
-\item[Resignations:] The process by which a member resigns membership.
+	\item[Expectations:] The duties and responsibilities of House members.
+	\item[Privileges:] The benefits offered to House members.
+	\item[Evaluations:] The process by which a member is reviewed and assessed.
+	\item[Resignations:] The process by which a member terminates House membership.
 	\item[Term:] The length of time the membership lasts.
 \end{description}
+
 \asection{Introductory Membership}
 \asubsection{Introductory Membership Qualifications}
-Introductory Membership is open to all RIT students.
+Introductory Membership is open to all students at the Rochester Institute of Technology.
 \asubsection{Introductory Membership Selection}
-Applicants notify the House of their interest in membership by submitting an application to the Evaluations Committee.
-They must then undergo the selection process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
+Applicants notify the House of their interest in membership by submitting an application to the Evaluations Director.
+They must then undergo the selection process as defined in \ref{Selection Processes}.
 \asubsection{Introductory Membership Expectations}
-Introductory members are expected to be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
-If an Introductory member fails to  obtain 60\% (rounded up to the nearest whole person) of the Resident  Members signatures in the Introductory packet, discussed in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}, said member will not receive use of Computer Science House  facilities, as described in \ref{Introductory Membership Privileges}, until successful completion  of Introductory Evaluations.
+Introductory members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
 \asubsection{Introductory Membership Privileges}
@@
 \asubsection{Introductory Membership Evaluations}
-Introductory members are evaluated on their performance during the introductory period.
-The introductory process is described in \ref{Operations of the Evaluations Committee}, \ref{The Introductory Process}.
+Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
 \asubsection{Introductory Membership Resignations}
-An introductory member may resign by submitting the request for termination of membership to the House Chairman, or Evaluations Director in writing before the completion of the introductory process.
+Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
-The introductory membership shall last until the end of the introductory process, at which time they will either have their membership revoked or have their membership status changed to Resident member or Non-Resident member.
+Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
 
-\asection{Resident Membership}
-\asubsection{Resident Membership Qualifications}
-Resident Membership is open to all RIT students who comply with the Residence Life policies regarding residence in the Residence Halls.
-\asubsection{Resident Membership Selection}
-Applicants notify the House of their interest in Resident Membership by submitting an application to the Evaluations Committee and must then undergo the Selection Process as described in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
-\asubsection{Resident Membership Expectations}
-Resident members are expected to live on the house and be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
-\asubsection{Resident Membership Privileges}
-Resident Members receive the right: to vote on all issues brought before the House, to have residency on the House, to hold an Executive Board office on the House, to use the Computer Science House facilities, to attend Computer Science House functions, to have priority for available housing on the House when returning from cooperative education as stated in \ref{Operations of the Evaluations Committee}, \ref{Housing Priority System}, to have guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process.
-\asubsection{Resident Membership Evaluations}
-Resident Members are evaluated semi-annually through the Evaluation Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
+\asection{Active Membership}
+\asubsection{Active Membership Qualifications}
+Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
+\asubsection{Active Membership Selection}
+Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
+\\*\\*
+Any Alumni Member in bad standing may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
+If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+The decision will be announced at the following House meeting.
+\asubsection{Active Membership Expectations}
+Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
+\asubsection{Active Membership Privileges}
+Active Members receive the right to:
+\begin{itemize}
+	\item Vote on all issues brought before the House
+	\item Reside on the House
+	\item Hold an Executive Board office on the House
+	\item Use Computer Science House facilities
+	\item Attend Computer Science House functions
+	\item Receive priority for available housing on the House when returning from cooperative education
+	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
+\end{itemize}
+\asubsection{Active Membership Evaluations}
+Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
 Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
-\asubsection{Resident Membership Resignations}
-A Resident member may resign by submitting in writing the reason for resignation to the House Chairman, or Evaluations Director.
+\asubsection{Active Membership Resignations}
+A Active member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
-\asubsection{Resident Membership Term}
-Resident Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.
-
-\asection{Non-Resident Membership}
-\asubsection{Non-Resident Membership Qualifications}
-Non-Resident membership is open to all RIT students.
-\asubsection{Non-Resident Membership Selection}
-Applicants notify the House of their interest in Non-Resident membership by submitting an application to the Evaluations Committee and must then undergo the Selection Process as described in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Students Attending RIT for at Least One Quarter} and \ref{Selection Process for First Quarter and Entering RIT Students}.
-Any house Alumni may become a Non-Resident member by notifying the Evaluations Committee of their intent to participate, at which point they are reinstated as Non-Resident members of the house.
-\asubsection{Non-Resident Membership Expectations}
-Non-Resident members are expected to be active participants in the House as defined in \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
-\asubsection{Non-Resident Membership Privileges}
-Non-Resident Members receive the right: to vote on all issues brought before the House, to use the Computer Science House facilities, to attend Computer Science House functions, to have priority for available housing on the House as stated in \ref{Operations of the Evaluations Committee}, \ref{Housing Priority System}.
-\asubsection{Non-Resident Membership Evaluations}
-Non-Resident Members are evaluated semi-annually through the Evaluation Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
-\asubsection{Non-Resident Membership Resignations}
-A Non-Resident Member may resign by submitting in writing the reason for resignation to the House Chairman, or Evaluations Director.
-The resignation will be read at the following House Meeting and become effective at that time.
-\asubsection{Non-Resident Membership Term}
-Non-Resident Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status according to \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
+\asubsection{Active Membership Term}
+Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.
 
@@
 \asubsection{Alumni Membership Qualifications}
-Alumni Membership is open to all prior members of Computer Science House who departed for reasons other than revocation of House Membership or failing the Objective Evaluation. 
+Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
 \asubsection{Alumni Membership Selection}
-Alumni Membership is the status of all prior members of Computer Science House who departed the house for any reasons other than failure of the Evaluations Process as described in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
+Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
+\\*\\*
+Active members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to EBoard for an exemption based on their circumstances. 
 \asubsection{Alumni Membership Expectations}
-There are no expectations associated with the Alumni Membership status, however those who are able are encouraged to adhere to \ref{Operations of the Evaluations Committee}, \ref{Expectations of House Members}.
+There are no expectations associated with the Alumni Membership status.
 \asubsection{Alumni Membership Privileges}
-Alumni Members, at the discretion of the Executive Board, shall receive the right: to the use of Computer Science House facilities and to attend Computer Science House functions.
+Alumni Members shall receive the right to:
+\begin{itemize}
+	\item Use Computer Science House facilities
+	\item Attend Computer Science House functions
+\end{itemize}
 \asubsection{Alumni Membership Evaluations}
-Alumni Members are not subject to the Evaluations Process.
+Alumni Members are not subject any evaluation.
 \asubsection{Alumni Membership Resignations}
@@
 \asubsection{Alumni Membership Term}
-Alumni Membership shall last until the member changes their membership status as described in the Qualifications and Selections sections of either Resident or Non-Resident Membership.
+Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.
 
@@
 \asubsection{Honorary Membership Selection}
-Any House member may nominate a candidate for Honorary Membership by submitting the name in writing to the Evaluations Committee.
-The Evaluation Committee then begins the Honorary Membership Selection Process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Honorary Members}.
+Any House member may nominate a candidate for Honorary Membership by submitting the name in writing to the Evaluations Director.
+The Evaluation Director then begins the Honorary Membership Selection Process as defined in \ref{Selection Process for Honorary Members}
 \asubsection{Honorary Membership Expectations}
@@
 \asubsection{Honorary Membership Resignations}
-An Honorary Member may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become effective at that time.
+An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
 \asubsection{Honorary Membership Term}
@@
 \asubsection{Advisory Membership Selection}
-Advisors are selected during the start of the academic year.
-Any House member may nominate a candidate for Advisory Membership by submitting the name in writing to the Executive Board.
-The candidates then participate in the Advisor Selection Process as defined in \ref{Operations of the Evaluations Committee}, \ref{Selection Process for Advisory Members}.
+The Executive Board may open nominations for Advisory Members. The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
 \asubsection{Advisory Membership Expectations}
-Advisors are encouraged to offer advise and assistance to the House in any capacity the Advisor is able to help.
+Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
 Advisors are also encouraged to meet the House members and occasionally attend House activities.
@@
 \asubsection{Advisory Membership Resignations}
-An Advisor may resign by submitting in writing the reason for resignation to the House Chairman. The resignation will be read at the following House Meeting and become effective at that time.
+An Advisor may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
 \asubsection{Advisory Membership Term}
-Advisory Membership shall last for one academic year or until the member resigns.
+Advisory Membership shall last until the member resigns.
 
+% ARTICLE IV - EXECUTIVE BOARD
 \article{Executive Board}
 The Executive Board is the main governing body of the House.
-Its purpose if to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
+Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
+It is composed of the seven permanent directors and the Chairman.
+\\*\\*
+There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
+Ad-hoc directorships are created on an as-needed basis.
+They are generally very task oriented and are chaired by a House member.
+A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
+Any large expenditures or large effect decisions must be brought before the entire House
 \asection{Members of the Executive Board}
@@
 	\item House Improvements Director
-    \item Root Type Persons Representative
+	\item Operational Communications Director
 	\item House History Director
@@
 	\item House Secretary
+	\item Ad Hoc Directors
 \end{itemize}
+\asection{Closed Executive Board}
+Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
+A closed Executive Board meeting may be called at any time by any member of the Executive Board.
+However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.
 
 \asection{Responsibilities}
-% For this section, we want items to use letters
-\renewcommand{\theenumi}{\alph{enumi}}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
 \asubsection{Responsibilities of the Executive Board}
 \begin{enumerate}
-\item To fulfill the responsibilities pertaining to its purpose as stated in the description of the Executive Board in the header paragraph for \ref{Executive Board} (Executive Board).
-\item To meet at least weekly during the standard operating session, as defined in \ref{General Operations of the House}, \ref{Standard Operating Session}, to discuss and report the operations of the House.
+	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
+	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
 	\item To report pertinent information to House members at the following House Meeting.
-\item To establish goals and expectations for the House for the upcoming year.
-\item To submit a yearly statement of goals and accomplishments of the present year to House members and to the Department of Residence Life.
-\item To act as a judicial board for any final ruling on the interpretation of the House Constitution, House document, or action taken by the House.
+	\item To maintain records of the goals defined by each previous Executive Board.
+	\item To act as a Judicial Board as defined in \ref{Judicial}.
+	\item To review major projects, as defined in \ref{Expectations of House Members},  presented to them by the Evaluations director.
+	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
+	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
+	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
 \end{enumerate}
@@
 	\item To act as a liaison to the academic and administrative departments at RIT.
-\item To act in collaboration with the Evaluations Director and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House.
+	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
 	\item To cast tie-breaking vote in a split decision in an Executive Board vote.
@@
 \begin{enumerate}
-\item To preside over Evaluations Committee Meetings
-\item To exercise general supervision over the operations of the Evaluations Committee.
-\item To oversee the selection of new House members.
-\item To oversee the evaluations of current House members.
-\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership status to Resident Membership.
+	\item To preside over Evaluations Meetings.
+	\item To exercise general supervision over Evaluations operations.
+	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
+	\item To oversee the Semi-Annual Evaluations of current House members.
+	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
 	\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House.
+	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
 	\item To prepare the House for Open Houses, tours, and special events.
@@
 \begin{enumerate}
-\item To preside over Social Committee Meetings
-\item To exercise general supervision over the operations of the Social Committee.
+	\item To preside over Social Meetings. House members are encouraged to bring ideas for social events to the meetings for discussion.
+	\item To exercise general supervision over Social operations.
 	\item To oversee the organization, initiation, and execution of House activities and events.
+	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year.
 \end{enumerate}
+
 \asubsection{Responsibilities of the Financial Director}
 \begin{enumerate}
-\item To oversee the Financial Committee.
+	\item To preside over Financial Meetings. House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
 	\item To supervise financial administrators and transactions involving house projects.
@@
 	\item To plan and enforce a House budget.
-\item To supervise House expenditures and financial transactions.
-\item To publish a quarterly House financial statement.
-\item To supervise the collection of quarterly House dues.
+	\item To oversee House finances and generation of House funds.
+	\item To publish a semesterly House financial statement.
+	\item To supervise the collection of semesterly House dues.
 	\item To oversee the planning and execution of fundraising events.
@@
 \begin{enumerate}
-\item To preside over Research and Development Committee Meetings
-\item To exercise general supervision over the operations of the Research and Development Committee.
-\item To oversee the organization and construction of technical projects for the House's benefit.
-\item To collaborate with the Operational Communications Committee in an attempt to fulfill the House's need for technical equipment.
+	\item To preside over Research and Development Meetings. House members are encouraged to bring ideas for projects to the meetings for discussion.
+	\item To exercise general supervision over Research and Development operations.
+	\item To oversee the planning, organization and construction of technical projects for the House's benefit.
+	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment.
 	\item To provide seminars and tutorials to educate House members in technical areas.
@@
 \begin{enumerate}
-\item To preside over House Improvements Committee Meetings.
-\item To exercise general supervision over the operations of the House Improvements Committee.
+	\item To preside over House Improvements Meetings.
+	\item To exercise general supervision over the House Improvements operations.
 	\item To oversee the organization and construction of physical improvements to the House.
@@
 
-\asubsection{Responsibilities of the Root Type Persons Representative}
+\asubsection{Responsibilities of the Operational Communications Director}
 \begin{enumerate}
@@
 	\item To report the status of the House computer systems and network to the Executive Board and House members.
-\item To oversee the implementation of maintenance and upgrades to the House Computer Systems and Network.
-\end{enumerate}
-
-\asubsection{Responsibilities of the Root Type Persons}
-\begin{enumerate}
-\item The Root Type Persons are responsible for improvement, maintenance, and management of the House's computer systems and networking equipment.
-\item There must always be at least two Root Type Persons at all times.
 \end{enumerate}
@@
 \begin{enumerate}
-\item To preside over House History Committee Meetings
-\item To exercise general supervision over the operations of the House History Committee.
-\item To oversee the upkeep of House Members records.
-\item To oversee the celebration of all House Member's birthdays.
-\item To oversee the production of a quarterly newsletter highlighting Computer Science House happenings and a yearly Alumni Directory.
+	\item To preside over House History Meetings.
+	\item To exercise general supervision over the House History operations.
 	\item To maintain, uphold, and promote house traditions.
-\item To collaborate with the Social Director(s) to ensure that all the Non-Resident, Alumni, and Advisory Members are informed of upcoming events.
+	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events.
+	\item To oversee the production and distribution of a semi-annual newsletter.
+	\item To oversee the creation of a yearbook outlining House events for the year.
 \end{enumerate}
@@
 
+\asubsection{Responsibilities of Ad Hoc Directorships}
+\begin{enumerate}
+	\item Ad-Hoc Directorships are responsible for the task for which they were created.
+	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director.
+\end{enumerate}
+
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director, House Improvements Director, House History Director}
+\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
 \begin{enumerate}
-\item Candidates must be Resident Members or Non-Resident Members during the term of office.
-\item Candidates must have at least two prior quarters House membership as either Resident or Non-Resident Membership.
+	\item Candidates must be Active Members during the term of office.
+	\item Candidates must have at least one full semester of House membership as an Active Member.
 	\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
 \end{enumerate}
-\asubsection{Qualifications to be the Root Type Persons Representative}
+\asubsection{Qualifications to be the Operational Communications Director}
 \begin{enumerate}
-\item Candidates must be a current Root Type Person.
-\item Candidates must be a currently Resident or Non-Resident House Member.
-\item A Root Type Person cannot be the representative if they currently hold any other Executive Board Position.
-\end{enumerate}
-\asubsection{Qualifications to be a Root Type Person}
-\begin{enumerate}
-\item Candidates must be a Resident Member in good standing, or be a Non-Resident Member and have been a Resident member within the last twelve months.
-\item Candidates may be granted an exemption by current Root Type Persons.  Such an exemption may be withdrawn at any time by the current Root Type Persons.
-\item Prior Root Type Persons are those members who are no longer current Resident or Non-Resident House members and have not been granted an extension by the current Root Type Persons.
-Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
-\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
+	\item Candidates must be a current Active Member.
+	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
 \end{enumerate}
 
-\asubsection{Qualifications to be the House Secretary}
+\asubsection{Qualifications to be the House Secretary on an Ad Hoc Director}
 \begin{enumerate}
-\item Candidates must be Resident Members on the House during the term of office.
-\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
+\item
+ Candidates must be Active Members.
 \end{enumerate}
@@
 \asubsection{Dual Directorship}
-Social Director is the only Executive Board position that allows for Dual Directorship.
+Social Director and Research and Development Director are the only Executive Board positions that allow for Dual Directorship.
 If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
@@
 Each different nomination must be a separate entry on the election ballot.
-\\The following special cases cover the operation of a dual directorship:
+
+The following special cases cover the operation of a dual directorship:
 \begin{itemize}
 	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
-The vacated office is then handled like any other vacated office; see \ref{Executive Board}, \ref{Resignations}.
+The vacated office is then handled like any other vacated office; see \ref{Resignations}.
 	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
@@
 	\item A member of a dual directorship may not hold any other Executive Board position.
-\item When attendance requirements call for the Social Directors to be present, both dual directorship members are to fulfill the requirements.
+	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.
 \end{itemize}
@@
 \begin{enumerate}
-\item The opening of the Executive Board position is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-Any House member may nominate any House member or members for a Dual Directorship if it is permitted for the respective office.
+	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
+Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
 	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.
@@
 In addition, an area will be provided to indicate a write-in selection of a candidate.
-\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Voting}, Voting.
-\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Voting}, Voting.
+	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Balloted Vote}.
+	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting.
 A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official.
@@
 	\item Each candidate will be given an equal amount of time before the Executive Board to present their platforms of candidacy.
-This Executive Board Meeting is closed to the Executive Board Members and House members with explicit invitation from the Executive Board.
+This Executive Board Meeting is open only to the Executive Board Members and House members with explicit invitation from the Executive Board.
 	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.
-After each candidate for an office has been presented and discussed, a simple majority Executive Board vote, as described in \ref{Voting}, Voting, is taken to determine the selection of candidates.
+After each candidate for an office has been presented and discussed, a simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine the selection of candidates.
 	\item All winners are notified and asked to accept or decline their selection.
@@
 \end{enumerate}
-\asubsection{Selection of the Root Type Persons Representative}
+\asubsection{Selection of the Operational Communications Director}
 \begin{enumerate}
-\item Root Type Persons Representative shall be chose by the current Root Type Persons.  The representative may change on a daily basis.
+	\item Root Type Persons Representative shall be chosen by the current Root Type Persons.
 \end{enumerate}
-\asubsection{Selection of Root Type Persons}
+\asubsection{Selection of Ad Hoc Directors}
 \begin{enumerate}
-\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Executive Board}, \ref{Qualifications to be a Root Type Person}.
-\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.  
-\item A list of all nominees who have accepted is presented to the Executive Board for approval.
-This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.
-A simple majority Executive Board vote, as described in \ref{Voting}, is taken to determine whether the nominations of the Root Type Persons are accepted.
-\end{enumerate}
-
-\asection{Evaluations}
-\begin{enumerate}
-\item All members of the Executive Board are subject to the Evaluation Process as stated in \ref{Operations of the Evaluations Committee}, \ref{Evaluations Process}.
+	\item When the Executive Board or a group of House members feels an Ad-hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
+	\item When the Ad-Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
 \end{enumerate}
@@
 An Executive Board Member may resign by submitting in writing the reason for resignation to the House Chairman.
-The resignation will be read at the following House Meeting and become e?ective at that time.
-The o?ce will become vacant and the selection process for a new member will begin at that time.
-The duties and responsibilities of a vacated o?ce are assumed by the Chairman or by a member of the Executive Board that is appointed at the Chairman’s discretion until the new member takes o?ce.
+The resignation will be read at the following House Meeting and become effective at that time.
+The office will become vacant and the selection process for a new member will begin at that time.
+The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
+
 \asection{Impeachment}
 \begin{enumerate}
-\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Voting}, \ref{Total Number of Possible Votes}.
+	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
 	\item The impeachment petition is then presented at an Executive Board Meeting.
@@
 	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
-Votes shall be collected and counted as described in \ref{Voting}, \ref{Secret Ballot}.
+Votes shall be collected and counted as described in \ref{Balloted Vote}.
 	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official.
-A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
+A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from oce.
 If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
-\item If the percentage of a?rmative votes equals or exceeds the minimum the impeached o?cer is relinquished of their position and any beneﬁts thereof and this position is treated like any other vacated position.
-A new selection and interim duty fulﬁllment procedure is followed similar to that of a resignation; see Article VI, Section 6.F.
+	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
+A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
 \end{enumerate}
@@
 \begin{enumerate}
-\item The Election Process for the following year's Executive Board members shall begin no later than the third week of the Spring Quarter.
-\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 30 of the following year.
+\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
+\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
 \item The term of an officer will be abbreviated due to resignation, impeachment, failure of the evaluation process, or change in membership status.
 \item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
+\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves. When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
 \end{enumerate}
 
-\article{House Committees}
-House Committees are the major work force of the House.
-There are two major types of committees: permanent and ad-hoc.
-There is one permanent committee for each major aspect of the government of the House, and each permanent committee is chaired by an Executive Board member.
-The ad-hoc committees are created on an as-needed basis.
-They are generally very task oriented and are chaired by a House member.
-A committee has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
-Any large expenditures or large effect decisions must be brought before the entire House.
-\asection{Evaluations Committee}
-\begin{enumerate}
-\item The Evaluations Committee is responsible for the screening, interviewing, and acceptance or rejection of prospective members to the House.
-The committee is also responsible for Semi-Annual Evaluations of current House members.
-\item Membership in the Evaluations Committee is open to any member of the house.  Evaluations Committee meetings are open to any member of the House.
-\item Semi-Annual Evaluations Meetings are open only to all current Resident and Non-Resident Members.
-These members must have attended the Criteria Definition Meeting held prior to the actual Semi-Annual Evaluations.
-All committee directors are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
-\end{enumerate}
-\asection{Social Committee}
-\begin{enumerate}
-\item The Social Committee is responsible for organizing and planning many of the House activities and social events.
-The committee is expected to ensure that there is a variety of activities for House members to participate in throughout the academic year.
-\item Membership in the Social Committee is open to any member of the House.
-House members with ideas for social events are encourages to approach the Social Director(s), discuss their ideas, and present them at a committee meeting.
-\end{enumerate}
-\asection{Research and Development Committee}
-\begin{enumerate}
-\item The Research and Development Committee is responsible for researching and planning House’s technical projects and activities.
-It is the responsibility of the committee to promote technical projects and seminars on ﬂoor and help develop the learning aspect of Computer Science House.
-\item  Membership in the Research and Development Committee is open to any member of the House.
-House members are encourage to work on technical projects or bring ideas for projects to the Research and Development Director for discussion and to present them at the committee meeting.
-\end{enumerate}
-\asection{House Improvements Committee}
-\begin{enumerate}
-\item The House Improvements Committee is responsible for the maintenance and upkeep of the House facilities, along with physical improvements to the living environment.
-\item Membership in the House Improvements Committee is open to any member of the House.  Members are encouraged to participate in some of the House Improvement projects.
-\end{enumerate}
-\asection{House History Committee}
-\begin{enumerate}
-\item The House History Committee is responsible for the maintenance and upkeep of House records of members and the production and distribution of a quarterly newsletter and a yearly Alumni Directory.
-\item The House History Committee is also responsible for the promotion of all Computer Science House traditions and leading the celebration of Computer Science House member's birthdays.
-The House History Committee will also present a yearbook outlining House events for the year to the House.
-\item Membership in the House History Committee is open to any member of the House.  House members are encouraged to participate in Committee activities.
-\end{enumerate}
-\asection{Operational Communications Committee}
-\begin{enumerate}
-\item The Operational Communications Committee is responsible for the improvement, maintenance, and management of the House's computer systems and networking equipment.
-\item Membership in the Operational Communications Committee is defined as any member who has been selected as a Root Type Person as defined in \ref{Executive Board}, \ref{Qualifications to be a Root Type Person}.
-\item The Operational Communications Committee is a self-governing committee making decisions by a simply majority vote.
-\end{enumerate}
-\asection{Financial Committee}
-\begin{enumerate}
-\item The Financial Committee is responsible for the generation of House funds.
-\item Membership in the Financial Committee is open to any member of the House.
-House members with ideas for fund-raising activities are encouraged to approach the Financial Director, discuss their ideas, and present them at a committee meeting.
-\item Included in the Financial Committee are those administrators responsible for overseeing those House privileges which require monetary commitment, for example: Drink Administrators.
-\end{enumerate}
-\asection{Ad-Hoc Committees}
-\begin{enumerate}
-\item Ad-Hoc Committees are responsible for the task for which they were created.
-When the task is completed, the committee dissolves.
-When the Executive Board or a group of House members feels an Ad-hoc Committee is necessary, they present their plans to the Executive Board and the Executive Board decides whether committee status is granted.
-\item When the Ad-Hoc Committee is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
-\item Any responsibilities for budgets or finances for the Ad-Hoc Committee are placed upon the assigned director.
-\item When an Ad-Hoc Committee Director resigns his duties, the committee dissolves and committee status must be reinstated with a new director.
-\end{enumerate}
+\asection{Appeals}
+Decisions made by the Executive Board may be appealed and overturned.
+To initiate an appeal, a Petition of Appeal must be presented to the Chairman affixed with signatures from one third of Active Members of house, or three voting members of Executive Board.
+After the petition has been presented, during the following House meeting, a discussion will be held where one petitioner and one Executive Board member will each make their case.
+After hearing from both representatives, there will be an Immediate Two-Thirds vote as defined in \ref{Two-Thirds} to confirm the appeal and thereby overturn the decision.
+Any decision that is overturned must be reevaluated by the Executive Board.
 
+% ARTICLE V - VOTING
 \article{Voting}
-There are two major ways to describe a vote: type of balloting and number of ballots required.
-A vote may be any combination of one type of balloting and one number of ballots required.
-There are also a number of definitions that need to be defined before the procedures can be defined.
+This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
 \asection{Definitions}
 \asubsection{Total Number of Possible Votes}
-The Total Number of Possible Votes is defined as the number of possible ballots that can be cast in a vote.
-In a House vote, it is the sum of the number of all Resident and Non-Resident members.
-In a formal Executive Board vote, it is defined as the number of all voting Executive Board members.
-In a committee vote, it is defined as the number of members present at the current committee meeting.
+The Total Number of Possible Votes is defined as the number of possible votes that can be cast in a single vote.
+\asubsubsection{House Vote} 
+The sum of the number of Active members.
+\asubsubsection{Executive Board Vote} 
+The number of voting Executive Board directorships.
+\asubsection{Total Number of Votes Cast}
+The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
 \asubsection{Quorum}
-A Quorum is defined as the minimum number of votes cast required for a vote to be official.
-It is usually defined as a fraction or a percentage of the total number of possible votes.
-A Quorum is reached if the number of votes cast, counting abstentions, is equal to or exceeding the minimum number of votes.
-\asubsection{Absent Ballot}
-An Absent Ballot is defined as any ballot that was not entered into the vote because a member eligible to vote did not vote or provide a means to indicate his or her vote.
-Absent Ballots are not counted towards a Quorum, but they are counted toward the total number of possible votes cast.
+A Quorum is defined by the minimum number of votes cast required for a vote to be official.
+It is a fraction or a percentage of the total number of possible votes.
+Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention.
+A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
 \asubsection{Proxy Ballot}
-A Proxy Ballot is defined as any ballot that was cast by one member on behalf of another member.
-Any member may cast Proxy Ballots for another member who is unable to actually participate in the vote and only by written permission for the specific vote.
-Proxy votes are only permissible where explicitly stated.
+A Proxy Vote is defined as any ballot that was cast by one member on behalf of another member.
+Any member may cast a Proxy Vote for another member who is unable to actually participate in the vote.
+A Proxy Vote must be explicitly written down and signed by the member not in attendance.
+The count of all Proxy Vote must be recorded and announced in all votes.
+Proxy Votes are only permissible where explicitly stated, at the discretion of the person chairing the vote.
 \asubsection{Abstention}
@@
 A means to abstain must always be provided in a vote.
-Abstentions are counted towards a quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
-\asubsection{Total Number of Votes Cast}
-The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
+Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
+\asubsection{Vote Counters}
+Vote Counters are the chairperson of the vote, and two randomly selected members.
 
-\asection{Type of Balloting}
-\asubsection{Secret Ballot}
-When a Secret Ballot is called for, the person chairing the vote will see that ballots are made with a means to indicate every possible choice in the vote.
-They are then distributed to each House member eligible to cast a ballot in the vote, and collected in the indicated ballot box for a pre-specified period of time, the length time depending on the nature of the vote.
-This time period must be a minimum of forty-eight hours in length for any constitutional modification vote, candidate selection vote, or officer removal vote, and twenty-four hours in length for any other vote.
-The minimum length of the time period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
-At the end of the voting period, the person chairing the vote collects the ballot box thus closing the voting.
-The votes are to be counted by person chairing the vote, and two House Members randomly selected, none of whom are directly involved in the vote.
-Being directly involved is defined as being a candidate in an election, or the accused or accuser in an impeachment.
-If every Executive Board member is directly involved in the vote, then a third House member is selected at random to count votes in place of the person chairing the vote.
-Any additional requirements to the voting procedure are described in the section pertaining to the actual vote.
+\asection{Types of Voting}
+\asubsection{Balloted Vote}
+\asubsubsection{Method of Vote} 
+Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
+A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
+At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period.
+The Vote Counters then tally the results.
+\asubsubsection{Voting Period} 
+For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
+For any other type of vote, the voting period must be at least twenty-four (24) hours.
+The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
 \asubsection{Immediate Vote}
-When an Immediate Vote is called for, the person chairing the vote will state all of the possible ways to vote and then call out each possibility one at a time.
+\asubsubsection{Method of Vote} 
+The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
 The chairing member will count the number of members casting their immediate vote for that possibility.
-When all of the possibilities have been voted upon, the totals will be tallied.
-Any additional requirements to the voting procedure are also described in the section pertaining to the actual vote.
-\asection{Number of Ballots Required}
-The Number of Ballots Required refers to the numbers required to achieve a quorum and for a vote to pass.
-Below are listed three standard votes.
+\asubsubsection{Voting Period} 
+An immediate vote lasts as long as it takes for all votes to be tallied.
+\asubsection{Secret Immediate Vote}
+\asubsubsection{Method of Vote} 
+The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
+Votes are kept anonymous.
+The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
+\asubsubsection{Voting Period}
+A secret immediate vote lasts as long as it takes for all votes to be tallied.
+\asubsection{Batch Vote}
+When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote.
+A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
+If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.
+
+\asection{Number of Votes Required}
+The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass.
+Below are listed four standard votes.
 Numbers for non-standard votes are defined in the section describing the actual vote.
-\asubsection{Simple Majority Vote}
-In a Simple Majority Vote a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
-A selection in the vote passes if the number of votes cast for that selection is larger than the number of votes cast for every other selection individually.
-\asubsection{Fifty Percent Vote}
-In a Fifty Percent Vote a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds fifty percent of the Total Number of Possible Votes.
-A selection in the vote passes if the number of votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast.
-\asubsection{Two-thirds Vote}
-In a Two-thirds Vote a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
-A selection in the vote passes if the number of votes cast for the selection equals or exceeds two-thirds of the Total Number of Votes Cast.
-\asubsection{Three Tiered Vote}
+\asubsection{Simple Majority}
+In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
+An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
+\asubsection{Fifty Percent}
+In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
+An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
+\asubsection{Two-Thirds}
+In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
+An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
+\asubsection{Three Tiered}
 When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest of highest option will only pass is the votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast.
-If neither the highest or lowest selection reaches fifty percent, the middle option will then be passed.
+If neither the highest or lowest selection reaches fifty percent, the middle option will then automatically be passed.
 In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.
-\asection{Ties Between Vote Selections}
-The action to take on a tie depends on whether or not the vote was a pass/fail vote or a multiple choice vote.
-In a pass/fail vote, if the number of votes cast for the pass selection equals the number of votes cast for the fail selection, then the vote failed.
-In a multiple choice vote, if multiple selections may pass, then a tie does not present a problem, however, if only one selection may pass, then the vote must either be recast or tabled according to the discretion of the person chairing the vote.
+
+\asection{Ties Between Vote Options}
+\asubsection{With Pass/Fail}
+If the number of votes cast for the pass option equals the number of votes cast for the fail option, then the vote has failed.
+\asubsection{With Multiple Options}
+If multiple options may pass, a tie does not present a problem.
+If only one option may pass, then the vote must be recast or tabled at the discretion of the person chairing the vote.
 In the event of a tie in an Executive Board vote, the Chairman may cast the tie-breaking vote.
+
+% ARTICLE VI - JUDICIAL
+\article{Judicial}
+The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
+\asection{Formation of a Judicial Board}
+A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
+If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board,  they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
+\asection{Judicial Investigation}
+The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
+\asection{Judicial Ruling}
+The Judicial Board may present an official ruling following the Judicial Investigation. This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
+
 \end{document}

### 2013-12-14 articles.tex
renamed constitution to articles

--- 2013-05-24 constitution.tex
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member.
-	\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
+	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
 \end{enumerate}
@@
 
-\asubsection{Qualifications to be the House Secretary on an Ad Hoc Director}
+\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
 \begin{enumerate}
@@
 \asubsection{Dual Directorship}
-Social Director and Research and Development Director are the only Executive Board positions that allow for Dual Directorship.
+Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
 If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
@@
 Each different nomination must be a separate entry on the election ballot.
+Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to to single or dual directorship.
 

### 2013-12-17 articles.tex
added some recent amenments, made small changes

@@
 % Define the external document to be bylaws for cross referencing purposes
-\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
+%\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
+\externaldocument{bylaws}[https://github.com/bencentra/Constitution/blob/master/bylaws.pdf?raw=true]
 
@@
 
-% % Adding an \asubsubsection -- I feel dirty
+% Adding an \asubsubsection -- I feel dirty
 \setcounter{secnumdepth}{5}
@@
 \\*\\*
-Any Alumni Member in bad standing may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
 If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
@@
 \asubsection{Active Membership Resignations}
-A Active member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.
-The resignation will take effect immediately and an announcement will be made at the following House Meeting.
+An Active Member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately.
 \asubsection{Active Membership Term}
@@
 \\*\\*
-Active members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to EBoard for an exemption based on their circumstances. 
+Active Members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to the Executive Board for an exemption based on their circumstances. 
 \asubsection{Alumni Membership Expectations}
@@
 	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
-	\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House.
 	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
@@
 Each different nomination must be a separate entry on the election ballot.
-Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to to single or dual directorship.
+Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to single or dual directorship.
 
@@
 \begin{enumerate}
-	\item Root Type Persons Representative shall be chosen by the current Root Type Persons.
+	\item A candidate for the Operational Communications Directorship shall be chosen by the current Root Type Persons.
+	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
+	\item The candidate is presented to the Executive Board for approval.
+This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
+A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
 \end{enumerate}
@@
 \asubsection{Three Tiered}
-When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest of highest option will only pass is the votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast.
-If neither the highest or lowest selection reaches fifty percent, the middle option will then automatically be passed.
+When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest or highest option will only pass if the votes cast for that selection exceed fifty percent of the Total Number of Votes Cast.
+If neither the highest or lowest selection exceeds fifty percent, the middle option will then automatically be passed.
 In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.

### 2013-12-17 bylaws.tex
added some recent amenments, made small changes

@@
 % Define the external document to be constitution for cross referencing purposes
-\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]
+%\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]
+\externaldocument{constitution}[https://github.com/bencentra/Constitution/blob/master/articles.pdf?raw=true]
 
@@
 \markright{{\rm CSH Constitution \hfill \datechanged \hfill Page }}
+
 % Reference example:
@@
 \bsection{Standard Operating Session}
-The Standard Operating Session for Computer Science House is during the fifteen weeks of Fall and Spring semesters.
+The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters.
 The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.

### 2014-03-06 articles.tex
fixed references, added makefile

@@
 % Comment out in final revision
-%\usepackage{showkeys}
+\usepackage{showkeys}
 
@@
 A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official.
-All winners are notified and asked to accept or decline their election.
+All winners are notified of their election, and they immediately assume the office for the term of the election.
 Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.
@@
 	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official.
-A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from oce.
+A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
 If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
@@
 Any decision that is overturned must be reevaluated by the Executive Board.
+
+Decisions made by the Executive Board may be appealed and overturned.
+To initiate an appeal, a Petition of Appeal must be presented to the Chairman affixed with signatures either one third of Active Members or three voting members of the Executive Board.
+After the petition is presented, the decision is overturned and will be reevaluated by the Executive Board at the upcoming Executive Board meeting.
 

### 2014-05-16 articles.tex
removed debug flag
housing eval, alumni membership, quorum fix

@@
 % Comment out in final revision
-\usepackage{showkeys}
+%\usepackage{showkeys}
 
@@
 Any non-semantic change to the Constitution should be presented to the House for discussion.
-After the discussion an immediate House vote is taken.
-A quorum of fifty percent of the number of all House members eligible to vote must be present in order for the vote to be official.
+After the discussion an immediate House vote is taken.A quorum of fifty percent of the Total Number of Possible Votes must be present in order for the vote to be official.
 A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.
@@
 The ballots are collected for a minimum of a forty-eight hour period.
-A quorum of two-thirds of the number of all House members eligible to vote must cast ballots for the vote to be official.
+A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
 A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
 The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
-There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official.
+There must be a There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
 A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
@@
 \end{itemize}
+Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum. Exceptions may be made at the discretion of the Evaluations Director.
 \asubsection{Active Membership Evaluations}
@@
 \asubsection{Alumni Membership Selection}
-Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
+Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
 \\*\\*
-Active Members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to the Executive Board for an exemption based on their circumstances. 
+Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing.
+This may be appealed to the Executive Board in order to pursue a different outcome.
 \asubsection{Alumni Membership Expectations}
@@
 	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting.
-A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official.
+A quorum of fifty-percent of the Total Number of Possible Votes is required for the elections to be official.
 All winners are notified of their election, and they immediately assume the office for the term of the election.
@@
 Votes shall be collected and counted as described in \ref{Balloted Vote}.
-	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official.
+	\item A quorum of two-thirds of the Total Number of Possible Votes is necessary for the vote to be official.
 A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
@@
 \asubsection{Total Number of Possible Votes}
-The Total Number of Possible Votes is defined as the number of possible votes that can be cast in a single vote.
-\asubsubsection{House Vote} 
-The sum of the number of Active members.
-\asubsubsection{Executive Board Vote} 
-The number of voting Executive Board directorships.
+The sum of the number of Active members eligible to vote (i.e. not on co-op)
 \asubsection{Total Number of Votes Cast}

### 2014-05-16 bylaws.tex
fixed references, added makefile
housing eval, alumni membership, quorum fix

@@
 On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
-A Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid.
+A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
 Neither absentee nor proxy votes are allowed.
@@
 The Housing Evaluation process occurs during the academic year.
-It is performed late Fall Semester after the Introductory Evaluation and is led by the Evaluations Director.
+It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director.
 The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).
@@
 \\* \\*
-A quorum of two-thirds of all Active (excluding Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
+A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
 \\* \\*
@@
 These requirements must be completed before the Membership Evaluation occurs.
-A secret Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid.
+A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
 Neither absentee nor proxy votes are allowed.

### 2014-05-16 articles.tex
and the rest

@@
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
+Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
 \asubsection{Active Membership Selection}
@@
 \asubsection{Active Membership Resignations}
-An Active Member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately.
+An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
+Instead of forfeiting membership, Active members who resign may elect to become Alumnias defined in \ref{Alumni Membership Selection}.
+The resignation will take effect immediately and an announcement will be made at the following House Meeting.
 \asubsection{Active Membership Term}
@@
 \begin{itemize}
-	\item House Secretary
 	\item Ad Hoc Directors
+\asubsection{House Secretary}
 \end{itemize}
@@
 \end{itemize}
-\asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director}
+\asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
 \begin{enumerate}
@@
 	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Balloted Vote}.
-	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting.
-A quorum of fifty-percent of the Total Number of Possible Votes is required for the elections to be official.
-All winners are notified of their election, and they immediately assume the office for the term of the election.
+	\item The winners are determined by a simple majority vote of the ballots cast as defined in 5.C.1, Voting.
+A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
+All winners are notified of their election.
+If the position is currently vacant, the winner immediately assumes office.
+If not, the winner will assume office at the end of the current term (\ref{Term}).
 Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.
-\end{enumerate}
-\asubsection{Selection of the Research and Development Director, House Secretary}
-\begin{enumerate}
-	\item  The opening of the Executive Board position is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-A House member may nominate any House member.
-	\item The candidates meeting the qualifications of the office that were nominated for, will be notified of their nomination.
-Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-A list of all nominees who have accepted their nominations will be posted shortly thereafter.
-	\item Each candidate will be given an equal amount of time before the Executive Board to present their platforms of candidacy.
-This Executive Board Meeting is open only to the Executive Board Members and House members with explicit invitation from the Executive Board.
-	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.
-After each candidate for an office has been presented and discussed, a simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine the selection of candidates.
-	\item All winners are notified and asked to accept or decline their selection.
-Any office whose winner declines the selection shall remain vacant and a new selection process shall begin for that office.
 \end{enumerate}
@@
 \end{enumerate}
+\asubsection{Selection of the House Secretary}
+The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary.
+The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.
 
@@
 A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
+	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of the Executive Board.
 \end{enumerate}
@@
 Decisions made by the Executive Board may be appealed and overturned.
-To initiate an appeal, a Petition of Appeal must be presented to the Chairman affixed with signatures from one third of Active Members of house, or three voting members of Executive Board.
-After the petition has been presented, during the following House meeting, a discussion will be held where one petitioner and one Executive Board member will each make their case.
-After hearing from both representatives, there will be an Immediate Two-Thirds vote as defined in \ref{Two-Thirds} to confirm the appeal and thereby overturn the decision.
-Any decision that is overturned must be reevaluated by the Executive Board.
-
-Decisions made by the Executive Board may be appealed and overturned.
-To initiate an appeal, a Petition of Appeal must be presented to the Chairman affixed with signatures either one third of Active Members or three voting members of the Executive Board.
-After the petition is presented, the decision is overturned and will be reevaluated by the Executive Board at the upcoming Executive Board meeting.
+To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
+After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
+If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
 

### 2014-05-16 bylaws.tex
and the rest

@@
 \bsection{Amount of House Dues}
-The amount of dues for Active Members living on floor will be fifty-five dollars (\$55.00) per Academic Semester.
-The amount of dues for Active Members living off floor twill be fifty dollars (\$50.00) per Academic Semester.
+The amount of dues for Active Members living on floor will be eighty dollars (\$80.00) per Academic Semester.
+The amount of dues for Active Members living off floor will be seventy-five dollars (\$75.00) per Academic Semester.
 \bsection{Collection of House Dues}
@@
 
-The suggested total operational budget is \$5544.
-This figure is based on yearly estimated on-floor member dues (\$110 x 56 members = \$6160) minus the 10\% reserved for Accumulated (Accum).
-Money allocated for Accum and off-floor member dues are deposited into the CSH Account and saved.
+The suggested total operational budget is \$8064.
+This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
 
@@
 \\* \\*
-If a member fails and has never passed an Membership Evaluation in the past, his membership will be revoked at the end of the year.
-If the member has previously passed an Membership Evaluation he will move to Alumni Membership status.
+If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
 In either case, the member forfeits his ability to be included on the following year’s roster.
@@
 If a member disagrees with the outcome of any evaluation, (e.g.
-is not asked to return to the House for the following year) and wishes to appeal the decision, he or she should immediately contact the Evaluations Director or the Chairman.
-At the following Executive Board meeting, the member will present his appeal to the Board.
-The Executive Board can uphold, overturn or conditionally overturn the Evaluation decision with a Simple Majority Vote as described in \ref{Simple Majority}.
+is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
 \\* \\*
-If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the Area Coordinator
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
 

### 2015-04-18 articles.tex
Make slight correction wrt requirements for membership

@@
 %\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
-\externaldocument{bylaws}[https://github.com/bencentra/Constitution/blob/master/bylaws.pdf?raw=true]
+\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
 
@@
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
+Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation, as well as any and all persons named William Orr.
 \asubsection{Active Membership Selection}

### 2015-09-18 bylaws.tex
fixed refs to point to ComputerScienceHouse repo, not mine

@@
 %\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]
-\externaldocument{constitution}[https://github.com/bencentra/Constitution/blob/master/articles.pdf?raw=true]
+\externaldocument{articles}[https://github.com/ComputerScienceHouse/Constitution/blob/master/articles.pdf?raw=true]
 
@@
 If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
-It is required that, for expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A quorum of one-half the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+\\*\\*
+For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
 This proposal includes the project budget, inventory of required resources, and a timeline for completion.
-It is also recommended that all expenditure approvals done at House meeting, regardless of amount, provide such a proposal.
 \\* \\*
 If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
-Miscellaneous purchases are deducted directly from the CSH Account, and therefore must have final approval of the Financial Director.
+This amount is to be directly subtracted from the general CSH account.
 \\* \\*

### 2015-10-10 articles.tex
Non-semantic grammatical fixes.

--- 2014-05-16 articles.tex
@@
 The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
-There must be a There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
+There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
 A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
@@
 \begin{enumerate}
-	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
+	\item To hold a weekly meeting, specific to their responsibilities, and submit notes to the House.
 	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
+	\item To publish a document at the end of each semester to all Members stating House'۪s accomplishments of that semester.
 	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
@@
 The office will become vacant and the selection process for a new member will begin at that time.
-The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman'۪s discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.

### 2015-10-11 articles.tex
Reverted second change.

@@
 \begin{enumerate}
-	\item To hold a weekly meeting, specific to their responsibilities, and submit notes to the House.
+	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
 	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To publish a document at the end of each semester to all Members stating House'۪s accomplishments of that semester.
+	\item To publish a document at the end of each semester to all Members stating House's accomplishments of that semester.
 	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
@@
 The office will become vacant and the selection process for a new member will begin at that time.
-The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman'۪s discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.

### 2015-10-11 articles.tex
Non-semantic grammatical fixes.

@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To publish a document at the end of each semester to all Members stating House's accomplishments of that semester.
+	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
 	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
@@
 The office will become vacant and the selection process for a new member will begin at that time.
-The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.

### 2015-12-11 articles.tex
non-semantic change
Add On-Floor Eboard Qualifications
Separated the qualifiations of Chairman and the Evaluations Director From the
qualifications of the Social Director(s), Financial Director, Research and
Development Director(s), House Improvements Director, House History Director.

The Chairman and Evaluations Director now have the additional responsibility to
reside On-Floor during the term of office.

@@
 The ballots are collected for a minimum of a forty-eight hour period.
-A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
+A quorum of two-thirds
+of the Total Number of Possible Votes must cast ballots for the vote to be official.
 A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
@@
 An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
-Instead of forfeiting membership, Active members who resign may elect to become Alumnias defined in \ref{Alumni Membership Selection}.
+Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
@@
 \asubsection{Alumni Membership Evaluations}
-Alumni Members are not subject any evaluation.
+Alumni Members are not subject to any evaluation.
 \asubsection{Alumni Membership Resignations}
@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
+\asubsection{Qualifications to be the Chairman, Evaluations Director}
+\begin{enumerate}
+	\item Candidates must be Active Members during the term of office.
+	\item Candidates must reside on floor during the term of office.
+	\item Candidates must have at least one full semester of House membership as an Active Member.
+	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
+\end{enumerate}
+\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
 \begin{enumerate}

### 2015-12-17 articles.tex
Added Alternatve Vote to voting options.

--- 2015-10-11 articles.tex
@@
 \asection{Types of Voting}
+\asubsection{Alternative Vote}
+\asubsubsection{Method of Vote}
+Each voter has one vote, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.
+
+Candidates are elected outright if they gain more than half the votes as first preferences.
+If not, the candidate who lost (the one with least first preferences) is eliminated and their votes move to the second preference marked on the ballot papers.
+This process continues until one candidate has half of the votes and is elected.
+\asubsubsection{Voting Period} 
+For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
+For any other type of vote, the voting period must be at least twenty-four (24) hours.
+The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
 \asubsection{Balloted Vote}

### 2015-12-17 articles.tex
Update articles.tex

@@
 In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Balloted Vote}.
-	\item The winners are determined by a simple majority vote of the ballots cast as defined in 5.C.1, Voting.
+	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
+	\item The winners are determined via the process described in \ref{Alternative Vote}.
 A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
@@
 \asubsubsection{Method of Vote}
-Each voter has one vote, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.
+Each voter has one vote, given to them in the form of a paper ballot, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.
 

### 2016-01-25 articles.tex
More final changes
Matt Gambogi helped make the text more consistent.

@@
 If not, the winner will assume office at the end of the current term (\ref{Term}).
-Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.
+Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
 \end{enumerate}
@@
 \asubsubsection{Method of Vote}
-Each voter has one vote, given to them in the form of a paper ballot, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.
+Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
+A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
+At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period.
+The Vote Counters then tally the results.
 
-Candidates are elected outright if they gain more than half the votes as first preferences.
-If not, the candidate who lost (the one with least first preferences) is eliminated and their votes move to the second preference marked on the ballot papers.
-This process continues until one candidate has half of the votes and is elected.
+Voters rank the options by placing a '1' by their first choice, a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of options.
+
 \asubsubsection{Voting Period} 
@@
 
+\asubsection{Alternative}
+The winning option is selected outright if it gains more than half the votes as a first preference.
+If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
+This process continues until one option has half of the votes and is elected.
+
 \asection{Ties Between Vote Options}

### 2016-01-25 articles.tex
Fixing blatant grammatical typo
Fixes typo noticed by @jeid64 in #13

--- 2015-12-17 articles.tex
@@
 \asection{Types of Voting}
-\asubsection{Alternative Vote}
-\asubsubsection{Method of Vote}
-Each voter has one vote, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.
-
-Candidates are elected outright if they gain more than half the votes as first preferences.
-If not, the candidate who lost (the one with least first preferences) is eliminated and their votes move to the second preference marked on the ballot papers.
-This process continues until one candidate has half of the votes and is elected.
-\asubsubsection{Voting Period} 
-For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
-For any other type of vote, the voting period must be at least twenty-four (24) hours.
-The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
 \asubsection{Balloted Vote}

### 2016-01-26 articles.tex
typo

--- 2016-01-25 articles.tex
@@
 
+\asection{Maintainers}
+
+\asubsection{Maintainer Qualifications}
+Maintainers must have Active or Alumni in good standing status.
+
+\asubsection{Maintainer Expectations}
+Maintainers are expected to:
+\begin{itemize}
+    \item Review changes to the Constitution for grammar, spelling, and internal consistency.
+    \item Participate in discussion of proposals.
+    \item Facilitate the creation of new changes to the Constitution by other members.
+    \item Be knowledgeable about the Constitution. 
+\end{itemize}
+Failure to adequately meet any of these expectations is grounds for revocation of maintainer status.
+
+\asubsection{Maintainer Resignations}
+Maintainers may resign at any time by notifying the current eboard and maintainer group.
+
+\asubsection{Maintainer Term}
+Maintainer status lasts until it is resigned, or revoked by Executive Board vote.
+
+\asubsection{Maintainer Selection}
+Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Exective Board may choose to approve or reject the nomination by Simple Majority vote.
+
 % ARTICLE III - MEMBERSHIP

### 2016-02-02 bylaws.tex

@@
 At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
-A quorum of one-half the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
 \\*\\*

### 2016-02-15 articles.tex
1 sentence = 1 line
Current diffs can be difficult to read because every paragraph inhabits
a single line. Giving each statement a line should make it easier to
track changes in the statement

@@
 
-\asubsection{ Non-Semantic Changes}
-Any non-semantic change to the Constitution should be presented to the House for discussion.
-After the discussion an immediate House vote is taken.A quorum of fifty percent of the Total Number of Possible Votes must be present in order for the vote to be official.
-A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.
+\asubsection{Non-Semantic Changes}
+There are two methods for non-semantic change to the Constitution.
+A Maintainer may approve any proposed change that does not affect the meaning of the document.
+Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
+A quorum of fifty percent of the Total Number of Possible Votes is required for passage.
 
@@
 The ballots are collected for a minimum of a forty-eight hour period.
-A quorum of two-thirds
-of the Total Number of Possible Votes must cast ballots for the vote to be official.
+A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
 A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
@@
 \asubsection{Maintainer Qualifications}
-Maintainers must have Active or Alumni in good standing status.
+Maintainers must be Active or Alumni in good standing.
 
@@
     \item Review changes to the Constitution for grammar, spelling, and internal consistency.
+    \item Keep a public record of changes to the Constitution.
     \item Participate in discussion of proposals.
@@
 \end{itemize}
-Failure to adequately meet any of these expectations is grounds for revocation of maintainer status.
+Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.
 
 \asubsection{Maintainer Resignations}
-Maintainers may resign at any time by notifying the current eboard and maintainer group.
+Maintainers may resign at any time by notifying the current Executive Board and Maintainer group.
 
 \asubsection{Maintainer Term}
-Maintainer status lasts until it is resigned, or revoked by Executive Board vote.
+Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
+If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
 
@@
 \end{itemize}
-Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum. Exceptions may be made at the discretion of the Evaluations Director.
+Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
+Exceptions may be made at the discretion of the Evaluations Director.
 \asubsection{Active Membership Evaluations}
@@
 \asubsection{Honorary Membership Resignations}
-An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
+An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman.
+The resignation will be read at the following House Meeting and become effective at that time.
 \asubsection{Honorary Membership Term}
@@
 \asubsection{Advisory Membership Selection}
-The Executive Board may open nominations for Advisory Members. The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
+The Executive Board may open nominations for Advisory Members.
+The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
 \asubsection{Advisory Membership Expectations}
@@
 \asubsection{Advisory Membership Resignations}
-An Advisor may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
+An Advisor may resign by submitting in writing the reason for resignation to the Chairman.
+The resignation will be read at the following House Meeting and become effective at that time.
 \asubsection{Advisory Membership Term}
@@
 \item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
-\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves. When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
+\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
+	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
 \end{enumerate}
@@
 \asection{Judicial Ruling}
-The Judicial Board may present an official ruling following the Judicial Investigation. This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
+The Judicial Board may present an official ruling following the Judicial Investigation.
+This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
 

### 2016-02-15 articles.tex

--- 2016-01-26 articles.tex
@@
 A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
-
-\asection{Maintainers}
-
-\asubsection{Maintainer Qualifications}
-Maintainers must have Active or Alumni in good standing status.
-
-\asubsection{Maintainer Expectations}
-Maintainers are expected to:
-\begin{itemize}
-    \item Review changes to the Constitution for grammar, spelling, and internal consistency.
-    \item Participate in discussion of proposals.
-    \item Facilitate the creation of new changes to the Constitution by other members.
-    \item Be knowledgeable about the Constitution. 
-\end{itemize}
-Failure to adequately meet any of these expectations is grounds for revocation of maintainer status.
-
-\asubsection{Maintainer Resignations}
-Maintainers may resign at any time by notifying the current eboard and maintainer group.
-
-\asubsection{Maintainer Term}
-Maintainer status lasts until it is resigned, or revoked by Executive Board vote.
-
-\asubsection{Maintainer Selection}
-Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Exective Board may choose to approve or reject the nomination by Simple Majority vote.
 
@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairman, Evaluations Director}
-\begin{enumerate}
-	\item Candidates must be Active Members during the term of office.
-	\item Candidates must reside on floor during the term of office.
-	\item Candidates must have at least one full semester of House membership as an Active Member.
-	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
-\end{enumerate}
-\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
+\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
 \begin{enumerate}

### 2016-02-26 bylaws.tex
Added House Meeting in ByLaws
Located in section 2.B in ByLaws

@@
 Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.
+\bsection{House Meeting}
+House Meetings occur weekly throughout the Standard Operating Session, all of which are chaired by the Chairman or an Active member chosen  by the Chairman.
+Throughout proceedings of a House Meeting each Executive Board member will make announcements and updates to inform members of house.
 

### 2016-02-27 bylaws.tex

--- 2016-02-02 bylaws.tex
@@
 \bylaw{Introduction}
-By-Laws will expand upon, while not redefining, Articles laid out in the Constitution. By-Laws provide additional depth and definition to the processes and operations of House.
+By-Laws will expand upon, while not redefining, Articles laid out in the Constitution.
+By-Laws provide additional depth and definition to the processes and operations of House.
 
@@
 Attendance is also required for a member to be evaluated, else they will receive no housing points.
-Any member unable to attend because of outstanding circumstances (e.g.
-away on co-op) may also submit an activity report and be voted on, though they may not vote.
+Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote.
 Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.
@@
 \\* \\*
-A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.
+A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither Absentee nor Proxy votes are allowed.
 \\* \\*
@@
 A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year.
-All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.These requirements are detailed in Article V under expectations for each category of membership.
+All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.
+These requirements are detailed in Article V under expectations for each category of membership.
 These requirements must be completed before the Membership Evaluation occurs.
@@
 \bsubsection{Off-Floor Status}
-Members with Off-Floor status do not have the right to live on the floor. They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
+Members with Off-Floor status do not have the right to live on the floor.
+They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
 

### 2016-02-29 bylaws.tex
Added Files via upload, 'board' Change
Changed all instances of 'Executive board' to 'Executive Board.'

@@
 If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
-If the Executive board disagrees with the Financial Director, the Executive board may grant an extension.
+If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
 If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
@@
 	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
-	\item A description of each Executive board position, including:
+	\item A description of each Executive Board position, including:
 	\begin{itemize}

### 2016-04-03 bylaws.tex
Change Executive Board Vote For RTPs
Change the RTP Approval discussion to only require the number of executive board
members required for a closed executive board meeting.

@@
 This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.
+	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
 		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2016-04-04 articles.tex
Added files via upload

--- 2016-02-15 articles.tex
@@
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal is presented the following week at the end of House Meeting.
+The discussion for the change is not required, but only members who stay until the end of discussion will receive ballots.
+At the end of discussion, ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.

### 2016-04-11 bylaws.tex
Update bylaws.tex

--- 2016-02-29 bylaws.tex
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2016-04-11 bylaws.tex
Remove Housing Evaluations
Members will now receive two Housing Points upon receiving a Passing status for
Membership Evaluations

--- 2016-02-29 bylaws.tex
@@
 \bsection{Evaluations Processes}
-During the academic year, a House member is evaluated by two different processes.
-The first process, known as the Housing Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House.
-The second process, known as the Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-These processes are separate from each other and should not interfere with one another.
+During the academic year, a House member is evaluated by the Membership Evaluation process.
+Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
 Semi-Annual Evaluations Meetings are open only to all current Active Members.
@@
 It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.
-\bsubsection{Housing Evaluation}
-The Housing Evaluation process occurs during the academic year.
-It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director.
-The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).
-\\* \\*
-All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant.
-A member’s failure to submit the activity report will result in that member receiving no housing points.
-Attendance is also required for a member to be evaluated, else they will receive no housing points.
-Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote.
-Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.
-\\* \\*
-The participating members, on a member by member basis, review the activity report provided by each member.
-The participating members may then choose to award one, two, or three housing points to each member.
-Points are awarded on the basis of contributions to House.
-Above average members receive three points, average members two points, and below average members one point.
-\\* \\*
-A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-Neither Absentee nor Proxy votes are allowed.
-\\* \\*
-All votes during the Housing Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in \ref{Three Tiered}.
 \bsubsection{Membership Evaluation}
@@
 Members who receive a pass have the option participate as an Active Member in the following the year and remain on the upcoming roster if applicable.
+Members who receive a pass will gain two Housing Points.
 \\* \\*
@@
 The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+Housing points are accumulated during the Membership Evaluation \ref{Membership Evaluation}.
 \\* \\*

### 2016-04-11 bylaws.tex

--- 2016-04-11 bylaws.tex
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2016-04-11 bylaws.tex
Selection of Advisory Members
Proposed amendment for 4.B.4 - Selection of Advisory Members.

@@
 	\item A discussion of the candidates will be held at the following House meeting.
-	\item Ballots will then be distributed for a secret ballot, fifty-percent House vote, as defined in \ref{Fifty Percent}.
-		If more than two advisors are selected via this process, the Executive Board may call for a revote amongst the candidates selected in order to reduce the number of advisors to a workable level.
-		If this decision is made, the candidates selected in the first ballot become the nominees for the second ballot and Step Three and Four are repeated.
-		This recast process may not be repeated a second time.
+    \item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty     
+        Percent}. Voting must remain open for a minimum of a forty-eight hour period. 
 	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
-		If one or more selected candidates decline the position, the Executive Board may begin a selection process for additional advisors.
-		Note that selected candidates who accept their selection remain selected, this additional selection process is only a means to bring the number of advisors up to a workable level.
-		If the additional advisor selection process is initiated, repeat Steps One through Five with the original nominations plus any additional nominations.
 \end{enumerate}

### 2016-04-13 articles.tex
Added files via upload

@@
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week at the end of House Meeting.
-The discussion for the change is not required, but only members who stay until the end of discussion will receive ballots.
-At the end of discussion, ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 \asection{Selection}
-\asubsection{Dual Directorship}
-Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
-If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
-If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative.
-Each different nomination must be a separate entry on the election ballot. 
-Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to single or dual directorship.
-
-The following special cases cover the operation of a dual directorship:
-\begin{itemize}
-	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
-		The vacated office is then handled like any other vacated office; see \ref{Resignations}.
-	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
-		The members of the dual directorship need not vote the same way in a vote.
-	\item A member of a dual directorship may not hold any other Executive Board position.
-	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.
-\end{itemize}
 \asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
@@
 	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
+		Any House member may nominate any eligible member for a Directorship.
 	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.

### 2016-04-17 articles.tex
Added confidentiality and safe environment to eboard responsibilities

--- 2016-04-04 articles.tex
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
+	\item To proactively maintain a safe and welcoming enviornment to House members.
+	\item To respect the privacy of House members who confide in confidence barring circumstances that allude endangerment of ones self or others.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-18 articles.tex
Removed safe environment text and updated confidentiality

@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To proactively maintain a safe and welcoming enviornment to House members.
-	\item To respect the privacy of House members who confide in confidence barring circumstances that allude endangerment of ones self or others.
+	\item To respect the privacy of House members who confide in confidence barring circumstances that allude endangerment of ones self or others or in the case of a Judicial Board.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-19 articles.tex
Added Leave of Absence section

@@
 	\item[Evaluations:] The process by which a member is reviewed and assessed.
+	\item[Leave of Absence:] The process by which a member may leave House for a period of time.
 	\item[Resignations:] The process by which a member terminates House membership.
@@
 \asubsection{Introductory Membership Expectations}
-Introductory members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
+Introductory Members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
 \asubsection{Introductory Membership Privileges}
-Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
+Introductory Members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
 \asubsection{Introductory Membership Evaluations}
-Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
+Introductory Members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
+\asubsection{Introductory Membership Leave of Absence}
+After completion of the Introductory Packet, an Introductory Member may request a leave of absence through the process described in \ref{Leave of Absence}.
+Their Evaluation Period will not continue for the duration of their absence, and will resume where they left off when they return.
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
+Introductory Members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
-Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
+Introductory Membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
 
@@
 \asubsection{Active Membership Expectations}
-Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
+Active Members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
 \asubsection{Active Membership Privileges}
@@
 Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+\asubsection{Active Membership Leave of Absence}
+An Active Member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
+\begin{itemize}
+	\item Forfeit their right to vote
+	\item Do not count towards quorum
+	\item Will not be required to attend House Meeting
+\end{itemize}
 \asubsection{Active Membership Resignations}
-An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
+An Active Member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
@@
 \asubsection{Alumni Membership Selection}
-Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
+Active Members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
 \\*\\*
-Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing.
+Active Members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing.
 This may be appealed to the Executive Board in order to pursue a different outcome.
@@
 Advisory Membership shall last until the member resigns.
+\asection{Leave of Absence}
+A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+Computer Science House recognizes the need for it's members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
+Upon approval of a leave of absence request, the Evaluations Director is notified and the members' leave begins immediately.
+A member is allowed to be physically present and also be on a leave of absence.
+The leave of absence can also be applied retroactively to the member at the discretion of the Evaluations Director.
+\asubsection{Leave of Absence Request}
+A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
+The request is then given to a staff member of Residence Life, excluding student employees, for approval.
+\asubsection{Leave of Absence Duration}
+A leave of absence can be granted for up to the length of one semester.
+\asubsection{Leave of Absence Extension}
+A leave of absence can be extended by submitting a new request.
+\asubsection{Leave of Absence Return}
+A member may return from a leave of absence whenever they choose to.
+\asubsection{Leave of Absence for an Executive Board Member}
+The duties and responsibilities of an Executive Board Member on leave are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the member returns from their leave.
 
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To respect the privacy of House members who confide in confidence barring circumstances that allude endangerment of ones self or others or in the case of a Judicial Board.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-19 articles.tex
Minor grammar changes and edited LOA return process

@@
 A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
-Computer Science House recognizes the need for it's members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
-Upon approval of a leave of absence request, the Evaluations Director is notified and the members' leave begins immediately.
+Computer Science House recognizes the need for its members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
+Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave begins immediately.
 A member is allowed to be physically present and also be on a leave of absence.
@@
 \asubsection{Leave of Absence Return}
-A member may return from a leave of absence whenever they choose to.
+A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writting notify the Evaluations Director to end their leave.
 \asubsection{Leave of Absence for an Executive Board Member}

### 2016-04-19 articles.tex
Updated confidentiality text to read better

--- 2016-04-18 articles.tex
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To respect the privacy of House members who confide in confidence barring circumstances that allude endangerment of ones self or others or in the case of a Judicial Board.
+	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others or in the case of a Judicial Board.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-19 articles.tex
preserve the line ending at EOF
Spelling fixes and adds clarity to confidentiality of the leave

--- 2016-04-19 articles.tex
@@
 \begin{itemize}
-	\item Forfeit their right to vote
-	\item Do not count towards quorum
+	\item Forfeits their right to vote
+	\item Does not count towards quorum
 	\item Will not be required to attend House Meeting
@@
 Advisory Membership shall last until the member resigns.
+
 \asection{Leave of Absence}
@@
 The request is then given to a staff member of Residence Life, excluding student employees, for approval.
+At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
 \asubsection{Leave of Absence Duration}
@@
 \asubsection{Leave of Absence Return}
-A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writting notify the Evaluations Director to end their leave.
+A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writing notify the Evaluations Director to end their leave.
 \asubsection{Leave of Absence for an Executive Board Member}

### 2016-04-20 articles.tex
Changed articles.tex based on House's suggestions
Redefined the process for semantic changes to be: 

+Any semantic change to the Constitution requires the change to be brought up at House Meeting and proposed in writing for discussion at the following House Meeting.
+The text of the change may be modified up until the aforementioned House Meeting. 
+At the beginning of the discussion period, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
+Attendance for the discussion on the change is not mandatory.

--- 2016-04-19 articles.tex
@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
-Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+Any semantic change to the Constitution requires the change to be brought up at House Meeting and proposed in writing for discussion at the following House Meeting.
+The text of the change may be modified up until the aforementioned House Meeting. 
+At the beginning of the discussion period, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
+Attendance for the discussion on the change is not mandatory.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others or in the case of a Judicial Board.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-21 articles.tex
update articles.tex for clarity
This text better reflects what I intended and makes reading easier.

@@
 Any semantic change to the Constitution requires the change to be brought up at House Meeting and proposed in writing for discussion at the following House Meeting.
-The text of the change may be modified up until the aforementioned House Meeting. 
-At the beginning of the discussion period, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
+The text of the change may be modified up until the House Meeting at which it is discussed. 
+Before beginning discussion, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
 Attendance for the discussion on the change is not mandatory.

### 2016-04-24 articles.tex
Updated to include cases of sexual assault

@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be brought up at House Meeting and proposed in writing for discussion at the following House Meeting.
-The text of the change may be modified up until the House Meeting at which it is discussed. 
-Before beginning discussion, ballots are distributed for a balloted House vote as described in \ref{Balloted Vote}.
-Attendance for the discussion on the change is not mandatory.
+Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
+Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
+The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
+	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-27 articles.tex
Removes non-semantic changes

@@
 Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
+\asubsection{Introductory Membership Leave of Absence}
+After completion of the Introductory Packet, an Introductory Member may request a leave of absence through the process described in \ref{Leave of Absence}.
+Their Evaluation Period will not continue for the duration of their absence, and will resume where they left off when they return.
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
+Introductory Mmmbers may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
-Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
+Introductory Membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
 
@@
 Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+\asubsection{Active Membership Leave of Absence}
+An Active Member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
+\begin{itemize}
+	\item Forfeits their right to vote
+	\item Does not count towards quorum
+	\item Will not be required to attend House Meeting
+\end{itemize}
 \asubsection{Active Membership Resignations}
-An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
+An Active Member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
@@
 
+\asection{Leave of Absence}
+A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+Computer Science House recognizes the need for its members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
+Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave begins immediately.
+A member is allowed to be physically present and also be on a leave of absence.
+The leave of absence can also be applied retroactively to the member at the discretion of the Evaluations Director.
+\asubsection{Leave of Absence Request}
+A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
+The request is then given to a staff member of Residence Life, excluding student employees, for approval.
+At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
+\asubsection{Leave of Absence Duration}
+A leave of absence can be granted for up to the length of one semester.
+\asubsection{Leave of Absence Extension}
+A leave of absence can be extended by submitting a new request.
+\asubsection{Leave of Absence Return}
+A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writing notify the Evaluations Director to end their leave.
+\asubsection{Leave of Absence for an Executive Board Member}
+The duties and responsibilities of an Executive Board Member on leave are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the member returns from their leave.
+
 % ARTICLE IV - EXECUTIVE BOARD
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board.
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.

### 2016-04-27 articles.tex
Missed a few semantic changes

@@
 \asubsection{Introductory Membership Resignations}
-Introductory Mmmbers may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
+Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
-Introductory Membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
+Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
 
@@
 \asubsection{Active Membership Resignations}
-An Active Member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
+An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.

### 2016-04-27 articles.tex
Added section for Appointment of an Interim Director
Creates new section for Appointment of an Interim Director which is then referenced in resignation as well as LOA of Eboard member

@@
 \asubsection{Introductory Membership Leave of Absence}
-After completion of the Introductory Packet, an Introductory Member may request a leave of absence through the process described in \ref{Leave of Absence}.
+After completion of the Introductory Packet, an Introductory member may request a leave of absence through the process described in \ref{Leave of Absence}.
 Their Evaluation Period will not continue for the duration of their absence, and will resume where they left off when they return.
@@
 \asubsection{Active Membership Leave of Absence}
-An Active Member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
+An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
 \begin{itemize}
@@
 \asubsection{Leave of Absence Return}
-A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writing notify the Evaluations Director to end their leave.
+A member may return from a leave of absence whenever they choose to.
+When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
 \asubsection{Leave of Absence for an Executive Board Member}
-The duties and responsibilities of an Executive Board Member on leave are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the member returns from their leave.
+The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
 
@@
 The resignation will be read at the following House Meeting and become effective at that time.
-The office will become vacant and the selection process for a new member will begin at that time.
+The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
+
+\asection{Appointment of an Interim Director}
 The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.

### 2016-04-27 articles.tex
Updates Evaluation Process and Executive Board Leave
Allow extension of evaluation process and further definition of eboard responsibilities

@@
 After completion of the Introductory Packet, an Introductory member may request a leave of absence through the process described in \ref{Leave of Absence}.
-Their Evaluation Period will not continue for the duration of their absence, and will resume where they left off when they return.
 \asubsection{Introductory Membership Resignations}
@@
 A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
-Computer Science House recognizes the need for its members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
-Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave begins immediately.
-A member is allowed to be physically present and also be on a leave of absence.
-The leave of absence can also be applied retroactively to the member at the discretion of the Evaluations Director.
+Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
+Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.
+A member is also allowed to be physically present and also be on a leave of absence.
 \asubsection{Leave of Absence Request}
@@
 The request is then given to a staff member of Residence Life, excluding student employees, for approval.
+A leave of absence start date can be backdated.
 At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
@@
 When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
+\asubsection{Modified Evaluations}
+A member may request their evaluation period to be extended by the duration of the leave or to end of the standard operating session, whichever comes first.
 \asubsection{Leave of Absence for an Executive Board Member}
 The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
+Upon returning, the member may assume their position and the interim director is removed.
+If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amonst the Executive Board to require a resignation from the Member.
 

### 2016-04-29 articles.tex
2.B.2 - Semantic Changes
Proposed amendment to modify the amendment process to match the current
method used at house meeting. Targets to resolve wording conflict where
the date of discussion may be ambiguously interpreted.

--- 2016-04-27 articles.tex
@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
-Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.
+Any modifications to the written proposal must be posted in the House during the week following the proposal.
+The final proposal is presented one week following the proposal's initial introduction at House Meeting for discussion.
+Ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 	\item[Evaluations:] The process by which a member is reviewed and assessed.
-	\item[Leave of Absence:] The process by which a member may leave House for a period of time.
 	\item[Resignations:] The process by which a member terminates House membership.
@@
 Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
-\asubsection{Introductory Membership Leave of Absence}
-After completion of the Introductory Packet, an Introductory Member may request a leave of absence through the process described in \ref{Leave of Absence}.
-Their Evaluation Period will not continue for the duration of their absence, and will resume where they left off when they return.
 \asubsection{Introductory Membership Resignations}
@@
 Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
-\asubsection{Active Membership Leave of Absence}
-An Active Member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
-\begin{itemize}
-	\item Forfeits their right to vote
-	\item Does not count towards quorum
-	\item Will not be required to attend House Meeting
-\end{itemize}
 \asubsection{Active Membership Resignations}
@@
 Advisory Membership shall last until the member resigns.
-
-\asection{Leave of Absence}
-A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
-Computer Science House recognizes the need for its members to take care of their personal issues and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
-Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave begins immediately.
-A member is allowed to be physically present and also be on a leave of absence.
-The leave of absence can also be applied retroactively to the member at the discretion of the Evaluations Director.
-\asubsection{Leave of Absence Request}
-A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
-The request is then given to a staff member of Residence Life, excluding student employees, for approval.
-At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
-\asubsection{Leave of Absence Duration}
-A leave of absence can be granted for up to the length of one semester.
-\asubsection{Leave of Absence Extension}
-A leave of absence can be extended by submitting a new request.
-\asubsection{Leave of Absence Return}
-A member may return from a leave of absence whenever they choose to. When a member wishes to return, they must in writing notify the Evaluations Director to end their leave.
-\asubsection{Leave of Absence for an Executive Board Member}
-The duties and responsibilities of an Executive Board Member on leave are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the member returns from their leave.
 

### 2016-05-02 bylaws.tex
Change dues to  for everyone

--- 2016-04-11 bylaws.tex
@@
 \bsection{Amount of House Dues}
-The amount of dues for Active Members living on floor will be eighty dollars (\$80.00) per Academic Semester.
-The amount of dues for Active Members living off floor will be seventy-five dollars (\$75.00) per Academic Semester.
+The amount of dues for Active Members living on or off floor will be eighty dollars (\$80.00) per Academic Semester.
 \bsection{Collection of House Dues}

### 2016-05-23 bylaws.tex
Removing mentions of on/off floor in section.
They aren't needed since we aren't using them to differentiate anymore.
Same dues price for all, and for all a good night.

--- 2016-04-29 bylaws.tex
@@
 \bsection{Amount of House Dues}
-The amount of dues for Active Members living on floor will be eighty dollars (\$80.00) per Academic Semester.
-The amount of dues for Active Members living off floor will be seventy-five dollars (\$75.00) per Academic Semester.
+The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
 \bsection{Collection of House Dues}

### 2016-05-23 bylaws.tex
Collect dues whenever, just not after Evals

@@
 \bsection{Collection of House Dues}
-At the start of the academic year, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
-Dues for off-floor members are to be collected at the start of each semester by the Financial Director.
+The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected during this period as well by the Financial Director.
 For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
 \\*\\*
@@
 This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
+\\*\\*
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
 \bsection{Breakdown of Dues for Directorship Budgets}

### 2016-06-19 bylaws.tex
Removing Housing evals

@@
 It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.
-\bsubsection{Housing Evaluation}
-The Housing Evaluation process occurs during the academic year.
-It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director.
-The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).
-\\* \\*
-All Active members who wish to be evaluated are required to submit an activity report in which they may log projects worked on, social events and seminars hosted or attended, and any other information they deem relevant.
-A member’s failure to submit the activity report will result in that member receiving no housing points.
-Attendance is also required for a member to be evaluated, else they will receive no housing points.
-Any member unable to attend because of outstanding circumstances (e.g. away on co-op) may also submit an activity report and be voted on, though they may not vote.
-Members in this situation should contact the Evaluations Director at least one day prior to the evaluation.
-\\* \\*
-The participating members, on a member by member basis, review the activity report provided by each member.
-The participating members may then choose to award one, two, or three housing points to each member.
-Points are awarded on the basis of contributions to House.
-Above average members receive three points, average members two points, and below average members one point.
-\\* \\*
-A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-Neither Absentee nor Proxy votes are allowed.
+\bsubsection{Housing Points}
+All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
 \\* \\*

### 2016-08-02 bylaws.tex
Removing Housing evals (#66)
Removing Housing evals

@@
 \bsection{Evaluations Processes}
-During the academic year, a House member is evaluated by two different processes.
-The first process, known as the Housing Evaluation, is an informal evaluation designed to recognize an individual's contributions to the House, as well as checkpoint an individual's involvement with the House.
-The second process, known as the Membership Evaluation, is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-These processes are separate from each other and should not interfere with one another.
+During the academic year, a House member is evaluated by the Membership Evaluation.
+The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
 Semi-Annual Evaluations Meetings are open only to all current Active Members.
@@
 All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
-\\* \\*
-All votes during the Housing Evaluation Process must be Closed Ballot, Three Tiered Vote as defined in \ref{Three Tiered}.
 \bsubsection{Membership Evaluation}

### 2016-08-18 articles.tex
Add Git Revision to Date

--- 2016-04-27 articles.tex
@@
 \documentclass{article}
+\providecommand{\RevisionInfo}{}
 % The xr package allows external references
@@
 %\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
-\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
+\externaldocument{bylaws}[bylaws.pdf]
 
@@
 % Last Modified Date
-\newcommand{\datechanged}{Proposed: \today}
+\newcommand{\datechanged}{Last Updated: \RevisionInfo}
 \date{\datechanged}

### 2016-08-28 bylaws.tex
Add Git Revision to Date (#68)
Fix pronoun ambiguity loopholes

@@
 %\externaldocument{constitution}[https://github.com/ComputerScienceHouse/Constitution/blob/master/constitution.pdf?raw=true]
-\externaldocument{articles}[https://github.com/ComputerScienceHouse/Constitution/blob/master/articles.pdf?raw=true]
+\externaldocument{articles}[articles.pdf]
 
@@
 % Last Modified Date
-\newcommand{\datechanged}{Last Updated \today}
+\newcommand{\datechanged}{Last Updated: \RevisionInfo}
 \date{\datechanged}
@@
 	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
-	\item If an Introductory Member fails to meet the requirements, his membership will be revoked.
+	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
 		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
@@
 At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
-It is incumbent upon each House member to provide the Evaluation Director with whatever information he or she feels is necessary to ensure an accurate evaluation.
+It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
 \bsubsection{Housing Points}
@@
 If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
-In either case, the member forfeits his ability to be included on the following year’s roster.
+In either case, the member forfeits their ability to be included on the following year’s roster.
 \\* \\*

### 2016-08-28 articles.tex

@@
 Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
+It is the responsibility of the Evaluations Director to notify the Operational Communications Director in order to disable any accounts associated with the Introductory Member.
 \asubsection{Introductory Membership Term}
@@
 The resignation will be read at the following House Meeting and become effective at that time.
+It is the responsibility of the Evaluations Director to notify the Operational Communications Director in order to disable any accounts associated with the Honorary Member.
 \asubsection{Honorary Membership Term}

### 2016-08-28 bylaws.tex
Add clause to allow for non-intro eval repeats

@@
 	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+		It is the responsibility of the Evaluations Director to notify the Operational Communications Director in order to disable any accounts associated with the Introductory Member.
 		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
@@
 If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately.
+It is the responsibility of the Evaluations Director to notify the Operational Communications Director in order to disable any accounts associated with the member.
 If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).

### 2016-09-07 bylaws.tex
Remove freshmen signatures from Packet

--- 2016-08-28 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A signature from: all Resident Active Memebers, each Executive Board member, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
 	\item A description of each Executive Board position, including:
@@
 
+\bsection{Code of Conduct}
+The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+\\* \\*
+Members are bound to the Code of Conduct revision that they sign when initially creating their account. Members may sign a more recent revision of the Code of Conduct to update their agreement.
+\bsubsection{Changes}
+The following process is used for making changes to the Code of Conduct document.
+\begin{enumerate}
+	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
+\end{enumerate}
 \end{document}

### 2016-09-09 bylaws.tex
Add fixed percentage requirements for the different types of signatures to obtain an account

--- 2016-08-28 bylaws.tex
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Successfully complete Introductory Evaluations or obtain greater than or equal to 60\% (rounded up to the nearest whole person) of each of the following types of signatures in the Introductory Packet:
+		\begin{itemize}
+			\item All Resident Active members and Executive Board members
+			\item All Introductory members residing on floor
+			\item Fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+		\end{itemize}
 \end{enumerate}

### 2016-09-12 bylaws.tex
Add quorum

--- 2016-08-28 bylaws.tex
@@
 	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
-		It is the responsibility of the Evaluations Director to notify the Operational Communications Director in order to disable any accounts associated with the Introductory Member.
 		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
@@
 	\item The application materials are then reviewed at an Evaluations meeting and the members present vote on whether to accept the person as an introductory member.
+	\item If the applicant has passed an Introductory Evaluation in the past an optional Simple Majority vote may be held to allow the applicant to automatically pass the Introductory Evaluation.
+Any member in attendance may motion for this vote to occur.
+A quorum of one-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
 \end{enumerate}
@@
 If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately.
-It is the responsibility of the Evaluations Director to notify the Operational Communications Director in order to disable any accounts associated with the member.
 If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).

### 2016-09-12 bylaws.tex
Add Process for Changes to Code of Conduct (#69)
Defines the Code of Conduct and the process by which changes to the Code
of Conduct can be make.

--- 2016-09-07 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from: all Resident Active Memebers, each Executive Board member, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
 	\item A description of each Executive Board position, including:

### 2016-09-18 bylaws.tex
Freshmen in Packet, Changes made to Articles 5

--- 2016-09-12 bylaws.tex
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required, non-Introductory signatures in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2016-09-18 bylaws.tex
Revised Packet Composition
Made the composition of the packet more specific so freshmen that are given Active Membership after their introductory evaluation are still considered in the same Introductory Members section.

--- 2016-09-12 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A signature from: all Resident members who have passed a Membership Evaluation, each Executive Board member, all resident Introductory members/Active members who have not passed a Membership Evaluation, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
 	\item A description of each Executive Board position, including:

### 2016-09-19 bylaws.tex
Updated text

@@
 \begin{itemize}
-	\item A signature from: all Resident members who have passed a Membership Evaluation, each Executive Board member, all resident Introductory members/Active members who have not passed a Membership Evaluation, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A signature from all Resident members who have passed a Membership Evaluation, each Executive Board member, all Resident Active members who have not passed a Membership Evaluation, all Resident Introductory members, and fifteen (15) of any combination of the following:
+	\begin{itemize}
+		\item Non-Resident members who have passed a Membership Evaluation 
+		\item Alumni members (not including Non-Resident Executive Board members)
+		\item Honorary members
+		\item Advisory members
+	\end{itemize}
 	\item A description of each Executive Board position, including:

### 2016-09-26 bylaws.tex
Resolves #54

--- 2016-09-18 bylaws.tex
@@
 \\* \\*
-If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately.
-If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
 In either case, the member forfeits their ability to be included on the following year’s roster.

### 2016-09-26 bylaws.tex
Adds missing `to`

@@
 \bsubsubsection{Outcomes}
-Members who receive a pass have the option participate as an Active Member in the following the year and remain on the upcoming roster if applicable.
+Members who receive a pass have the option to participate as an Active Member in the following the year and remain on the upcoming roster if applicable.
 \\* \\*

### 2016-09-26 bylaws.tex
Removes extraneous `the`

--- 2016-09-26 bylaws.tex
@@
 \bsubsubsection{Outcomes}
-Members who receive a pass have the option participate as an Active Member in the following the year and remain on the upcoming roster if applicable.
+Members who receive a pass have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
 \\* \\*

### 2016-09-26 bylaws.tex
Fixes capitalization to conform to `Active Members` as a proper name

@@
 \bsubsubsection{Voting} 
-A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year.
+A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
 All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.

### 2016-09-26 bylaws.tex
Removes extraneous `all`
Resolves clash between simple and non-simple tense

@@
 The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-Semi-Annual Evaluations Meetings are open only to all current Active Members.
+Semi-Annual Evaluations Meetings are open only to current Active Members.
 All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
@@
 A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
-All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.
+All Active Members will be held to the requirements and evaluated unless they have received an exemption from the Executive Board prior to the event.
 These requirements are detailed in Article V under expectations for each category of membership.

### 2016-09-26 bylaws.tex
Resolving grammar problems in Evaluations Processes (#80)
* Resolves #54

* Adds missing `to`

* Removes extraneous `the`

* Fixes capitalization to conform to `Active Members` as a proper name

* Removes extraneous `all`

* Resolves clash between simple and non-simple tense

* Removes awkward reference to `pass reception`

@@
 \bsubsubsection{Outcomes}
-Members who receive a pass have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
 \\* \\*

### 2016-10-02 bylaws.tex
Revised Packet Text
Made packet text more descriptive

--- 2016-09-26 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
+	\begin{itemize}
+		\item Non-Resident members who have passed a Membership Evaluation 
+		\item Alumni members (not including Non-Resident Executive Board members)
+		\item Honorary members
+		\item Advisory members
+	\end{itemize}
 	\item A description of each Executive Board position, including:
@@
 \bsubsubsection{Voting} 
-A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
+A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year.
 All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.
@@
 \bsubsubsection{Outcomes}
-Members who receive a pass have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+Members who receive a pass have the option participate as an Active Member in the following the year and remain on the upcoming roster if applicable.
 \\* \\*
-If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
-If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+If a member fails and has never passed an Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed an Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
 In either case, the member forfeits their ability to be included on the following year’s roster.
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required, non-Introductory signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2016-10-05 bylaws.tex
updated typos
line 7: officialized -> finalized
line 279: made run on sentence into 2 separate sentences to remove comma splice
updated typos (#82)
* updated typos

line 7: officialized -> finalized
line 279: made run on sentence into 2 separate sentences to remove comma splice

* changed "it" to "the conditional"

line 279 clarified language.

--- 2016-09-26 bylaws.tex
@@
 %  then printed, signed, notarized, and placed in the House filing cabinet
-%  if changes are to be officialized.
+%  if changes are to be finalized.
 
@@
 A member may be given a conditional to complete as a means of making up for missing requirements.
-A conditional may be proposed by any member present at the Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+A conditional may be proposed by any member present at the Evaluation. If the conditional is approved by the Evaluations Director, it is then voted on by House.
 Each conditional consists of a set of additional requirements a deadline for completing them.

### 2016-10-12 bylaws.tex

@@
 \begin{itemize}
-	\item A signature from: all Resident members, each Executive Board member, all Introductory members who reside on Floor, and fifteen (15) Non-Resident and/or Alumni members (not including Non-Resident Executive Board members)
+	\item A signature from all Resident members who have passed a Membership Evaluation, each Executive Board member, all Resident Active members who have not passed a Membership Evaluation, all Resident Introductory members, and fifteen (15) of any combination of the following:
+	\begin{itemize}
+		\item Non-Resident members who have passed a Membership Evaluation 
+		\item Alumni members (not including Non-Resident Executive Board members)
+		\item Honorary members
+		\item Advisory members
+	\end{itemize}
 	\item A description of each Executive Board position, including:

### 2016-10-23 articles.tex
Change to qualifications of OpComm Director
The qualifications of the OpComm Director are now consistent with the rest of the Executive Board's.
Fixed Issues with Chairman
Chairman is now a non-voting position, but still is the tie breaker. Secretary is now a non-voting member of eboard.

--- 2016-08-18 articles.tex
@@
 \asection{Members of the Executive Board}
-\asubsection{Chairman}
 \asubsection{Voting Members}
@@
 	\item Ad Hoc Directors
-\asubsection{House Secretary}
+        \item House Secretary
+        \item Chairman
 \end{itemize}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member.
-	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
+	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected.
 \end{enumerate}
@@
 	\item Candidates must be a current Active Member.
-	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
+	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
 \end{enumerate}

### 2016-10-30 bylaws.tex
Change Packet Failure Effects
Failure to Get an Account After Packet is Failure to Complete Introductory Evaluations

--- 2016-10-12 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from all Resident members who have passed a Membership Evaluation, each Executive Board member, all Resident Active members who have not passed a Membership Evaluation, all Resident Introductory members, and fifteen (15) of any combination of the following:
+	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
 	\begin{itemize}
@@
 \end{itemize}
+After the second week of the Introductory Packet, Introductory Members who have received less than 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) will have their membership revoked.
 \bsubsection{Expectations of an Introductory Member}
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required, non-Introductory signatures in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet.
 \end{enumerate}

### 2016-11-07 bylaws.tex
New Packet
Freshmen get to try packet again before the end of their evaluation period.

@@
 	\item A list of seven (7) major House technical achievements
-\end{itemize}
-After the second week of the Introductory Packet, Introductory Members who have received less than 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) will have their membership revoked.
+\end{itemize} \\
+At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet.
+The results of this Introductory Packet may only affect the number of signatures evaluated at the Introductory Evaluation.
 \bsubsection{Expectations of an Introductory Member}
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2016-11-07 bylaws.tex
Amendment Proposal to requirements to get account
Amendment Proposal: If an introductory member fails to meet the requirement to get an account after they have completed the two week packet period, the introductory member may have the Evals Director bring up a vote at one preceding house member to give the introductory member an account. This vote may happen once during the introductory member's 10 week evaluation process. The vote is a simple majority barring meeting Quorum

--- 2016-10-19 bylaws.tex
@@
 \end{enumerate}
-
+\item Amendment Proposal: If an introductory member fails to meet the requirement of reaching 60\% to get an account after they have completed the two week packet period, the introsuctory member may have the Evals Director bring up a vote at one following house member to give the introductory member an account.
+This vote may happen once during the introductory member's 10 week evaluation process.
+The vote is a simple majority vote barring having enough member to meet Quorum
 \bsection{Code of Conduct}

### 2016-11-07 bylaws.tex
Spelling, structure, syntax, nonsemantic changes
There were a lot of changes to the original submission so here's a summary:

Generally, I attempted to write the intended proposal in the style of the document.
Split up the sentences a bit more to separate out different parts of the new process.
Referred to the percentage requirement less explicitly, to minimize the risk of future contradiction creation.
Switched simple majority to 50% pass because there should only be two vote options (yes/no).

@@
 	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
+	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
+	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
+	This may occur only once per Introductory Evaluation Process.
 \end{enumerate}
-\item Amendment Proposal: If an introductory member fails to meet the requirement of reaching 60\% to get an account after they have completed the two week packet period, the introsuctory member may have the Evals Director bring up a vote at one following house member to give the introductory member an account.
-This vote may happen once during the introductory member's 10 week evaluation process.
-The vote is a simple majority vote barring having enough member to meet Quorum
+
 \bsection{Code of Conduct}

### 2016-11-07 bylaws.tex
Added Simple Majority specification to Evals votes
Fixes #27

@@
 	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
-	\item The application materials are then reviewed at an Evaluations meeting and the members present vote on whether to accept the person as an introductory member.
+	\item The application materials are then reviewed at an Evaluations meeting. 
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an introductory member.
 \end{enumerate}
@@
 	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
-	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
-	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
-	This may occur only once per Introductory Evaluation Process.
 \end{enumerate}

### 2016-11-07 bylaws.tex
Add files via upload
Changed 50% to 60%

--- 2016-11-07 bylaws.tex
@@
 	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
+\end{enumerate}
+\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 60\% majority vote at a House Meeting.
  	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
  	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
-	This may occur only once per Introductory Evaluation Process.
-\end{enumerate}
-
-\bsection{Code of Conduct}
+ 	This may occur only once per Introductory Evaluation Process.\bsection{Code of Conduct}
 The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.

### 2016-11-07 bylaws.tex
Fixed random heading deletion and bad \item loc

--- 2016-11-07 bylaws.tex
@@
 	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
+	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 60\% majority vote at a House Meeting.
  	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
  	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
-	This may occur only once per Introductory Evaluation Process.
+ 	This may occur only once per Introductory Evaluation Process.\bsection{Code of Conduct}
 \end{enumerate}

### 2016-11-10 articles.tex
Small Aesthetic Changes
i) Chairman, Secretary, Ad Hoc Director is now the order of non-Voting
Executive Board members.
ii) added (s) to Research and Development since there can be two
directors for the position.
Appeal of an Executive Board decision
Members can take a petition to house meeting and can have a vote there to appeal an executive board decision.

@@
 	\item Financial Director
-	\item Research and Development Director
+	\item Research and Development Director(s)
 	\item House Improvements Director
@@
 \begin{itemize}
-	\item Ad Hoc Directors
+	\item Chairman 
         \item House Secretary
-        \item Chairman
+        \item Ad Hoc Director
 \end{itemize}
@@
 \asection{Appeals}
+\asubsection{Executive Board Appeal}
 Decisions made by the Executive Board may be appealed and overturned.
@@
 If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
+\asubsection{House Appeal} 
+To initiate an appeal to House of an Executive Board decision, a petition with the signatures of two-thirds of Active Members must be brought to a House Meeting.
+After the appeal is presented and discussed, a Two-Thirds vote is held by the attending members.
+If the vote passes, attending members may discuss and make a new ruling by a Two-Thirds vote.
 

### 2016-11-10 bylaws.tex
Fixed the text.
Meanings clarified, made process easier and more layed out.

--- 2016-11-07 bylaws.tex
@@
 \end{itemize}
+At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director.
+The results of the new Introductory Packet may only affect the number of signatures evaluated at the Introductory Evaluation and, as long as the Introductory Member receives the appropriate number of packet signatures that would normally be required in the \ref{Creation of Accounts} process.
 \bsubsection{Expectations of an Introductory Member}
@@
 	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
-	\item The application materials are then reviewed at an Evaluations meeting. 
-	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an introductory member.
+	\item The application materials are then reviewed at an Evaluations meeting and the members present vote on whether to accept the person as an introductory member.
 \end{enumerate}

### 2016-11-10 bylaws.tex
Oops. Fixed*
Fixed better.

@@
 At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director.
-The results of the new Introductory Packet may only affect the number of signatures evaluated at the Introductory Evaluation and, as long as the Introductory Member receives the appropriate number of packet signatures that would normally be required in the \ref{Creation of Accounts} process.
+Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again.
+The results of the new Introductory Packet will also affect the number of signatures evaluated at the Introductory Evaluations.
 \bsubsection{Expectations of an Introductory Member}

### 2016-11-10 bylaws.tex
Eboard decides budget

--- 2016-11-07 bylaws.tex
@@
 All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
-\bsection{Breakdown of Dues for Directorship Budgets}
-\begin{center}
-\begin{tabular}[c]{l c}
-Directorship Name & Percentage of Dues \\
-\hline
-\hline
-Operational Communications & 20\% \\
-\hline
-Evaluations \& Selections & 5\% \\
-\hline
-House History & 10\% \\
-\hline
-House Improvements & 15\% \\
-\hline
-Research and Development & 20\% \\
-\hline
-Social & 20\% \\
-\hline
-Accumulated & 10\% \\
-\hline
-\end{tabular}
-\end{center}
-
-The suggested total operational budget is \$8064.
-This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
-Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+\bsection{Derivation of Directorship Budgets}
+At the start of each operating session the Executive Board will create a proposed budget.
+Said budget will define the percentage of funds allotted for each director and what portion will be set aside for deposit into Computer Science House's accumulated funds.
+The total operational budget is to be defined by the Financial Director based on dues collection.
+\\*\\*
+In order for the budget to take effect it must pass a Two-Thirds Majority Executive Board vote with the Financial Director in favor.
 
@@
 	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 60\% majority vote at a House Meeting.
- 	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
- 	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
- 	This may occur only once per Introductory Evaluation Process.\bsection{Code of Conduct}
 \end{enumerate}

### 2016-11-13 bylaws.tex
updated text

--- 2016-11-10 bylaws.tex
@@
 Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again.
-The results of the new Introductory Packet will also affect the number of signatures evaluated at the Introductory Evaluations.
+The results of the new Introductory Packet will replace the results of the first attempt to be evaluated at the Introductory Evaluations (if the score is improved.
+If the results of packet the did not improve, the original packet score is evaluated).
 \bsubsection{Expectations of an Introductory Member}

### 2016-11-14 articles.tex
fixed some things
fixed lines and position

@@
 \asection{Appeals}
+Decisions made by the Executive Board may be appealed and overturned.
 \asubsection{Executive Board Appeal}
-Decisions made by the Executive Board may be appealed and overturned.
 To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.

### 2016-11-14 articles.tex
Moves semantic change discussion from House Meeting to History Discussion

--- 2016-10-23 articles.tex
@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
+Any semantic change to the Constitution requires the change to be proposed in writing for a History Disussion meeting.
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal, along with a summary of the discussion, is presented the following week at House Meeting and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.

### 2016-11-14 articles.tex
Non-semantic wording update

@@
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal, along with a summary of the discussion, is presented the following week at House Meeting and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal and a summary of the discussion are presented the following week at House Meeting and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.

### 2016-11-14 articles.tex
Clarified Semantic Change Discussions
Exactly when house wide discussions of semantic changes should be held is currently vague and unclear.  Currently, we have discussion on amendments one week after their proposal.  The current wording could easily be interpreted as meaning otherwise.  This change would require proposed amendments to be discussed immediately after being proposed, rather than one week later.  This change would prevent members from voting no on an amendment simply because they don't like the wording as they would have been able to discuss their issues involving wording and phr

@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for a History Disussion meeting.
+Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.  
+Discussion of the wording and the implications of the change should be held immediately following the proposal.
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal and a summary of the discussion are presented the following week at House Meeting and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.

### 2017-01-05 articles.tex
Add History Discussion to the History Directorship
Fix Spelling Mistakes

@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.  
-Discussion of the wording and the implications of the change should be held immediately following the proposal.
+Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
@@
 \asubsection{Maintainer Selection}
-Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Exective Board may choose to approve or reject the nomination by Simple Majority vote.
+Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Executive Board may choose to approve or reject the nomination by Simple Majority vote.
 
@@
 Upon returning, the member may assume their position and the interim director is removed.
-If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amonst the Executive Board to require a resignation from the Member.
+If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amongst the Executive Board to require a resignation from the Member.
 
@@
 For any other type of vote, the voting period must be at least twenty-four (24) hours.
-The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
+The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
 \asubsection{Balloted Vote}
@@
 For any other type of vote, the voting period must be at least twenty-four (24) hours.
-The minimum length of the voting period may be explicitly lengthed, but never shortened, in the text describing the actual vote.
+The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
 \asubsection{Immediate Vote}

### 2017-01-05 bylaws.tex
Style + Grammar
1) 1 sentence = 1 line
2) No sentences allowed within a parenthetical statement because English.
Fix Spelling Mistakes

--- 2016-11-10 bylaws.tex
@@
 The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
-Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.
+Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.
 
@@
 All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
-\bsection{Derivation of Directorship Budgets}
-At the start of each operating session the Executive Board will create a proposed budget.
-Said budget will define the percentage of funds allotted for each director and what portion will be set aside for deposit into Computer Science House's accumulated funds.
-The total operational budget is to be defined by the Financial Director based on dues collection.
-\\*\\*
-In order for the budget to take effect it must pass a Two-Thirds Majority Executive Board vote with the Financial Director in favor.
+\bsection{Breakdown of Dues for Directorship Budgets}
+\begin{center}
+\begin{tabular}[c]{l c}
+Directorship Name & Percentage of Dues \\
+\hline
+\hline
+Operational Communications & 20\% \\
+\hline
+Evaluations \& Selections & 5\% \\
+\hline
+House History & 10\% \\
+\hline
+House Improvements & 15\% \\
+\hline
+Research and Development & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+Accumulated & 10\% \\
+\hline
+\end{tabular}
+\end{center}
+
+The suggested total operational budget is \$8064.
+This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
 
@@
 \item Complete the Introductory Packet
-\item Be an active participant in an the Introductory Project
+\item Be an active participant in the Introductory Project
 \item Attend at least one House directorship meeting for each week of the process

### 2017-01-05 articles.tex
Refomat lines
Last year the document was re-formatted to have sentences be on separate
lines in order to increase readability of the source and subsequent diff
files.

@@
 \asubsection{Maintainer Selection}
-Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Executive Board may choose to approve or reject the nomination by Simple Majority vote.
+Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
+The Executive Board may choose to approve or reject the nomination by Simple Majority vote.
 
@@
 \asubsection{Introductory Membership Evaluations}
-Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
+Introductory members are evaluated on their performance during the introductory period.
+The introductory evaluation process is described in \ref{Introductory Evaluation}.
 \asubsection{Introductory Membership Leave of Absence}
@@
 \asubsection{Active Membership Leave of Absence}
-An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}. For the duration of an absence, a member:
+An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
+For the duration of an absence, a member:
 \begin{itemize}
@@
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
-	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
+	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.
+		The constitution should remain up to date with current practices.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Social Meetings. House members are encouraged to bring ideas for social events to the meetings for discussion.
+	\item To preside over Social Meetings.
+		House members are encouraged to bring ideas for social events to the meetings for discussion.
 	\item To exercise general supervision over Social operations.
@@
 \begin{enumerate}
-	\item To preside over Financial Meetings. House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
+	\item To preside over Financial Meetings.
+		House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
 	\item To supervise financial administrators and transactions involving house projects.
@@
 \begin{enumerate}
-	\item To preside over Research and Development Meetings. House members are encouraged to bring ideas for projects to the meetings for discussion.
+	\item To preside over Research and Development Meetings.
+		House members are encouraged to bring ideas for projects to the meetings for discussion.
 	\item To exercise general supervision over Research and Development operations.
@@
 \begin{enumerate}
-\item
- Candidates must be Active Members.
+\item Candidates must be Active Members.
 \end{enumerate}

### 2017-01-05 bylaws.tex
Refomat lines
Last year the document was re-formatted to have sentences be on separate
lines in order to increase readability of the source and subsequent diff
files.
Convert All Indents to Tabs
The majority of the documents were using tabs, so it made sense to
switch to that for a unified format.
Remove extraneous whitespace
Change href tags to url tags
Not sure why href tags wouldn't show up, but URLs will now properly show
up as hyperlinks in the compiled PDFs.

@@
 \\*\\*
-All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+After this date, dues collection is suspended until the start of the next academic year.
 \bsection{Breakdown of Dues for Directorship Budgets}
@@
 	\item A discussion of the candidates will be held at the following House meeting.
-    \item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty     
-        Percent}. Voting must remain open for a minimum of a forty-eight hour period. 
+	\item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty Percent}.
+		Voting must remain open for a minimum of a forty-eight hour period.
 	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
@@
 \bsubsection{Membership Evaluation}
-The Membership Evaluation process occurs once per academic year. It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+The Membership Evaluation process occurs once per academic year.
+It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
 \bsubsubsection{Voting} 
@@
 A member may be given a conditional to complete as a means of making up for missing requirements.
-A conditional may be proposed by any member present at the Evaluation. If the conditional is approved by the Evaluations Director, it is then voted on by House.
+A conditional may be proposed by any member present at the Evaluation.
+If the conditional is approved by the Evaluations Director, it is then voted on by House.
 Each conditional consists of a set of additional requirements a deadline for completing them.
@@
 	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
-	\item Candidates may be granted an exemption by current Root Type Persons. Such an exemption may be withdrawn at any time by the current Root Type Persons.
+	\item Candidates may be granted an exemption by current Root Type Persons.
+		Such an exemption may be withdrawn at any time by the current Root Type Persons.
 	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
@@
 \bsection{Creation of Accounts}
-Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
+Root Type Persons have the authority to manage user accounts for House systems.
+Before members may receive an account they must:
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 \bsection{Code of Conduct}
-The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
 \\* \\*
-Members are bound to the Code of Conduct revision that they sign when initially creating their account. Members may sign a more recent revision of the Code of Conduct to update their agreement.
+Members are bound to the Code of Conduct revision that they sign when initially creating their account.
+Members may sign a more recent revision of the Code of Conduct to update their agreement.
 \bsubsection{Changes}

### 2017-02-09 bylaws.tex

--- 2017-01-05 bylaws.tex
@@
 The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
-Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.
+Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.
 
@@
 All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
-\bsection{Breakdown of Dues for Directorship Budgets}
+\bsection{Derivation of Directorship Budgets}
+The total operational budget is to be defined by the Financial Director based on dues collection. The budget below outlines the percentage allotment for each director. 
 \begin{center}
@@
 \hline
-House Improvements & 15\% \\
+House Improvements & 20\% \\
 \hline
-Research and Development & 20\% \\
+Research and Development & 15\% \\
 \hline
@@
 \hline
-Accumulated & 10\% \\
+Addition to Accumulated Funds& 10\% \\
 \hline
@@
 \end{center}
-
-The suggested total operational budget is \$8064.
-This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
-Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+During the Operating Session, the Financial Director may propose an amended distribution that must be approved by a Simple Majority Executive Board vote.
 
@@
 \item Complete the Introductory Packet
-\item Be an active participant in the Introductory Project
+\item Be an active participant in an the Introductory Project
 \item Attend at least one House directorship meeting for each week of the process

### 2017-02-12 articles.tex
Convert All Indents to Tabs
The majority of the documents were using tabs, so it made sense to
switch to that for a unified format.
Revoke membership of advisors who no longer meet qualifications

--- 2016-11-14 articles.tex
@@
 \asubsection{Advisory Membership Term}
-Advisory Membership shall last until the member resigns.
+Advisory Membership shall last until the Advisor no longer meets the qualifications as defined in \ref{Advisory Membership Qualifications} or until the Advisor resigns.
 

### 2017-02-24 articles.tex
Various Non Semantic Fixes (#95)
* Fix Spelling Mistakes

* Refomat lines

Last year the document was re-formatted to have sentences be on separate
lines in order to increase readability of the source and subsequent diff
files.

* Convert All Indents to Tabs

The majority of the documents were using tabs, so it made sense to
switch to that for a unified format.

* Remove extraneous whitespace

* Change href tags to url tags

Not sure why href tags wouldn't show up, but URLs will now properly show
up as hyperlinks in the compiled PDFs.
Slight Grammatical Change
Reacclimate: Acclimate assumes it

--- 2017-01-05 articles.tex
@@
 A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
-Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence as well as acclimating back to the culture of House upon their return.
+Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence as well as reacclimate back to the culture of House upon their return.
 Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.

### 2017-02-24 articles.tex

@@
 A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
-Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence as well as reacclimate back to the culture of House upon their return.
+Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence. 
+House will also help to reacclimate any returning member back to the culture of House upon their return.
 Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.

### 2017-03-01 articles.tex
swapped an apostrophe for one that actually compiles (#98)

@@
 \asection{Appointment of an Interim Director}
-The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.

### 2017-04-28 bylaws.tex
Changed Introductory Project Evaluations Process

@@
 \bsubsection{Introductory Executive Board}
-An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
+An Introductory Executive Board is elected by the introductory members to lead and manage the project as well as represent the introductory project participants to House.
 The Introductory Executive Board consists of three members:
@@
 The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
+\bsubsubsection{Introductory Project Evaluations Process}
+The Evaluations Director determines whether each introductory member passes or fails the Introductory Project by using information gathered from the Introductory Project Executive Board and the Introductory Project Advisors.
+The Evaluations Director then reports the status of each Introductory Member's Introductory Project Evaluation to said Introductory Member.
 \bsubsection{The Introductory Packet}

### 2017-05-04 articles.tex
Specify 'Votes Collected' (#101)
Additional wording so intent of the Alternative Vote could be better understood.

--- 2017-03-01 articles.tex
@@
 \asubsection{Alternative}
-The winning option is selected outright if it gains more than half the votes as a first preference.
+The winning option is selected outright if it gains more than half the votes collected as a first preference.
 If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
-This process continues until one option has half of the votes and is elected.
+This process continues until one option has half of the votes collected and is elected.
 

### 2017-05-04 bylaws.tex

--- 2017-02-24 bylaws.tex
@@
 	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 60\% majority vote at a House Meeting.
+ 	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
+ 	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
+ 	This may occur only once per Introductory Evaluation Process.\bsection{Code of Conduct}
 \end{enumerate}

### 2017-05-05 articles.tex

--- 2017-03-01 articles.tex
@@
 \asubsection{Alternative}
-The winning option is selected outright if it gains more than half the votes as a first preference.
+The winning option is selected outright if it gains more than half the votes cast as a first preference.
 If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
-This process continues until one option has half of the votes and is elected.
+This process continues until one option has half of the votes cast and is elected.
 

### 2017-05-17 articles.tex

@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
+Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.  
+Discussion of the wording and the implications of the change should be held immediately following the proposal.
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.

### 2017-05-17 articles.tex

--- 2017-05-05 articles.tex
@@
 Decisions made by the Executive Board may be appealed and overturned.
+\asubsection{Executive Board Appeal}
 To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
@@
 If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
+\asubsection{House Appeal} 
+To initiate an appeal to House of an Executive Board decision, a petition with the signatures of two-thirds of Active Members must be brought to a House Meeting. 
+After the appeal is presented and discussed, a Two-Thirds vote is held by the attending members. 
+If the vote passes, attending members may discuss and make a new ruling by a Two-Thirds vote.
 

### 2017-05-17 bylaws.tex

--- 2017-04-28 bylaws.tex
@@
 \bsubsection{Introductory Executive Board}
-An Introductory Executive Board is elected by the introductory members to lead and manage the project as well as represent the introductory project participants to House.
+An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
 The Introductory Executive Board consists of three members:
@@
 The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
-\bsubsubsection{Introductory Project Evaluations Process}
-The Evaluations Director determines whether each introductory member passes or fails the Introductory Project by using information gathered from the Introductory Project Executive Board and the Introductory Project Advisors.
-The Evaluations Director then reports the status of each Introductory Member's Introductory Project Evaluation to said Introductory Member.
 \bsubsection{The Introductory Packet}
@@
 \end{itemize}
+At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director.
+Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again. 
+The best completion percentage of the two Introductory Packets will be presented at the Introductory Evaluation.
 \bsubsection{Expectations of an Introductory Member}

### 2017-05-17 bylaws.tex

@@
 \end{itemize}
-At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director.
-Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again. 
-The best completion percentage of the two Introductory Packets will be presented at the Introductory Evaluation.
+After the second week of the Introductory Packet, Introductory Members who have received less than 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) will have their membership revoked.
 \bsubsection{Expectations of an Introductory Member}
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet.
 \end{enumerate}

### 2017-06-07 articles.tex

--- 2017-05-17 articles.tex
@@
 \asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.  
-Discussion of the wording and the implications of the change should be held immediately following the proposal.
+Any semantic change to the Constitution requires the change to be proposed in writing for a History Disussion meeting.
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal and a summary of the discussion are presented the following week at House Meeting and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 	\item To oversee the creation of a yearbook outlining House events for the year.
+	\item To preside over House History Discussion meetings, which must be held if there are upcoming \ref{Semantic Changes} to the Constitution but are otherwise held at the director's discretion.
 \end{enumerate}

### 2017-06-20 articles.tex

--- 2017-05-17 articles.tex
@@
 \asubsection{Advisory Membership Term}
-Advisory Membership shall last until the Advisor no longer meets the qualifications as defined in \ref{Advisory Membership Qualifications} or until the Advisor resigns.
+Advisory Membership shall last until the member resigns.
 
@@
 	\item House Secretary
-	\item Ad Hoc Director
+	\item Ad Hoc Director (s)
 \end{itemize}

### 2017-06-20 articles.tex
Removed all trailing whitespacs from .tex files
Fix Git Revision Insertion for Makefile (#108)

Fixed periods and capitalization

Add more instructions to readme

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

@@
 \begin{enumerate}
-	\item To enhance the education experience of its members.
-	\item To offer students educational programming with an emphasis in computers.
-	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community.
-	\item To provide a friendly and comfortable living environment in the residence halls.
+	\item To enhance the education experience of its members
+	\item To offer students educational programming with an emphasis in computers
+	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
+	\item To provide a friendly and comfortable living environment in the residence halls
 \end{enumerate}
@@
 \begin{itemize}
-	\item Review changes to the Constitution for grammar, spelling, and internal consistency.
-	\item Keep a public record of changes to the Constitution.
-	\item Participate in discussion of proposals.
-	\item Facilitate the creation of new changes to the Constitution by other members.
-	\item Be knowledgeable about the Constitution.
+	\item Review changes to the Constitution for grammar, spelling, and internal consistency
+	\item Keep a public record of changes to the Constitution
+	\item Participate in discussion of proposals
+	\item Facilitate the creation of new changes to the Constitution by other members
+	\item Be knowledgeable about the Constitution
 \end{itemize}
@@
 \begin{description}
-	\item[Qualifications:] What qualifications an applicant needs to apply.
-	\item[Selection:] The process by which an applicant gains membership.
-	\item[Expectations:] The duties and responsibilities of House members.
-	\item[Privileges:] The benefits offered to House members.
-	\item[Evaluations:] The process by which a member is reviewed and assessed.
-	\item[Leave of Absence:] The process by which a member may leave House for a period of time.
-	\item[Resignations:] The process by which a member terminates House membership.
-	\item[Term:] The length of time the membership lasts.
+	\item[Qualifications:] What qualifications an applicant needs to apply
+	\item[Selection:] The process by which an applicant gains membership
+	\item[Expectations:] The duties and responsibilities of House members
+	\item[Privileges:] The benefits offered to House members
+	\item[Evaluations:] The process by which a member is reviewed and assessed
+	\item[Leave of Absence:] The process by which a member may leave House for a period of time
+	\item[Resignations:] The process by which a member terminates House membership
+	\item[Term:] The length of time the membership lasts
 \end{description}
@@
 	\item House Secretary
-	\item Ad Hoc Director (s)
+	\item Ad Hoc Director(s)
 \end{itemize}
@@
 \begin{enumerate}
-	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
-	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
-	\item To report pertinent information to House members at the following House Meeting.
-	\item To maintain records of the goals defined by each previous Executive Board.
-	\item To act as a Judicial Board as defined in \ref{Judicial}.
-	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director.
-	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board.
-	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
-	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.
+	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
+	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
+	\item To report pertinent information to House members at the following House Meeting
+	\item To maintain records of the goals defined by each previous Executive Board
+	\item To act as a Judicial Board as defined in \ref{Judicial}
+	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
+	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
+	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board
+	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
+	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}
 		The constitution should remain up to date with current practices.
@@
 \begin{enumerate}
-	\item To preside over Executive Board and House Meetings.
-	\item To exercise general supervision over the operations of the Executive Board.
-	\item To exercise general supervision over regular House activities.
-	\item To act as a liaison to the academic and administrative departments at RIT.
-	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
-	\item To cast tie-breaking vote in a split decision in an Executive Board vote.
+	\item To preside over Executive Board and House Meetings
+	\item To exercise general supervision over the operations of the Executive Board
+	\item To exercise general supervision over regular House activities
+	\item To act as a liaison to the academic and administrative departments at RIT
+	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
+	\item To cast tie-breaking vote in a split decision in an Executive Board vote
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Evaluations Meetings.
-	\item To exercise general supervision over Evaluations operations.
-	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
-	\item To oversee the Semi-Annual Evaluations of current House members.
-	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
-	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
-	\item To prepare the House for Open Houses, tours, and special events.
+	\item To preside over Evaluations Meetings
+	\item To exercise general supervision over Evaluations operations
+	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
+	\item To oversee the Semi-Annual Evaluations of current House members
+	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
+	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
+	\item To prepare the House for Open Houses, tours, and special events
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Social Meetings.
+	\item To preside over Social Meetings
 		House members are encouraged to bring ideas for social events to the meetings for discussion.
-	\item To exercise general supervision over Social operations.
-	\item To oversee the organization, initiation, and execution of House activities and events.
-	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year.
+	\item To exercise general supervision over Social operations
+	\item To oversee the organization, initiation, and execution of House activities and events
+	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Financial Meetings.
+	\item To preside over Financial Meetings
 		House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
-	\item To supervise financial administrators and transactions involving house projects.
-	\item To maintain financial and inventory records of House capital and assets.
-	\item To plan and enforce a House budget.
-	\item To oversee House finances and generation of House funds.
-	\item To publish a semesterly House financial statement.
-	\item To supervise the collection of semesterly House dues.
-	\item To oversee the planning and execution of fundraising events.
+	\item To supervise financial administrators and transactions involving house projects
+	\item To maintain financial and inventory records of House capital and assets
+	\item To plan and enforce a House budget
+	\item To oversee House finances and generation of House funds
+	\item To publish a semesterly House financial statement
+	\item To supervise the collection of semesterly House dues
+	\item To oversee the planning and execution of fundraising events
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Research and Development Meetings.
+	\item To preside over Research and Development Meetings
 		House members are encouraged to bring ideas for projects to the meetings for discussion.
-	\item To exercise general supervision over Research and Development operations.
-	\item To oversee the planning, organization and construction of technical projects for the House's benefit.
-	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment.
-	\item To provide seminars and tutorials to educate House members in technical areas.
+	\item To exercise general supervision over Research and Development operations
+	\item To oversee the planning, organization and construction of technical projects for the House's benefit
+	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
+	\item To provide seminars and tutorials to educate House members in technical areas
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over House Improvements Meetings.
-	\item To exercise general supervision over the House Improvements operations.
-	\item To oversee the organization and construction of physical improvements to the House.
-	\item To oversee the general maintenance of the appearance of the House.
+	\item To preside over House Improvements Meetings
+	\item To exercise general supervision over the House Improvements operations
+	\item To oversee the organization and construction of physical improvements to the House
+	\item To oversee the general maintenance of the appearance of the House
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings.
-	\item To report the status of the House computer systems and network to the Executive Board and House members.
+	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
+	\item To report the status of the House computer systems and network to the Executive Board and House members
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over House History Meetings.
-	\item To exercise general supervision over the House History operations.
-	\item To maintain, uphold, and promote house traditions.
-	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events.
-	\item To oversee the production and distribution of a semi-annual newsletter.
-	\item To oversee the creation of a yearbook outlining House events for the year.
+	\item To preside over House History Meetings
+	\item To exercise general supervision over the House History operations
+	\item To maintain, uphold, and promote house traditions
+	\item To collaborate with the Social Director(s) to ensure that all the Active, Alumni, and Advisory Members are informed of upcoming events
+	\item To oversee the production and distribution of a semi-annual newsletter
+	\item To oversee the creation of a yearbook outlining House events for the year
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To ensure that minutes are recorded and posted for Executive Board Meetings.
-	\item To ensure that minutes are recorded and posted for House Meetings.
-	\item To oversee the maintenance of Executive Board records and documents.
-	\item To provide administrative assistance to the Executive Board.
-	\item To oversee the maintenance of the Activities Information Centers.
-	\item To record all votes cast during House Meetings and Open Executive Board Meetings.
+	\item To ensure that minutes are recorded and posted for Executive Board Meetings
+	\item To ensure that minutes are recorded and posted for House Meetings
+	\item To oversee the maintenance of Executive Board records and documents
+	\item To provide administrative assistance to the Executive Board
+	\item To oversee the maintenance of the Activities Information Centers
+	\item To record all votes cast during House Meetings and Open Executive Board Meetings
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Ad-Hoc Directorships are responsible for the task for which they were created.
-	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director.
+	\item Ad-Hoc Directorships are responsible for the task for which they were created
+	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Candidates must be Active Members during the term of office.
-	\item Candidates must reside on floor during the term of office.
-	\item Candidates must have at least one full semester of House membership as an Active Member.
-	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected.
+	\item Candidates must be Active Members during the term of office
+	\item Candidates must reside on floor during the term of office
+	\item Candidates must have at least one full semester of House membership as an Active Member
+	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Candidates must be Active Members during the term of office.
-	\item Candidates must have at least one full semester of House membership as an Active Member.
-	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
+	\item Candidates must be Active Members during the term of office
+	\item Candidates must have at least one full semester of House membership as an Active Member
+	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
 \end{enumerate}
@@
 	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
-	\item Candidates must be a current Active Member.
-	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
+	\item Candidates must be a current Active Member
+	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position
 \end{enumerate}
@@
 \begin{enumerate}
-\item Candidates must be Active Members.
+\item Candidates must be Active Members
 \end{enumerate}

### 2017-06-20 bylaws.tex
Removed all trailing whitespacs from .tex files
Fix Git Revision Insertion for Makefile (#108)

Fixed periods and capitalization

Add more instructions to readme

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

ran script to add periods to end of any bullet points

removed all periods at end of \item

removed periods

maunally edited the punctuation

@@
 \bsection{The Introductory Process}
-The Introductory Process is designed to provide an easy means for introductory members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
 \bsubsection{The Evaluation Period}
@@
 \bsubsection{Introductory Executive Board}
-An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
+An Introductory Executive Board is elected by the Introductory Members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
 The Introductory Executive Board consists of three members:
@@
 \item Attend at least two seminars relating to computing or electronics
-\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations.
+\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
 \end{itemize}
@@
 \begin{enumerate}
-	\item The applicant submits an application to the Evaluations Director for review.
-	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
-	\item The application materials are then reviewed at an Evaluations meeting.
-	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an introductory member.
+	\item The applicant submits an application to the Evaluations Director for review
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members
+	\item The application materials are then reviewed at an Evaluations meeting
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
 \end{enumerate}

### 2017-06-24 bylaws.tex
Fixed periods and capitalization

@@
 \begin{enumerate}
-	\item The applicant submits an application to the Evaluations Director for review
-	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members
-	\item The application materials are then reviewed at an Evaluations meeting
+	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
+	\item The application materials are then reviewed at an Evaluations meeting.
 	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.

### 2017-09-23 articles.tex
Removed all trailing whitespacs from .tex files
Corrected singular noun used in non voting eboard member section
Fixed periods and capitalization
Remove RHA, update formal name for ResLife

--- 2017-06-20 articles.tex
@@
 \asection{Derivation of Authority}
-The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Department of Residence Life in conjunction with the Residence Halls Association.
+The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Residence Life.
 
@@
 \begin{enumerate}
-	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
+	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
 	\item Candidates must be a current Active Member.

### 2017-09-24 articles.tex

--- 2017-06-20 articles.tex
@@
 The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
+If a member comes forward with allegations that abusive speech, bullying, or threats are occurring to them from another member, a Judicial proceeding is immediately started, without the need for Executive Board approval.
+In the case of a member coming forward with an accusation of assault or more serious actions, the matter and all information known about it is immediately forwarded to The Department of Residence Life and/or the relevant department at RIT, bypassing any Executive Board decisions.
 \asection{Formation of a Judicial Board}
 A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
-If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
+If either of the two non-Chairman member of the Executive Board are deemed biased, unfit for a position on the Judicial Board, or are involved in the Judicial as an accuser or accused, the Judicial Board will instead be composed of 2 non-Executive Board members randomly chosen from active on-floor members, and the Chairman.
+If the Chairman is deemed biased, unfit for a position on the Judicial Board, or involved in the Judicial as an accuser or accused, the Judicial Board will be composed of 3 non-Executive Board members randomly chosen from active on-floor members.
 \asection{Judicial Investigation}
 The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
+For Judicial proceedings initiated from a claim of abusive speech, bullying, or threats, the accuser is able to directly introduce evidence (including witnesses) to the meeting the Judicial decision occurs at.
+It is also required that all witnesses be interviewed by the board during the decision making meeting.
 \asection{Judicial Ruling}
@@
 This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
+From a Judicial proceedings initiated from a claim of abusive speech, bullying, or threats, if the claims are found to be true and are severe enough that it can be classified as extreme (the member claims they were encouraged to commit suicide, feel physically unsafe, are unable to be in their room without fear), or the offender has refused to heed previous warnings concerning actions towards the accuser, them the offender's membership is immediately removed, and the incident, along with all known pertinent information, is elevated to RIT and/or The Department of Residence Life’s attention.
 

### 2017-09-26 articles.tex

--- 2017-06-20 articles.tex
@@
 \begin{enumerate}
-	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
-	\item Candidates must be a current Active Member
-	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position
+	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
+	\item Candidates must be a current Active Member.
+	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
 \end{enumerate}

### 2017-09-28 bylaws.tex
By-Law VI: Use of Intellectual Property
major House project -> major project
Add table of contents to articles/bylaws (#118)
Reduced scope of branch - removed subjective expectation
major House project -> major project (#119)
bylaws: Update standard operating session length
This reflects the new semester schedule RIT has switched to.

@@
 \usepackage{hyperref}
+% Reformat section titles
+\usepackage{titlesec}
 
@@
 \newcommand{\bsubsection}[1]{\subsubsection{#1} \label{#1}}
-\renewcommand{\thesection}{By-Law \Roman{section}}
-\renewcommand{\thesubsection}{Section \arabic{section}.\Alph{subsection}}
+\renewcommand{\thesection}{\Roman{section}}
+\renewcommand{\thesubsection}{\arabic{section}.\Alph{subsection}}
 \renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}
+\titleformat{\section}{\normalfont\Large\bfseries}{By-Law \thesection}{1em}{}
+\titleformat{\subsection}{\normalfont\large\bfseries}{Section \thesubsection}{1em}{}
 
@@
 
+\tableofcontents
+
 % BY-LAW I - INTRODUCTION
@@
 \bsection{Standard Operating Session}
-The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters.
+The Standard Operating Session for Computer Science House is during the twenty-eight weeks of Fall and Spring semesters.
 The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
@@
 \\* \\*
-The member must participate significantly in at least one major House project during the academic year.
+The member must participate significantly in at least one major project during the academic year.
 The member is required to submit a description for this major project to the Executive Board for approval.

### 2017-10-02 bylaws.tex
Clarify membership meeting requirements
Allow ad-hoc directorship meetings to count towards both
the introductory evaluations process as well as the spring
evaluations process

@@
 \item Be an active participant in the Introductory Project
-\item Attend at least one House directorship meeting for each week of the process
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
 \item Attend at least one House social event during the process
@@
 \bsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings).
 Members are also required to actively participate in a majority of House activities.

### 2017-10-02 bylaws.tex
House directorship meeting -> permanent directorship meeting (#123)

--- 2017-09-28 bylaws.tex
@@
 \item Be an active participant in the Introductory Project
-\item Attend at least one House directorship meeting for each week of the process
+\item Attend at least one permanent directorship meeting for each week of the process
 \item Attend at least one House social event during the process
@@
 \end{enumerate}
+
+% BY-LAW VI - USE OF INTELLECTUAL PROPERTY
+\bylaw{Use of Intellectual Property}
+Computer Science House's name, logos, and all related trademarks and trade names are the property of Computer Science House and cannot be used without the express permission of the Executive Board.
+
 \end{document}

### 2017-10-29 articles.tex
Add table of contents to articles/bylaws

@@
 \newcommand{\asubsection}[1]{\subsubsection{#1} \label{#1}}
-\renewcommand{\thesection}{Article \Roman{section}}
-\renewcommand{\thesubsection}{Section \arabic{section}.\Alph{subsection}}
+\renewcommand{\thesection}{\Roman{section}}
+\renewcommand{\thesubsection}{\arabic{section}.\Alph{subsection}}
 \renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}
+\titleformat{\section}{\normalfont\Large\bfseries}{Article \thesection}{1em}{}
+\titleformat{\subsection}{\normalfont\large\bfseries}{Section \thesubsection}{1em}{}
 
@@
 
+\tableofcontents
+
 % ARTICLE I - INTRODUCTION

### 2017-10-29 bylaws.tex

--- 2017-10-02 bylaws.tex
@@
 \bsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings).
-Members are also required to actively participate in a majority of House activities.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
 \\* \\*

### 2017-10-30 bylaws.tex
Scale directorship meeting requirement by semester

@@
 \bsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
 \\* \\*

### 2017-10-30 bylaws.tex
Fix Merge Issues from #122

--- 2017-10-29 bylaws.tex
@@
 \bsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings).
 \\* \\*

### 2018-01-28 articles.tex

@@
 \begin{enumerate}
-	\item To preside over Social Meetings
-		House members are encouraged to bring ideas for social events to the meetings for discussion.
+	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
 	\item To exercise general supervision over Social operations
@@
 \begin{enumerate}
-	\item To preside over Financial Meetings
-		House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
+	\item To preside over Financial Meetings in which House members are encouraged to bring ideas for fund-raising activities
 	\item To supervise financial administrators and transactions involving house projects
@@
 \begin{enumerate}
-	\item To preside over Research and Development Meetings
-		House members are encouraged to bring ideas for projects to the meetings for discussion.
+	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
 	\item To exercise general supervision over Research and Development operations

### 2018-02-02 articles.tex
Temporary Ammendments added and Temporary Ammendment

@@
 
+% ARTICLE VII - TEMPORARY AMENDMENTS
+\article{Temporary Amendments}
+In the case that an amendment should be temporary, the amendment's changes should be listed here. 
+Each of these amendments is given a designated period of time, and will cease to exist immedietely. 
+If at any point interpretation of the changes needs to be made, the Executive Board will use the process defined in \ref{Judicial} to come to an agreement on how to proceed. 
+Occasionaly, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
+\asection{Changes to Evaluations}
+During the 2018-2019 period the following will supercede the text otherwise found in this document.
+\asubsection{Changes}
+\asubsubsection{Removal of Introductory Project}
+\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
+Additionally, \ref{Introductory Executive Board} will also no longer be elected or perform any duties during the described period. 
+\asubsubsection{Change of Packet Percentage}
+\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+During the described period, the percentage of required signatures in the Introductory Packet is increased to 75\%. 
+\asubsubsection{Changes to Packet Distribution}
+Introductory Members will recieve an \ref{The Introductory Packet} at the begining of the second week of each semester. 
+Any applicants who wish to become Introductory Members after the third week of each semester will recieve their packet during the begining of the second week of the following semester. 
+During the first, second, or third week of each semester, any applicant may have their application evaluated during a standard Evaluations Directorship Meeting or during either House Meeting or an Executive Board Meeting.
+\asubsubsection{PR Director} 
+Public Relations Director is added to \ref{Voting Members}, and is given the following responsibilities during the described period.  
+\begin{enumerate}
+	\item To preside over Public Relations Directorship Meetings.
+	\item To exercise general supervision over the Public Relations operations.
+	\item To communicate clearly with the Rochester Institute of Technology's extended community.
+	\item To collaborate with the Social and Evaluations Directors to ensure that \ref{The Introductory Process} is directed correctly.
+	\item To advertise any events run by Evaluations Director and/or Social Director(s) that are intended to be attended by RIT Students whom are not Computer Science House Members.  
+\end{enumerate}
+\asubsubsection{Evaluations and Social Directorship Changes}
+The Evalutations Director and Social Director(s) will have the following additional responsibilities during the described period. 
+\begin{enumerate}
+	\item To preside over a number of events intended to produce interest in CSH, especially in RIT students during the begining weeks of each semester.
+\end{enumerate}
+\asubsubsection{Evaluation Period}
+During the described period, the \ref{The Introductory Process} will begin during the first week of each semester or when the Evaluations Director otherwise chooses to initiates it.
+The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period. 
+\subsubsection{Referendum}
+During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
 \end{document}

### 2018-02-06 articles.tex
Fixed some spelling mistakes

@@
 In the case that an amendment should be temporary, the amendment's changes should be listed here. 
-Each of these amendments is given a designated period of time, and will cease to exist immedietely. 
+Each of these amendments is given a designated period of time, and will cease to exist immediately.
 If at any point interpretation of the changes needs to be made, the Executive Board will use the process defined in \ref{Judicial} to come to an agreement on how to proceed. 
@@
 \asubsubsection{Evaluations and Social Directorship Changes}
-The Evalutations Director and Social Director(s) will have the following additional responsibilities during the described period. 
+The Evaluations Director and Social Director(s) will have the following additional responsibilities during the described period. 
 \begin{enumerate}

### 2018-02-13 bylaws.tex
Moving Housing Point Allocation to Spring Evals

--- 2017-10-30 bylaws.tex
@@
 The suggested total operational budget is \$8064.
-This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
+This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
 Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
@@
 It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
-\bsubsection{Housing Points}
-All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
 \bsubsection{Membership Evaluation}
@@
 Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+All members who pass Membership Evaluation will recieve two housing points for use in the following academic years.
 \\* \\*
@@
 The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+Housing points are accumulated during the Membership Evaluation described in \ref{Membership Evaluation}.
 \\* \\*

### 2018-02-15 articles.tex

--- 2018-01-28 articles.tex
@@
 
+% ARTICLE VII - TEMPORARY AMENDMENTS
+\article{Temporary Amendments}
+In the case that an amendment should be temporary, the amendment's changes should be listed here. 
+Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
+If at any point interpretation of the changes needs to be made, the Executive Board will use the process defined in \ref{Judicial} to come to an agreement on how to proceed. 
+Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
+\asection{Changes to Evaluations}
+During the 2018-2019 period the following will supercede the text otherwise found in this document.
+\asubsection{Changes}
+\asubsubsection{Removal of Introductory Project}
+\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
+Additionally, \ref{Introductory Executive Board} will no longer be elected or perform any duties during the described period. 
+\asubsubsection{Change of Packet Percentage}
+\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+During the described period, the percentage of required signatures in the Introductory Packet will be increased to 75\%. 
+\asubsubsection{Changes to Packet Times}
+Introductory Members will recieve \ref{The Introductory Packet} following the House Meeting or Evaluations Directorship meeting of the second week of each semester. 
+Each Introductory Member will submit their packet at the end of week 3. 
+\asubsubsection{PR Director} 
+The Public Relations Director will be added to \ref{Voting Members}. 
+The Public Relations Director will be given half of Accumulated's budget (5\% of the total Directorships Budget.) 
+The Public Relations Director will be given the following responsibilities during the described period. 
+\begin{enumerate}
+	\item To preside over Public Relations Directorship Meetings.
+	\item To exercise general supervision over Public Relations operations.
+	\item To communicate clearly with Rochester Institute of Technology's extended community.
+	\item To collaborate with the Social and Evaluations Directors to ensure that \ref{The Introductory Process} is directed correctly.
+	\item To advertise any events run by Evaluations Director and/or Social Director(s) that are intended to be attended by RIT Students whom are not Computer Science House Members.  
+\end{enumerate}
+\asubsubsection{Evaluation Period}
+During the described period, the \ref{The Introductory Process} will begin during the first week of each semester.
+The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period.
+Additionally, \ref{Introductory Evaluation} occurs between the sixth and tenth week of each semester. 
+\subsubsection{Referendum}
+During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
 \end{document}

### 2018-09-23 bylaws.tex
Update packet signature requirements
- Requires signature of all active members (both on- and off-floor)
- Lowers requirement of alumni (non-active members), advisors, etc. to 10

--- 2017-10-30 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
+	\item A signature from all Active members, all Introductory Resident members, each Executive Board member, and ten (10) of any combination of the following:
 	\begin{itemize}
-		\item Non-Resident members who have passed a Membership Evaluation
 		\item Alumni members (not including Non-Resident Executive Board members)

### 2018-09-23 bylaws.tex
Remove 'essay' requirement from intro packet

@@
 \begin{itemize}
-	\item A signature from all Active members, all Introductory Resident members, each Executive Board member, and ten (10) of any combination of the following:
+	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
 	\begin{itemize}
+		\item Non-Resident members who have passed a Membership Evaluation
 		\item Alumni members (not including Non-Resident Executive Board members)
@@
 	\end{itemize}
-	\item A description of each Executive Board position, including:
-	\begin{itemize}
-		\item The responsibilities of the position
-		\item The name(s) of the position’s member(s)
-		\item The position’s weekly meeting time
-	\end{itemize}
-	\item A list of seven (7) annual House social events
-	\item A list of seven (7) major House technical achievements
 \end{itemize}

### 2018-09-30 bylaws.tex
Remove redundant phrasing

--- 2018-09-23 bylaws.tex
@@
 \begin{itemize}
-	\item A signature from all Active members, all Introductory Resident members, each Executive Board member, and ten (10) of any combination of the following:
+	\item A signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
 	\begin{itemize}
-		\item Alumni members (not including Non-Resident Executive Board members)
+		\item Alumni members
 		\item Honorary members

### 2018-10-09 articles.tex
Remove Pedantic Wording
Judicial Process automatically covers the Temporary Amendment section.
Make a line way more parsable.

@@
 Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
-If at any point interpretation of the changes needs to be made, the Executive Board will use the process defined in \ref{Judicial} to come to an agreement on how to proceed. 
 Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
@@
 	\item To collaborate with the Social and Evaluations Directors to ensure that \ref{The Introductory Process} is directed correctly.
-	\item To advertise any events run by Evaluations Director and/or Social Director(s) that are intended to be attended by RIT Students whom are not Computer Science House Members.  
+	\item To advertize any Computer Science House events that require communication with the larger RIT community.
 \end{enumerate}

### 2018-10-09 articles.tex
Delet PR

@@
 Each Introductory Member will submit their packet at the end of week 3. 
-\asubsubsection{PR Director} 
-The Public Relations Director will be added to \ref{Voting Members}. 
-The Public Relations Director will be given half of Accumulated's budget (5\% of the total Directorships Budget.) 
-The Public Relations Director will be given the following responsibilities during the described period. 
-\begin{enumerate}
-	\item To preside over Public Relations Directorship Meetings.
-	\item To exercise general supervision over Public Relations operations.
-	\item To communicate clearly with Rochester Institute of Technology's extended community.
-	\item To collaborate with the Social and Evaluations Directors to ensure that \ref{The Introductory Process} is directed correctly.
-	\item To advertize any Computer Science House events that require communication with the larger RIT community.
-\end{enumerate}
 \asubsubsection{Evaluation Period}

### 2018-10-28 articles.tex
Remove Freshman Project. Add Minor Project.

@@
 	\item To act as a Judicial Board as defined in \ref{Judicial}
+	\item To review minor projects, as defined in \ref{The Introductory Process}, presented to them by the Evaluations director
 	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
@@
 \asubsection{Changes}
-\asubsubsection{Removal of Introductory Project}
-\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
-Additionally, \ref{Introductory Executive Board} will no longer be elected or perform any duties during the described period. 
 \asubsubsection{Change of Packet Percentage}

### 2018-10-28 bylaws.tex
Remove Freshman Project. Add Minor Project.

@@
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
-\bsubsection{The Introductory Project}
-Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
-\bsubsection{Introductory Executive Board}
-An Introductory Executive Board is elected by the Introductory Members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
-The Introductory Executive Board consists of three members:
-\begin{itemize}
-	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
-	\item A Vice President, who assists the President in leadership and representation.
-	\item A Treasurer, who manages the finances for the project.
-\end{itemize}
-Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
-\bsubsubsection{The Project}
-The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
-All of the proceeds go to a charity chosen in advance by the participants.
-The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
-\bsubsubsection{Introductory Project Advisors}
-The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
-The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
+\bsubsection{The Minor Project}
+The member must participate significantly in at least one minor project during the Introductory Process. The
+member is required to submit a description for this minor project to the Executive Board for approval. 
 \bsubsection{The Introductory Packet}
@@
 \item Complete the Introductory Packet
-\item Be an active participant in the Introductory Project
+\item Complete a Minor Project
 \item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)

### 2018-10-28 bylaws.tex
Better define minor project

@@
 \bsubsection{The Minor Project}
-The member must participate significantly in at least one minor project during the Introductory Process. The
-member is required to submit a description for this minor project to the Executive Board for approval. 
+The Introductory Member must pass at least one minor project during the Introductory Process. 
+The minor project is a small, technical project that shows a passion and ability to learn new things.
+The project should involve something the Introductory Member has never worked with before, or taking what they know a step further.
+The project, although small, should be complete or at least somewhat functional such that it can be demoed/displayed.
+The Introductory Member is required to submit a description for this minor project to the Executive Board for approval. 
 \bsubsection{The Introductory Packet}

### 2018-11-07 articles.tex
Clarifies Resignation
Check one:
[] Semantic Change: something about the meaning of the text is different
[x] Non-semantic Change: Spelling, grammar, or formatting changes.

Summary of change(s):
Probably a good idea to specify they are resigning a position they have.

--- 2018-10-09 articles.tex
@@
 \asection{Resignations}
-An Executive Board Member may resign by submitting in writing the reason for resignation to the House Chairman.
+An Executive Board Member may resign an Executive Board position currently held by submitting in writing the reason for resignation to the House Chairman.
 The resignation will be read at the following House Meeting and become effective at that time.

### 2018-12-10 articles.tex
Grammar.
Remove Freshman Project
Clarifies Resignation (#137)
* Clarifies Resignation

Check one:
[] Semantic Change: something about the meaning of the text is different
[x] Non-semantic Change: Spelling, grammar, or formatting changes.

Summary of change(s):
Probably a good idea to specify they are resigning a position they have.

* Gambogi added a good suggestion.

Co-Authored-By: saucetray <justinsostreofficial@gmail.com>
Update to Wording
Updating How Bad Standing Votes Work

--- 2018-10-09 articles.tex
@@
 Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
-If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
-The decision will be announced at the following House meeting.
+If a majority is in favor of the return, the Alumni is removed from bad standing.
 \asubsection{Active Membership Expectations}
@@
 \asection{Resignations}
-An Executive Board Member may resign by submitting in writing the reason for resignation to the House Chairman.
+An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
 The resignation will be read at the following House Meeting and become effective at that time.

### 2018-12-10 articles.tex
Secretary Responsibilities Update

@@
 Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
-If a majority is in favor of the return, the Alumni is removed from bad standing.
+If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+The decision will be announced at the following House meeting.
 \asubsection{Active Membership Expectations}
@@
 	\item To provide administrative assistance to the Executive Board
-	\item To oversee the maintenance of the Activities Information Centers
 	\item To record all votes cast during House Meetings and Open Executive Board Meetings

### 2019-01-17 articles.tex
Update articles.tex
Added James Forcier

Co-Authored-By: saucetray <justinsostreofficial@gmail.com>
Remove the Temporary Amendment
The temporary amendment was taken apart bit by bit until all the useful parts of it were gone. All that remained was the ability to make temporary amendment, made the packet percentage to get an account higher, and disallowed intro members from reapplying/applying past the first week of each semester. I'd like to propose we don't cause this semester's intro members to go through a half-deconstructed process which we will get rid of entirely at the last HM of the se

@@
 	\item To provide administrative assistance to the Executive Board
+	\item To oversee the maintenance of the Activities Information Centers
 	\item To record all votes cast during House Meetings and Open Executive Board Meetings
@@
 This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
-
-% ARTICLE VII - TEMPORARY AMENDMENTS
-\article{Temporary Amendments}
-In the case that an amendment should be temporary, the amendment's changes should be listed here. 
-Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
-Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
-\asection{Changes to Evaluations}
-During the 2018-2019 period the following will supercede the text otherwise found in this document.
-\asubsection{Changes}
-\asubsubsection{Removal of Introductory Project}
-\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
-Additionally, \ref{Introductory Executive Board} will no longer be elected or perform any duties during the described period. 
-\asubsubsection{Change of Packet Percentage}
-\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-During the described period, the percentage of required signatures in the Introductory Packet will be increased to 75\%. 
-\asubsubsection{Changes to Packet Times}
-Introductory Members will recieve \ref{The Introductory Packet} following the House Meeting or Evaluations Directorship meeting of the second week of each semester. 
-Each Introductory Member will submit their packet at the end of week 3. 
-\asubsubsection{Evaluation Period}
-During the described period, the \ref{The Introductory Process} will begin during the first week of each semester.
-The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period.
-Additionally, \ref{Introductory Evaluation} occurs between the sixth and tenth week of each semester. 
-\subsubsection{Referendum}
-During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
 \end{document}

### 2019-02-01 bylaws.tex
Remove Freshman Project
Specify range for start and end of Introductory Process

--- 2018-10-28 bylaws.tex
@@
 \bsubsection{The Evaluation Period}
-The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
-The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
-\bsubsection{The Minor Project}
-The member must participate significantly in at least one minor project during the Introductory Process. The
-member is required to submit a description for this minor project to the Executive Board for approval. 
+The Process will begin between the first and fourth week of each semester, then last between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
 \bsubsection{The Introductory Packet}
@@
 \item Complete the Introductory Packet
-\item Complete a Minor Project
 \item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
@@
 The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
-Occurs once per academic year as part of the Introductory Process.
+Occurs between the sixth and tenth week of each semester.
 \bsubsubsection{Voting}

### 2019-02-01 bylaws.tex
Remove unneccessary enumeration from Introductory Packet requirements

--- 2018-10-28 bylaws.tex
@@
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
-\bsubsection{The Minor Project}
-The member must participate significantly in at least one minor project during the Introductory Process. The
-member is required to submit a description for this minor project to the Executive Board for approval. 
 \bsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
-\begin{itemize}
-	\item A signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
 \begin{itemize}
@@
 	\item Advisory members
-	\end{itemize}
 \end{itemize}

### 2019-02-01 bylaws.tex
Allow Evaluations Director to extend an Introductory Packet

@@
 \bsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
+\begin{itemize}
+	\item A signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
 	\begin{itemize}
@@
 	\end{itemize}
+\end{itemize}
+At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
 \bsubsection{Expectations of an Introductory Member}

### 2019-02-18 articles.tex
Elections Must Be Held for the Executive Board
We should have a process which requires elections to be held once someone resigns instead of having a possible interim director forever at the discretion of the Executive Board.
Update articles.tex
Spelling is Hard....
Awkward wording... sorta.
A Vote to Delay

@@
 The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time. 
+Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place. 
+If necessary, the Chairman may bring a vote and chair the vote during before an election deadline to delay the election by a specified time and the vote will qualify as a fifty percent vote.
 

### 2019-02-18 articles.tex
Update articles.tex

@@
 Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place. 
-If necessary, the Chairman may bring a vote and chair the vote during before an election deadline to delay the election by a specified time and the vote will qualify as a fifty percent vote.
+If necessary, the Chairman may bring a vote and chair the vote during before an election deadline to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote.
 

### 2019-02-18 articles.tex
Update articles.tex

--- 2019-02-18 articles.tex
@@
 Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place. 
-If necessary, the Chairman may bring a vote and chair the vote during before an election deadline to delay the election by a specified time and the vote will qualify as a fifty percent vote.
+If necessary, the Chairman may chair a vote during before an election deadline to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote.
+See fifty percent vote \ref{Fifty Percent}.
 

### 2019-02-18 articles.tex
Update articles.tex

@@
 Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place. 
-If necessary, the Chairman may chair a vote during before an election deadline to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote.
+If necessary, the Chairman may chair a vote before an election deadline at house meeting to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote.
 See fifty percent vote \ref{Fifty Percent}.

### 2019-02-18 articles.tex
New Section

--- 2019-02-18 articles.tex
@@
 Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
-If necessary, the Chairman may chair a vote during before an election deadline to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote.
-See fifty percent vote \ref{Fifty Percent}.
 
@@
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
+
+\asection{Delaying Election}
+If necessary, the Chairman may chair a vote before an election deadline at house meeting to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote.
+See fifty percent vote \ref{Fifty Percent}.
+If the vote fails, the election deadline already established will stay in effect.
 

### 2019-02-18 articles.tex
Update articles.tex

--- 2019-02-18 articles.tex
@@
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
+
+\asection{Delaying an Election}
+During a House Meeting prior to the election, the Chairman may chair a fifty percent vote to postpone the election by a specified time period. See \ref{Fifty Vote}.
+If the vote fails, the election must be held on normal time.
 

### 2019-02-25 bylaws.tex
Update Packet Requirement
Call me crazy, but maybe someone who got 60% of the required should not get an account.

--- 2019-02-01 bylaws.tex
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 75\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2019-02-25 articles.tex
Update articles.tex

@@
 \asection{Delaying an Election}
-During a House Meeting prior to the election, the Chairman may chair a fifty percent vote to postpone the election by a specified time period. See \ref{Fifty Vote}.
+During a House Meeting prior to the election, the Chairman may chair a immediate fifty percent vote to postpone the election by a specified time period.
+See \ref{Fifty Percent}.
+This vote cannot take place for elections taking place for the next standard operating year's Executive Board.
 If the vote fails, the election must be held on normal time.

### 2019-02-25 articles.tex
Fixing Inconsistent Membership Status (#151)

--- 2019-02-18 articles.tex
@@
 \asubsection{Active Membership Term}
-Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.
+Active Membership shall last until the member: resigns or changes membership status.
 
@@
 The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
-Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
 
@@
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
-
-\asection{Delaying an Election}
-During a House Meeting prior to the election, the Chairman may chair a fifty percent vote to postpone the election by a specified time period. See \ref{Fifty Vote}.
-If the vote fails, the election must be held on normal time.
 
@@
 \item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
-\item The term of an officer will be abbreviated due to resignation, impeachment, failure of the evaluation process, or change in membership status.
+\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
 \item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.

### 2019-03-01 articles.tex
Capitalise 'standard operating session'
'standard operating session' doesen't refer to the Standard Operating
Session.

@@
 \asubsection{Modified Evaluations}
-A member may request their evaluation period to be extended by the duration of the leave or to end of the standard operating session, whichever comes first.
+A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
 \asubsection{Leave of Absence for an Executive Board Member}
@@
 	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
-	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
+	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
 	\item To report pertinent information to House members at the following House Meeting
@@
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
-	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}
+	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}
 		The constitution should remain up to date with current practices.
@@
 \asubsection{Vote Counters}
-Vote Counters are the chairperson of the vote, and two randomly selected members.
+The chairperson of the vote is a vote counter and will additionally select two other members to count votes.
 

### 2019-03-01 articles.tex

--- 2019-02-25 articles.tex
@@
 This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
-
-% ARTICLE VII - TEMPORARY AMENDMENTS
-\article{Temporary Amendments}
-In the case that an amendment should be temporary, the amendment's changes should be listed here. 
-Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
-Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
-\asection{Changes to Evaluations}
-During the 2018-2019 period the following will supercede the text otherwise found in this document.
-\asubsection{Changes}
-\asubsubsection{Change of Packet Percentage}
-\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-During the described period, the percentage of required signatures in the Introductory Packet will be increased to 75\%. 
-\asubsubsection{Changes to Packet Times}
-Introductory Members will recieve \ref{The Introductory Packet} following the House Meeting or Evaluations Directorship meeting of the second week of each semester. 
-Each Introductory Member will submit their packet at the end of week 3. 
-\asubsubsection{Evaluation Period}
-During the described period, the \ref{The Introductory Process} will begin during the first week of each semester.
-The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period.
-Additionally, \ref{Introductory Evaluation} occurs between the sixth and tenth week of each semester. 
-\subsubsection{Referendum}
-During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
 \end{document}

### 2019-03-01 bylaws.tex
Outdated Housing Points Reference
If I'm reading this correctly... this is simply referring to winter evals that doesn't exist anymore.

--- 2019-02-01 bylaws.tex
@@
 \bsubsection{The Evaluation Period}
-The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
-The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
+The Process will begin between the first and fourth week of each semester, then last between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
 \bsubsection{The Introductory Packet}

### 2019-03-01 articles.tex
Remove the notarize reference
We don't require this per the constitution

--- 2019-03-01 articles.tex
@@
 % -This document must be ratified by the House (as per the Constitution),
-%  then printed, signed, notarized, and placed in the House filing cabinet
 %  if changes are to be officialized.
@@
 \asubsection{Modified Evaluations}
-A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
+A member may request their evaluation period to be extended by the duration of the leave or to end of the standard operating session, whichever comes first.
 \asubsection{Leave of Absence for an Executive Board Member}
@@
 	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
-	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
+	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
 	\item To report pertinent information to House members at the following House Meeting
@@
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
-	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}
+	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}
 		The constitution should remain up to date with current practices.

### 2019-03-01 bylaws.tex
Remove the notarize reference
We don't require this per the constitution

--- 2019-02-25 bylaws.tex
@@
 % -This document must be ratified by the House (as per the Constitution),
-%  then printed, signed, notarized, and placed in the House filing cabinet
 %  if changes are to be finalized.
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 75\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
 \end{enumerate}

### 2019-03-02 articles.tex
Merge the by-laws into the articles

--- 2019-03-01 articles.tex
@@
 %\usepackage{showkeys}
-
-% Define the external document to be bylaws for cross referencing purposes
-%\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
-\externaldocument{bylaws}[bylaws.pdf]
 
@@
 % Adding an \asubsubsection -- I feel dirty
-\setcounter{secnumdepth}{5}
+%\setcounter{secnumdepth}{5}
 \newcommand{\asubsubsection}[1]{\paragraph{#1} \label{#1}}
 \renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}
+
+% Adding \a(sub){3,4}section during merge of bylaws and articles -- I feel _really_ dirty
+\setcounter{secnumdepth}{7}
+\setcounter{tocdepth}{7}
+\newcommand{\asubsubsubsection}[1]{\parindent=0em\subparagraph{#1} \label{#1}}
+\renewcommand{\thesubparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}.\arabic{subparagraph}}
+
+\newcounter{asubsubsubsubsection}[subparagraph]
+\renewcommand{\theasubsubsubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}.\arabic{subparagraph}.\Alph{asubsubsubsubsection}}
+\newcommand{\asubsubsubsubsection}[1]{\parindent=0em\refstepcounter{asubsubsubsubsection}\par\textbf{\theasubsubsubsubsection\hspace{1em}#1 \label{#1}}}
 
@@
 It is reviewed annually by the Department of Residence Life.
-The House Constitution is comprised of two sections: articles and by-laws.
-Articles define the major aspects of the House.
-A by-law may expand on rules outlined in an article, but they must never contradict a Constitutional article.
 
@@
 
-% ARTICLE III - MEMBERSHIP
+% ARTICLE III - GENERAL OPERATIONS OF THE HOUSE
+\article{General Operations of the House}
+\asection{Standard Operating Session}
+The Standard Operating Session for Computer Science House is during the twenty-eight weeks of Fall and Spring semesters.
+The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
+Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.
+
+% ARTICLE IV - MEMBERSHIP
 \article{Membership}
@@
 
-% ARTICLE IV - EXECUTIVE BOARD
+% ARTICLE V - EXECUTIVE BOARD
 \article{Executive Board}
@@
 
+\asection{Operations}
+\asubsection{Operations of the Evaluations Directorship}
+\asubsubsection{The Introductory Process}
+The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+\asubsubsubsection{The Evaluation Period}
+The Process will begin between the first and fourth week of each semester, then last between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
+\asubsubsubsection{The Introductory Packet}
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+\begin{itemize}
+	\item Alumni members
+	\item Honorary members
+	\item Advisory members
+\end{itemize}
+At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+\asubsubsubsection{Expectations of an Introductory Member}
+Before the end of the Process, an Introductory Member is expected to:
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Complete the Introductory Packet
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
+\end{itemize}
+
+\asubsubsubsection{Introductory Evaluation}
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
+Occurs between the sixth and tenth week of each semester.
+\asubsubsubsubsection{Introductory Voting}
+On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Introductory Outcomes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
+		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+		Each conditional consists of a set of additional requirements a deadline for completing them.
+		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+		A conditional member who does not meet these additional requirements forfeits membership.
+\end{enumerate}
+\asubsubsection{Selection Processes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\asubsubsubsection{Selection Process for Students Attending RIT for at Least One Semester}
+\begin{enumerate}
+	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
+	\item The application materials are then reviewed at an Evaluations meeting.
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member must also pay dues.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsubsection{Selection Process for First Semester and Entering RIT Students}
+\begin{enumerate}
+	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
+		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
+	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
+		An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member must also pay dues.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsubsection{Selection Process for Honorary Members}
+\begin{enumerate}
+	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
+	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
+	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
+	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
+		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
+	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
+\end{enumerate}
+\asubsubsubsection{Selection Process for Advisory Members}
+\begin{enumerate}
+	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members.
+		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
+	\item After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.
+	\item A discussion of the candidates will be held at the following House meeting.
+	\item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty Percent}.
+		Voting must remain open for a minimum of a forty-eight hour period.
+	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
+\end{enumerate}
+
+\asubsubsection{Evaluations Processes}
+During the academic year, a House member is evaluated by the Membership Evaluation.
+The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+Semi-Annual Evaluations Meetings are open only to current Active Members.
+All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
+\\* \\*
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
+It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
+\asubsubsubsection{Housing Points}
+All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
+\asubsubsubsection{Membership Evaluation}
+The Membership Evaluation process occurs once per academic year.
+It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+\asubsubsubsubsection{Voting}
+A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
+All Active Members will be held to the requirements and evaluated unless they have received an exemption from the Executive Board prior to the event.
+These requirements are detailed in Article VI under expectations for each category of membership.
+These requirements must be completed before the Membership Evaluation occurs.
+A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Outcomes}
+Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+\\* \\*
+If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+In either case, the member forfeits their ability to be included on the following year’s roster.
+\\* \\*
+A member may be given a conditional to complete as a means of making up for missing requirements.
+A conditional may be proposed by any member present at the Evaluation.
+If the conditional is approved by the Evaluations Director, it is then voted on by House.
+Each conditional consists of a set of additional requirements a deadline for completing them.
+When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+A conditional member who does not meet these additional requirements will have failed the evaluation.
+\asubsubsubsection{Appeals Process}
+If a member disagrees with the outcome of any evaluation, (e.g.
+is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+\\* \\*
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
+
+\asubsubsection{Expectations of House Members}
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+\\* \\*
+The member must participate significantly in at least one major project during the academic year.
+The member is required to submit a description for this major project to the Executive Board for approval.
+As an option to this requirement, the member may instead assist on a large number of House activities and projects.
+However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
+This participation will be evaluated by the Executive Board.
+
+\asubsubsection{Housing Status}
+All Active and Introductory Members have a housing status.
+This status indicates their right to priority housing on the floor.
+Any Alumni Member in good standing will maintain their previous On Floor status upon a return to Active membership.
+\asubsubsubsection{On-Floor Status}
+Members with On-Floor status are eligible to live on the floor.
+To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
+The Evaluations Director will then bring them up for vote at the next meeting.
+\asubsubsubsection{Off-Floor Status}
+Members with Off-Floor status do not have the right to live on the floor.
+They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
+
+\asubsubsection{Housing Priority System}
+The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
+The member with top priority is the member with on-floor status and the most Housing Priority Points.
+Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+\\* \\*
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
+\asubsubsubsection{Single Room Assignments}
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
+If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
+This process continues until a member selects to move into the single room.
+Once in a single room, a House member retains the assignment until voluntarily giving it up.
+It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
+\asubsubsubsection{Double Rooms as Single rooms}
+During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
+It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
+This only applies if there is a totally vacant room.
+
+\asubsection{Operations of the Financial Directorship}
+\asubsubsection{Amount of House Dues}
+The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
+\asubsubsection{Collection of House Dues}
+The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected during this period as well by the Financial Director.
+For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+\\*\\*
+If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
+If the Financial Director deems their situation appropriate, they may grant an extension for payment.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
+If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
+If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
+\\*\\*
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+After this date, dues collection is suspended until the start of the next academic year.
+\asubsubsection{Breakdown of Dues for Directorship Budgets}
+\begin{center}
+\begin{tabular}[c]{l c}
+Directorship Name & Percentage of Dues \\
+\hline
+\hline
+Operational Communications & 20\% \\
+\hline
+Evaluations \& Selections & 5\% \\
+\hline
+House History & 10\% \\
+\hline
+House Improvements & 15\% \\
+\hline
+Research and Development & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+Accumulated & 10\% \\
+\hline
+\end{tabular}
+\end{center}
+
+The suggested total operational budget is \$8064.
+This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+
+\asubsubsection{Expenditure Approval}
+All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
+A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+\\* \\*
+If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+\\*\\*
+For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+\\* \\*
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+This amount is to be directly subtracted from the general CSH account.
+\\* \\*
+Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
+
+\asubsection{Operations of the Operational Communications Directorship}
+The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+It is a self-governing committee making decisions by a simply majority vote.
+Membership is composed of all Root Type Persons.
+
+\asubsubsection{Selection of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
+		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
+\end{enumerate}
+
+\asubsubsection{Qualifications of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
+	\item Candidates may be granted an exemption by current Root Type Persons.
+		Such an exemption may be withdrawn at any time by the current Root Type Persons.
+	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
+		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
+	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+\end{enumerate}
+
+\asubsubsection{Creation of Accounts}
+Root Type Persons have the authority to manage user accounts for House systems.
+Before members may receive an account they must:
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+\end{enumerate}
+
+\asubsubsection{Code of Conduct}
+The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+\\* \\*
+Members are bound to the Code of Conduct revision that they sign when initially creating their account.
+Members may sign a more recent revision of the Code of Conduct to update their agreement.
+\asubsubsubsection{Changes}
+The following process is used for making changes to the Code of Conduct document.
+\begin{enumerate}
+	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
+\end{enumerate}
+
 \asection{Qualifications}
@@
 
-% ARTICLE V - VOTING
+% ARTICLE VI - VOTING
 \article{Voting}
@@
 
-% ARTICLE VI - JUDICIAL
+% ARTICLE VII - JUDICIAL
 \article{Judicial}

### 2019-03-02 articles.tex
Allow the Secretary to do their job

--- 2019-03-01 articles.tex
@@
 \asection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
+Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, the House Secretary, and those with the express permission of the Executive Board.
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.

### 2019-03-04 articles.tex

@@
 \asection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, the House Secretary, and those with the express permission of the Executive Board.
+Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.

### 2019-03-31 articles.tex
Reference

@@
 % -This document must be ratified by the House (as per the Constitution),
+%  then printed, signed, notarized, and placed in the House filing cabinet
 %  if changes are to be officialized.
@@
 \asubsection{Active Membership Term}
-Active Membership shall last until the member: resigns or changes membership status.
+Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.
 
@@
 The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
+Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
+The Chairman may chair an immediate fifty percent vote \ref{\ref{Fifty Percent} to postpone the election by a specified time period with a spoken reason.
+The vote may not take place for elections for year end elections.
 
@@
 \item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
-\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
+\item The term of an officer will be abbreviated due to resignation, impeachment, failure of the evaluation process, or change in membership status.
 \item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
@@
 \asubsection{Vote Counters}
-The chairperson of the vote is a vote counter and will additionally select two other members to count votes.
+Vote Counters are the chairperson of the vote, and two randomly selected members.
 
@@
 The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
-\asubsection{Immediate Vote}
+\asubsection}
 \asubsubsection{Method of Vote}
@@
 This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
+
+% ARTICLE VII - TEMPORARY AMENDMENTS
+\article{Temporary Amendments}
+In the case that an amendment should be temporary, the amendment's changes should be listed here. 
+Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
+Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
+\asection{Changes to Evaluations}
+During the 2018-2019 period the following will supercede the text otherwise found in this document.
+\asubsection{Changes}
+\asubsubsection{Change of Packet Percentage}
+\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+During the described period, the percentage of required signatures in the Introductory Packet will be increased to 75\%. 
+\asubsubsection{Changes to Packet Times}
+Introductory Members will recieve \ref{The Introductory Packet} following the House Meeting or Evaluations Directorship meeting of the second week of each semester. 
+Each Introductory Member will submit their packet at the end of week 3. 
+\asubsubsection{Evaluation Period}
+During the described period, the \ref{The Introductory Process} will begin during the first week of each semester.
+The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period.
+Additionally, \ref{Introductory Evaluation} occurs between the sixth and tenth week of each semester. 
+\subsubsection{Referendum}
+During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
 \end{document}

### 2019-03-31 articles.tex
Max's Edit

@@
 \asection{Resignations}
+\asection{Resignations}
 An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
@@
 Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
-The Chairman may chair an immediate fifty percent vote \ref{\ref{Fifty Percent} to postpone the election by a specified time period with a spoken reason.
-The vote may not take place for elections for year end elections.
+To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.
 
@@
 The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
-\asubsection}
+\asubsection{Immediate Vote}
 \asubsubsection{Method of Vote}

### 2019-04-09 constitution.tex
Replaced all instances of Chairman with Chairperson

@@
 
-% Define the external document to be bylaws for cross referencing purposes
-\externaldocument{bylaws}[https://github.com/ComputerScienceHouse/Constitution/blob/master/bylaws.pdf?raw=true]
-
 % Title page information
@@
 \newcommand{\asubsection}[1]{\subsubsection{#1} \label{#1}}
-\renewcommand{\thesection}{Article \Roman{section}}
-\renewcommand{\thesubsection}{Section \arabic{section}.\Alph{subsection}}
+\renewcommand{\thesection}{\Roman{section}}
+\renewcommand{\thesubsection}{\arabic{section}.\Alph{subsection}}
 \renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}
+\titleformat{\section}{\normalfont\Large\bfseries}{Article \thesection}{1em}{}
+\titleformat{\subsection}{\normalfont\large\bfseries}{Section \thesubsection}{1em}{}
 
-% % Adding an \asubsubsection -- I feel dirty
-\setcounter{secnumdepth}{5}
+% Adding an \asubsubsection -- I feel dirty
+%\setcounter{secnumdepth}{5}
 \newcommand{\asubsubsection}[1]{\paragraph{#1} \label{#1}}
 \renewcommand{\theparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}}
+
+% Adding \a(sub){3,4}section during merge of bylaws and articles -- I feel _really_ dirty
+\setcounter{secnumdepth}{7}
+\setcounter{tocdepth}{7}
+\newcommand{\asubsubsubsection}[1]{\parindent=0em\subparagraph{#1} \label{#1}}
+\renewcommand{\thesubparagraph}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}.\arabic{subparagraph}}
+
+\newcounter{asubsubsubsubsection}[subparagraph]
+\renewcommand{\theasubsubsubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}.\Alph{paragraph}.\arabic{subparagraph}.\Alph{asubsubsubsubsection}}
+\newcommand{\asubsubsubsubsection}[1]{\parindent=0em\refstepcounter{asubsubsubsubsection}\par\textbf{\theasubsubsubsubsection\hspace{1em}#1 \label{#1}}}
 
@@
 It is reviewed annually by the Department of Residence Life.
-The House Constitution is comprised of two sections: articles and by-laws.
-Articles define the major aspects of the House.
-A by-law may expand on rules outlined in an article, but they must never contradict a Constitutional article.
 
-\asubsection{ Non-Semantic Changes}
-Any non-semantic change to the Constitution should be presented to the House for discussion.
-After the discussion an immediate House vote is taken.
-A quorum of fifty percent of the number of all House members eligible to vote must be present in order for the vote to be official.
-A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.
+\asubsection{Non-Semantic Changes}
+There are two methods for non-semantic change to the Constitution.
+A Maintainer may approve any proposed change that does not affect the meaning of the document.
+Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
+A quorum of fifty percent of the Total Number of Possible Votes is required for passage.
 
@@
 The ballots are collected for a minimum of a forty-eight hour period.
-A quorum of two-thirds of the number of all House members eligible to vote must cast ballots for the vote to be official.
+A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
 A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
 The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
-There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official.
+There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
 A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
 
-% ARTICLE III - MEMBERSHIP
+\asection{Maintainers}
+
+\asubsection{Maintainer Qualifications}
+Maintainers must be Active or Alumni in good standing.
+
+\asubsection{Maintainer Expectations}
+Maintainers are expected to:
+\begin{itemize}
+	\item Review changes to the Constitution for grammar, spelling, and internal consistency
+	\item Keep a public record of changes to the Constitution
+	\item Participate in discussion of proposals
+	\item Facilitate the creation of new changes to the Constitution by other members
+	\item Be knowledgeable about the Constitution
+\end{itemize}
+Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.
+
+\asubsection{Maintainer Resignations}
+Maintainers may resign at any time by notifying the current Executive Board and Maintainer group.
+
+\asubsection{Maintainer Term}
+Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
+If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
+
+\asubsection{Maintainer Selection}
+Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
+The Executive Board may choose to approve or reject the nomination by Simple Majority vote.
+
+% ARTICLE III - GENERAL OPERATIONS OF THE HOUSE
+\article{General Operations of the House}
+\asection{Standard Operating Session}
+The Standard Operating Session for Computer Science House is during the twenty-eight weeks of Fall and Spring semesters.
+The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
+Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.
+
+% ARTICLE IV - MEMBERSHIP
 \article{Membership}
@@
 \begin{description}
-	\item[Qualifications:] What qualifications an applicant needs to apply.
-	\item[Selection:] The process by which an applicant gains membership.
-	\item[Expectations:] The duties and responsibilities of House members.
-	\item[Privileges:] The benefits offered to House members.
-	\item[Evaluations:] The process by which a member is reviewed and assessed.
-	\item[Resignations:] The process by which a member terminates House membership.
-	\item[Term:] The length of time the membership lasts.
+	\item[Qualifications:] What qualifications an applicant needs to apply
+	\item[Selection:] The process by which an applicant gains membership
+	\item[Expectations:] The duties and responsibilities of House members
+	\item[Privileges:] The benefits offered to House members
+	\item[Evaluations:] The process by which a member is reviewed and assessed
+	\item[Leave of Absence:] The process by which a member may leave House for a period of time
+	\item[Resignations:] The process by which a member terminates House membership
+	\item[Term:] The length of time the membership lasts
 \end{description}
@@
 \asubsection{Introductory Membership Evaluations}
-Introductory members are evaluated on their performance during the introductory period. The introductory evaluation process is described in \ref{Introductory Evaluation}.
+Introductory members are evaluated on their performance during the introductory period.
+The introductory evaluation process is described in \ref{Introductory Evaluation}.
+\asubsection{Introductory Membership Leave of Absence}
+After completion of the Introductory Packet, an Introductory member may request a leave of absence through the process described in \ref{Leave of Absence}.
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
+Introductory members may resign by submitting the request for termination of membership to the Chairperson, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
@@
 \end{itemize}
+Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
+Exceptions may be made at the discretion of the Evaluations Director.
 \asubsection{Active Membership Evaluations}
@@
 Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+\asubsection{Active Membership Leave of Absence}
+An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
+For the duration of an absence, a member:
+\begin{itemize}
+	\item Forfeits their right to vote
+	\item Does not count towards quorum
+	\item Will not be required to attend House Meeting
+\end{itemize}
 \asubsection{Active Membership Resignations}
-A Active member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.
+An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
+Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
 \asubsection{Active Membership Term}
-Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.
+Active Membership shall last until the member: resigns or changes membership status.
 
@@
 \asubsection{Alumni Membership Selection}
-Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
+Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
 \\*\\*
-Active members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to EBoard for an exemption based on their circumstances. 
+Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing.
+This may be appealed to the Executive Board in order to pursue a different outcome.
 \asubsection{Alumni Membership Expectations}
@@
 \asubsection{Honorary Membership Resignations}
-An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
+An Honorary Member may resign by submitting in writing the reason for resignation to the Chairperson.
+The resignation will be read at the following House Meeting and become effective at that time.
 \asubsection{Honorary Membership Term}
@@
 \asubsection{Advisory Membership Resignations}
-An Advisor may resign by submitting in writing the reason for resignation to the Chairman. The resignation will be read at the following House Meeting and become effective at that time.
+An Advisor may resign by submitting in writing the reason for resignation to the Chairperson.
+The resignation will be read at the following House Meeting and become effective at that time.
 \asubsection{Advisory Membership Term}
@@
 
-% ARTICLE IV - EXECUTIVE BOARD
+\asection{Leave of Absence}
+A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
+House will also help to reacclimate any returning member back to the culture of House upon their return.
+Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.
+A member is also allowed to be physically present and also be on a leave of absence.
+\asubsection{Leave of Absence Request}
+A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
+The request is then given to a staff member of Residence Life, excluding student employees, for approval.
+A leave of absence start date can be backdated.
+At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
+\asubsection{Leave of Absence Duration}
+A leave of absence can be granted for up to the length of one semester.
+\asubsection{Leave of Absence Extension}
+A leave of absence can be extended by submitting a new request.
+\asubsection{Leave of Absence Return}
+A member may return from a leave of absence whenever they choose to.
+When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
+\asubsection{Modified Evaluations}
+A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
+\asubsection{Leave of Absence for an Executive Board Member}
+The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
+Upon returning, the member may assume their position and the interim director is removed.
+If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amongst the Executive Board to require a resignation from the Member.
+
+% ARTICLE V - EXECUTIVE BOARD
 \article{Executive Board}
@@
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
-It is composed of the seven permanent directors and the Chairman.
+It is composed of the seven permanent directors and the Chairperson.
 \\*\\*
@@
 \begin{itemize}
+	\item Chairperson
 	\item House Secretary
-	\item Ad Hoc Directors
+	\item Ad Hoc Director(s)
 \end{itemize}
 \asection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
+Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.
+However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.
 
@@
 \begin{enumerate}
-	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
-	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
-	\item To report pertinent information to House members at the following House Meeting.
-	\item To maintain records of the goals defined by each previous Executive Board.
-	\item To act as a Judicial Board as defined in \ref{Judicial}.
-	\item To review major projects, as defined in \ref{Expectations of House Members},  presented to them by the Evaluations director.
-	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
-	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
-	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
+	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
+	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
+	\item To report pertinent information to House members at the following House Meeting
+	\item To maintain records of the goals defined by each previous Executive Board
+	\item To act as a Judicial Board as defined in \ref{Judicial}
+	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
+	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
+	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board
+	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
+	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}
+		The constitution should remain up to date with current practices.
 \end{enumerate}
 
-\asubsection{Responsibilities of the Chairman}
+\asubsection{Responsibilities of the Chairperson}
 \begin{enumerate}
-	\item To preside over Executive Board and House Meetings.
-	\item To exercise general supervision over the operations of the Executive Board.
-	\item To exercise general supervision over regular House activities.
-	\item To act as a liaison to the academic and administrative departments at RIT.
-	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
-	\item To cast tie-breaking vote in a split decision in an Executive Board vote.
+	\item To preside over Executive Board and House Meetings
+	\item To exercise general supervision over the operations of the Executive Board
+	\item To exercise general supervision over regular House activities
+	\item To act as a liaison to the academic and administrative departments at RIT
+	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
+	\item To cast tie-breaking vote in a split decision in an Executive Board vote
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Evaluations Meetings.
-	\item To exercise general supervision over Evaluations operations.
-	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members.
-	\item To oversee the Semi-Annual Evaluations of current House members.
-	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency.
-	\item To act in collaboration with the Chairman and an additional Executive Board member who is chosen by a simple majority vote among the members of the Executive board as a judicial board for any initial ruling on the interpretation of the House Constitution, House document, or action taken by the House.
-	\item To act as a part of a Judicial Board as defined in \ref{Judicial}.
-	\item To prepare the House for Open Houses, tours, and special events.
+	\item To preside over Evaluations Meetings
+	\item To exercise general supervision over Evaluations operations
+	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
+	\item To oversee the Semi-Annual Evaluations of current House members
+	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
+	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
+	\item To prepare the House for Open Houses, tours, and special events
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Social Meetings. House members are encouraged to bring ideas for social events to the meetings for discussion.
-	\item To exercise general supervision over Social operations.
-	\item To oversee the organization, initiation, and execution of House activities and events.
-	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year.
+	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
+	\item To exercise general supervision over Social operations
+	\item To oversee the organization, initiation, and execution of House activities and events
+	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Financial Meetings. House members are encouraged to bring ideas for fund-raising activities to the meetings for discussion.
-	\item To supervise financial administrators and transactions involving house projects.
-	\item To maintain financial and inventory records of House capital and assets.
-	\item To plan and enforce a House budget.
-	\item To oversee House finances and generation of House funds.
-	\item To publish a semesterly House financial statement.
-	\item To supervise the collection of semesterly House dues.
-	\item To oversee the planning and execution of fundraising events.
+	\item To preside over Financial Meetings in which House members are encouraged to bring ideas for fund-raising activities
+	\item To supervise financial administrators and transactions involving house projects
+	\item To maintain financial and inventory records of House capital and assets
+	\item To plan and enforce a House budget
+	\item To oversee House finances and generation of House funds
+	\item To publish a semesterly House financial statement
+	\item To supervise the collection of semesterly House dues
+	\item To oversee the planning and execution of fundraising events
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Research and Development Meetings. House members are encouraged to bring ideas for projects to the meetings for discussion.
-	\item To exercise general supervision over Research and Development operations.
-	\item To oversee the planning, organization and construction of technical projects for the House's benefit.
-	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment.
-	\item To provide seminars and tutorials to educate House members in technical areas.
+	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
+	\item To exercise general supervision over Research and Development operations
+	\item To oversee the planning, organization and construction of technical projects for the House's benefit
+	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
+	\item To provide seminars and tutorials to educate House members in technical areas
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To ensure that minutes are recorded and posted for Executive Board Meetings.
-	\item To ensure that minutes are recorded and posted for House Meetings.
-	\item To oversee the maintenance of Executive Board records and documents.
-	\item To provide administrative assistance to the Executive Board.
-	\item To oversee the maintenance of the Activities Information Centers.
-	\item To record all votes cast during House Meetings and Open Executive Board Meetings.
+	\item To ensure that minutes are recorded and posted for Executive Board Meetings
+	\item To ensure that minutes are recorded and posted for House Meetings
+	\item To oversee the maintenance of Executive Board records and documents
+	\item To provide administrative assistance to the Executive Board
+	\item To record all votes cast during House Meetings and Open Executive Board Meetings
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Ad-Hoc Directorships are responsible for the task for which they were created.
-	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director.
+	\item Ad-Hoc Directorships are responsible for the task for which they were created
+	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director
+\end{enumerate}
+
+\asection{Operations}
+\asubsection{Operations of the Evaluations Directorship}
+\asubsubsection{The Introductory Process}
+The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+\asubsubsubsection{The Evaluation Period}
+The Process will begin between the first and fourth week of each semester, then last between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
+\asubsubsubsection{The Introductory Packet}
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+\begin{itemize}
+	\item Alumni members
+	\item Honorary members
+	\item Advisory members
+\end{itemize}
+At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+\asubsubsubsection{Expectations of an Introductory Member}
+Before the end of the Process, an Introductory Member is expected to:
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Complete the Introductory Packet
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
+\end{itemize}
+
+\asubsubsubsection{Introductory Evaluation}
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
+Occurs between the sixth and tenth week of each semester.
+\asubsubsubsubsection{Introductory Voting}
+On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Introductory Outcomes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
+		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+		Each conditional consists of a set of additional requirements a deadline for completing them.
+		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+		A conditional member who does not meet these additional requirements forfeits membership.
+\end{enumerate}
+\asubsubsection{Selection Processes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\asubsubsubsection{Selection Process for Students Attending RIT for at Least One Semester}
+\begin{enumerate}
+	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
+	\item The application materials are then reviewed at an Evaluations meeting.
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member must also pay dues.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsubsection{Selection Process for First Semester and Entering RIT Students}
+\begin{enumerate}
+	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
+		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
+	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
+		An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member must also pay dues.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsubsection{Selection Process for Honorary Members}
+\begin{enumerate}
+	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
+	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
+	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
+	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
+		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
+	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
+\end{enumerate}
+\asubsubsubsection{Selection Process for Advisory Members}
+\begin{enumerate}
+	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members.
+		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
+	\item After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.
+	\item A discussion of the candidates will be held at the following House meeting.
+	\item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty Percent}.
+		Voting must remain open for a minimum of a forty-eight hour period.
+	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
+\end{enumerate}
+
+\asubsubsection{Evaluations Processes}
+During the academic year, a House member is evaluated by the Membership Evaluation.
+The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+Semi-Annual Evaluations Meetings are open only to current Active Members.
+All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
+\\* \\*
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
+It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
+\asubsubsubsection{Housing Points}
+All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
+\asubsubsubsection{Membership Evaluation}
+The Membership Evaluation process occurs once per academic year.
+It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+\asubsubsubsubsection{Voting}
+A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
+All Active Members will be held to the requirements and evaluated unless they have received an exemption from the Executive Board prior to the event.
+These requirements are detailed in Article VI under expectations for each category of membership.
+These requirements must be completed before the Membership Evaluation occurs.
+A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Outcomes}
+Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+\\* \\*
+If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+In either case, the member forfeits their ability to be included on the following year’s roster.
+\\* \\*
+A member may be given a conditional to complete as a means of making up for missing requirements.
+A conditional may be proposed by any member present at the Evaluation.
+If the conditional is approved by the Evaluations Director, it is then voted on by House.
+Each conditional consists of a set of additional requirements a deadline for completing them.
+When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+A conditional member who does not meet these additional requirements will have failed the evaluation.
+\asubsubsubsection{Appeals Process}
+If a member disagrees with the outcome of any evaluation, (e.g.
+is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+\\* \\*
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
+
+\asubsubsection{Expectations of House Members}
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+\\* \\*
+The member must participate significantly in at least one major project during the academic year.
+The member is required to submit a description for this major project to the Executive Board for approval.
+As an option to this requirement, the member may instead assist on a large number of House activities and projects.
+However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
+This participation will be evaluated by the Executive Board.
+
+\asubsubsection{Housing Status}
+All Active and Introductory Members have a housing status.
+This status indicates their right to priority housing on the floor.
+Any Alumni Member in good standing will maintain their previous On Floor status upon a return to Active membership.
+\asubsubsubsection{On-Floor Status}
+Members with On-Floor status are eligible to live on the floor.
+To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
+The Evaluations Director will then bring them up for vote at the next meeting.
+\asubsubsubsection{Off-Floor Status}
+Members with Off-Floor status do not have the right to live on the floor.
+They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
+
+\asubsubsection{Housing Priority System}
+The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
+The member with top priority is the member with on-floor status and the most Housing Priority Points.
+Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+\\* \\*
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
+\asubsubsubsection{Single Room Assignments}
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
+If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
+This process continues until a member selects to move into the single room.
+Once in a single room, a House member retains the assignment until voluntarily giving it up.
+It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
+\asubsubsubsection{Double Rooms as Single rooms}
+During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
+It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
+This only applies if there is a totally vacant room.
+
+\asubsection{Operations of the Financial Directorship}
+\asubsubsection{Amount of House Dues}
+The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
+\asubsubsection{Collection of House Dues}
+The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected during this period as well by the Financial Director.
+For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+\\*\\*
+If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
+If the Financial Director deems their situation appropriate, they may grant an extension for payment.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
+If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
+If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
+\\*\\*
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+After this date, dues collection is suspended until the start of the next academic year.
+\asubsubsection{Breakdown of Dues for Directorship Budgets}
+\begin{center}
+\begin{tabular}[c]{l c}
+Directorship Name & Percentage of Dues \\
+\hline
+\hline
+Operational Communications & 20\% \\
+\hline
+Evaluations \& Selections & 5\% \\
+\hline
+House History & 10\% \\
+\hline
+House Improvements & 15\% \\
+\hline
+Research and Development & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+Accumulated & 10\% \\
+\hline
+\end{tabular}
+\end{center}
+
+The suggested total operational budget is \$8064.
+This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+
+\asubsubsection{Expenditure Approval}
+All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
+A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+\\* \\*
+If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+\\*\\*
+For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+\\* \\*
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+This amount is to be directly subtracted from the general CSH account.
+\\* \\*
+Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
+
+\asubsection{Operations of the Operational Communications Directorship}
+The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+It is a self-governing committee making decisions by a simply majority vote.
+Membership is composed of all Root Type Persons.
+
+\asubsubsection{Selection of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
+		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
+\end{enumerate}
+
+\asubsubsection{Qualifications of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
+	\item Candidates may be granted an exemption by current Root Type Persons.
+		Such an exemption may be withdrawn at any time by the current Root Type Persons.
+	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
+		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
+	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+\end{enumerate}
+
+\asubsubsection{Creation of Accounts}
+Root Type Persons have the authority to manage user accounts for House systems.
+Before members may receive an account they must:
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+\end{enumerate}
+
+\asubsubsection{Code of Conduct}
+The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+\\* \\*
+Members are bound to the Code of Conduct revision that they sign when initially creating their account.
+Members may sign a more recent revision of the Code of Conduct to update their agreement.
+\asubsubsubsection{Changes}
+The following process is used for making changes to the Code of Conduct document.
+\begin{enumerate}
+	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
 \end{enumerate}
@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
+\asubsection{Qualifications to be the Chairperson, Evaluations Director}
 \begin{enumerate}
-	\item Candidates must be Active Members during the term of office.
-	\item Candidates must have at least one full semester of House membership as an Active Member.
-	\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
+	\item Candidates must be Active Members during the term of office
+	\item Candidates must reside on floor during the term of office
+	\item Candidates must have at least one full semester of House membership as an Active Member
+	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
+\end{enumerate}
+\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
+\begin{enumerate}
+	\item Candidates must be Active Members during the term of office
+	\item Candidates must have at least one full semester of House membership as an Active Member
+	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
+	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
 	\item Candidates must be a current Active Member.
-	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
+	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
 \end{enumerate}
 
-\asubsection{Qualifications to be the House Secretary on an Ad Hoc Director}
+\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
 \begin{enumerate}
-\item
- Candidates must be Active Members.
+\item Candidates must be Active Members
 \end{enumerate}
@@
 Each different nomination must be a separate entry on the election ballot.
+Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to single or dual directorship.
 
@@
 \end{itemize}
-\asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director}
+\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
 \begin{enumerate}
@@
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Balloted Vote}.
-	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting.
-A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official.
-All winners are notified and asked to accept or decline their election.
-Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.
-\end{enumerate}
-\asubsection{Selection of the Research and Development Director, House Secretary}
-\begin{enumerate}
-	\item  The opening of the Executive Board position is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-A House member may nominate any House member.
-	\item The candidates meeting the qualifications of the office that were nominated for, will be notified of their nomination.
-Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-A list of all nominees who have accepted their nominations will be posted shortly thereafter.
-	\item Each candidate will be given an equal amount of time before the Executive Board to present their platforms of candidacy.
-This Executive Board Meeting is open only to the Executive Board Members and House members with explicit invitation from the Executive Board.
-	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the office in discussion, in which case the member is absent and their vote is abstained.
-After each candidate for an office has been presented and discussed, a simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine the selection of candidates.
-	\item All winners are notified and asked to accept or decline their selection.
-Any office whose winner declines the selection shall remain vacant and a new selection process shall begin for that office.
+	\item At the end of the voting period, the Chairperson will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
+	\item The winners are determined via the process described in \ref{Alternative Vote}.
+		A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
+		All winners are notified of their election.
+		If the position is currently vacant, the winner immediately assumes office.
+		If not, the winner will assume office at the end of the current term (\ref{Term}).
+		Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Root Type Persons Representative shall be chosen by the current Root Type Persons.
+	\item A candidate for the Operational Communications Directorship shall be chosen by the current Root Type Persons.
+	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
+	\item The candidate is presented to the Executive Board for approval.
+		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
+		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
 \end{enumerate}
@@
 \end{enumerate}
+\asubsection{Selection of the House Secretary}
+The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary.
+The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.
 
 \asection{Resignations}
-An Executive Board Member may resign by submitting in writing the reason for resignation to the House Chairman.
+An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
 The resignation will be read at the following House Meeting and become effective at that time.
-The office will become vacant and the selection process for a new member will begin at that time.
-The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman’s discretion until the new member takes office.
+The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
+
+\asection{Appointment of an Interim Director}
+The duties and responsibilities of a vacated office are assumed by the Chairperson or by an Active member that is appointed at the Chairperson's discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
@@
 		Votes shall be collected and counted as described in \ref{Balloted Vote}.
-	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official.
-A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from oce.
+	\item A quorum of two-thirds of the Total Number of Possible Votes is necessary for the vote to be official.
+		A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
 		If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
@@
 		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
+	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of the Executive Board.
 \end{enumerate}
@@
 \item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
-\item The term of an officer will be abbreviated due to resignation, impeachment, failure of the evaluation process, or change in membership status.
+\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
 \item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
-\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves. When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
+\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
+	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
 \end{enumerate}
@@
 Decisions made by the Executive Board may be appealed and overturned.
-To initiate an appeal, a Petition of Appeal must be presented to the Chairman affixed with signatures from one third of Active Members of house, or three voting members of Executive Board.
-After the petition has been presented, during the following House meeting, a discussion will be held where one petitioner and one Executive Board member will each make their case.
-After hearing from both representatives, there will be an Immediate Two-Thirds vote as defined in \ref{Two-Thirds} to confirm the appeal and thereby overturn the decision.
-Any decision that is overturned must be reevaluated by the Executive Board.
+To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
+After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
+If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
 
-% ARTICLE V - VOTING
+% ARTICLE VI - VOTING
 \article{Voting}
@@
 \asubsection{Vote Counters}
-Vote Counters are the chairperson of the vote, and two randomly selected members.
+The chairperson of the vote is a vote counter and will additionally select two other members to count votes.
 
 \asection{Types of Voting}
+\asubsection{Alternative Vote}
+\asubsubsection{Method of Vote}
+Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
+A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
+At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period.
+The Vote Counters then tally the results.
+
+Voters rank the options by placing a '1' by their first choice, a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of options.
+
+\asubsubsection{Voting Period}
+For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
+For any other type of vote, the voting period must be at least twenty-four (24) hours.
+The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
 \asubsection{Balloted Vote}
@@
 \asubsection{Three Tiered}
-When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest of highest option will only pass is the votes cast for that selection exceeds fifty percent of the Total Number of Votes Cast.
-If neither the highest or lowest selection reaches fifty percent, the middle option will then automatically be passed.
+When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest or highest option will only pass if the votes cast for that selection exceed fifty percent of the Total Number of Votes Cast.
+If neither the highest or lowest selection exceeds fifty percent, the middle option will then automatically be passed.
 In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.
+
+\asubsection{Alternative}
+The winning option is selected outright if it gains more than half the votes cast as a first preference.
+If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
+This process continues until one option has half of the votes cast and is elected.
 
@@
 If only one option may pass, then the vote must be recast or tabled at the discretion of the person chairing the vote.
-In the event of a tie in an Executive Board vote, the Chairman may cast the tie-breaking vote.
+In the event of a tie in an Executive Board vote, the Chairperson may cast the tie-breaking vote.
 
-% ARTICLE VI - JUDICIAL
+% ARTICLE VII - JUDICIAL
 \article{Judicial}
@@
 \asection{Formation of a Judicial Board}
-A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
-If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board,  they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
+A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
+If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
 \asection{Judicial Investigation}
@@
 \asection{Judicial Ruling}
-The Judicial Board may present an official ruling following the Judicial Investigation. This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
-
+The Judicial Board may present an official ruling following the Judicial Investigation.
+This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
 \end{document}

### 2019-04-20 bylaws.tex
Spring is Objective

--- 2019-03-01 bylaws.tex
@@
 \end{itemize}
+At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
 \bsubsection{Expectations of an Introductory Member}
@@
 \bsubsubsection{Voting}
-A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
-All Active Members will be held to the requirements and evaluated unless they have received an exemption from the Executive Board prior to the event.
+A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum objective requirements in order to continue as an Active Member in the following year.
+Any Active Member who has met all the minimum objective requirements will be added to a batch that will not be voted on and no member can be pulled.
+This batch will not be eligable to be voted on and all members in this batch will pass the membership evaluations in the beginning of the meeting.
+
+All Active Members will be held to the requirements and evaluated objectively unless they have received an exemption from the Executive Board prior to the event.
 These requirements are detailed in Article V under expectations for each category of membership.

### 2019-04-20 bylaws.tex
Clean up

@@
 A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum objective requirements in order to continue as an Active Member in the following year. 
-Any Active Member who has met all the minimum objective requirements will be added to a batch that will not be voted on and no member can be pulled.
-This batch will not be eligable to be voted on and all members in this batch will pass the membership evaluations in the beginning of the meeting.
-
+Any Active Member who has met all the minimum objective requirements as defined in Bylaw \ref{Expectations of House Members} will be added to a Batch Vote that will not be voted on and no member can be pulled.
+The alternative for pulling an member is an appeals process before the Membership Evaluation occurs. 
+All members in this batch will pass the membership evaluations at the beginning of the meeting. 
 All Active Members will be held to the requirements and evaluated objectively unless they have received an exemption from the Executive Board prior to the event.
-These requirements are detailed in Article V under expectations for each category of membership.
+These requirements are detailed Bylaw \ref{Expectations of House Members} for membership.
 These requirements must be completed before the Membership Evaluation occurs.
@@
 House may choose any of the Outcomes for each member.
+
 \bsubsubsection{Outcomes}

### 2019-04-20 bylaws.tex
Separate Objectivity
Shorten and clean up Spring Evals Voting
Update to match current practice
Capitalise all the defined things

--- 2019-04-20 bylaws.tex
@@
 \bsubsubsection{Voting}
-A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum objective requirements in order to continue as an Active Member in the following year.
-Any Active Member who has met all the minimum objective requirements will be added to a batch that will not be voted on and no member can be pulled.
-This batch will not be eligable to be voted on and all members in this batch will pass the membership evaluations in the beginning of the meeting.
+All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
+Evaluations will hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
+Exceptions to the requirements may be made, and House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
+These requirements must be completed before the Membership Evaluation occurs.
+A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
 
-All Active Members will be held to the requirements and evaluated objectively unless they have received an exemption from the Executive Board prior to the event.
-These requirements are detailed in Article V under expectations for each category of membership.
-These requirements must be completed before the Membership Evaluation occurs.
-A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-Neither absentee nor proxy votes are allowed.
-House may choose any of the Outcomes for each member.
 \bsubsubsection{Outcomes}

### 2019-04-20 bylaws.tex
Automatically pass All Green at Spring Evals

@@
 \bsubsubsection{Voting}
+Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
 All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.

### 2019-04-21 articles.tex
Cool
Simplify the requirements for nominations
By current practice, we don't restrict nomination only to qualified
members, so we should update that, so we can bring up candidates and
determine whether their merit should override the qualifications of a
seat.

--- 2019-03-04 articles.tex
@@
 	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
-	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.
+		Any House member may nominate any member or pair of members where appropriate for a Directorship.
+	\item The candidates will be notified of their nomination.
 		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
@@
 	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
-		The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.
+		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
@@
 		If not, the winner will assume office at the end of the current term (\ref{Term}).
-		Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
+		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
 \end{enumerate}

### 2019-04-22 articles.tex
Chairman -> Chair

@@
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
+Introductory members may resign by submitting the request for termination of membership to the Chari, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
@@
 \asubsection{Active Membership Resignations}
-An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
+An Active member may resign by submitting, in writing, the reason for resignation to the Chair, or Evaluations Director.
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
@@
 \asubsection{Honorary Membership Resignations}
-An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman.
+An Honorary Member may resign by submitting in writing the reason for resignation to the Chair.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 \asubsection{Advisory Membership Resignations}
-An Advisor may resign by submitting in writing the reason for resignation to the Chairman.
+An Advisor may resign by submitting in writing the reason for resignation to the Chair.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
-It is composed of the seven permanent directors and the Chairman.
+It is composed of the seven permanent directors and the Chair.
 \\*\\*
@@
 \begin{itemize}
-	\item Chairman
+	\item Chair
 	\item House Secretary
@@
 \asection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
+Closed Executive Board Meetings are open only to the Chair, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.
+However, the Chair and at least two-thirds of the Voting Members must be present for the meeting to be called.
 
@@
 
-\asubsection{Responsibilities of the Chairman}
+\asubsection{Responsibilities of the Chair}
 \begin{enumerate}
@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairman, Evaluations Director}
+\asubsection{Qualifications to be the Chair, Evaluations Director}
 \begin{enumerate}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member
-	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected
+	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chair, should they be elected
 \end{enumerate}
@@
 \end{itemize}
-\asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
+\asubsection{Selection of the Chair, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
 \begin{enumerate}
 	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-		Any House member may nominate any member or pair of members where appropriate for a Directorship.
-	\item The candidates will be notified of their nomination.
+		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
+	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.
 		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
@@
 	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
-		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
+		The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
+	\item At the end of the voting period, the Chair will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
 	\item The winners are determined via the process described in \ref{Alternative Vote}.
@@
 		If not, the winner will assume office at the end of the current term (\ref{Term}).
-		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
+		Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
 \end{enumerate}
@@
 \asection{Resignations}
-An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
+An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chair.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 \asection{Appointment of an Interim Director}
-The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by the Chair or by an Active member that is appointed at the Chair's discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
@@
 If only one option may pass, then the vote must be recast or tabled at the discretion of the person chairing the vote.
-In the event of a tie in an Executive Board vote, the Chairman may cast the tie-breaking vote.
+In the event of a tie in an Executive Board vote, the Chair may cast the tie-breaking vote.
 
@@
 \asection{Formation of a Judicial Board}
-A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
-If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
+A Judicial Board is made up of the Chair, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
+If either the Chair or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
 \asection{Judicial Investigation}

### 2019-04-22 articles.tex
Correct spelling of 'Chair'

@@
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chari, or Evaluations Director in writing before the completion of the introductory process.
+Introductory members may resign by submitting the request for termination of membership to the Chair, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}

### 2019-04-22 articles.tex
Differentiate Chair from chairperson of the vote
Standardises the use of 'chairperson of the vote' when referring to the
chair of a specific vote and not the Chair of House

--- 2019-04-21 articles.tex
@@
 There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
-Ad-hoc directorships are created on an as-needed basis.
+Ad-Hoc directorships are created on an as-needed basis.
 They are generally very task oriented and are chaired by a House member.
@@
 	\item House Secretary
-	\item Ad Hoc Director(s)
+	\item Ad-Hoc Director(s)
 \end{itemize}
@@
 
-\asubsection{Responsibilities of Ad Hoc Directorships}
+\asubsection{Responsibilities of Ad-Hoc Directorships}
 \begin{enumerate}
@@
 
-\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
+\asubsection{Qualifications to be the House Secretary or an Ad-Hoc Director}
 \begin{enumerate}
@@
 	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-		Any House member may nominate any member or pair of members where appropriate for a Directorship.
-	\item The candidates will be notified of their nomination.
+		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
+	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.
 		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
@@
 	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
-		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
+		The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
@@
 \end{enumerate}
-\asubsection{Selection of Ad Hoc Directors}
+\asubsection{Selection of Ad-Hoc Directors}
 \begin{enumerate}
-	\item When the Executive Board or a group of House members feels an Ad-hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
+	\item When the Executive Board or a group of House members feels an Ad-Hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
 	\item When the Ad-Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
@@
 \item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
-\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
-	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
+\item When the task of an Ad-Hoc Directorship has been completed, the directorship dissolves.
+	When an Ad-Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
 \end{enumerate}

### 2019-04-23 bylaws.tex
Allow Evaluations Appeals
This updates to current practice, and allows all evaluations decisions
to be appealed.

--- 2019-04-20 bylaws.tex
@@
 \end{enumerate}
+\bsubsection{Appeals Process}
+If a member disagrees with the outcome of any evaluation, (e.g.
+is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+\\* \\*
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
 \bsection{Selection Processes}
@@
 \bsubsubsection{Voting}
-A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum objective requirements in order to continue as an Active Member in the following year. 
-Any Active Member who has met all the minimum objective requirements as defined in Bylaw \ref{Expectations of House Members} will be added to a Batch Vote that will not be voted on and no member can be pulled.
-The alternative for pulling an member is an appeals process before the Membership Evaluation occurs. 
-All members in this batch will pass the membership evaluations at the beginning of the meeting. 
-All Active Members will be held to the requirements and evaluated objectively unless they have received an exemption from the Executive Board prior to the event.
-These requirements are detailed Bylaw \ref{Expectations of House Members} for membership.
+A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
+All Active Members will be held to the requirements and evaluated unless they have received an exemption from the Executive Board prior to the event.
+These requirements are detailed in Article V under expectations for each category of membership.
 These requirements must be completed before the Membership Evaluation occurs.
@@
 House may choose any of the Outcomes for each member.
-
 \bsubsubsection{Outcomes}

### 2019-07-31 membership-agreement.tex
Add combined membership agreement and code of conduct

\documentclass{article}
\usepackage{hyperref}
\usepackage{showkeys}
\usepackage{enumerate}

% Title page information
\title{
\textbf{Computer Science House}\\
Membership Agreement and Code of Conduct}
\author{}

% Last Modified Date
\newcommand{\datechanged}{Last Updated: \today}
\date{\datechanged}

% Fix margins
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}

\pagestyle{myheadings}
\markright{{\rm CSH Membership Agreement \hfill \datechanged \hfill Page }}

\begin{document}
\maketitle

\section*{Our Pledge}

In the interest of fostering an open and welcoming environment, we as
members of Computer Science House pledge to make membership and
participation in our community a harassment-free experience for everyone,
regardless of age, body size, disability, ethnicity, sex characteristics,
gender identity and expression, level of experience, education,
socio-economic status, nationality, personal appearance, race, religion,
or sexual identity and orientation. In the interest of being good
citizens in the wider RIT community, we also pledge to abide by the
\href{https://www.rit.edu/studentaffairs/studentconduct/code-conduct}
{RIT Student Code of Conduct} and uphold its values.

\section*{Our Standards}

Examples of behavior that contributes to creating a positive environment
include:

\begin{itemize}
    \item Using welcoming and inclusive language
    \item Being respectful of differing viewpoints and experiences
    \item Gracefully accepting constructive criticism
    \item Focusing on what is best for the community
    \item Showing empathy towards other community members
\end{itemize}

\begin{flushleft}
Examples of unacceptable behavior by participants include (but are not
limited to):
\end{flushleft}

\begin{itemize}
    \item The use of sexualized language or imagery and unwelcome sexual
          attention or advances
    \item Inflammatory behavior, insulting/derogatory comments, and personal
          or political attacks
    \item Public or private harassment
    \item Publishing others’ private information, such as a physical or
          electronic address, without explicit permission
\end{itemize}

\section*{Our Responsibilities}

Computer Science House’s Executive Board (E-board) is responsible for
clarifying the standards of acceptable behavior and are expected to take
appropriate and fair corrective action in response to any instances of
unacceptable behavior. E-Board has the right and responsibility to remove,
edit, or reject posts, comments, or other media that is not aligned to this
Code of Conduct from official CSH communication or collaboration platforms,
or to ban temporarily or permanently any member from these platforms for
other behaviors that they deem inappropriate, threatening, offensive, or
harmful.

\section*{Scope}

This Code of Conduct applies within all CSH spaces, and it also applies when
an individual is representing CSH or its community in public spaces. Examples
of representing CSH include using an official CSH e-mail address, posting via
an official social media account, or acting as an appointed representative at
an online or offline event. Representation of CSH may be further defined and
clarified by E-Board.

\section*{Enforcement}

Instances of abusive, harassing, or otherwise unacceptable behavior may be
reported by contacting CSH E-board at
\href{mailto:eboard@csh.rit.edu}{eboard@csh.rit.edu}. All complaints will
be reviewed and investigated and will result in a response that is deemed
necessary and appropriate to the circumstances. E-board is expected to
reasonably protect the privacy of the reporter of an incident, but may
escalate the report to res-life or other RIT faculty at their discretion.
Further details of specific enforcement policies may be posted separately.
Members who do not follow or enforce the Code of Conduct in good faith may
face temporary or permanent repercussions as determined by E-Board.

\section*{Attribution}

This Code of Conduct is adapted from the
\href{https://www.contributor-covenant.org/}{Contributor Covenant},
version 1.4, available at \\
\href{https://www.contributor-covenant.org/version/1/4/code-of-conduct.html}
{https://www.contributor-covenant.org/version/1/4/code-of-conduct.html} \\
For answers to common questions about this code of conduct, see
\href{https://www.contributor-covenant.org/faq}
{https://www.contributor-covenant.org/faq}.

\section*{Commitment}

I, \makebox[2.5in]{\hrulefill}, hereby agree to the following conditions for
membership in Computer Science House:

\begin{enumerate}
    \item I will abide by the qualifications and expectations of a member,
          as well as follow the general rules of the House, as outlined in the CSH
          Constitution for the entirety of my membership.
    \item I commit to making Computer Science House a friendly and welcoming
          community by embracing the values set forth in this Code of Conduct.
    \item I will abide by the guidelines and rules set forth in the CSH
          Computer Code of Conduct regarding CSH services and member privileges for
          the entirety of my membership.
    \item If I am to fail in the evaluations process, I will revoke my spot
          in the housing queue and on the housing board.
\end{enumerate}

I understand that should I violate any of the above conditions, I may be
subject to sanctions as outlined in the CSH Constitution.

\noindent
\begin{tabular}{ll}
\\[8ex]
\makebox[3.5in]{\hrulefill} & \makebox[2.5in]{\hrulefill}\\
Signature & Date\\
\end{tabular}

\end{document}

### 2019-08-01 membership-agreement.tex
Clarify that housing registration will not be revoked

@@
           the entirety of my membership.
-    \item If I am to fail in the evaluations process, I will revoke my spot
-          in the housing queue and on the housing board.
+    \item If I am to fail in the evaluations process, I understand that I will be
+          removed from any housing queue or board. If I am already registered to live
+          on CSH the following year, I understand my spot will not be revoked.
 \end{enumerate}

### 2019-09-16 articles.tex
Remove notarization reference
Merge the bylaws into the articles
Yeets bylaws.tex.

Resolves #147

@@
 %  changed.
-% -This document must be ratified by the House (as per the Constitution),
-%  then printed, signed, notarized, and placed in the House filing cabinet
-%  if changes are to be officialized.
+% -This document must be ratified by the House (as per the Constitution) if
+%  changes are to be officialized.
 
@@
 \providecommand{\RevisionInfo}{}
-% The xr package allows external references
-\usepackage{xr-hyper}
 \usepackage{hyperref}
@@
 
+\asection{Operations}
+\asubsection{Operations of the Financial Directorship}
+\asubsubsection{Amount of House Dues}
+The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
+\asubsubsection{Collection of House Dues}
+The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected during this period as well by the Financial Director.
+For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+\\*\\*
+If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
+If the Financial Director deems their situation appropriate, they may grant an extension for payment.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
+If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
+If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
+\\*\\*
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+After this date, dues collection is suspended until the start of the next academic year.
+\asubsubsection{Breakdown of Dues for Directorship Budgets}
+\begin{center}
+\begin{tabular}[c]{l c}
+Directorship Name & Percentage of Dues \\
+\hline
+\hline
+Operational Communications & 20\% \\
+\hline
+Evaluations \& Selections & 5\% \\
+\hline
+House History & 10\% \\
+\hline
+House Improvements & 15\% \\
+\hline
+Research and Development & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+Accumulated & 10\% \\
+\hline
+\end{tabular}
+\end{center}
+
+The suggested total operational budget is \$8064.
+This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+
+\asubsubsection{Expenditure Approval}
+All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
+A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+\\* \\*
+If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+\\*\\*
+For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+\\* \\*
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+This amount is to be directly subtracted from the general CSH account.
+\\* \\*
+Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
+
+% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
+\asubsection{Operations of the Evaluations Directorship}
+\asubsubsection{The Introductory Process}
+The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+\asubsubsubsection{The Evaluation Period}
+The Process will begin between the first and fourth week of each semester, then last between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
+\asubsubsubsection{The Introductory Packet}
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+\begin{itemize}
+	\item Alumni members
+	\item Honorary members
+	\item Advisory members
+\end{itemize}
+At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+\asubsubsubsection{Expectations of an Introductory Member}
+Before the end of the Process, an Introductory Member is expected to:
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Complete the Introductory Packet
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
+\end{itemize}
+
+\asubsubsubsection{Introductory Evaluation}
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
+Occurs between the sixth and tenth week of each semester.
+\asubsubsubsubsection{Voting}
+On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Outcomes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
+		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+		Each conditional consists of a set of additional requirements a deadline for completing them.
+		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+		A conditional member who does not meet these additional requirements forfeits membership.
+\end{enumerate}
+\asubsubsection{Selection Processes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\asubsubsubsection{Selection Process for Students Attending RIT for at Least One Semester}
+\begin{enumerate}
+	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
+	\item The application materials are then reviewed at an Evaluations meeting.
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member must also pay dues.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsubsection{Selection Process for First Semester and Entering RIT Students}
+\begin{enumerate}
+	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
+		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
+	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
+		An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member must also pay dues.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsubsection{Selection Process for Honorary Members}
+\begin{enumerate}
+	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
+	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
+	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
+	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
+		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
+	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
+\end{enumerate}
+\asubsubsubsection{Selection Process for Advisory Members}
+\begin{enumerate}
+	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members.
+		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
+	\item After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.
+	\item A discussion of the candidates will be held at the following House meeting.
+	\item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty Percent}.
+		Voting must remain open for a minimum of a forty-eight hour period.
+	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
+\end{enumerate}
+
+\asubsubsection{Evaluations Processes}
+During the academic year, a House member is evaluated by the Membership Evaluation.
+The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+Semi-Annual Evaluations Meetings are open only to current Active Members.
+All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
+\\* \\*
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
+It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
+\asubsubsubsection{Housing Points}
+All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
+\asubsubsubsection{Membership Evaluation}
+The Membership Evaluation process occurs once per academic year.
+It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+\asubsubsubsubsection{Voting}
+All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
+Evaluations will hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
+Exceptions to the requirements may be made, and House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
+These requirements must be completed before the Membership Evaluation occurs.
+A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+
+\asubsubsubsubsection{Outcomes}
+Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+\\* \\*
+If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+In either case, the member forfeits their ability to be included on the following year’s roster.
+\\* \\*
+A member may be given a conditional to complete as a means of making up for missing requirements.
+A conditional may be proposed by any member present at the Evaluation.
+If the conditional is approved by the Evaluations Director, it is then voted on by House.
+Each conditional consists of a set of additional requirements a deadline for completing them.
+When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+A conditional member who does not meet these additional requirements will have failed the evaluation.
+\asubsubsubsection{Appeals Process}
+If a member disagrees with the outcome of any evaluation, (e.g.
+is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+\\* \\*
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
+
+\asubsubsection{Expectations of House Members}
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+\\* \\*
+The member must participate significantly in at least one major project during the academic year.
+The member is required to submit a description for this major project to the Executive Board for approval.
+As an option to this requirement, the member may instead assist on a large number of House activities and projects.
+However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
+This participation will be evaluated by the Executive Board.
+
+\asubsubsection{Housing Status}
+All Active and Introductory Members have a housing status.
+This status indicates their right to priority housing on the floor.
+Any Alumni Member in good standing will maintain their previous On Floor status upon a return to Active membership.
+\asubsubsubsection{On-Floor Status}
+Members with On-Floor status are eligible to live on the floor.
+To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
+The Evaluations Director will then bring them up for vote at the next meeting.
+\asubsubsubsection{Off-Floor Status}
+Members with Off-Floor status do not have the right to live on the floor.
+They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
+
+\asubsubsection{Housing Priority System}
+The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
+The member with top priority is the member with on-floor status and the most Housing Priority Points.
+Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+\\* \\*
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
+\asubsubsubsection{Single Room Assignments}
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
+If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
+This process continues until a member selects to move into the single room.
+Once in a single room, a House member retains the assignment until voluntarily giving it up.
+It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
+\asubsubsubsection{Double Rooms as Single rooms}
+During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
+It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
+This only applies if there is a totally vacant room.
+
+\asubsection{Operations of the Operational Communications Directorship}
+The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+It is a self-governing committee making decisions by a simply majority vote.
+Membership is composed of all Root Type Persons.
+
+\asubsubsection{Selection of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
+		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
+\end{enumerate}
+
+\asubsubsection{Qualifications of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
+	\item Candidates may be granted an exemption by current Root Type Persons.
+		Such an exemption may be withdrawn at any time by the current Root Type Persons.
+	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
+		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
+	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+\end{enumerate}
+
+\asubsubsection{Creation of Accounts}
+Root Type Persons have the authority to manage user accounts for House systems.
+Before members may receive an account they must:
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+\end{enumerate}
+
+\asubsubsection{Code of Conduct}
+The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+\\* \\*
+Members are bound to the Code of Conduct revision that they sign when initially creating their account.
+Members may sign a more recent revision of the Code of Conduct to update their agreement.
+\asubsubsubsection{Changes}
+The following process is used for making changes to the Code of Conduct document.
+\begin{enumerate}
+	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
+\end{enumerate}
+
 \asection{Qualifications}

### 2019-09-16 constitution.tex
Rename articles.tex -> constitution.tex

@@
 %  changed.
-% -This document must be ratified by the House (as per the Constitution),
-%  if changes are to be officialized.
+% -This document must be ratified by the House (as per the Constitution) if
+%  changes are to be officialized.
 
@@
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chairperson, or Evaluations Director in writing before the completion of the introductory process.
+Introductory members may resign by submitting the request for termination of membership to the Chairman, or Evaluations Director in writing before the completion of the introductory process.
 \asubsection{Introductory Membership Term}
@@
 \asubsection{Active Membership Resignations}
-An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
+An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
@@
 \asubsection{Honorary Membership Resignations}
-An Honorary Member may resign by submitting in writing the reason for resignation to the Chairperson.
+An Honorary Member may resign by submitting in writing the reason for resignation to the Chairman.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 \asubsection{Advisory Membership Resignations}
-An Advisor may resign by submitting in writing the reason for resignation to the Chairperson.
+An Advisor may resign by submitting in writing the reason for resignation to the Chairman.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
-It is composed of the seven permanent directors and the Chairperson.
+It is composed of the seven permanent directors and the Chairman.
 \\*\\*
 There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
-Ad-hoc directorships are created on an as-needed basis.
+Ad Hoc directorships are created on an as-needed basis.
 They are generally very task oriented and are chaired by a House member.
@@
 \begin{itemize}
-	\item Chairperson
+	\item Chairman
 	\item House Secretary
@@
 \asection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
+Closed Executive Board Meetings are open only to the Chairman, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.
+However, the Chairman and at least two-thirds of the Voting Members must be present for the meeting to be called.
 
@@
 
-\asubsection{Responsibilities of the Chairperson}
+\asubsection{Responsibilities of the Chairman}
 \begin{enumerate}
@@
 \begin{enumerate}
-	\item Ad-Hoc Directorships are responsible for the task for which they were created
-	\item Any responsibilities budgets or finances for the Ad-Hoc Directorship are placed upon the assigned director
+	\item Ad Hoc Directorships are responsible for the task for which they were created
+	\item Any responsibilities budgets or finances for the Ad Hoc Directorship are placed upon the assigned director
 \end{enumerate}
@@
 \asection{Operations}
+\asubsection{Operations of the Financial Directorship}
+\asubsubsection{Amount of House Dues}
+The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
+\asubsubsection{Collection of House Dues}
+The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected during this period as well by the Financial Director.
+For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+\\*\\*
+If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
+If the Financial Director deems their situation appropriate, they may grant an extension for payment.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
+If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
+If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
+\\*\\*
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+After this date, dues collection is suspended until the start of the next academic year.
+\asubsubsection{Breakdown of Dues for Directorship Budgets}
+\begin{center}
+\begin{tabular}[c]{l c}
+Directorship Name & Percentage of Dues \\
+\hline
+\hline
+Operational Communications & 20\% \\
+\hline
+Evaluations \& Selections & 5\% \\
+\hline
+House History & 10\% \\
+\hline
+House Improvements & 15\% \\
+\hline
+Research and Development & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+Accumulated & 10\% \\
+\hline
+\end{tabular}
+\end{center}
+
+The suggested total operational budget is \$8064.
+This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
+Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+
+\asubsubsection{Expenditure Approval}
+All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
+A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+\\* \\*
+If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+\\*\\*
+For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+\\* \\*
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+This amount is to be directly subtracted from the general CSH account.
+\\* \\*
+Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
+
+% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
 \asubsection{Operations of the Evaluations Directorship}
@@
 \item Complete the Introductory Packet
-\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
 \item Attend at least one House social event during the process
@@
 Occurs between the sixth and tenth week of each semester.
-\asubsubsubsubsection{Introductory Voting}
+\asubsubsubsubsection{Voting}
 On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
@@
 House may choose any of the Outcomes for each member.
-\asubsubsubsubsection{Introductory Outcomes}
+\asubsubsubsubsection{Outcomes}
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 \asubsubsubsubsection{Voting}
-A quorum of members, on a member by member basis, ensures that each Active Member has met the minimum requirements in order to continue as an Active Member in the following year.
-All Active Members will be held to the requirements and evaluated unless they have received an exemption from the Executive Board prior to the event.
-These requirements are detailed in Article VI under expectations for each category of membership.
+All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
+Evaluations will hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
+Exceptions to the requirements may be made, and House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
 These requirements must be completed before the Membership Evaluation occurs.
-A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
 Neither absentee nor proxy votes are allowed.
-House may choose any of the Outcomes for each member.
+
 \asubsubsubsubsection{Outcomes}
@@
 \asubsubsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
 \\* \\*
@@
 This only applies if there is a totally vacant room.
-
-\asubsection{Operations of the Financial Directorship}
-\asubsubsection{Amount of House Dues}
-The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
-\asubsubsection{Collection of House Dues}
-The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
-During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
-Dues for off-floor members are to be collected during this period as well by the Financial Director.
-For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
-Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
-\\*\\*
-If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
-If the Financial Director deems their situation appropriate, they may grant an extension for payment.
-If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
-If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
-If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
-This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
-\\*\\*
-All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
-After this date, dues collection is suspended until the start of the next academic year.
-\asubsubsection{Breakdown of Dues for Directorship Budgets}
-\begin{center}
-\begin{tabular}[c]{l c}
-Directorship Name & Percentage of Dues \\
-\hline
-\hline
-Operational Communications & 20\% \\
-\hline
-Evaluations \& Selections & 5\% \\
-\hline
-House History & 10\% \\
-\hline
-House Improvements & 15\% \\
-\hline
-Research and Development & 20\% \\
-\hline
-Social & 20\% \\
-\hline
-Accumulated & 10\% \\
-\hline
-\end{tabular}
-\end{center}
-
-The suggested total operational budget is \$8064.
-This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
-Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
-
-\asubsubsection{Expenditure Approval}
-All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
-Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
-A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
-\\* \\*
-If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
-At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
-A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
-\\*\\*
-For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
-This proposal includes the project budget, inventory of required resources, and a timeline for completion.
-\\* \\*
-If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
-This amount is to be directly subtracted from the general CSH account.
-\\* \\*
-Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
 
@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairperson, Evaluations Director}
+\asubsection{Qualifications to be the Chairman, Evaluations Director}
 \begin{enumerate}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member
-	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
+	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairman, should they be elected
 \end{enumerate}
@@
 Each different nomination must be a separate entry on the election ballot.
-Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to single or dual directorship.
+Non-voting Executive Board positions (i.e. Ad Hoc Directors) are not restricted to single or dual directorship.
 
@@
 \end{itemize}
-\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
+\asubsection{Selection of the Chairman, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
 \begin{enumerate}
 	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
-	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.
+		Any House member may nominate any member or pair of members where appropriate for a Directorship.
+	\item The candidates will be notified of their nomination.
 		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
@@
 	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
-		The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.
+		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chairperson will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
+	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
 	\item The winners are determined via the process described in \ref{Alternative Vote}.
@@
 \begin{enumerate}
-	\item When the Executive Board or a group of House members feels an Ad-hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
-	\item When the Ad-Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
+	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
+	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
 \end{enumerate}
@@
 \asection{Resignations}
-An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
+An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 \asection{Appointment of an Interim Director}
-The duties and responsibilities of a vacated office are assumed by the Chairperson or by an Active member that is appointed at the Chairperson's discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by the Chairman or by an Active member that is appointed at the Chairman's discretion until the new member takes office.
 The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
@@
 If only one option may pass, then the vote must be recast or tabled at the discretion of the person chairing the vote.
-In the event of a tie in an Executive Board vote, the Chairperson may cast the tie-breaking vote.
+In the event of a tie in an Executive Board vote, the Chairman may cast the tie-breaking vote.
 
@@
 \asection{Formation of a Judicial Board}
-A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
-If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
+A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
+If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
 \asection{Judicial Investigation}

### 2019-09-16 constitution.tex
Replace: Chairman -> Chairperson

--- 2019-04-09 constitution.tex
@@
 There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
-Ad-hoc directorships are created on an as-needed basis.
+Ad Hoc directorships are created on an as-needed basis.
 They are generally very task oriented and are chaired by a House member.
@@
 The count of all Proxy Vote must be recorded and announced in all votes.
-Proxy Votes are only permissible where explicitly stated, at the discretion of the person chairing the vote.
+Proxy Votes are only permissible where explicitly stated, at the discretion of the Chair of the Vote.
 \asubsection{Abstention}
@@
 \asubsection{Vote Counters}
-The chairperson of the vote is a vote counter and will additionally select two other members to count votes.
+The Chair of the Vote is a vote counter and will additionally select two other members to count votes.
 
@@
 A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
-At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period.
+At the end of the voting period, the Chair of the Vote collects the ballots, closing the voting period.
 The Vote Counters then tally the results.
@@
 \asubsubsection{Method of Vote}
-The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
+The Chair of the Vote will state all possible ways to vote, then call out each possibility one at a time.
 The chairing member will count the number of members casting their immediate vote for that possibility.
@@
 \asubsubsection{Method of Vote}
-The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
+The Chair of the Vote will state all possible ways to vote, then call out each possibility one at a time.
 Votes are kept anonymous.
@@
 If multiple options may pass, a tie does not present a problem.
-If only one option may pass, then the vote must be recast or tabled at the discretion of the person chairing the vote.
+If only one option may pass, then the vote must be recast or tabled at the discretion of the Chair of the Vote.
 In the event of a tie in an Executive Board vote, the Chairperson may cast the tie-breaking vote.

### 2019-10-01 constitution.tex
Replace the old Housing Evaluations
* Describe our current process
* Use 1 (one) housing point rather than 2 since we don't do 1-3 now
* Fix broken references

@@
 The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
+Each Active Member with On-Floor Status who passes the Membership Evaluation is granted one (1) Housing Priority Point.
 \\* \\*
@@
 \asubsubsubsection{Single Room Assignments}
-When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
 If that House member declines the option, it will be offered to the member with the next highest Housing Priority.

### 2019-11-01 constitution.tex
Set housing points to two
Correct Intro Members being required to pay dues during intro process
Capitalize Introductory Evaluations

--- 2019-09-16 constitution.tex
@@
 Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
 The member does, however, have the right to use Computer Science House's facilities.

### 2019-11-03 constitution.tex
Add a missing 'and' to conditional description
Correct single room ties

--- 2019-10-01 constitution.tex
@@
 Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
-Each Active Member with On-Floor Status who passes the Membership Evaluation is granted one (1) Housing Priority Point.
+Each Active Member with On-Floor Status who passes the Membership Evaluation is granted two (2) Housing Priority Points.
 \\* \\*
@@
 When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
 If that House member declines the option, it will be offered to the member with the next highest Housing Priority.

### 2019-11-05 constitution.tex
Fixes Active Membership Requirements and Packet
Active Membership is better

--- 2019-11-01 constitution.tex
@@
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
+Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed their
+last Introductory Evaluation or their most recent Membership Evaluation.
 \asubsection{Active Membership Selection}

### 2019-11-05 constitution.tex
Update constitution.tex

@@
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members whom passed a Membership Evaluation, all Introductory Resident members, and ten (10) of any combination of the following:
 \begin{itemize}
@@
 \asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active
+Membership.
 Occurs between the sixth and tenth week of each semester.

### 2019-11-05 constitution.tex
Update constitution.tex

@@
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
+As defined, a member who has not passed at least one Membership Evaluation cannot become an Alumni and will
+no longer have any membership standing with House.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
@@
 \asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active
-Membership.
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
 Occurs between the sixth and tenth week of each semester.

### 2019-11-05 constitution.tex
Update constitution.tex

@@
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
 Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.

### 2019-11-05 constitution.tex
Update constitution.tex
Elections are Mandatory
This has already passed but it needed to be updated.

--- 2019-11-05 constitution.tex
@@
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed their
-last Introductory Evaluation or their most recent Membership Evaluation.
+Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
 \asubsection{Active Membership Selection}
@@
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members whom passed a Membership Evaluation, all Introductory Resident members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
 \begin{itemize}
@@
 \asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active
-Membership.
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
 Occurs between the sixth and tenth week of each semester.
@@
 
+Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
+To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.
 \asection{Appointment of an Interim Director}

### 2019-11-05 constitution.tex
Update constitution.tex

@@
 		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
-		Each conditional consists of a set of additional requirements a deadline for completing them.
+		Each conditional consists of a set of additional requirements and a deadline for completing them.
 		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
@@
 
-Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
-To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.
 \asection{Appointment of an Interim Director}

### 2019-11-05 constitution.tex
Don't elect OpComm, Ad Hocs, or the Secretary

@@
 
-\asection{Resignations}
+\asection{Executive Board Resignations}
 An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
@@
 The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
+Following a resignation, the Selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
+To postpone such a Selection, the Chairperson may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
 

### 2019-11-24 constitution.tex

--- 2019-11-05 constitution.tex
@@
 The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
+Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
+Each Active Member with On-Floor Status who passes the Membership Evaluation is granted two (2) Housing Priority Points.
 \\* \\*
@@
 \asubsubsubsection{Single Room Assignments}
-When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
 If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
@@
 The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
-
 Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
 To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.
+
 \asection{Appointment of an Interim Director}

### 2019-12-09 constitution.tex
Update constitution.tex
Co-Authored-By: Max Meinhold <mxmeinhold@gmail.com>

--- 2019-11-05 constitution.tex
@@
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
+Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed their most recent Introductory Evaluation or their most recent Membership Evaluation.
 \asubsection{Active Membership Selection}
@@
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}. 
+As defined, a member who has not passed at least one Membership Evaluation cannot become an Alumni and will no longer have any membership standing with House.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
@@
 \asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
 Occurs between the sixth and tenth week of each semester.
@@
 		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
-		Each conditional consists of a set of additional requirements and a deadline for completing them.
+		Each conditional consists of a set of additional requirements a deadline for completing them.
 		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.

### 2019-12-09 constitution.tex
Update constitution.tex
Co-Authored-By: Max Meinhold <mxmeinhold@gmail.com>

@@
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members whom passed a Membership Evaluation, all Introductory Resident members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members whom have passed a Membership Evaluation, all Introductory Resident members, and ten (10) of any combination of the following:
 \begin{itemize}

### 2020-01-17 constitution.tex

--- 2019-11-24 constitution.tex
@@
 The member does, however, have the right to use Computer Science House's facilities.
-The member must also pay dues.
+The member is not required to pay dues during the Introductory Process.
 \\* \\*
@@
 The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
-Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
-To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.
+Following a resignation, the Selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
+To postpone such a Selection, the Chairperson may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
 

### 2020-04-09 constitution.tex
rm 'Housing Points'
We use the 'Housing Priority System' and 'Housing Priority Points'. We
don't need to also define 'Housing Points' in a different place, with a
conflicting definition.

@@
 It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
-\asubsubsubsection{Housing Points}
-All members may notify the evaluations director before the end of the academic year that they would like to receive two housing points for use in the next academic year.
 \asubsubsubsection{Membership Evaluation}
@@
 Members with Off-Floor status do not have the right to live on the floor.
-They still have access to all other privileges associated with their membership, and may still accumulate Housing Points.
+They still have access to all other privileges associated with their membership, and may still accumulate Housing Priority Points.
 
@@
 Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
-Each Active Member with On-Floor Status who passes the Membership Evaluation is granted two (2) Housing Priority Points.
+Each Active Member who passes the Membership Evaluation is granted two (2) Housing Priority Points.
 \\* \\*

### 2020-04-12 constitution.tex
Correct inconsistency in Intro Period extensions
Correct undefined Resignation references
Resignation -> Executive Board Resignation

--- 2020-01-17 constitution.tex
@@
 	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
-		The vacated office is then handled like any other vacated office; see \ref{Resignations}.
+		The vacated office is then handled like any other vacated office; see \ref{Executive Board Resignations}.
 	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
@@
 	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
-		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
+		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Executive Board Resignations}.
 	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of the Executive Board.

### 2020-04-30 constitution.tex
removed requirement for chair and evals to be on floor
removed requirement for failed intro and active members to move off-floor

@@
 Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
-Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
 \asubsection{Active Membership Leave of Absence}
@@
 	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
-		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
 	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.

### 2020-08-17 constitution.tex
Reword ambiguous membership evaluation

--- 2020-04-12 constitution.tex
@@
 All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
-Evaluations will hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
-Exceptions to the requirements may be made, and House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
+The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
+Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
 These requirements must be completed before the Membership Evaluation occurs.

### 2020-09-08 constitution.tex

@@
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
+If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
 \asubsubsubsection{The Introductory Packet}

### 2020-10-08 constitution.tex
Adds the ability for eboard or the evaluations director to remove a member from the list of required signatures (5.D.2.A.2)

--- 2020-04-30 constitution.tex
@@
 Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
 \asubsection{Active Membership Leave of Absence}
@@
 At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+Additionally, at the discretion of the Evaluations director or the Executive Board, any member can be removed from the list of required signatures if the member is not actively engaging with Introductory Members.
+The removed member must then be alerted by the Evaluations director and informed of how they can again become a required signature.
+This decision can be overwritten by the Executive Board through a simple majority vote of the voting members of the Executive Board.
 \asubsubsubsection{Expectations of an Introductory Member}
@@
 	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+		In addition, the participant is asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
 	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.

### 2020-10-09 constitution.tex
Adding chairperson debate section

--- 2020-09-08 constitution.tex
@@
 \end{enumerate}
+\asubsection{Selection of the Chairperson}
+\begin{enumerate}
+	\item Each candidate for the position of Chairperson will be requested to appear in a debate with all other candidates for the position.
+		A debate will be presented in front of House and will consist of questions generated by the House, but not given to the candidates before the debate.
+	\item All other processes as described in \ref{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)} still apply in addition to the terms described above.
+\end{enumerate}
 \asubsection{Selection of the Operational Communications Director}

### 2021-03-01 constitution.tex
Improved Formatting
Proposed amendment now has 1 sentence per line
Update constitution.tex
removed trailing spaces
Removed Trailing Space on Line 531
Your welcome mom

--- 2020-09-08 constitution.tex
@@
 \asubsubsubsubsection{Voting}
+Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
 All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.

### 2021-04-25 constitution.tex
Added fullstop to line 360

@@
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
-	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}
+	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
 		The constitution should remain up to date with current practices.

### 2021-04-25 constitution.tex
Redefining dues exemptions process

@@
 Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
-\\*\\*
+\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
 If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
-If the Financial Director deems their situation appropriate, they may grant an extension for payment.
+If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
 If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
-If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
+If the Executive Board disagrees with the Financial Director, the Executive Board may reduce or extend the member's payment.
 If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
-This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
-\\*\\*
+In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues.
+Additional time and reduction of dues may both be given to a member in an appropriate situation.
 All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).

### 2021-09-21 constitution.tex
Better wording on "extend the payment"
Co-authored-by: Harlan Haskins <harlan@apple.com>
allow honorary and advisory members accounts without completion of packet
Added Polygamy/Polyamory Directorship
Removes spending committees, redifines limits on directorships using their budgets

--- 2021-04-25 constitution.tex
@@
 All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
-Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
-A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+Single expenditures may not exceed five percent of a directorship's budget (5\%) and total expenditures may not exceed ten percent (10\%).
+A single expenditure is defined as one line item on a receipt, and a total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
 \\* \\*
 If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
-At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
-A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
 \\*\\*

### 2021-09-26 constitution.tex
Fixes language describing large purchases that must be presented to house

--- 2021-04-25 constitution.tex
@@
 If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
-If the Executive Board disagrees with the Financial Director, the Executive Board may reduce or extend the member's payment.
+If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
 If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
@@
 Root Type Persons have the authority to manage user accounts for House systems.
-Before members may receive an account they must:
+Before introductory, active, or alumni members may receive an account they must:
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 \end{enumerate}
+Accounts for honorary and advisory members may be created at the discretion of the Root Type Persons.
 

### 2021-11-20 constitution.tex
Updated formatting of directorship budget table
Added vertical lines on both sides and a horizontal line at the top
Updated introductory process timeline to new proposal

@@
 \begin{center}
-\begin{tabular}[c]{l c}
+\begin{tabular}[c]{|l c|}
+\hline
 Directorship Name & Percentage of Dues \\
@@
 \asubsubsubsection{The Evaluation Period}
-The Process will begin between the first and fourth week of each semester, then last between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
+The Process will begin between the first and second week of each semester, then last six (6) weeks, starting when the Evaluations Director initiates it.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
 If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
+The Introductory Process may be held twice a semester at the discretion of the evaluations director.
+If the evaluations director deems it necessary, the second intro process must begin within a week of the first process ending, and must last the same six (6) weeks.
 \asubsubsubsection{The Introductory Packet}
@@
 The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
-Occurs between the sixth and tenth week of each semester.
+Occurs during the sixth week of each semester.
+If the evaluations director chooses to hold a second Introductory Process, the Introductory Evaluation will also occur during the twelfth week of each semester.
+
 \asubsubsubsubsection{Voting}

### 2021-11-21 constitution.tex
Updated phrasing based on mom's suggestion

@@
 \asubsubsubsection{The Evaluation Period}
-The Process will begin between the first and second week of each semester, then last six (6) weeks, starting when the Evaluations Director initiates it.
+The Process will occur either once or twice a semester, and will last for six (6) weeks.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
@@
 The Introductory Process may be held twice a semester at the discretion of the evaluations director.
-If the evaluations director deems it necessary, the second intro process must begin within a week of the first process ending, and must last the same six (6) weeks.
+If deemed necessary, the second intro process must begin within nine (9) days of the first process ending.
 \asubsubsubsection{The Introductory Packet}
@@
 The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
-Occurs during the sixth week of each semester.
-If the evaluations director chooses to hold a second Introductory Process, the Introductory Evaluation will also occur during the twelfth week of each semester.
+Occurs at the conclusion of the final week of the Process.
 

### 2021-11-21 constitution.tex
Fixed formatting issues

@@
 \asubsubsubsection{The Evaluation Period}
-The Process will occur either once or twice a semester, and will last for six (6) weeks.
+The Process will occur either once or twice a semester, at the discretion of the Evaluations Director, and will last for six (6) weeks.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
 If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
-The Introductory Process may be held twice a semester at the discretion of the evaluations director.
-If deemed necessary, the second intro process must begin within nine (9) days of the first process ending.
+If deemed necessary by the Evaluations Director, the second intro process must begin within nine (9) days of the first process ending.
 \asubsubsubsection{The Introductory Packet}

### 2021-11-21 constitution.tex
Readded definition of intro process initialization

@@
 \asubsubsubsection{The Evaluation Period}
-The Process will occur either once or twice a semester, at the discretion of the Evaluations Director, and will last for six (6) weeks.
+The Process will occur either once or twice per semester, at the discretion of the Evaluations Director, and will last for six (6) weeks.
+The Process shall be initiated by the Evaluations Director during either the first or second week of each semester.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.

### 2021-11-21 constitution.tex
Added eboard abilityto initiate second process

@@
 \asubsubsubsection{The Evaluation Period}
-The Process will occur either once or twice per semester, at the discretion of the Evaluations Director, and will last for six (6) weeks.
+The Process will occur either once or twice per semester, at the discretion of the Evaluations Director, or by an Executive Board simple majority vote, and will last for six (6) weeks.
 The Process shall be initiated by the Evaluations Director during either the first or second week of each semester.

### 2021-11-21 constitution.tex
Moved evals and eboard discretion logic to prevent flaw with starting

--- 2021-11-21 constitution.tex
@@
 \asubsubsubsection{The Evaluation Period}
-The Process will occur either once or twice per semester, at the discretion of the Evaluations Director, and will last for six (6) weeks.
+The Process will occur either once or twice per semester, and will last for six (6) weeks.
 The Process shall be initiated by the Evaluations Director during either the first or second week of each semester.
@@
 If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
-If deemed necessary by the Evaluations Director, the second intro process must begin within nine (9) days of the first process ending.
+If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
 \asubsubsubsection{The Introductory Packet}

### 2021-11-29 constitution.tex
Fixed edge cases for starting the process

@@
 The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evaluations Director during either the first or second week of each semester.
+The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
@@
 If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
+If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
 \asubsubsubsection{The Introductory Packet}

### 2022-02-12 constitution.tex
introduce requirements for active members to vote at intro evals

@@
 A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+In order for a Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
 Neither absentee nor proxy votes are allowed.
 House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Expectations of Voting Members}
+The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote.
+Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\end{itemize}
+
 \asubsubsubsubsection{Outcomes}

### 2022-02-12 constitution.tex
updated the constitution to refelct our current active membership evaluation process.

--- 2021-11-29 constitution.tex
@@
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
-Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
+Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
 \asubsection{Active Membership Leave of Absence}

### 2022-02-12 constitution.tex
Requires imps to be on floor in order to run

--- 2021-11-29 constitution.tex
@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairperson, Evaluations Director}
+\asubsection{Qualifications to be the Chairperson, Evaluations Director, House Improvements Director}
 \begin{enumerate}
@@
 \end{enumerate}
-\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
+\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House History Director}
 \begin{enumerate}

### 2022-02-13 constitution.tex
Clarify Election Qualification Overrides
Add clarification to how qualifications for an EBoard candidate are
overriden via Constitutional Override.

@@
 \asection{Qualifications}
-\asubsection{Qualifications to be the Chairperson, Evaluations Director, House Improvements Director}
+\asubsection{Qualifications to be the Chairperson, Evaluations Director}
 \begin{enumerate}
@@
 \end{enumerate}
-\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House History Director}
+\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
 \begin{enumerate}
@@
 \end{enumerate}
+
+\asubsection{Overriding Directorships Qualifications}
+Qualifications pertaining to a specific directorship election can be overriding via a Constitutional Override, as explained in \ref{Semantic Changes}.
+Overrides will apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
 

### 2022-02-13 constitution.tex
constitution: add a process for waiving candidacy requirements

@@
 
-\asubsection{Overriding Directorships Qualifications}
-Qualifications pertaining to a specific directorship election can be overriding via a Constitutional Override, as explained in \ref{Semantic Changes}.
-Overrides will apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
+\asubsection{Waiving of Requirements}
+\begin{enumerate}
+  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
+    \begin{enumerate}
+      \item Candidates must have at least one full semester of House membership as an Active Member
+      \item Candidates must reside on floor during the term of office
+    \end{enumerate}
+  \item This process waives the enumerated requirements for a given election for all candidates on a per-directorship basis
+\end{enumerate}
 

### 2022-02-13 constitution.tex
waivers: clarify usage of the process, add dual directorship waiver

@@
       \item Candidates must reside on floor during the term of office
+      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
     \end{enumerate}
-  \item This process waives the enumerated requirements for a given election for all candidates on a per-directorship basis
+  \item This process operates for one requirement at a time
+  \item This process operates for one voting executive board position or the Chairperson at a time
+  \item This process operates on the current election only
+  \item Any requirements waived using this process are waived for all candidates for the given position for the current election process
 \end{enumerate}

### 2022-02-14 constitution.tex
Add Active Member Requirement for Elections

--- 2022-02-13 constitution.tex
@@
 
-\asubsection{Waiving of Requirements}
-\begin{enumerate}
-  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
-    \begin{enumerate}
-      \item Candidates must have at least one full semester of House membership as an Active Member
-      \item Candidates must reside on floor during the term of office
-    \end{enumerate}
-  \item This process waives the enumerated requirements for a given election for all candidates on a per-directorship basis
-\end{enumerate}
-
 \asection{Selection}
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
+	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event.
+This will be treated as a House Meeting, with the expectation that all Active Members will attend and attendance will be taken.
+If the speeches take place at a traditional House Meeting, only one attendance will be taken.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-14 constitution.tex
Change to make a formal requirement for Active Members

@@
 \asubsubsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Elections, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
 \\* \\*
@@
 	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
-This will be treated as a House Meeting, with the expectation that all Active Members will attend and attendance will be taken.
-If the speeches take place at a traditional House Meeting, only one attendance will be taken.
+		All Active Members are expected to attend this Election, as specified in \ref{Expectations of House Members}.
+		Exemptions to attendance may be given at the discretion of the Evaluations Director.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-14 constitution.tex
Reword and Styling

--- 2022-02-14 constitution.tex
@@
 
+\asubsection{Overriding Directorships Qualifications}
+When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in \ref{Qualifications}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
+
 \asection{Selection}
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
-	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event.
-This will be treated as a House Meeting, with the expectation that all Active Members will attend and attendance will be taken.
-If the speeches take place at a traditional House Meeting, only one attendance will be taken.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-14 constitution.tex
constitution: reorder waivable requirements for consistency

@@
 
-\asubsection{Overriding Directorships Qualifications}
-When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in \ref{Qualifications}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
+\asubsection{Waiving of Requirements}
+\begin{enumerate}
+  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
+    \begin{enumerate}
+      \item Candidates must reside on floor during the term of office
+      \item Candidates must have at least one full semester of House membership as an Active Member
+      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
+    \end{enumerate}
+  \item This process operates for one requirement at a time
+  \item This process operates for one voting executive board position or the Chairperson at a time
+  \item This process operates on the current election only
+  \item Any requirements waived using this process are waived for all candidates for the given position for the current election process
+\end{enumerate}
 

### 2022-02-14 constitution.tex
qualifications: address review feedback

--- 2022-02-14 constitution.tex
@@
 
-\asubsection{Overriding Directorships Qualifications}
-When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in \ref{Qualifications}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
+\asubsection{Waiving of Qualifications}
+\begin{enumerate}
+  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
+    \begin{enumerate}
+      \item Candidates must reside on floor during the term of office.
+      \item Candidates must have at least one full semester of House membership as an Active Member.
+      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
+    \end{enumerate}
+  \item Each vote to waive a qualification may only apply to a single Qualification and a single Selection.
+  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if if the waiver passes.
+\end{enumerate}
 

### 2022-02-14 constitution.tex
Waiving of Qualifications: fix typos

@@
     \end{enumerate}
-  \item Each vote to waive a qualification may only apply to a single Qualification and a single Selection.
-  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if if the waiver passes.
+  \item Each vote to waive a Qualification must only apply to a single Qualification and a single Selection.
+  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
 \end{enumerate}

### 2022-02-15 constitution.tex
constitution: review feedback

@@
 \begin{enumerate}
-  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
+  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
     \begin{enumerate}
@@
     \end{enumerate}
-  \item Each vote to waive a Qualification must only apply to a single Qualification and a single Selection.
-  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
+  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
+  \item A Two-Thirds Immediate Vote, as defined in \ref{Two-Thirds} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
+  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
+  \item Waivers always apply to all Candidates for the Executive Board position.
 \end{enumerate}

### 2022-02-15 constitution.tex
Add references to range of qualifications

--- 2022-02-14 constitution.tex
@@
 \usepackage{titlesec}
+\usepackage{cleveref}
 
@@
 
-\asubsection{Waiving of Qualifications}
-\begin{enumerate}
-  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
-    \begin{enumerate}
-      \item Candidates must reside on floor during the term of office.
-      \item Candidates must have at least one full semester of House membership as an Active Member.
-      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
-    \end{enumerate}
-  \item Each vote to waive a Qualification must only apply to a single Qualification and a single Selection.
-  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
-\end{enumerate}
+\asubsection{Guidelines on Overriding Executive Board Qualifications}
+\begin{itemize}
+\item This section provides no definitions, instead serving to clarify the applicability of Overrides to Qualifications in the Selection of members of the Executive Board.
+\item When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in sections {\crefname{Qualifications}{}{}\crefrange{Qualifications to be the Chairperson, Evaluations Director}{Qualifications to be the House Secretary or an Ad Hoc Director}}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
+\end{itemize}
 

### 2022-02-15 constitution.tex
Allows Active Members to propose changes to the COC

@@
 \usepackage{titlesec}
-\usepackage{cleveref}
 
@@
 \begin{enumerate}
-	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item An Active Member drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
 	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
@@
 \end{enumerate}
-
-\asubsection{Guidelines on Overriding Executive Board Qualifications}
-\begin{itemize}
-\item This section provides no definitions, instead serving to clarify the applicability of Overrides to Qualifications in the Selection of members of the Executive Board.
-\item When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in sections {\crefname{Qualifications}{}{}\crefrange{Qualifications to be the Chairperson, Evaluations Director}{Qualifications to be the House Secretary or an Ad Hoc Director}}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
-\end{itemize}
 

### 2022-02-15 constitution.tex
Reword Elections and Requirements

@@
 \asubsubsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Executive Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
 \\* \\*
@@
 \begin{enumerate}
-	\item An Active Member drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
 	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
+	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
+		All Active Members are expected to attend candidate speeches as specified in \ref{Expectations of House Members}.
+		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-15 constitution.tex
Reword Elections and Requirements

@@
 		All Active Members are expected to attend candidate speeches as specified in \ref{Expectations of House Members}.
-		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
+		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will note is as an Absence with Reason.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-15 constitution.tex
Changes bad standing votes so that all of house may participate

--- 2022-02-15 constitution.tex
@@
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
-If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
-The decision will be announced at the following House meeting.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next House meeting.
+If Fifty Percent of Active Members present are in favor of the return (as defined in \ref{Fifty Percent}), the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
 \asubsection{Active Membership Expectations}

### 2022-02-15 constitution.tex
reworded 5.D.2.A.2 to reflect current packet procedures

@@
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next House meeting.
-If Fifty Percent of Active Members present are in favor of the return (as defined in \ref{Fifty Percent}), the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
+If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+The decision will be announced at the following House meeting.
 \asubsection{Active Membership Expectations}
@@
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active Members who have passed a Membership Evaluation, all Active Resident Members, all Introductory Resident Members, and ten (10) of any combination of the following:
 \begin{itemize}

### 2022-02-16 constitution.tex
waivers: move towards 3/4 vote

@@
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active Members who have passed a Membership Evaluation, all Active Resident Members, all Introductory Resident Members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
 \begin{itemize}
@@
 
+\asubsection{Waiving of Qualifications}
+\begin{enumerate}
+  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
+    \begin{enumerate}
+      \item Candidates must reside on floor during the term of office.
+      \item Candidates must have at least one full semester of House membership as an Active Member.
+      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
+    \end{enumerate}
+  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
+  \item A Three-Quarters Immediate Vote, as defined in \ref{Three-Quarters} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
+  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
+  \item Waivers always apply to all Candidates for the Executive Board position.
+\end{enumerate}
+
 \asection{Selection}
@@
 An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
+\asubsection{Three-Quarters}
+In a three-quarters Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds three-quarters the Total Number of Possible Votes.
+An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
 \asubsection{Three Tiered}

### 2022-02-16 constitution.tex
Reword Reference to Expectations

--- 2022-02-15 constitution.tex
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
+	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
+		All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of House Members}.
+		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-17 constitution.tex
Reword candidate speeches
Co-authored-by: Max Meinhold <mxmeinhold@gmail.com>
remove opcomm

--- 2022-02-15 constitution.tex
@@
 	\item House Improvements Director
-	\item Operational Communications Director
 	\item House History Director
@@
 	\item To oversee the planning, organization and construction of technical projects for the House's benefit
-	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
 	\item To provide seminars and tutorials to educate House members in technical areas
@@
 	\item To oversee the general maintenance of the appearance of the House
-\end{enumerate}
-
-\asubsection{Responsibilities of the Operational Communications Director}
-\begin{enumerate}
-	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
-	\item To report the status of the House computer systems and network to the Executive Board and House members
 \end{enumerate}
@@
 \hline
-Operational Communications & 20\% \\
-\hline
 Evaluations \& Selections & 5\% \\
 \hline
-House History & 10\% \\
+House History & 15\% \\
 \hline
-House Improvements & 15\% \\
+House Improvements & 20\% \\
 \hline
-Research and Development & 20\% \\
+Research and Development & 25\% \\
 \hline
-Social & 20\% \\
+Social & 25\% \\
 \hline
@@
 
-\asubsection{Operations of the Operational Communications Directorship}
-The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
-It is a self-governing committee making decisions by a simply majority vote.
-Membership is composed of all Root Type Persons.
-
-\asubsubsection{Selection of a Root Type Person}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
-	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
-		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
-		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
-\end{enumerate}
-
-\asubsubsection{Qualifications of a Root Type Person}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
-	\item Candidates may be granted an exemption by current Root Type Persons.
-		Such an exemption may be withdrawn at any time by the current Root Type Persons.
-	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
-		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
-	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
-\end{enumerate}
-
 \asubsubsection{Creation of Accounts}
-Root Type Persons have the authority to manage user accounts for House systems.
+Executive Members have the authority to manage user accounts for House systems.
 Before introductory, active, or alumni members may receive an account they must:
@@
 \end{enumerate}
-Accounts for honorary and advisory members may be created at the discretion of the Root Type Persons.
+Accounts for honorary and advisory members may be created at the discretion of Executive Board.
 
@@
 \begin{enumerate}
-	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item A Active Member drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
 	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
@@
 	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
-\end{enumerate}
-\asubsection{Qualifications to be the Operational Communications Director}
-\begin{enumerate}
-	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
-	\item Candidates must be a current Active Member.
-	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
 \end{enumerate}
@@
 \end{enumerate}
-\asubsection{Selection of the Operational Communications Director}
-\begin{enumerate}
-	\item A candidate for the Operational Communications Directorship shall be chosen by the current Root Type Persons.
-	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
-	\item The candidate is presented to the Executive Board for approval.
-		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
-		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
-\end{enumerate}
+
 \asubsection{Selection of Ad Hoc Directors}

### 2022-02-24 constitution.tex

--- 2022-02-16 constitution.tex
@@
 A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
 Neither absentee nor proxy votes are allowed.
 House may choose any of the Outcomes for each member.
+\asubsubsubsubsection{Expectations of Voting Members}
+The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
+Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\end{itemize}
+
 \asubsubsubsubsection{Outcomes}
@@
 \asubsubsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Executive Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
 \\* \\*
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
-	\item The date and time of the candidate(s)'s speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
-		All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of House Members}.
-		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-02-25 constitution.tex
Three-Quarters Vote: nit, fix capitalisation

@@
 A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
 Neither absentee nor proxy votes are allowed.
 House may choose any of the Outcomes for each member.
-\asubsubsubsubsection{Expectations of Voting Members}
-The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
-Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
-\begin{itemize}
-\item Attend all House meetings during the process
-\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
-\item Attend at least one House social event during the process
-\item Attend at least two seminars relating to computing or electronics
-\end{itemize}
-
 \asubsubsubsubsection{Outcomes}
@@
 An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
+\asubsection{Three-Quarters}
+In a Three-Quarters Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds three-quarters the Total Number of Possible Votes.
+An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
 \asubsection{Three Tiered}

### 2022-03-23 constitution.tex
Active Membership Privileges: WiC jacket
updated wording to fit style guidelines

--- 2022-02-24 constitution.tex
@@
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
-If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
-The decision will be announced at the following House meeting.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
+If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
 \asubsection{Active Membership Expectations}

### 2022-03-23 constitution.tex
Clarifies the voting members must be Eboard

--- 2022-02-24 constitution.tex
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
+	\item The date and time of candidate speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
+		All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of House Members}.
+		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.

### 2022-03-27 constitution.tex
constitution: by-laws don't exist anymore

@@
 \\* \\*
-At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
 It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
@@
 \article{Judicial}
-The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
+The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
 \asection{Formation of a Judicial Board}

### 2022-04-03 constitution.tex
Ban Abe
Add a Public Relations Director to the Executive Board

--- 2022-03-23 constitution.tex
@@
 	\item House History Director
+	\item Public Relations Director
 \end{itemize}
@@
 	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
+\end{enumerate}
+
+\asubsection{Responsibilities of the Public Relations Director}
+\begin{enumerate}
+	\item To preside over Public Relations Directorship Meetings
+	\item To operate House social media accounts intended to represent House as a whole
+	\item To oversee the organization, initiation, and execution of House philanthropic events
+	\item To preserve and improve the public image of House
+	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
+
 \end{enumerate}
@@
 \hline
-Accumulated & 10\% \\
+Public Relations & 5\% \\
+\hline
+Accumulated & 5\% \\
 \hline
@@
 \end{enumerate}
-\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
+\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
 \begin{enumerate}
@@
 \end{itemize}
-\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
+\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s), Public Relations Director}
 \begin{enumerate}

### 2022-04-10 constitution.tex
added term to expectations

--- 2022-03-23 constitution.tex
@@
 A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
+Inorder to be counted in quorum for, and to vote in, an Introductory Evaluation, each Active Member must complete the requirements outlined in \ref{Expectations of Voting Members} within the current Operating Session, prior to the beginning of the evaluation.
 Neither absentee nor proxy votes are allowed.
@@
 \asubsubsubsubsection{Expectations of Voting Members} 
-The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
-Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
+Any of the folowing requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
 \begin{itemize}

### 2022-04-10 constitution.tex
delayed intro process

@@
 The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
+The Process shall be initiated by the Evaluations Director during either the third or fourth week of each semester.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
@@
 A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-Inorder to be counted in quorum for, and to vote in, an Introductory Evaluation, each Active Member must complete the requirements outlined in \ref{Expectations of Voting Members} within the current Operating Session, prior to the beginning of the evaluation.
+In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
 Neither absentee nor proxy votes are allowed.
@@
 \asubsubsubsubsection{Expectations of Voting Members}
-Any of the folowing requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
+The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
+Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
 \begin{itemize}

### 2022-04-12 constitution.tex
removed impossible second intro process

@@
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.
+However, the Chairperson and at least two-thirds of the Voting Members of the Executive Board must be present for the meeting to be called.
 
@@
 The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evaluations Director during either the third or fourth week of each semester.
+The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
 The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.

### 2022-04-20 constitution.tex
Change alumni in bad standing vote to align with recent practice

@@
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
 If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
@@
 This may be appealed to the Executive Board in order to pursue a different outcome.
+Any Alumni Member in bad standing may become an Alumni in good standing by notifying the Evaluations Director of their intent to be brought up for a vote, who will bring them up for a Simple Majority vote at the next House meeting.
 \asubsection{Alumni Membership Expectations}

### 2022-08-27 constitution.tex
Removes ability for RTP's to overide requirments

--- 2022-04-12 constitution.tex
@@
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
-If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
+If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+The decision will be announced at the following House meeting.
 \asubsection{Active Membership Expectations}
@@
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
 \asubsection{Active Membership Leave of Absence}
@@
 	\item House History Director
-	\item Public Relations Director
 \end{itemize}
@@
 A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairperson and at least two-thirds of the Voting Members of the Executive Board must be present for the meeting to be called.
+However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.
 
@@
 	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
-\end{enumerate}
-
-\asubsection{Responsibilities of the Public Relations Director}
-\begin{enumerate}
-	\item To preside over Public Relations Directorship Meetings
-	\item To operate House social media accounts intended to represent House as a whole
-	\item To oversee the organization, initiation, and execution of House philanthropic events
-	\item To preserve and improve the public image of House
-	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
-
 \end{enumerate}
@@
 \hline
-Public Relations & 5\% \\
-\hline
-Accumulated & 5\% \\
+Accumulated & 10\% \\
 \hline
@@
 \\* \\*
-At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
 It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
@@
 	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
-	\item Candidates may be granted an exemption by current Root Type Persons.
-		Such an exemption may be withdrawn at any time by the current Root Type Persons.
 	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
@@
 \end{enumerate}
-\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
+\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
 \begin{enumerate}
@@
 \end{itemize}
-\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s), Public Relations Director}
+\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
 \begin{enumerate}
@@
 \article{Judicial}
-The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
+The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
 \asection{Formation of a Judicial Board}

### 2023-01-30 constitution.tex
normal pull request

--- 2022-04-12 constitution.tex
@@
 	\item Any responsibilities budgets or finances for the Ad Hoc Directorship are placed upon the assigned director
+\end{enumerate}
+
+\asubsection{Responsibilities of Committees}
+\begin{enumerate}
+	\item Committees are responsible for the task for which they were created
+	\item Any responsibilities of the Committee are placed upon the assigned Lead
 \end{enumerate}
@@
 
-\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
+\asubsection{Qualifications to be the House Secretary, an Ad Hoc Director, or a Committee Lead}
 \begin{enumerate}
@@
 The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.
+\asubsection{Selection of Committee Leads}
+\begin{enumerate}
+	\item When a group of House members feels a Committee is necessary, a public declaration may be made during House Meeting, stating the purpose of the Committee.
+	\item When a Committee is declared it is automatically granted status and a Lead is appointed, but all other aspects of a Committee's operation are at the Lead's discretion.
+	\item When a Committee is granted status it is never granted a budget.
+\end{enumerate}
 
@@
 	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
+\item When the task of a Committee has been completed, the Committee dissolves.
+	A Committee may be dissolved at any time by a simple majority vote of the Executive Board.
 \end{enumerate}

### 2023-04-19 constitution.tex

--- 2022-04-20 constitution.tex
@@
 \\*\\*
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
 If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
@@
 This may be appealed to the Executive Board in order to pursue a different outcome.
-Any Alumni Member in bad standing may become an Alumni in good standing by notifying the Evaluations Director of their intent to be brought up for a vote, who will bring them up for a Simple Majority vote at the next House meeting.
 \asubsection{Alumni Membership Expectations}

### 2023-09-03 constitution.tex
Fix "simple majority vote" from RTP Voting (#25)

@@
 The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
-It is a self-governing committee making decisions by a simply majority vote.
+It is a self-governing committee making decisions by a simple majority vote.
 Membership is composed of all Root Type Persons.

### 2023-09-09 constitution.tex
fixed major projects being presented to eboard by evals (#26)
Update Batch Vote Voting Chair Language. (#21)

@@
 	\item To act as a Judicial Board as defined in \ref{Judicial}
-	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
+	\item To review major projects, as defined in \ref{Expectations of House Members}
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
@@
 \asubsection{Batch Vote}
-When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote.
+When a Batch Vote is called for by the Chair of the Vote, a subset of the voting docket may be amended to a single vote.
 A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.

### 2023-09-09 constitution.tex
Removed Section formerly 6.C.5, Three Tiered Vote (#18)

@@
 An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
-\asubsection{Three Tiered}
-When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest or highest option will only pass if the votes cast for that selection exceed fifty percent of the Total Number of Votes Cast.
-If neither the highest or lowest selection exceeds fifty percent, the middle option will then automatically be passed.
-In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.
 

### 2023-09-09 constitution.tex
Add Anti-Hazing, Anti-Discrimination Clauses. (#19)

@@
 This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
+
+% ARTICLE VIII - ADHERENCE TO UNIVERSITY POLICIES
+\article{ADHERENCE TO UNIVERSITY POLICIES}
+\asection{Anti-Hazing}
+\asubsection{RIT Hazing Policy (RIT Student Conduct Process; IV. RIT Code of Conduct; 14. Hazing/Failure to Report
+Hazing)}
+Hazing/Failure to Report Hazing.
+Behavior, regardless of intent, which endangers the emotional, or physical health and safety of a Student for the purpose of membership, affiliation with, or maintaining membership in, a group or Student Organization.
+Hazing includes any level of participation, such as being in the presence, having awareness of hazing, or failing to report hazing.
+Examples of hazing include, but are not limited to, beating or branding, sleep deprivation or causing excessive fatigue, threats of harm, forcing or coercing consumption of food, water, alcohol or other drugs, or other substances, verbal abuse, embarrassing, humiliating, or degrading acts, or activities that induce, cause or require the Student to perform a duty or task which is not consistent with fraternal law, ritual or policy or involves a violation of local, state or federal laws, or the RIT Code of Conduct.
+\asubsection{NY State Hazing Law}
+\asubsubsection{§ 120.16 Hazing in the first degree.}
+A person is guilty of hazing in the first degree when, in the course of
+another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in
+conduct which creates a substantial risk of physical injury to such other person or a third person and thereby
+causes such injury. Hazing in the first degree is a class A misdemeanor.
+\asubsubsection{§ 120.17 Hazing in the second degree.}
+A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person.
+Hazing in the second degree is a violation.
+
+\asection{Anti-Discrimination Clause}
+This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity and gender expression, religion, age marital state, national origin, disability or veteran status.
+This policy will include but is not limited to, recruiting, membership, organization activities or opportunities to hold or run for club office.
+
+\asection{Statement of Compliance with University Regulations}
+This organization shall comply with all university and Center for Campus Life policies and regulations, and local, state and federal laws.
+
 \end{document}

### 2023-09-25 constitution.tex
Replaced paranthetical with "on the issue" (#24)
removed reference to physical packet document

@@
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active Members who have passed a Membership Evaluation, all Active Resident Members, all Introductory Resident Members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
 \begin{itemize}
@@
 \asubsection{Total Number of Possible Votes}
-The sum of the number of Active members eligible to vote (i.e. not on co-op)
+The sum of the number of Active members eligible to vote on the issue.
 \asubsection{Total Number of Votes Cast}

### 2023-09-27 constitution.tex
Resolve #49 Full Membership (#52)
* removed reference to full membership

* found and removed another reference to full membership

--- 2023-09-09 constitution.tex
@@
 \asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of full Resident or Non-Resident Membership.
-Occurs at the conclusion of the final week of the Process.
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
+It occurs at the conclusion of the final week of the Process.
 
@@
 		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
-	\item A subset of applications will be selected to move onto the House Fall Semester, are granted full membership privileges (including On-Floor status), and must participate in the Introductory Process as defined in \ref{The Introductory Process}.
-		An additional subset will be given Off-Floor status, but otherwise receive the same privileges and responsibilities.
+        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
+            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
+            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
 \end{enumerate}

### 2023-10-09 constitution.tex
Removed Section formerly 5.D.2.A.4.C, Alternate Housing, which violates RIT housing (#20)
* Removed Section formerly 5.D.2.A.4.C

* Re-added Three Tiered Vote

---------

Co-authored-by: Sam-Cordry <samcordry@gmail.com>
Co-authored-by: Robert Hochgraf <robehoco@gmail.com>
Resolve #7 Fix Financial Information/Calculations in 5.D.1.C (#34)
* Draft New Language for 5.D.1.C

* Update Draft per Feedback

@@
 \hline
-Evaluations \& Selections & 5\% \\
+Evaluations & 5\% \\
 \hline
@@
 
-The suggested total operational budget is \$8064.
-This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
-Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.
+% The suggested total operating budget is $8360.
+% This figure comes from having approximately 55 on-floor members with $80 per semester dues (totaling $8800) minus 5% set aside for Accumulated.
+
+Dues collected from on-floor members are to be distributed into directorship budgets as shown in the above table.
+Money allocated for Accumulated or collected from off-floor members is deposited into the CSH Account and saved.
 
@@
 An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
-
 \asubsection{Alternative}

### 2023-10-27 constitution.tex
Removed Privacy Issue Concerning Judicial Board (#27)

@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
-	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board
+	\item To respect the privacy of House Members confiding in the Executive Board, barring situations related to sexual assault or endangerment of oneself or others
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester

### 2023-10-28 constitution.tex
Updated list of active member priveledges

@@
 	\item Vote on all issues brought before the House
-	\item Reside on the House
-	\item Hold an Executive Board office on the House
+	\item Hold an E-Board position
 	\item Use Computer Science House facilities
-	\item Attend Computer Science House functions
-	\item Receive priority for available housing on the House when returning from cooperative education
-	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
+	\item Receive priority for on-floor housing (if they have On-Floor Status)
 \end{itemize}
@@
 
-\asection{Statement of Compliance with University Regulations}
+\asection{Statement of Compl
+iance with University Regulations}
 This organization shall comply with all university and Center for Campus Life policies and regulations, and local, state and federal laws.

### 2023-10-29 constitution.tex
Merge 2.C.3 and 2.C.4 (#97)
Allow Maintainers to be Alumni in bad standing (#98)

--- 2023-10-28 constitution.tex
@@
 \asubsection{Maintainer Qualifications}
-Maintainers must be Active or Alumni in good standing.
+Maintainers must be Active or Alumni Members.
 
@@
 
-\asubsection{Maintainer Resignations}
-Maintainers may resign at any time by notifying the current Executive Board and Maintainer group.
-
 \asubsection{Maintainer Term}
 Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
+A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.
 If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.

### 2023-10-29 constitution.tex
Move Closed E-Board section (#104)
Removed unnecessary colon (#119)
Removed explicit number of weeks in standard operating session (#116)

@@
 \asection{Standard Operating Session}
-The Standard Operating Session for Computer Science House is during the twenty-eight weeks of Fall and Spring semesters.
+The Standard Operating Session for Computer Science House is during the Fall and Spring semesters.
 The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
@@
 \asubsection{Active Membership Term}
-Active Membership shall last until the member: resigns or changes membership status.
+Active Membership shall last until the member resigns or changes membership status.
 
@@
 \end{itemize}
-\asection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
-A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairperson and at least two-thirds of the Voting Members of the Executive Board must be present for the meeting to be called.
 
@@
 \end{enumerate}
+
+\asection{Closed Executive Board}
+Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
+A closed Executive Board meeting may be called at any time by any member of the Executive Board.
+However, the Chairperson and at least two-thirds of the Voting Members of the Executive Board must be present for the meeting to be called.
 

### 2023-10-29 constitution.tex
Changed wording (#117)

@@
 \asubsection{Active Membership Selection}
-Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
+Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
 \\*\\*

### 2023-10-29 constitution.tex
Resolve #94 Remove list of directors (#121)
* Removed list of directors

* Added bullet point in responsibilities of each voting member stating that they can vote
Fixed wording (#118)

@@
 \asubsection{Active Membership Privileges}
-Active Members receive the right to:
+Active Members receive the privilege to:
 \begin{itemize}
@@
 Any large expenditures or large effect decisions must be brought before the entire House
-\asection{Members of the Executive Board}
-\asubsection{Voting Members}
-\begin{itemize}
-	\item Evaluations Director
-	\item Social Director(s)
-	\item Financial Director
-	\item Research and Development Director(s)
-	\item House Improvements Director
-	\item Operational Communications Director
-	\item House History Director
-	\item Public Relations Director
-\end{itemize}
-\asubsection{Non-Voting Members}
-\begin{itemize}
-	\item Chairperson
-	\item House Secretary
-	\item Ad Hoc Director(s)
-\end{itemize}
 
 \asection{Responsibilities}
+
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 	\item To prepare the House for Open Houses, tours, and special events
-\end{enumerate}
-
-\asubsection{Responsibilities of the Social Director}
+	\item To vote on issues presented to the Executive Board
+\end{enumerate}
+
+\asubsection{Responsibilities of the Social Director(s)}
 \begin{enumerate}
@@
 	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
+	\item To vote on issues presented to the Executive Board
 \end{enumerate}
@@
 	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
+	\item To vote on issues presented to the Executive Board
 
@@
 	\item To oversee the planning and execution of fundraising events
-\end{enumerate}
-
-\asubsection{Responsibilities of the Research and Development Director}
+	\item To vote on issues presented to the Executive Board
+\end{enumerate}
+
+\asubsection{Responsibilities of the Research and Development Director(s)}
 \begin{enumerate}
@@
 	\item To provide seminars and tutorials to educate House members in technical areas
+	\item To vote on issues presented to the Executive Board
 \end{enumerate}
@@
 	\item To oversee the general maintenance of the appearance of the House
+	\item To vote on issues presented to the Executive Board
 \end{enumerate}
@@
 	\item To report the status of the House computer systems and network to the Executive Board and House members
+	\item To vote on issues presented to the Executive Board
 \end{enumerate}
@@
 	\item To oversee the creation of a yearbook outlining House events for the year
+	\item To vote on issues presented to the Executive Board
 \end{enumerate}

### 2023-10-30 constitution.tex
Removed last sentence (#120)
Fixed wording (#111)
Removed 2a (#113)

@@
 \asection{Name}
-The name of this Special Interest House shall be Computer Science House.
+The name of this Special Interest House is Computer Science House.
 
@@
 \article{Constitutional Structure}
-
-\asection{House Charter}
-The House Charter is a document drafted by the department of Residence Life, setting down the guidelines within which this House operates and from which it derives its authority.
 
@@
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
-It is composed of the seven permanent directors and the Chairperson.
 \\*\\*

### 2023-10-31 constitution.tex
Update #44 Review Responsibilities of the Research and Development Director (#64)
* Update 5.C.7 per Discussion

* Readd and reword point (d) of 5.C.7

* Remove period at end of point (d)
Removed last line (#114)
Add quorum requirement for Maintainer nominations (#99)

@@
 The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.
-It is reviewed annually by the Department of Residence Life.
 
@@
 Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
-The Executive Board may choose to approve or reject the nomination by Simple Majority vote.
+The Executive Board may choose to approve or reject the nomination by Simple Majority vote with a quorum of seventy-five percent of the Total Number of Possible Votes.
 
@@
 	\item To oversee the planning, organization and construction of technical projects for the House's benefit
-	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
+	\item To strive to fulfill the House's need for technical equipment
 	\item To provide seminars and tutorials to educate House members in technical areas

### 2023-11-01 constitution.tex
Resolve #84 Condense 2.C.2 (#115)
* Condensed bulleted list of maintainer expectations

* Readded bullet point about keeping public record of changes
Resolve #58 Reduce number of words (#124)
* Reduce number of words

* Added latex comments defining incoming and current RIT students

@@
 \begin{itemize}
+	\item Be knowledgeable about the Constitution
 	\item Review changes to the Constitution for grammar, spelling, and internal consistency
+	\item Participate in discussion of proposals and amendments
 	\item Keep a public record of changes to the Constitution
-	\item Participate in discussion of proposals
-	\item Facilitate the creation of new changes to the Constitution by other members
-	\item Be knowledgeable about the Constitution
 \end{itemize}
@@
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\asubsubsubsection{Selection Process for Students Attending RIT for at Least One Semester}
+
+% Current RIT students is defined as students who have attended RIT for at least 1 full semester
+\asubsubsubsection{Selection Process for Current RIT Students}
 \begin{enumerate}
@@
 Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
-\asubsubsubsection{Selection Process for First Semester and Entering RIT Students}
+
+% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
+\asubsubsubsection{Selection Process for Incoming RIT Students}
 \begin{enumerate}

### 2023-11-01 constitution.tex
Resolve #29 Alumni Housing Status (#54)
* fixed ambiguity around alumni housing status

* Resolve #49 Full Membership (#52)

* removed reference to full membership

* found and removed another reference to full membership

* clarified alumni housing status

* Removed Section formerly 5.D.2.A.4.C, Alternate Housing, which violates RIT housing (#20)

* Removed Section formerly 5.D.2.A.4.C

* Re-added Three Tiered Vote

---------

Co-authored-by: Sam-Cordry <samcordry@gmail.com>
Co-authored-by: Robert Hochgraf <robehoco@gmail.com>

* Resolve #7 Fix Financial Information/Calculations in 5.D.1.C (#

@@
 Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
+They will retain their previous Housing Status if applicable.
 \\*\\*
 Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
-If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+If the vote passes the Alumni is reinstated as an Active Member effective immediately.
 \asubsection{Active Membership Expectations}
@@
 \asubsubsection{Housing Status}
-All Active and Introductory Members have a housing status.
+All Alumni, Active, and Introductory Members have a housing status.
 This status indicates their right to priority housing on the floor.
-Any Alumni Member in good standing will maintain their previous On Floor status upon a return to Active membership.
+Alumni Members in good standing keep the housing status they had as Active Members.
+Alumni Members in bad standing have Off-Floor status.
 \asubsubsubsection{On-Floor Status}

### 2023-11-01 constitution.tex
Combine Honorary and Advisory Memberships v1 (#23)

@@
 Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.
-
-\asection{Honorary Membership}
+\asection{Honorary and Advisory Memberships}
 \asubsection{Honorary Membership Qualifications}
 Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
-\asubsection{Honorary Membership Selection}
-Any House member may nominate a candidate for Honorary Membership by submitting the name in writing to the Evaluations Director.
-The Evaluation Director then begins the Honorary Membership Selection Process as defined in \ref{Selection Process for Honorary Members}
+\asubsection{Advisory Membership Qualifications}
+Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
+\asubsection{Honorary and Advisory Membership Selection}
+\begin{enumerate}
+	\item A House Member submits to the Evaluations Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
+The nomination must specify the type of membership the nominee is nominated for.
+	\item The Evaluations Director performs preliminary research on the candidate and presents the findings.
+	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.
+	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as defined in \ref{Two-Thirds}.
+		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
+	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
+    \item Candidates selected for Advisory Membership are notified of their acceptance as House Advisors and asked to accept or decline
+        the selection.
+\end{enumerate}
 \asubsection{Honorary Membership Expectations}
 Honorary Members are encouraged to remain in contact with the House.
-\asubsection{Honorary Membership Privileges}
-Honorary Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
-\asubsection{Honorary Membership Evaluations}
-Honorary Members are not subject to formal evaluations.
-\asubsection{Honorary Membership Resignations}
-An Honorary Member may resign by submitting in writing the reason for resignation to the Chairperson.
-The resignation will be read at the following House Meeting and become effective at that time.
-\asubsection{Honorary Membership Term}
-Honorary Membership shall last until the member resigns.
-
-\asection{Advisory Membership}
-\asubsection{Advisory Membership Qualifications}
-Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
-\asubsection{Advisory Membership Selection}
-The Executive Board may open nominations for Advisory Members.
-The candidates then participate in the Advisory Selection Process as defined in \ref{Selection Process for Advisory Members}
 \asubsection{Advisory Membership Expectations}
 Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
-Advisors are also encouraged to meet the House members and occasionally attend House activities.
-\asubsection{Advisory Membership Privileges}
-Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
-\asubsection{Advisory Membership Evaluations}
-Advisors are not subject to formal evaluations.
-\asubsection{Advisory Membership Resignations}
-An Advisor may resign by submitting in writing the reason for resignation to the Chairperson.
+Advisors are also encouraged to meet House members and occasionally attend House activities.
+\asubsection{Honorary and Advisory Membership Privileges}
+Honorary and Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
+\asubsection{Honorary and Advisory Membership Evaluations}
+Honorary and Advisory Members are not subject to formal evaluations.
+\asubsection{Honorary and Advisory Membership Resignations}
+An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chairperson.
 The resignation will be read at the following House Meeting and become effective at that time.
-\asubsection{Advisory Membership Term}
-Advisory Membership shall last until the member resigns.
+\asubsection{Honorary and Advisory Membership Term}
+Honorary and Advisory Memberships shall last until the member resigns.
 

### 2023-11-06 constitution.tex
Resolve #67 4.B.4 Remove Last Paragraph (#74)
* Remove voting exemption paragraph in 4.B.4

* Resolve changes to just those pertinent to the PR

---------

Co-authored-by: Sam-Cordry <samcordry@gmail.com>
Resolve #71 Condense Leave of Absence (#130)
* Codensed leave of absence

* Made requested changes

* Fixed formatting to be 1 sentence per line

@@
 \end{itemize}
-Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
-Exceptions may be made at the discretion of the Evaluations Director.
 \asubsection{Active Membership Evaluations}
@@
 \asection{Leave of Absence}
-A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
-Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
-House will also help to reacclimate any returning member back to the culture of House upon their return.
-Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.
-A member is also allowed to be physically present and also be on a leave of absence.
-\asubsection{Leave of Absence Request}
-A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
-The request is then given to a staff member of Residence Life, excluding student employees, for approval.
-A leave of absence start date can be backdated.
-At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
-\asubsection{Leave of Absence Duration}
-A leave of absence can be granted for up to the length of one semester.
-\asubsection{Leave of Absence Extension}
-A leave of absence can be extended by submitting a new request.
-\asubsection{Leave of Absence Return}
-A member may return from a leave of absence whenever they choose to.
-When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
-\asubsection{Modified Evaluations}
-A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
-\asubsection{Leave of Absence for an Executive Board Member}
-The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
-Upon returning, the member may assume their position and the interim director is removed.
-If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amongst the Executive Board to require a resignation from the Member.
+A Leave of Absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence, located at \url{https://www.rit.edu/policies/d021}.
+Additionally, the member should notify the Evaluations Director of their Leave, at which point they become exempt from all House requirements until they return.
 

### 2024-01-30 constitution.tex
Moved sentence to 5.E (#145)

@@
 \asection{Qualifications}
+Elected or selected candidates may not hold more then one simultaneous Executive Board positions, and must therefore resign their current position or decline the other position should they be elected or selected to another position.
 \asubsection{Qualifications to be the Chairperson, Evaluations Director}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member
-	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
 \end{enumerate}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member
-	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
 \end{enumerate}

### 2024-01-30 constitution.tex
Changed last bullet point in 5.F.1 to clarify that only one of the two members has to be present (#142)

@@
 	\item A member of a dual directorship may not hold any other Executive Board position.
-	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.
+	\item When attendance requirements call for the dual directorship position to be present, at least one of the members of the dual directorship is to fulfill the requirements.
 \end{itemize}

### 2024-01-30 constitution.tex
Resolve #78 - change reslife to student development (#112)
* Fixed wording

* Changed student development to campus life

* Made requested changes

@@
 \asection{Derivation of Authority}
-The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Residence Life.
+The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Campus Life and the Department of Residence Life.
 

### 2024-01-30 constitution.tex
i am an eepy bingus :clown: (#143)

@@
 \asubsubsection{Expenditure Approval}
-All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
-Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
-A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+All House expenditures must be approved by the Financial Director and the Director whose budget is going to be used for the expenditure.
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures (funds drawn for a specific event, project, piece of equipment, or service) may not exceed one-hundred dollars (\$100).
 \\* \\*
 If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
-At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+At the Financial Director's discretion, a Spending Committee may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not exceeding three-hundred dollars (\$300).
 A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
 \\*\\*
-For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
-This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+For expenditures exceeding \$300 in total funding, a Spending Presentation must be presented to House at a House meeting.
+This presentation includes the funds required for the expenditure, inventory of required resources, and (if applicable) a timeline for completion.
 \\* \\*

### 2024-01-30 constitution.tex
Resolve #36 Membership Evaluations Only Occur Once A Year (#48)
* Replaced references to Semi-Annual Membership Evaluations

* Changed 'current house members' to 'active members'

---------

Co-authored-by: Ella Soccoli <soccoli2015@gmail.com>

@@
 	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
-	\item To oversee the Semi-Annual Evaluations of current House members
+	\item To oversee the Membership Evaluations of Active Members
 	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
@@
 The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-Semi-Annual Evaluations Meetings are open only to current Active Members.
-All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
+All Executive Board members are expected to attend the Membership Evaluation to assist in the evaluations of House Members.
 \\* \\*

### 2024-01-30 constitution.tex
Update #41 Review Responsibilities of the Social Director (#63)
* Update 5.C.4 per Discussion

* reverted socials responsibilities to two bullet points with added clarification

---------

Co-authored-by: Jeremy Smart <jeremy3141592@gmail.com>

@@
 	\item To exercise general supervision over Social operations
-	\item To oversee the organization, initiation, and execution of House activities and events
-	\item To ensure that there is a variety of activities for House members to participate in throughout the academic year
-	\item To vote on issues presented to the Executive Board
+	\item To oversee the organization, initiation, and execution of House social activities
+  \item To ensure that there is a variety of events for House members to participate in throughout the academic year
 \end{enumerate}

### 2024-01-30 constitution.tex
Resolve #51 Add abbreviations section (#55)
* Drafted abbreviations section

* Added abbreviations section, finished replacements for Chair and Evals

* Finished abbreviations section

* Added newlines between sections in the tex document to make it easier to read

* Made requested changes

@@
 \usepackage{hyperref}
+
 % Reformat section titles
@@
 \author{Computer Science House Constitution Committee}
+
 % Last Modified Date
@@
 
+\article{Abbreviations and Definitions}
+Many of the commonly used abbreviations will be listed here, and the abbreviations will be used throughout the rest of the document.
+
+\begin{enumerate}
+	\item Chairperson - Chair
+	\item Evaluations - Evals
+	\item Research and Development - R\&D
+	\item House Improvements - IMPs
+	\item Operational Communications - OpComm
+	\item House History - History
+	\item Public Relations - PR
+	\item Socials - Social
+	\item Financials - Financial
+	\item Root Type Person - RTP
+	\item Introductory - Intro
+	\item Executive Board - E-Board
+	\item Department of Residence Life - ResLife
+	\item Constitutional Maintainer - Maintainer
+\end{enumerate}
+
 % ARTICLE II - CONSTITUTIONAL STRUCTURE
@@
 \end{itemize}
-Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.
+Failure to meet any of these expectations is grounds for revocation of Maintainer status by E-Board.
 
@@
 A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.
+
 If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
@@
 \asubsection{Maintainer Selection}
-Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
-The Executive Board may choose to approve or reject the nomination by Simple Majority vote with a quorum of seventy-five percent of the Total Number of Possible Votes.
+Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
+E-Board may choose to approve or reject the nomination by Simple Majority vote.
 
@@
 \asection{Introductory Membership}
+
 \asubsection{Introductory Membership Qualifications}
-Introductory Membership is open to all students at the Rochester Institute of Technology.
+Intro Membership is open to all RIT students.
+
 \asubsection{Introductory Membership Selection}
-Applicants notify the House of their interest in membership by submitting an application to the Evaluations Director.
+Applicants notify the House of their interest in membership by submitting an application to the Evals Director.
 They must then undergo the selection process as defined in \ref{Selection Processes}.
+
 \asubsection{Introductory Membership Expectations}
-Introductory members are expected to meet all the requirements of the Introductory Process, as described in \ref{Expectations of an Introductory Member}.
+Intro members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.
+
 \asubsection{Introductory Membership Privileges}
-Introductory members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
+Intro members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
+
 \asubsection{Introductory Membership Evaluations}
-Introductory members are evaluated on their performance during the introductory period.
-The introductory evaluation process is described in \ref{Introductory Evaluation}.
+Intro Members are evaluated on their performance during the intro period.
+The Intro Evals process is described in \ref{Introductory Evaluation}.
+
 \asubsection{Introductory Membership Leave of Absence}
-After completion of the Introductory Packet, an Introductory member may request a leave of absence through the process described in \ref{Leave of Absence}.
+After completion of the Intro Packet, an Intro member may request a leave of absence through the process described in \ref{Leave of Absence}.
+
 \asubsection{Introductory Membership Resignations}
-Introductory members may resign by submitting the request for termination of membership to the Chairperson, or Evaluations Director in writing before the completion of the introductory process.
+Intro members may resign by submitting the request for termination of membership to the Chair or Evals Director in writing before the completion of the intro process.
 \asubsection{Introductory Membership Term}
-Introductory membership shall last until the end of the introductory process, at which time active membership is granted or membership is revoked.
+Intro membership shall last until the end of the Intro Process, at which time active membership is granted or membership is revoked.
 
 \asection{Active Membership}
+
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
+Active Membership is open to all students currently enrolled at RIT who have passed the Intro Evals and their most recent Membership Evals.
+
 \asubsection{Active Membership Selection}
-Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
-They will retain their previous Housing Status if applicable.
+Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director.
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
-If the vote passes the Alumni is reinstated as an Active Member effective immediately.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evals Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
+If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+
 \asubsection{Active Membership Expectations}
 Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
+
 \asubsection{Active Membership Privileges}
@@
 	\item Vote on all issues brought before the House
-	\item Hold an E-Board position
+	\item Reside on the House
+	\item Hold an E-Board office on the House
 	\item Use Computer Science House facilities
-	\item Receive priority for on-floor housing (if they have On-Floor Status)
+	\item Attend Computer Science House functions
+	\item Receive priority for available housing on the House when returning from cooperative education
+	\item Guaranteed housing in compliance with ResLife policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
 \end{itemize}
+Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
+Exceptions may be made at the discretion of the Evals Director.
+
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+Active Members are evaluated annually through the Evals Process as described in \ref{Evaluations Processes}.
+
 \asubsection{Active Membership Leave of Absence}
@@
 \end{itemize}
+
 \asubsection{Active Membership Resignations}
-An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
+An Active member may resign by submitting, in writing, the reason for resignation to the Chair or Evals Director.
 Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
+
 \asubsection{Active Membership Term}
@@
 \asection{Alumni Membership}
+
 \asubsection{Alumni Membership Qualifications}
-Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
+Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evals and departed for reasons other than revocation of House Membership.
+
 \asubsection{Alumni Membership Selection}
-Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
+Active members who depart house (i.e. resign) after passing the current operating session's Membership Evals are considered to be Alumni in good standing.
 \\*\\*
-Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing.
-This may be appealed to the Executive Board in order to pursue a different outcome.
+Active members who depart house without passing the current operating session's Membership Evals are considered to be Alumni in bad standing.
+This may be appealed to E-Board in order to pursue a different outcome.
+
 \asubsection{Alumni Membership Expectations}
 There are no expectations associated with the Alumni Membership status.
+
 \asubsection{Alumni Membership Privileges}
@@
 \end{itemize}
+
 \asubsection{Alumni Membership Evaluations}
 Alumni Members are not subject to any evaluation.
+
 \asubsection{Alumni Membership Resignations}
 There are no resignations associated with Alumni Membership status.
+
 \asubsection{Alumni Membership Term}
 Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.
+
 \asection{Honorary and Advisory Memberships}
@@
 \asubsection{Advisory Membership Qualifications}
-Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
+Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.
 \asubsection{Honorary and Advisory Membership Selection}
 \begin{enumerate}
-	\item A House Member submits to the Evaluations Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
+	\item A House Member submits to the Evals Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
 The nomination must specify the type of membership the nominee is nominated for.
-	\item The Evaluations Director performs preliminary research on the candidate and presents the findings.
-	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
-		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.
+	\item The Evals Director performs preliminary research on the candidate and presents the findings.
+	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.
 	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as defined in \ref{Two-Thirds}.
@@
 \asubsection{Honorary and Advisory Membership Resignations}
-An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chairperson.
+An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chair.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 % ARTICLE V - EXECUTIVE BOARD
-\article{Executive Board}
-The Executive Board is the main governing body of the House.
+\article{E-Board}
+The E-Board is the main governing body of the House.
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
+
 \\*\\*
-There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
+There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
 Ad Hoc directorships are created on an as-needed basis.
@@
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\asubsection{Responsibilities of the Executive Board}
+
+\asubsection{Responsibilities of E-Board}
 \begin{enumerate}
 	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
-	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
+	\item To meet, as an E-Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
 	\item To report pertinent information to House members at the following House Meeting
-	\item To maintain records of the goals defined by each previous Executive Board
+	\item To maintain records of the goals defined by each previous E-Board
 	\item To act as a Judicial Board as defined in \ref{Judicial}
@@
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
-	\item To respect the privacy of House Members confiding in the Executive Board, barring situations related to sexual assault or endangerment of oneself or others
+	\item To respect the privacy of House Members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
 	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
@@
 
-\asubsection{Responsibilities of the Chairperson}
-\begin{enumerate}
-	\item To preside over Executive Board and House Meetings
-	\item To exercise general supervision over the operations of the Executive Board
+\asubsection{Responsibilities of the Chair}
+\begin{enumerate}
+	\item To preside over E-Board and House Meetings
+	\item To exercise general supervision over the operations of E-Board
 	\item To exercise general supervision over regular House activities
@@
 	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
-	\item To cast tie-breaking vote in a split decision in an Executive Board vote
+	\item To cast tie-breaking vote in a split decision in an E-Board vote
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Evaluations Meetings
-	\item To exercise general supervision over Evaluations operations
+	\item To preside over Evals Meetings
+	\item To exercise general supervision over Evals operations
 	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
-	\item To oversee the Membership Evaluations of Active Members
-	\item To collaborate with the Residence Life Advisor to determine room change selection and any changes of membership residency
+	\item To oversee the Membership Evals of Active Members
+	\item To collaborate with the ResLife Advisor to determine room change selection and any changes of membership residency
 	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
@@
 
-\asubsection{Responsibilities of the Public Relations Director}
-\begin{enumerate}
-	\item To preside over Public Relations Directorship Meetings
+\asubsection{Responsibilities of the PR Director}
+\begin{enumerate}
+	\item To preside over PR Directorship Meetings
 	\item To operate House social media accounts intended to represent House as a whole
@@
 	\item To preserve and improve the public image of House
-	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
-	\item To vote on issues presented to the Executive Board
-
+	\item To collaborate with other E-Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
+	\item To vote on issues presented to E-Board
 \end{enumerate}
@@
 
-\asubsection{Responsibilities of the Research and Development Director(s)}
-\begin{enumerate}
-	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
-	\item To exercise general supervision over Research and Development operations
+\subsubsection{Responsibilities of the R\&D Director}
+\begin{enumerate}
+	\item To preside over R\&D Meetings in which House members are encouraged to bring ideas for projects
+	\item To exercise general supervision over R\&D operations
 	\item To oversee the planning, organization and construction of technical projects for the House's benefit
@@
 
-\asubsection{Responsibilities of the House Improvements Director}
-\begin{enumerate}
-	\item To preside over House Improvements Meetings
-	\item To exercise general supervision over the House Improvements operations
+\asubsection{Responsibilities of the IMPs Director}
+\begin{enumerate}
+	\item To preside over IMPs Meetings
+	\item To exercise general supervision over the IMPs operations
 	\item To oversee the organization and construction of physical improvements to the House
@@
 
-\asubsection{Responsibilities of the Operational Communications Director}
-\begin{enumerate}
-	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
-	\item To report the status of the House computer systems and network to the Executive Board and House members
-	\item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\asubsection{Responsibilities of the House History Director}
-\begin{enumerate}
-	\item To preside over House History Meetings
-	\item To exercise general supervision over the House History operations
+\asubsection{Responsibilities of the OpComm Director}
+\begin{enumerate}
+	\item To represent the RTPs at E-Board Meetings and at House Meetings
+	\item To report the status of the House computer systems and network to E-Board and House members
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
+\asubsection{Responsibilities of the History Director}
+\begin{enumerate}
+	\item To preside over History Meetings
+	\item To exercise general supervision over the History operations
 	\item To maintain, uphold, and promote house traditions
@@
 \begin{enumerate}
-	\item To ensure that minutes are recorded and posted for Executive Board Meetings
+	\item To ensure that minutes are recorded and posted for E-Board Meetings
 	\item To ensure that minutes are recorded and posted for House Meetings
-	\item To oversee the maintenance of Executive Board records and documents
-	\item To provide administrative assistance to the Executive Board
-	\item To record all votes cast during House Meetings and Open Executive Board Meetings
+	\item To oversee the maintenance of E-Board records and documents
+	\item To provide administrative assistance to E-Board
+	\item To record all votes cast during House Meetings and Open E-Board Meetings
 \end{enumerate}
@@
 \asection{Operations}
+
 \asubsection{Operations of the Financial Directorship}
+
 \asubsubsection{Amount of House Dues}
 The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
+
 \asubsubsection{Collection of House Dues}
-The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+The collection period of house dues will be decided in conjunction with ResLife and Housing.
 During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
@@
 Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+
 \asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
@@
 If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
-If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
-If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
-If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
-In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to E-Board.
+If E-Board disagrees with the Financial Director, E-Board may reduce the required payment or extend the payment deadline.
+If E-Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+In the case the Financial Director or E-Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
 Additional time and reduction of dues may both be given to a member in an appropriate situation.
-All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+All dues must be collected in full before the annual Membership Evals (\ref{Membership Evaluation}).
 After this date, dues collection is suspended until the start of the next academic year.
+
 \asubsubsection{Breakdown of Dues for Directorship Budgets}
@@
 \hline
-Operational Communications & 20\% \\
+OpComm & 20\% \\
 \hline
-Evaluations & 5\% \\
+Evals & 5\% \\
 \hline
-House History & 10\% \\
+History & 10\% \\
 \hline
-House Improvements & 15\% \\
+IMPs & 15\% \\
 \hline
-Research and Development & 20\% \\
+R\&D & 20\% \\
 \hline
@@
 \hline
-Public Relations & 5\% \\
+PR & 5\% \\
 \hline
@@
 \asubsection{Operations of the Evaluations Directorship}
+
 \asubsubsection{The Introductory Process}
-The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+The Intro Process is designed to provide an easy means for Intro Members to meet existing House members, learn history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+
 \asubsubsubsection{The Evaluation Period}
 The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
-The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
-If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
-If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
-If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
+The Process shall be initiated by the Evals Director during either the first and second week of each semester.
+E-Board may hold a closed ballot Simple Majority vote to extend the Intro Process or the Intro Packet.
+If an Intro Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
+If deemed necessary by the Evals Director, or by an E-Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
+If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the Intro Process.
+
 \asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
+
+Each Intro Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Intro Members, and ten (10) of any combination of the following:
 \begin{itemize}
@@
 \end{itemize}
-At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+At the discretion of the Evals Director, any Intro Packet may be extended to accommodate extenuating circumstances.
+
 \asubsubsubsection{Expectations of an Introductory Member}
-Before the end of the Process, an Introductory Member is expected to:
+Before the end of the Process, an Intro Member is expected to:
 \begin{itemize}
 \item Attend all House meetings during the process
-\item Complete the Introductory Packet
+\item Complete the Intro Packet
 \item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
@@
 \asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
+
+The Introductory Evaluation is the process by which House chooses which Intro Members to extend an offer of Active Membership.
 It occurs at the conclusion of the final week of the Process.
@@
 \asubsubsubsubsection{Voting}
-On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+
+On a member by member basis, this evaluation process determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
 A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
@@
 House may choose any of the Outcomes for each member.
+
 \asubsubsubsubsection{Expectations of Voting Members}
-The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
-Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
+
+The following requirements must be met by the beginning of the Introductory Evals for an Active Member to be allowed to vote. 
+Any of these requirements may be waived by the Evals Director or a simple majority vote by E-Board
 \begin{itemize}
@@
 \begin{enumerate}
-	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
-	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
-	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
-		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+
+	\item Intro Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Intro Member fails to meet the requirements, their membership will be revoked.
+	\item An Intro member may be given a conditional to complete as a means of making up for missing requirements.
+		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evals Director, is then voted on by House.
 		Each conditional consists of a set of additional requirements and a deadline for completing them.
-		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+		When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
 		A conditional member who does not meet these additional requirements forfeits membership.
 \end{enumerate}
+
 \asubsubsection{Selection Processes}
@@
 \begin{enumerate}
-	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant submits an application to the Evals Director for review.
 	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
-	\item The application materials are then reviewed at an Evaluations meeting.
-	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
-\end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+	\item The application materials are then reviewed at an Evals meeting.
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Intro Member.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the Intro Process.
+This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
 The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Introductory Process.
+The member is not required to pay dues during the Intro Process.
 \\* \\*
@@
 \begin{enumerate}
-	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
-		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
-        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
-            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
-            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
-\end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+	\item During Spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
+		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
+        \item A subset of applicants will be offered Introductory Membership and must participate in the Intro Process defined in \ref{The Introductory Process}. 
+            A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor. 
+            The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the Intro Process.
+This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
 The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Introductory Process.
+The member is not required to pay dues during the Intro Process.
 \\* \\*
 Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+
 \asubsubsubsection{Selection Process for Honorary Members}
 \begin{enumerate}
-	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
-	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
-	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
-		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
+	\item A House Member submits to the Evals Director a nomination for a person they feel is deserving of Honorary Membership.
+	\item The Evals Director performs some preliminary research on the candidate and presents the findings.
+	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
 	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
@@
 \end{enumerate}
+
 \asubsubsubsection{Selection Process for Advisory Members}
 \begin{enumerate}
-	\item When there is a perceived need, the Executive Board may open nominations for Advisory Members.
+	\item When there is a perceived need, E-Board may open nominations for Advisory Members.
 		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
-	\item After the close of the nomination collection period, the Executive Board will arrange some means for the House to meet with the nominees.
+	\item After the close of the nomination collection period, E-Board will arrange some means for the House to meet with the nominees.
 	\item A discussion of the candidates will be held at the following House meeting.
@@
 \asubsubsection{Evaluations Processes}
-During the academic year, a House member is evaluated by the Membership Evaluation.
-The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-All Executive Board members are expected to attend the Membership Evaluation to assist in the evaluations of House Members.
+During the academic year, a House member is evaluated by the Membership Evals.
+The Membership Evals is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+Semi-Annual Evals Meetings are open only to current Active Members.
+All E-Board members are expected to attend the Membership Evals to assist in the evaluations of House members.
 \\* \\*
-At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
-It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
+At the beginning of any Evals Process listed herein, the Evals Director must read the sections of the Computer Science House Constitution used during the respective Evals Process.
+It is incumbent upon each House member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.
+
 \asubsubsubsection{Membership Evaluation}
 The Membership Evaluation process occurs once per academic year.
-It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+It is performed as part of the Evals Process that takes place during the spring semester to comply with RIT Housing deadlines.
+
 \asubsubsubsubsection{Voting}
-Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
-All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
-The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
+Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evals passes their Membership Evals without being voted on or evaluated by the quorum.
+All Active Members who have not recieved an exemption from E-Board prior to the Membership Evals will be evaluated on a Member by Member basis by a quorum of Active Members.
+The Membership Evals shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
 Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
-These requirements must be completed before the Membership Evaluation occurs.
+These requirements must be completed before the Membership Evals occurs.
 A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
@@
 \asubsubsubsubsection{Outcomes}
-Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+Members who pass Membership Evals have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
 \\* \\*
-If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
-If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+If a member fails and has never passed a Membership Evals in the past, their membership will be revoked immediately.
+If the member has previously passed a Membership Evals they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
 In either case, the member forfeits their ability to be included on the following year’s roster.
@@
 A conditional may be proposed by any member present at the Evaluation.
-If the conditional is approved by the Evaluations Director, it is then voted on by House.
+If the conditional is approved by the Evals Director, it is then voted on by House.
 Each conditional consists of a set of additional requirements a deadline for completing them.
-When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
 A conditional member who does not meet these additional requirements will have failed the evaluation.
+
 \asubsubsubsection{Appeals Process}
@@
 \\* \\*
-If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
+If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.
 
 \asubsubsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Executive Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and E-Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
 \\* \\*
 The member must participate significantly in at least one major project during the academic year.
-The member is required to submit a description for this major project to the Executive Board for approval.
+The member is required to submit a description for this major project to E-Board for approval.
 As an option to this requirement, the member may instead assist on a large number of House activities and projects.
 However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
-This participation will be evaluated by the Executive Board.
+This participation will be evaluated by E-Board.
 
 \asubsubsection{Housing Status}
-All Alumni, Active, and Introductory Members have a housing status.
+All Alumni, Active, and Intro Members have a housing status.
 This status indicates their right to priority housing on the floor.
@@
 Alumni Members in bad standing have Off-Floor status.
+
 \asubsubsubsection{On-Floor Status}
 Members with On-Floor status are eligible to live on the floor.
-To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
-The Evaluations Director will then bring them up for vote at the next meeting.
+To be granted On-Floor status, members may notify the Evals Director that they would like to come up for a vote.
+The Evals Director will then bring them up for vote at the next meeting.
+
 \asubsubsubsection{Off-Floor Status}
@@
 The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
-Each Active Member who passes the Membership Evaluation is granted two (2) Housing Priority Points.
+Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evals.
+Each Active Member who passes the Membership Evals is granted two (2) Housing Priority Points.
 \\* \\*
 In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
+
 \asubsubsubsection{Single Room Assignments}
@@
 Once in a single room, a House member retains the assignment until voluntarily giving it up.
-It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
+It should be noted that members selecting this option must agree to any additional charges applied by ResLife for residing in a single room.
+
 \asubsubsubsection{Double Rooms as Single rooms}
@@
 
-\asubsection{Operations of the Operational Communications Directorship}
-The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+\asubsection{Operations of the OpComm Directorship}
+The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
 It is a self-governing committee making decisions by a simple majority vote.
-Membership is composed of all Root Type Persons.
-
-\asubsubsection{Selection of a Root Type Person}
+Membership is composed of all RTPs.
+
+\asubsubsection{Selection of an RTP}
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
 \begin{enumerate}
-	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Nominations are taken from the RTPs and Prior RTPs meeting the selection criteria in \ref{Qualifications of an RTP}.
 	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
-		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
-		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
-\end{enumerate}
-
-\asubsubsection{Qualifications of a Root Type Person}
+	\item A list of all nominees who have accepted is presented to E-Board for approval.
+		This E-Board Meeting is closed to E-Board Members, RTPs, and House members with explicit invitation from the E-Board.
+	\item If an E-Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+		A simple majority E-Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the RTPs are accepted.
+\end{enumerate}
+
+\asubsubsection{Qualifications of an RTP}
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
-	\item Candidates may be granted an exemption by current Root Type Persons.
-		Such an exemption may be withdrawn at any time by the current Root Type Persons.
-	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
-		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
-	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+	\item Candidates may be granted an exemption by current RTPs.
+		Such an exemption may be withdrawn at any time by the current RTPs.
+	\item Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
+		Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
+	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior RTPs.
 \end{enumerate}
@@
 \asubsubsection{Creation of Accounts}
-Root Type Persons have the authority to manage user accounts for House systems.
-Before introductory, active, or alumni members may receive an account they must:
+RTPs have the authority to manage user accounts for House systems.
+Before intro, active, or alumni members may receive an account they must:
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-\end{enumerate}
-Accounts for honorary and advisory members may be created at the discretion of the Root Type Persons.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evals) in the Intro Packet or successfully complete Introductory Evals.
+\end{enumerate}
+Accounts for honorary and advisory members may be created at the discretion of the RTPs.
 
@@
 Members may sign a more recent revision of the Code of Conduct to update their agreement.
+
 \asubsubsubsection{Changes}
@@
 \begin{enumerate}
-	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item An RTP drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
 	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
@@
 Elected or selected candidates may not hold more then one simultaneous Executive Board positions, and must therefore resign their current position or decline the other position should they be elected or selected to another position.
-\asubsection{Qualifications to be the Chairperson, Evaluations Director}
+
+\asubsection{Qualifications to be the Chair, Evals Director}
 \begin{enumerate}
@@
 \end{enumerate}
-\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
+
+\subsubsection{Qualifications to be the Social Director(s), Financial Director, R\&D Director(s), IMPs Director, History Director, PR Director}
 \begin{enumerate}
@@
 \end{enumerate}
-\asubsection{Qualifications to be the Operational Communications Director}
-\begin{enumerate}
-	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
+
+\asubsection{Qualifications to be the OpComm Director}
+\begin{enumerate}
+	\item Candidates must be a current RTP \ref{Operations of the OpComm Directorship}.
 	\item Candidates must be a current Active Member.
-	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
+	\item An RTP cannot be the director if they currently hold any other voting E-Board Position.
 \end{enumerate}
@@
 \begin{enumerate}
-  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
+  \item House may choose to waive the following subset of the Qualifications for E-Board positions (defined under \ref{Qualifications}) for all Candidates:
     \begin{enumerate}
@@
       \item Candidates must have at least one full semester of House membership as an Active Member.
-      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
-    \end{enumerate}
-  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
+      \item Social and R\&D are the only voting E-Board positions that allow for Dual Directorship.
+    \end{enumerate}
+  \item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
   \item A Three-Quarters Immediate Vote, as defined in \ref{Three-Quarters} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
-  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
-  \item Waivers always apply to all Candidates for the Executive Board position.
+  \item Each vote to waive a Qualification must only apply to a single Qualification for a single E-Board position.
+  \item Waivers always apply to all Candidates for the E-Board position.
 \end{enumerate}
@@
 \asection{Selection}
+
 \asubsection{Dual Directorship}
-Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
+Social and R\&D are the only voting E-Board positions that allow for Dual Directorship.
 If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
@@
 Each different nomination must be a separate entry on the election ballot.
-Non-voting Executive Board positions (i.e. Ad Hoc Directors) are not restricted to single or dual directorship.
+Non-voting E-Board positions (i.e. Ad Hoc Directors) are not restricted to single or dual directorship.
 
@@
 	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
-		The vacated office is then handled like any other vacated office; see \ref{Executive Board Resignations}.
-	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
+		The vacated office is then handled like any other vacated office; see \ref{E-Board Resignations}.
+	\item During an official E-Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
 		The members of the dual directorship need not vote the same way in a vote.
-	\item A member of a dual directorship may not hold any other Executive Board position.
+	\item A member of a dual directorship may not hold any other E-Board position.
 	\item When attendance requirements call for the dual directorship position to be present, at least one of the members of the dual directorship is to fulfill the requirements.
 \end{itemize}
-\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s), Public Relations Director}
-\begin{enumerate}
-	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
+
+\subsubsection{Selection of the Chair, Evals Director, Social Director(s), Financial Director, IMPs Director, History Director,  R\&D Director(s), PR Director}
+\begin{enumerate}
+	\item The opening of the E-Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
 		Any House member may nominate any member or pair of members where appropriate for a Directorship.
@@
 		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
-	\item The date and time of candidate speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
+	\item The date and time of candidate speeches will be announced by a member of E-Board at least five (5) days prior to the event. 
 		All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of House Members}.
-		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
+		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evals Director, who will record the reason with the absence.
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.
@@
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chairperson will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
+	\item At the end of the voting period, the Chair will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
 	\item The winners are determined via the process described in \ref{Alternative Vote}.
@@
 \end{enumerate}
-\asubsection{Selection of the Operational Communications Director}
-\begin{enumerate}
-	\item A candidate for the Operational Communications Directorship shall be chosen by the current Root Type Persons.
+
+\asubsection{Selection of the OpComm Director}
+\begin{enumerate}
+	\item A candidate for the OpComm Directorship shall be chosen by the current RTPs.
 	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
-	\item The candidate is presented to the Executive Board for approval.
-		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
-		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
-\end{enumerate}
+	\item The candidate is presented to E-Board for approval.
+		This E-Board meeting is closed to the E-Board Members, RTPs, and House members with explicit invitation from E-Board.
+	\item All current Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
+		A simple majority E-Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
+\end{enumerate}
+
 \asubsection{Selection of Ad Hoc Directors}
 \begin{enumerate}
-	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
+	\item When E-Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to E-Board and E-Board decides by simple majority vote whether directorship status is granted.
 	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
 \end{enumerate}
+
 \asubsection{Selection of the House Secretary}
-The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary.
-The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.
-
-\asection{Executive Board Resignations}
-An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
+E-Board may choose to select a current voting E-Board member, or to select any interested Active member, as House Secretary.
+The selection process can be an informal appointment, or follow an election process similar to other voting E-Board positions.
+
+\asection{E-Board Resignations}
+An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 Following a resignation, the Selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
-To postpone such a Selection, the Chairperson may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
+To postpone such a Selection, the Chair may call for an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
 
 \asection{Appointment of an Interim Director}
-The duties and responsibilities of a vacated office are assumed by the Chairperson or by an Active member that is appointed at the Chairperson's discretion until the new member takes office.
-The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
+The duties and responsibilities of a vacated office are assumed by the Chair or by an Active member that is appointed at the Chair's discretion until the new member takes office.
+The vote of a vacated E-Board position shall be cast as an abstention in all E-Board matters where this vote is required to be cast.
 
@@
 \begin{enumerate}
-	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
-	\item The impeachment petition is then presented at an Executive Board Meeting.
-		The member(s) initiating the petition present their case to the Executive Board.
-		The Executive Board then questions the accused member of the allegations.
-	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
-		If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed.
+	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
+	\item The impeachment petition is then presented at an E-Board Meeting.
+		The member(s) initiating the petition present their case to E-Board.
+		E-Board then questions the accused member of the allegations.
+	\item E-Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
+		If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
 		This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
-	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
+	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
 	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
@@
 	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
-		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Executive Board Resignations}.
-	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of the Executive Board.
+		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{E-Board Resignations}.
+	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of E-Board.
 \end{enumerate}
@@
 \begin{enumerate}
-\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
+\item The Election Process for the following year's E-Board members shall begin in the middle of Spring semester.
 \item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
@@
 \asection{Appeals}
-Decisions made by the Executive Board may be appealed and overturned.
-To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
-After the appeal is presented, a Simple Majority vote is held by the Executive Board whether or not to overturn and reevaluate the decision.
-If the vote passes, the Executive Board may discuss and make a new ruling by another Simple Majority vote.
+Decisions made by E-Board may be appealed and overturned.
+To initiate an appeal, a member must have the support of three voting E-Board Members, or a petition with the signatures of one-third of Active Members.
+After the appeal is presented, a Simple Majority vote is held by E-Board whether or not to overturn and reevaluate the decision.
+If the vote passes, E-Board may discuss and make a new ruling by another Simple Majority vote.
 
@@
 This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
+
 \asection{Definitions}
@@
 The sum of the number of Active members eligible to vote on the issue.
+
 \asubsection{Total Number of Votes Cast}
 The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
+
 \asubsection{Quorum}
@@
 A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
+
 \asubsection{Proxy Ballot}
@@
 Proxy Votes are only permissible where explicitly stated, at the discretion of the Chair of the Vote.
+
 \asubsection{Abstention}
@@
 Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
+
 \asubsection{Vote Counters}
@@
 \asection{Types of Voting}
+
 \asubsection{Alternative Vote}
+
 \asubsubsection{Method of Vote}
@@
 The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
+
 \asubsection{Balloted Vote}
+
 \asubsubsection{Method of Vote}
@@
 The Vote Counters then tally the results.
+
 \asubsubsection{Voting Period}
@@
 The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
+
 \asubsection{Immediate Vote}
+
 \asubsubsection{Method of Vote}
@@
 The chairing member will count the number of members casting their immediate vote for that possibility.
+
 \asubsubsection{Voting Period}
 An immediate vote lasts as long as it takes for all votes to be tallied.
+
 \asubsection{Secret Immediate Vote}
+
 \asubsubsection{Method of Vote}
@@
 The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
+
 \asubsubsection{Voting Period}
 A secret immediate vote lasts as long as it takes for all votes to be tallied.
+
 \asubsection{Batch Vote}
@@
 Numbers for non-standard votes are defined in the section describing the actual vote.
+
 \asubsection{Simple Majority}
@@
 An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
+
 \asubsection{Fifty Percent}
@@
 An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
+
 \asubsection{Two-Thirds}
@@
 An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
+
 \asubsection{Three-Quarters}
@@
 An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
+
 \asubsection{Alternative}
@@
 \asection{Ties Between Vote Options}
+
 \asubsection{With Pass/Fail}
 If the number of votes cast for the pass option equals the number of votes cast for the fail option, then the vote has failed.
+
 \asubsection{With Multiple Options}
@@
 If only one option may pass, then the vote must be recast or tabled at the discretion of the Chair of the Vote.
-In the event of a tie in an Executive Board vote, the Chairperson may cast the tie-breaking vote.
+In the event of a tie in an E-Board vote, the Chair may cast the tie-breaking vote.
 
@@
 \article{Judicial}
-The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
+E-Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
+
 \asection{Formation of a Judicial Board}
-A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
-If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
+A Judicial Board is made up of the Chair, the Evals director, and an additional voting member of E-Board chosen by a majority vote among E-Board.
+If either the Chair or Evals Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of E-Board by means of a simple majority vote amongst the remaining E-Board members.
+
 \asection{Judicial Investigation}
 The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
+
 \asection{Judicial Ruling}
 The Judicial Board may present an official ruling following the Judicial Investigation.
-This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
+This ruling may be appealed in the same manner as an E-Board decision \ref{Appeals}.
 
@@
 \article{ADHERENCE TO UNIVERSITY POLICIES}
+
 \asection{Anti-Hazing}
+
 \asubsection{RIT Hazing Policy (RIT Student Conduct Process; IV. RIT Code of Conduct; 14. Hazing/Failure to Report
@@
 Examples of hazing include, but are not limited to, beating or branding, sleep deprivation or causing excessive fatigue, threats of harm, forcing or coercing consumption of food, water, alcohol or other drugs, or other substances, verbal abuse, embarrassing, humiliating, or degrading acts, or activities that induce, cause or require the Student to perform a duty or task which is not consistent with fraternal law, ritual or policy or involves a violation of local, state or federal laws, or the RIT Code of Conduct.
+
 \asubsection{NY State Hazing Law}
+
 \asubsubsection{§ 120.16 Hazing in the first degree.}
@@
 causes such injury. Hazing in the first degree is a class A misdemeanor.
+
 \asubsubsection{§ 120.17 Hazing in the second degree.}

### 2024-02-20 constitution.tex
Removed extra newline that caused document to fail to compile (#151)
Clarify voting member of E-Board (#150)
Reordered dues table from most to least budget (#131)
Move Open House responsibilities to PR (#149)

@@
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
-
 \\*\\*
 There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
+A voting E-Board member is considered to be any person with a non-zero vote on E-Board.
+% Defined this way so that (for example) each member in a dual directorship is each considered to be a voting member on E-Board.
 Ad Hoc directorships are created on an as-needed basis.
@@
 A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
-Any large expenditures or large effect decisions must be brought before the entire House
+Any large expenditures or large effect decisions must be brought before the entire House.
 
@@
 	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
-	\item To prepare the House for Open Houses, tours, and special events
 	\item To vote on issues presented to the Executive Board
@@
 	\item To collaborate with other E-Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
+    \item To oversee the preparation of House for Open Houses, tours, and special events
 	\item To vote on issues presented to E-Board
@@
 \hline
-Evals & 5\% \\
+R\&D & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+IMPs & 15\% \\
 \hline
@@
 \hline
-IMPs & 15\% \\
-\hline
-R\&D & 20\% \\
-\hline
-Social & 20\% \\
+Evaluations & 5\% \\
 \hline

### 2024-02-20 constitution.tex
Reword 5.D.1.B.1 since it was really long and repeated a lot of the same information. (#144)
* mmmmmmmmmm member dues are yummy why cant we eat them?

* Add language to explicitly allow for reduction and extension

---------

Co-authored-by: Sam Cordry <samcordry@gmail.com>
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>

@@
 \asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
-If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
-If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
-If the Financial Director deems their situation inappropriate for extension, the member may appeal to E-Board.
-If E-Board disagrees with the Financial Director, E-Board may reduce the required payment or extend the payment deadline.
-If E-Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
-In the case the Financial Director or E-Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
-Additional time and reduction of dues may both be given to a member in an appropriate situation.
-All dues must be collected in full before the annual Membership Evals (\ref{Membership Evaluation}).
+If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
+The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
+If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
+If appealed, E-Board may provide an extension and/or reduction to the member.
+If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
 After this date, dues collection is suspended until the start of the next academic year.

### 2024-02-28 constitution.tex
Updated qualifications of an RTP (#153)

@@
 \begin{enumerate}
-	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
-	\item Candidates may be granted an exemption by current RTPs.
-		Such an exemption may be withdrawn at any time by the current RTPs.
+	\item Candidates must be Active Members
+\end{enumerate}
+
+\asubsubsection{Prior RTPs}
+\begin{enumerate}
 	\item Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.

### 2024-02-28 constitution.tex
Resolves #46 - Review Responsibilities of OpComm Director (#154)
* Updated responsibilities of opcomm director

* Fixed wording
134 Define intro process (#152)
* Fixed wording of definition of intro process

* Updated wording

@@
 	\item Financials - Financial
+	\item Executive Board - E-Board
 	\item Root Type Person - RTP
+	\item Constitutional Maintainer - Maintainer
 	\item Introductory - Intro
-	\item Executive Board - E-Board
 	\item Department of Residence Life - ResLife
-	\item Constitutional Maintainer - Maintainer
 \end{enumerate}
@@
 	\item To report the status of the House computer systems and network to E-Board and House members
+	\item To facilitate communications with RIT Information and Technology Services
 	\item To vote on issues presented to E-Board
@@
 \asubsubsection{The Introductory Process}
-The Intro Process is designed to provide an easy means for Intro Members to meet existing House members, learn history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+The Intro Process allows Intro Members to learn about House and demonstrate their interest in becoming Active Members.
+During this period, Intro Members will meet existing House Members, learn House History, and be evaluated for Active Membership by existing House members.
 

### 2024-03-03 constitution.tex
resolve #37 - VOTING AMENDMENT 🎉 (#135)
:yippee: :party-kirby: :dancing_penguin:

@@
 A Maintainer may approve any proposed change that does not affect the meaning of the document.
-Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
-A quorum of fifty percent of the Total Number of Possible Votes is required for passage.
+Alternatively, the change may be presented to the House for discussion followed by an Immediate One-Half Vote with fifty percent Quorum.
 
@@
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with Two-Thirds Quorum \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
-A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
-A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
-The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
-There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
-A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
+The Constitution may be overridden by an Nine-Tenths Immediate Vote with eighty-five percent Quorum.
 
@@
 \end{itemize}
+
 Failure to meet any of these expectations is grounds for revocation of Maintainer status by E-Board.
@@
 \asubsection{Maintainer Term}
-Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
-A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.
-
+Maintainer status lasts until it is resigned, or until it is revoked by an E-Board Vote.
 If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
@@
 Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
-E-Board may choose to approve or reject the nomination by Simple Majority vote.
+E-Board may choose to approve or reject the nomination by an E-Board Vote.
 
@@
 \asubsection{Active Membership Selection}
-Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director.
+
+Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
+They will retain their previous Housing Status if applicable.
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evals Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
+Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate.
+The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent Quorum at the next House meeting.
+
 If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
@@
 \end{itemize}
-Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
-Exceptions may be made at the discretion of the Evals Director.
 
@@
 \asubsection{Advisory Membership Qualifications}
-Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.
+Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
 \asubsection{Honorary and Advisory Membership Selection}
@@
 		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.
+
 	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as defined in \ref{Two-Thirds}.
@@
 \asubsection{Honorary and Advisory Membership Resignations}
+
 An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chair.
@@
   \item To ensure that there is a variety of events for House members to participate in throughout the academic year
+  \item To vote on issues presented to the Executive Board
 \end{enumerate}
@@
 \\* \\*
-If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
-At the Financial Director's discretion, a Spending Committee may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not exceeding three-hundred dollars (\$300).
-A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+If the above amounts are to be exceeded, the expenditure must be approved by an Immediate Relative Majority Vote at a House meeting before the funds may be appropriated.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A Two-Thirds Immediate Vote with twenty-five percent Quorum is required to approve the purchase.
 \\*\\*
@@
 \\* \\*
-If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent Quorum, regardless of the amount.
 This amount is to be directly subtracted from the general CSH account.
@@
 The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evals Director during either the first and second week of each semester.
-E-Board may hold a closed ballot Simple Majority vote to extend the Intro Process or the Intro Packet.
-If an Intro Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
-If deemed necessary by the Evals Director, or by an E-Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
-If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the Intro Process.
-
+The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
+The Executive Board may approve an extension to the Introductory Process by an Executive Board Vote.
+If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
+If deemed necessary by the Evaluations Director, or by an Executive Board Vote, the second intro process must begin within nine (9) days of the first process ending.
+If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
 \asubsubsubsection{The Introductory Packet}
-
-Each Intro Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Intro Members, and ten (10) of any combination of the following:
+Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
+
 \begin{itemize}
@@
 \end{itemize}
-At the discretion of the Evals Director, any Intro Packet may be extended to accommodate extenuating circumstances.
+At the discretion of the Evals Director or an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.
 
@@
 \asubsubsubsection{Introductory Evaluation}
-
-The Introductory Evaluation is the process by which House chooses which Intro Members to extend an offer of Active Membership.
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
 It occurs at the conclusion of the final week of the Process.
@@
 \asubsubsubsubsection{Voting}
-
-On a member by member basis, this evaluation process determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
-A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
+On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+An Immediate Relative Majority Vote with two-thirds Quorum is required for the evaluation to be valid.
+For an Active Member to be eligible to vote during the evaluation process they must meet the requirements outlined in \ref{Expectations of Voting Members}.
+
 Neither absentee nor proxy votes are allowed.
@@
 \asubsubsubsubsection{Expectations of Voting Members}
-
-The following requirements must be met by the beginning of the Introductory Evals for an Active Member to be allowed to vote. 
-Any of these requirements may be waived by the Evals Director or a simple majority vote by E-Board
+The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
+Any of these requirements may be waived by the Evals Director or an E-Board Vote.
+
 \begin{itemize}
@@
 \begin{enumerate}
-
-	\item Intro Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
-	\item If an Intro Member fails to meet the requirements, their membership will be revoked.
-	\item An Intro member may be given a conditional to complete as a means of making up for missing requirements.
-		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evals Director, is then voted on by House.
+	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
+		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
 		Each conditional consists of a set of additional requirements and a deadline for completing them.
@@
 	\item The application materials are then reviewed at an Evals meeting.
-	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Intro Member.
+	Then an Immediate Relative Majority Vote of attending members is held on whether or not to accept the person as an Intro Member.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item During Spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
-		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
-        \item A subset of applicants will be offered Introductory Membership and must participate in the Intro Process defined in \ref{The Introductory Process}. 
-            A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor. 
-            The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
+	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
+		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
+        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
+            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
+            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item A House Member submits to the Evals Director a nomination for a person they feel is deserving of Honorary Membership.
-	\item The Evals Director performs some preliminary research on the candidate and presents the findings.
-	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
-		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
-	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as described in \ref{Two-Thirds}.
+	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
+	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
+	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
+		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
+	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds Balloted Vote with two-thirds Quorum.
 		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
@@
 	\item A discussion of the candidates will be held at the following House meeting.
-	\item Ballots are distributed for each nominee as a fifty-percent House vote defined in \ref{Fifty Percent}.
+	\item Ballots are distributed for each nominee as a One-Half Balloted Vote with fifty percent Quorum.
 		Voting must remain open for a minimum of a forty-eight hour period.
@@
 Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
-These requirements must be completed before the Membership Evals occurs.
-A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+These requirements must be completed before the Membership Evaluation occurs.
+A Secret Immediate Relative Majority vote with two-thirds Quorum is required for the evaluation to be valid.
 Neither absentee nor proxy votes are allowed.
@@
 A conditional may be proposed by any member present at the Evaluation.
-If the conditional is approved by the Evals Director, it is then voted on by House.
+If the conditional is approved by the Evaluations Director, it is then voted on by House as described in \ref{Voting}.
 Each conditional consists of a set of additional requirements a deadline for completing them.
@@
 \asubsubsection{Housing Status}
-All Alumni, Active, and Intro Members have a housing status.
+All Alumni, Active, and Introductory Members have a housing status.
 This status indicates their right to priority housing on the floor.
@@
 Members with On-Floor status are eligible to live on the floor.
-To be granted On-Floor status, members may notify the Evals Director that they would like to come up for a vote.
-The Evals Director will then bring them up for vote at the next meeting.
+To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
+The Evaluations Director will then bring them up for a One-Half Immediate vote among attending Active members at the next evaluations meeting.
+If the Evaluations Director determines that too few members are present to hold a vote, the member will be brought up for a vote at the next evaluations meeting.
 
@@
 
-\asubsection{Operations of the OpComm Directorship}
-The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
-It is a self-governing committee making decisions by a simple majority vote.
-Membership is composed of all RTPs.
+\asubsection{Operations of the Operational Communications Directorship}
+The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+It is a self-governing committee making decisions by Immediate Relative Majority vote (two-thirds Quorum) of Current Root Type Persons.
+Membership is composed of all Root Type Persons.
 
@@
 	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-	\item A list of all nominees who have accepted is presented to E-Board for approval.
-		This E-Board Meeting is closed to E-Board Members, RTPs, and House members with explicit invitation from the E-Board.
-	\item If an E-Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
-		A simple majority E-Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the RTPs are accepted.
+	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
+		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+		An Executive Board Vote is taken to determine whether the nominations of the Root Type Persons are accepted.
 \end{enumerate}
@@
 	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
-	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a One-Half Balloted House vote (fifty percent Quorum) as described in \ref{Balloted Vote}.
 \end{enumerate}
@@
     \end{enumerate}
-  \item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
-  \item A Three-Quarters Immediate Vote, as defined in \ref{Three-Quarters} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
-  \item Each vote to waive a Qualification must only apply to a single Qualification for a single E-Board position.
-  \item Waivers always apply to all Candidates for the E-Board position.
+  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
+  \item A Three-Quarters Immediate Vote with three-quarters Quorum is then taken to determine whether the proposed waiver shall take effect.
+  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
+  \item Waivers always apply to all Candidates for the Executive Board position.
 \end{enumerate}
@@
 		The members of the dual directorship need not vote the same way in a vote.
-	\item A member of a dual directorship may not hold any other E-Board position.
-	\item When attendance requirements call for the dual directorship position to be present, at least one of the members of the dual directorship is to fulfill the requirements.
+	\item A member of a dual directorship may not hold any other Executive Board position.
+	\item When attendance requirements call for the dual directorship position to be present, both directorship members must be present to fulfill the requirements.
+	\item Dual directorships must have both members present for to count towards Quorum in an Executive Board Vote.
 \end{itemize}
@@
 	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.
-	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
+	\item Ballots will then be distributed for a Balloted Vote \ref{Balloted Vote} and voting will be open for a minimum of a forty-eight hour period.
 		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
 		In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chair will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
-	\item The winners are determined via the process described in \ref{Alternative Vote}.
-		A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
+	\item At the end of the voting period, the Chairperson will terminate voting.
+	\item The winners are determined via the process described in \ref{Ranked Choice}.
+		A fifty-percent Quorum is required for the election to be official.
 		All winners are notified of their election.
@@
 		If not, the winner will assume office at the end of the current term (\ref{Term}).
-		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
+		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Ranked Choice}.
 \end{enumerate}
@@
 	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
-	\item The candidate is presented to E-Board for approval.
-		This E-Board meeting is closed to the E-Board Members, RTPs, and House members with explicit invitation from E-Board.
-	\item All current Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
-		A simple majority E-Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
+	\item The candidate is presented to the Executive Board for approval.
+		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
+		An Executive Board Vote is taken to determine whether the candidate is selected for the position.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item When E-Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to E-Board and E-Board decides by simple majority vote whether directorship status is granted.
+	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board.
+  An Executive Board Vote is taken to determine whether directorship status is granted.
 	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
@@
 Following a resignation, the Selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
-To postpone such a Selection, the Chair may call for an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
+To postpone such a Selection, the Chairperson may chair an Immediate Relative Majority Vote \ref{Immediate Vote} \ref{Relative Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
 
@@
 \begin{enumerate}
-	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
-	\item The impeachment petition is then presented at an E-Board Meeting.
-		The member(s) initiating the petition present their case to E-Board.
-		E-Board then questions the accused member of the allegations.
-	\item E-Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
-		If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
+	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
+	\item The impeachment petition is then presented at an Executive Board Meeting.
+		The member(s) initiating the petition present their case to the Executive Board.
+		The Executive Board then questions the accused member of the allegations.
+	\item An Executive Board Vote is taken on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
+		If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed.
 		This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
@@
 	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
-		Votes shall be collected and counted as described in \ref{Balloted Vote}.
-	\item A quorum of two-thirds of the Total Number of Possible Votes is necessary for the vote to be official.
-		A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
+		Votes shall be collected and counted for a Two-Thirds Balloted Vote described in \ref{Balloted Vote}.
+	\item A two-thirds Quorum is necessary for the vote to be official.
+		If the resolution passes, the accused officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
 		If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
-	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
-		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{E-Board Resignations}.
-	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of E-Board.
+		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Executive Board Resignations}.
+	\item House Secretary can be impeached according to the above process, or may be dismissed by an Executive Board Vote.
 \end{enumerate}
@@
 \asection{Appeals}
-Decisions made by E-Board may be appealed and overturned.
-To initiate an appeal, a member must have the support of three voting E-Board Members, or a petition with the signatures of one-third of Active Members.
-After the appeal is presented, a Simple Majority vote is held by E-Board whether or not to overturn and reevaluate the decision.
-If the vote passes, E-Board may discuss and make a new ruling by another Simple Majority vote.
+Decisions made by the Executive Board may be appealed and overturned.
+To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
+After the appeal is presented, an Executive Board Vote is taken to determine whether or not to overturn and reevaluate the decision.
+If the vote passes, the Executive Board may discuss and make a new ruling by another Executive Board Vote.
 
@@
 \asection{Definitions}
-\asubsection{Total Number of Possible Votes}
-The sum of the number of Active members eligible to vote on the issue.
-
-\asubsection{Total Number of Votes Cast}
-The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
+\asubsection{Eligible Votes}
+The number of Active members eligible to vote on the issue.
+\asubsection{Votes Cast}
+The number of ballots cast in a vote, excluding Abstentions.
 
 \asubsection{Quorum}
-A Quorum is defined by the minimum number of votes cast required for a vote to be official.
-It is a fraction or a percentage of the total number of possible votes.
+The minimum Votes Cast for vote to be considered valid.
 Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention.
-A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
-
-\asubsection{Proxy Ballot}
-A Proxy Vote is defined as any ballot that was cast by one member on behalf of another member.
-Any member may cast a Proxy Vote for another member who is unable to actually participate in the vote.
-A Proxy Vote must be explicitly written down and signed by the member not in attendance.
+A Quorum is expressed as a fraction or percentage of Eligible Votes (rounded up to the nearest vote) unless otherwise specified in the text of the vote.
+\asubsection{Proxy Vote}
+A vote cast by one member on behalf of another.
+Proxy Votes are only permissible at the discretion of the Chair of the Vote, and may be disallowed in the text describing the vote.
+Proxy Votes must be documented in writing and signed by the absent member.
 The count of all Proxy Vote must be recorded and announced in all votes.
-Proxy Votes are only permissible where explicitly stated, at the discretion of the Chair of the Vote.
 
 \asubsection{Abstention}
-An Abstention is defined as a vote indicating a neutral position in the vote.
+An Abstention is a neutral vote that counts towards the Quorum but not towards determining the outcome of a vote.
 A means to abstain must always be provided in a vote.
-Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
-
 \asubsection{Vote Counters}
@@
 
-\asection{Types of Voting}
-
-\asubsection{Alternative Vote}
-
+\asection{Voting Procedures}
+\asubsection{Balloted Vote}
 \asubsubsection{Method of Vote}
-Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
-A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
-At the end of the voting period, the Chair of the Vote collects the ballots, closing the voting period.
-The Vote Counters then tally the results.
-
-Voters rank the options by placing a '1' by their first choice, a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of options.
-
+Votes are cast on ballots that provide a means to indicate every possible option in the vote.
 \asubsubsection{Voting Period}
@@
 
-\asubsection{Balloted Vote}
-
-\asubsubsection{Method of Vote}
-Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
-A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
+The voting period opens once ballots are distributed to each House member eligible to cast a vote.
 At the end of the voting period, the Chair of the Vote collects the ballots, closing the voting period.
 The Vote Counters then tally the results.
-
-\asubsubsection{Voting Period}
-For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
-For any other type of vote, the voting period must be at least twenty-four (24) hours.
-The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
 
@@
 The chairing member will count the number of members casting their immediate vote for that possibility.
-
+Any members that count towards Quorum that do not explicitly cast a vote will have their vote counted as an Abstention.
 \asubsubsection{Voting Period}
-An immediate vote lasts as long as it takes for all votes to be tallied.
-
-\asubsection{Secret Immediate Vote}
-
-\asubsubsection{Method of Vote}
-The Chair of the Vote will state all possible ways to vote, then call out each possibility one at a time.
-Votes are kept anonymous.
-The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
-
-\asubsubsection{Voting Period}
-A secret immediate vote lasts as long as it takes for all votes to be tallied.
+An Immediate Vote lasts as long as it takes for all votes to be tallied.
+\asubsubsection{Secret Immediate Vote}
+An Immediate Vote in which votes are kept anonymous.
+\asubsubsection{Executive Board Vote}
+In an Executive Board Vote, only Voting Members of the Executive Board are eligible to vote.
+Unless otherwise specified, Executive Board votes are Immediate Relative Majority votes with a fifty percent Quorum.
 
 \asubsection{Batch Vote}
-When a Batch Vote is called for by the Chair of the Vote, a subset of the voting docket may be amended to a single vote.
+When a Batch Vote is called for by the Chair of the Vote, a non-empty subset of the voting docket may be amended to a single vote.
 A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
@@
 
-\asection{Number of Votes Required}
-The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass.
-Below are listed four standard votes.
-Numbers for non-standard votes are defined in the section describing the actual vote.
-
-\asubsection{Simple Majority}
-In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
-An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
-
-\asubsection{Fifty Percent}
-In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
-An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
-
-\asubsection{Two-Thirds}
-In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
-An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
-
-\asubsection{Three-Quarters}
-In a Three-Quarters Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds three-quarters the Total Number of Possible Votes.
-An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
-
-\asubsection{Alternative}
+\asection{Approval Criteria}
+Approval Criteria are the rules that determine whether an option in a vote has passed.
+\asubsection{Relative Majority}
+In a Relative Majority vote, an option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
+\asubsection{Fractional}
+In a Fractional vote, an option in the vote passes if the number of votes cast for that option exceeds a specified fraction of the Votes Cast, rounded up to the nearest vote.
+The fraction is specified in the text describing the vote (eg, "Two-Thirds Vote").
+\asubsection{Ranked Choice}
+In a Ranked Choice vote, voters rank the options by placing a '1' by their first choice, a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of options.
+
 The winning option is selected outright if it gains more than half the votes cast as a first preference.
-If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
+If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballots.
 This process continues until one option has half of the votes cast and is elected.
@@
 \asubsection{With Multiple Options}
-If multiple options may pass, a tie does not present a problem.
 If only one option may pass, then the vote must be recast or tabled at the discretion of the Chair of the Vote.
-In the event of a tie in an E-Board vote, the Chair may cast the tie-breaking vote.
+In the event of a tie in an Executive Board Vote, the Chairperson may cast the tie-breaking vote.
 
@@
 \article{Judicial}
-E-Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
-
+The Executive Board may approve a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
 \asection{Formation of a Judicial Board}
-A Judicial Board is made up of the Chair, the Evals director, and an additional voting member of E-Board chosen by a majority vote among E-Board.
-If either the Chair or Evals Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of E-Board by means of a simple majority vote amongst the remaining E-Board members.
+A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board.
+If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of an Executive Board Vote of the remaining members.
 

### 2024-03-05 constitution.tex
Merge PR #147 (resolve #13 reorganize sections)
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>

@@
 
-\asubsection{Non-Semantic Changes}
-There are two methods for non-semantic change to the Constitution.
-A Maintainer may approve any proposed change that does not affect the meaning of the document.
-Alternatively, the change may be presented to the House for discussion followed by an Immediate One-Half Vote with fifty percent Quorum.
-
-\asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
-Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with Two-Thirds Quorum \ref{Balloted Vote}.
-The ballots are collected for a minimum of a forty-eight hour period.
-The Constitution may be overridden by an Nine-Tenths Immediate Vote with eighty-five percent Quorum.
-
-\asection{Maintainers}
-
-\asubsection{Maintainer Qualifications}
-Maintainers must be Active or Alumni Members.
-
-\asubsection{Maintainer Expectations}
-Maintainers are expected to:
-\begin{itemize}
-	\item Be knowledgeable about the Constitution
-	\item Review changes to the Constitution for grammar, spelling, and internal consistency
-	\item Participate in discussion of proposals and amendments
-	\item Keep a public record of changes to the Constitution
-\end{itemize}
-
-Failure to meet any of these expectations is grounds for revocation of Maintainer status by E-Board.
-
-\asubsection{Maintainer Term}
-Maintainer status lasts until it is resigned, or until it is revoked by an E-Board Vote.
-If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
-
-\asubsection{Maintainer Selection}
-Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
-E-Board may choose to approve or reject the nomination by an E-Board Vote.
-
-% ARTICLE III - GENERAL OPERATIONS OF THE HOUSE
-\article{General Operations of the House}
 \asection{Standard Operating Session}
@@
 
+\asubsubsection{Selection Processes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+
+% Current RIT students is defined as students who have attended RIT for at least 1 full semester
+\asubsubsubsection{Selection Process for Current RIT Students}
+\begin{enumerate}
+	\item The applicant submits an application to the Evaluations Director for review.
+	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
+	\item The application materials are then reviewed at an Evaluations meeting.
+	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member is not required to pay dues during the Introductory Process.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+
+% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
+\asubsubsubsection{Selection Process for Incoming RIT Students}
+\begin{enumerate}
+	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
+		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
+        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
+            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
+            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
+\end{enumerate}
+Note: Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member is not required to pay dues during the Introductory Process.
+\\* \\*
+Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+
 \asubsection{Introductory Membership Expectations}
@@
 \asubsection{Introductory Membership Evaluations}
-Intro Members are evaluated on their performance during the intro period.
-The Intro Evals process is described in \ref{Introductory Evaluation}.
+\asubsection{The Introductory Process}
+The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
+\asubsection{The Evaluation Period}
+The Process will occur either once or twice per semester, and will last for six (6) weeks.
+The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
+The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
+If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
+If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
+If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
+\asubsection{The Introductory Packet}
+Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
+\begin{itemize}
+	\item Alumni members
+	\item Honorary members
+	\item Advisory members
+\end{itemize}
+At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+\asubsubsection{Expectations of an Introductory Member}
+Before the end of the Process, an Introductory Member is expected to:
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Complete the Introductory Packet
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
+\end{itemize}
+
+\asubsubsection{Introductory Evaluation}
+The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
+It occurs at the conclusion of the final week of the Process.
+
+\asubsubsubsection{Voting}
+On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
+A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
+Neither absentee nor proxy votes are allowed.
+House may choose any of the Outcomes for each member.
+
+\asubsubsubsection{Outcomes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
+	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
+	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
+		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
+		Each conditional consists of a set of additional requirements and a deadline for completing them.
+		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+		A conditional member who does not meet these additional requirements forfeits membership.
+\end{enumerate}
 
@@
 Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
+Active voting members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
+
+\asubsubsection{Expectations of House Members}
+Active members are required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Executive Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+\\* \\*
+Active members must participate significantly in at least one major project during the academic year.
+Members are required to submit a description for this major project to the Executive Board for approval.
+As an option to this requirement, members may instead assist on a large number of House activities and projects.
+However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
+This participation will be evaluated by the Executive Board.
 
@@
 
+\asubsubsection{Expectations of Voting Members}
+The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
+Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
+\begin{itemize}
+\item Attend all House meetings during the process
+\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
+\item Attend at least one House social event during the process
+\item Attend at least two seminars relating to computing or electronics
+\end{itemize}
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated annually through the Evals Process as described in \ref{Evaluations Processes}.
+Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+
+% ACTIVE MEMBERSHIP EVALUATIONS
+
+\asubsubsection{Evaluations Processes}
+During the academic year, a House member is evaluated by the Membership Evaluation.
+The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+Semi-Annual Evaluations Meetings are open only to current Active Members.
+All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
+\\* \\*
+At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
+It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
+\asubsubsubsection{Membership Evaluation}
+The Membership Evaluation process occurs once per academic year.
+It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+\asubsubsubsubsection{Voting}
+Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
+All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
+The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
+Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
+These requirements must be completed before the Membership Evaluation occurs.
+A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Neither absentee nor proxy votes are allowed.
+
+\asubsubsubsubsection{Outcomes}
+Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+\\* \\*
+If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
+If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
+In either case, the member forfeits their ability to be included on the following year’s roster.
+\\* \\*
+A member may be given a conditional to complete as a means of making up for missing requirements.
+A conditional may be proposed by any member present at the Evaluation.
+If the conditional is approved by the Evaluations Director, it is then voted on by House.
+Each conditional consists of a set of additional requirements a deadline for completing them.
+When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
+A conditional member who does not meet these additional requirements will have failed the evaluation.
+\asubsubsubsection{Appeals Process}
+If a member disagrees with the outcome of any evaluation, (e.g.
+is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+\\* \\*
+If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
 
@@
 
-% ARTICLE V - EXECUTIVE BOARD
-\article{E-Board}
-The E-Board is the main governing body of the House.
+% ARTICLE V - OFFICERS OF THE HOUSE
+\article{Officers of the House}
+\asection{Executive Board}
+The Executive Board is the main governing body of the House.
+
 Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
@@
 
-\asection{Responsibilities}
+\asubsection{Responsibilities}
 
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-
-\asubsection{Responsibilities of E-Board}
+\asubsubsection{Responsibilities of E-Board}
+
 \begin{enumerate}
@@
 
-\asubsection{Responsibilities of the Evaluations Director}
+\asubsubsection{Responsibilities of the Evaluations Director}
 \begin{enumerate}
@@
 
-\asubsection{Responsibilities of the Social Director(s)}
+\asubsubsection{Responsibilities of the Social Director(s)}
 \begin{enumerate}
@@
 
-\asubsection{Responsibilities of the Financial Director}
+\asubsubsection{Responsibilities of the Financial Director}
 \begin{enumerate}
@@
 
-\asubsection{Responsibilities of the House Secretary}
+\asubsubsection{Responsibilities of the House Secretary}
 \begin{enumerate}
@@
 
-\asubsection{Responsibilities of Ad Hoc Directorships}
+\asubsubsection{Responsibilities of Ad Hoc Directorships}
 \begin{enumerate}
@@
 
-\asection{Closed Executive Board}
+\asubsection{Closed Executive Board}
 Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
@@
 
-\asection{Operations}
-
-\asubsection{Operations of the Financial Directorship}
-
-\asubsubsection{Amount of House Dues}
-The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
-
-\asubsubsection{Collection of House Dues}
-The collection period of house dues will be decided in conjunction with ResLife and Housing.
-During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
-Dues for off-floor members are to be collected during this period as well by the Financial Director.
-For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
-Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
-
-\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
-If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
-The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
-If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
-If appealed, E-Board may provide an extension and/or reduction to the member.
-If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
-All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
-After this date, dues collection is suspended until the start of the next academic year.
-
-\asubsubsection{Breakdown of Dues for Directorship Budgets}
-\begin{center}
-\begin{tabular}[c]{|l c|}
-\hline
-Directorship Name & Percentage of Dues \\
-\hline
-\hline
-OpComm & 20\% \\
-\hline
-R\&D & 20\% \\
-\hline
-Social & 20\% \\
-\hline
-IMPs & 15\% \\
-\hline
-History & 10\% \\
-\hline
-Evaluations & 5\% \\
-\hline
-PR & 5\% \\
-\hline
-Accumulated & 5\% \\
-\hline
-\end{tabular}
-\end{center}
-
-% The suggested total operating budget is $8360.
-% This figure comes from having approximately 55 on-floor members with $80 per semester dues (totaling $8800) minus 5% set aside for Accumulated.
-
-Dues collected from on-floor members are to be distributed into directorship budgets as shown in the above table.
-Money allocated for Accumulated or collected from off-floor members is deposited into the CSH Account and saved.
-
-\asubsubsection{Expenditure Approval}
-All House expenditures must be approved by the Financial Director and the Director whose budget is going to be used for the expenditure.
-Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures (funds drawn for a specific event, project, piece of equipment, or service) may not exceed one-hundred dollars (\$100).
-\\* \\*
-If the above amounts are to be exceeded, the expenditure must be approved by an Immediate Relative Majority Vote at a House meeting before the funds may be appropriated.
-At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
-A Two-Thirds Immediate Vote with twenty-five percent Quorum is required to approve the purchase.
-\\*\\*
-For expenditures exceeding \$300 in total funding, a Spending Presentation must be presented to House at a House meeting.
-This presentation includes the funds required for the expenditure, inventory of required resources, and (if applicable) a timeline for completion.
-\\* \\*
-If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent Quorum, regardless of the amount.
-This amount is to be directly subtracted from the general CSH account.
-\\* \\*
-Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
-
-% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
-\asubsection{Operations of the Evaluations Directorship}
-
-\asubsubsection{The Introductory Process}
-The Intro Process allows Intro Members to learn about House and demonstrate their interest in becoming Active Members.
-During this period, Intro Members will meet existing House Members, learn House History, and be evaluated for Active Membership by existing House members.
-
-\asubsubsubsection{The Evaluation Period}
-The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
-The Executive Board may approve an extension to the Introductory Process by an Executive Board Vote.
-If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
-If deemed necessary by the Evaluations Director, or by an Executive Board Vote, the second intro process must begin within nine (9) days of the first process ending.
-If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
-\asubsubsubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
-
-\begin{itemize}
-	\item Alumni members
-	\item Honorary members
-	\item Advisory members
-\end{itemize}
-At the discretion of the Evals Director or an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.
-
-\asubsubsubsection{Expectations of an Introductory Member}
-Before the end of the Process, an Intro Member is expected to:
-\begin{itemize}
-\item Attend all House meetings during the process
-\item Complete the Intro Packet
-\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
-\item Attend at least one House social event during the process
-\item Attend at least two seminars relating to computing or electronics
-\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
-\end{itemize}
-
-\asubsubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
-It occurs at the conclusion of the final week of the Process.
-
-\asubsubsubsubsection{Voting}
-On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
-An Immediate Relative Majority Vote with two-thirds Quorum is required for the evaluation to be valid.
-For an Active Member to be eligible to vote during the evaluation process they must meet the requirements outlined in \ref{Expectations of Voting Members}.
-
-Neither absentee nor proxy votes are allowed.
-House may choose any of the Outcomes for each member.
-
-\asubsubsubsubsection{Expectations of Voting Members}
-The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
-Any of these requirements may be waived by the Evals Director or an E-Board Vote.
-
-\begin{itemize}
-\item Attend all House meetings during the process
-\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
-\item Attend at least one House social event during the process
-\item Attend at least two seminars relating to computing or electronics
-\end{itemize}
-
-\asubsubsubsubsection{Outcomes}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
-	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
-	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
-		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
-		Each conditional consists of a set of additional requirements and a deadline for completing them.
-		When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
-		A conditional member who does not meet these additional requirements forfeits membership.
-\end{enumerate}
-
-\asubsubsection{Selection Processes}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-
-% Current RIT students is defined as students who have attended RIT for at least 1 full semester
-\asubsubsubsection{Selection Process for Current RIT Students}
-\begin{enumerate}
-	\item The applicant submits an application to the Evals Director for review.
-	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
-	\item The application materials are then reviewed at an Evals meeting.
-	Then an Immediate Relative Majority Vote of attending members is held on whether or not to accept the person as an Intro Member.
-\end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the Intro Process.
-This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
-The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Intro Process.
-\\* \\*
-Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
-
-% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
-\asubsubsubsection{Selection Process for Incoming RIT Students}
-\begin{enumerate}
-	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
-		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
-        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
-            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
-            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
-\end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the Intro Process.
-This means that until the member has passed the Introductory Evals, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
-The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Intro Process.
-\\* \\*
-Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
-
-\asubsubsubsection{Selection Process for Honorary Members}
-\begin{enumerate}
-	\item A House Member submits to the Evaluations Director a nomination for a person they feel is deserving of Honorary Membership.
-	\item The Evaluations Director performs some preliminary research on the candidate and presents the findings.
-	\item The Executive Board decides whether or not to present the nomination to the House for a secret ballot House vote.
-		If the Executive Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become an Honorary Member.
-	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds Balloted Vote with two-thirds Quorum.
-		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
-	\item The candidate is notified of their selection as an Honorary Member and presented with the honor.
-\end{enumerate}
-
-\asubsubsubsection{Selection Process for Advisory Members}
-\begin{enumerate}
-	\item When there is a perceived need, E-Board may open nominations for Advisory Members.
-		After an announcement at House Meeting, during a 72-hour period, any House Member may submit a nomination.
-	\item After the close of the nomination collection period, E-Board will arrange some means for the House to meet with the nominees.
-	\item A discussion of the candidates will be held at the following House meeting.
-	\item Ballots are distributed for each nominee as a One-Half Balloted Vote with fifty percent Quorum.
-		Voting must remain open for a minimum of a forty-eight hour period.
-	\item All candidates selected are notified of their acceptance as House Advisors and asked to accept or decline the selection.
-\end{enumerate}
-
-\asubsubsection{Evaluations Processes}
-During the academic year, a House member is evaluated by the Membership Evals.
-The Membership Evals is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-Semi-Annual Evals Meetings are open only to current Active Members.
-All E-Board members are expected to attend the Membership Evals to assist in the evaluations of House members.
-\\* \\*
-At the beginning of any Evals Process listed herein, the Evals Director must read the sections of the Computer Science House Constitution used during the respective Evals Process.
-It is incumbent upon each House member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.
-
-\asubsubsubsection{Membership Evaluation}
-The Membership Evaluation process occurs once per academic year.
-It is performed as part of the Evals Process that takes place during the spring semester to comply with RIT Housing deadlines.
-
-\asubsubsubsubsection{Voting}
-Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evals passes their Membership Evals without being voted on or evaluated by the quorum.
-All Active Members who have not recieved an exemption from E-Board prior to the Membership Evals will be evaluated on a Member by Member basis by a quorum of Active Members.
-The Membership Evals shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
-Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
-These requirements must be completed before the Membership Evaluation occurs.
-A Secret Immediate Relative Majority vote with two-thirds Quorum is required for the evaluation to be valid.
-Neither absentee nor proxy votes are allowed.
-
-\asubsubsubsubsection{Outcomes}
-Members who pass Membership Evals have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
-\\* \\*
-If a member fails and has never passed a Membership Evals in the past, their membership will be revoked immediately.
-If the member has previously passed a Membership Evals they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
-In either case, the member forfeits their ability to be included on the following year’s roster.
-\\* \\*
-A member may be given a conditional to complete as a means of making up for missing requirements.
-A conditional may be proposed by any member present at the Evaluation.
-If the conditional is approved by the Evaluations Director, it is then voted on by House as described in \ref{Voting}.
-Each conditional consists of a set of additional requirements a deadline for completing them.
-When the deadline expires, the conditional will be brought before E-Board who will assess its completeness.
-A conditional member who does not meet these additional requirements will have failed the evaluation.
-
-\asubsubsubsection{Appeals Process}
-If a member disagrees with the outcome of any evaluation, (e.g.
-is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
-\\* \\*
-If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.
-
-\asubsubsection{Expectations of House Members}
-Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and E-Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
-\\* \\*
-The member must participate significantly in at least one major project during the academic year.
-The member is required to submit a description for this major project to E-Board for approval.
-As an option to this requirement, the member may instead assist on a large number of House activities and projects.
-However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
-This participation will be evaluated by E-Board.
-
-\asubsubsection{Housing Status}
-All Alumni, Active, and Introductory Members have a housing status.
-This status indicates their right to priority housing on the floor.
-Alumni Members in good standing keep the housing status they had as Active Members.
-Alumni Members in bad standing have Off-Floor status.
-
-\asubsubsubsection{On-Floor Status}
-Members with On-Floor status are eligible to live on the floor.
-To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
-The Evaluations Director will then bring them up for a One-Half Immediate vote among attending Active members at the next evaluations meeting.
-If the Evaluations Director determines that too few members are present to hold a vote, the member will be brought up for a vote at the next evaluations meeting.
-
-\asubsubsubsection{Off-Floor Status}
-Members with Off-Floor status do not have the right to live on the floor.
-They still have access to all other privileges associated with their membership, and may still accumulate Housing Priority Points.
-
-\asubsubsection{Housing Priority System}
-The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
-The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evals.
-Each Active Member who passes the Membership Evals is granted two (2) Housing Priority Points.
-\\* \\*
-In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
-
-\asubsubsubsection{Single Room Assignments}
-When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
-In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
-If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
-This process continues until a member selects to move into the single room.
-Once in a single room, a House member retains the assignment until voluntarily giving it up.
-It should be noted that members selecting this option must agree to any additional charges applied by ResLife for residing in a single room.
-
-\asubsubsubsection{Double Rooms as Single rooms}
-During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
-It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
-This only applies if there is a totally vacant room.
-
-\asubsection{Operations of the Operational Communications Directorship}
-The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
-It is a self-governing committee making decisions by Immediate Relative Majority vote (two-thirds Quorum) of Current Root Type Persons.
-Membership is composed of all Root Type Persons.
-
-\asubsubsection{Selection of an RTP}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Nominations are taken from the RTPs and Prior RTPs meeting the selection criteria in \ref{Qualifications of an RTP}.
-	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
-		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
-		An Executive Board Vote is taken to determine whether the nominations of the Root Type Persons are accepted.
-\end{enumerate}
-
-\asubsubsection{Qualifications of an RTP}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Candidates must be Active Members
-\end{enumerate}
-
-\asubsubsection{Prior RTPs}
-\begin{enumerate}
-	\item Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
-		Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
-	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior RTPs.
-\end{enumerate}
-
-\asubsubsection{Creation of Accounts}
-RTPs have the authority to manage user accounts for House systems.
-Before intro, active, or alumni members may receive an account they must:
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evals) in the Intro Packet or successfully complete Introductory Evals.
-\end{enumerate}
-Accounts for honorary and advisory members may be created at the discretion of the RTPs.
-
-\asubsubsection{Code of Conduct}
-The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
-\\* \\*
-Members are bound to the Code of Conduct revision that they sign when initially creating their account.
-Members may sign a more recent revision of the Code of Conduct to update their agreement.
-
-\asubsubsubsection{Changes}
-The following process is used for making changes to the Code of Conduct document.
-\begin{enumerate}
-	\item An RTP drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
-	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
-	\item The final proposal is presented at the next House Meeting and ballots are distributed for a One-Half Balloted House vote (fifty percent Quorum) as described in \ref{Balloted Vote}.
-\end{enumerate}
-
-\asection{Qualifications}
-Elected or selected candidates may not hold more then one simultaneous Executive Board positions, and must therefore resign their current position or decline the other position should they be elected or selected to another position.
-
-\asubsection{Qualifications to be the Chair, Evals Director}
+\asubsection{Qualifications}
+\asubsubsection{Qualifications to be the Chair, Evals Director}
 \begin{enumerate}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member
-\end{enumerate}
-
-\subsubsection{Qualifications to be the Social Director(s), Financial Director, R\&D Director(s), IMPs Director, History Director, PR Director}
+	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
+\end{enumerate}
+\asubsubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
 \begin{enumerate}
@@
 	\item Candidates must have at least one full semester of House membership as an Active Member
-\end{enumerate}
-
-\asubsection{Qualifications to be the OpComm Director}
-\begin{enumerate}
-	\item Candidates must be a current RTP \ref{Operations of the OpComm Directorship}.
+	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
+\end{enumerate}
+\asubsubsection{Qualifications to be the Operational Communications Director}
+\begin{enumerate}
+	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
 	\item Candidates must be a current Active Member.
-	\item An RTP cannot be the director if they currently hold any other voting E-Board Position.
-\end{enumerate}
-
-\asubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
+	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
+\end{enumerate}
+
+\asubsubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
 \begin{enumerate}
@@
 
-\asubsection{Waiving of Qualifications}
-\begin{enumerate}
-  \item House may choose to waive the following subset of the Qualifications for E-Board positions (defined under \ref{Qualifications}) for all Candidates:
+\asubsubsection{Waiving of Qualifications}
+\begin{enumerate}
+  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
     \begin{enumerate}
@@
       \item Candidates must have at least one full semester of House membership as an Active Member.
-      \item Social and R\&D are the only voting E-Board positions that allow for Dual Directorship.
+      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
     \end{enumerate}
@@
 
-\asection{Selection}
-
-\asubsection{Dual Directorship}
-Social and R\&D are the only voting E-Board positions that allow for Dual Directorship.
+\asubsection{Selection}
+\asubsubsection{Dual Directorship}
+Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
+
 If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
@@
 An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
+
 The resignation will be read at the following House Meeting and become effective at that time.
@@
 
-\asection{Impeachment}
+\asubsection{Impeachment}
 \begin{enumerate}
@@
 
-\asection{Term}
+\asubsection{Term}
 \begin{enumerate}
@@
 If the vote passes, the Executive Board may discuss and make a new ruling by another Executive Board Vote.
+
+\asection{Maintainers}
+
+\asubsection{Maintainer Qualifications}
+Maintainers must be Active or Alumni Members.
+
+\asubsection{Maintainer Expectations}
+Maintainers are expected to:
+\begin{itemize}
+	\item Be knowledgeable about the Constitution
+	\item Review changes to the Constitution for grammar, spelling, and internal consistency
+	\item Participate in discussion of proposals and amendments
+	\item Keep a public record of changes to the Constitution
+\end{itemize}
+Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.
+
+\asubsection{Maintainer Term}
+Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
+A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.
+If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
+
+\asubsection{Maintainer Selection}
+Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
+The Executive Board may choose to approve or reject the nomination by Simple Majority vote with a quorum of seventy-five percent of the Total Number of Possible Votes.
+
+\asection{Root Type Persons}
+The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
+It is a self-governing committee making decisions by a simple majority vote.
+Membership is composed of all Root Type Persons.
+
+\asubsection{Selection of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
+		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
+	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
+\end{enumerate}
+
+\asubsubsection{Qualifications of a Root Type Person}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
+	\item Candidates may be granted an exemption by current Root Type Persons.
+		Such an exemption may be withdrawn at any time by the current Root Type Persons.
+	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
+		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
+	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
+\end{enumerate}
+
+\asubsubsection{Creation of Accounts}
+Root Type Persons have the authority to manage user accounts for House systems.
+Before introductory, active, or alumni members may receive an account they must:
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
+	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
+\end{enumerate}
+Accounts for honorary and advisory members may be created at the discretion of the Root Type Persons.
+
+\asubsubsection{Code of Conduct}
+The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+\\* \\*
+Members are bound to the Code of Conduct revision that they sign when initially creating their account.
+Members may sign a more recent revision of the Code of Conduct to update their agreement.
+\asubsubsubsection{Changes}
+The following process is used for making changes to the Code of Conduct document.
+\begin{enumerate}
+	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
+\end{enumerate}
+
+% ARTICLE III - GENERAL OPERATIONS OF THE HOUSE
+\article{General Operations of the House}
+
+% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
+\asection{Financial Operations of the House}
+\asubsection{Amount of House Dues}
+The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
+\asubsection{Collection of House Dues}
+The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
+During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
+Dues for off-floor members are to be collected during this period as well by the Financial Director.
+For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
+Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
+If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
+If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
+If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
+If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
+If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues.
+Additional time and reduction of dues may both be given to a member in an appropriate situation.
+All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+After this date, dues collection is suspended until the start of the next academic year.
+\asubsection{Breakdown of Dues for Directorship Budgets}
+\begin{center}
+\begin{tabular}[c]{|l c|}
+\hline
+Directorship Name & Percentage of Dues \\
+\hline
+\hline
+Operational Communications & 20\% \\
+\hline
+Evaluations & 5\% \\
+\hline
+House History & 10\% \\
+\hline
+House Improvements & 15\% \\
+\hline
+Research and Development & 20\% \\
+\hline
+Social & 20\% \\
+\hline
+Public Relations & 5\% \\
+\hline
+Accumulated & 5\% \\
+\hline
+\end{tabular}
+\end{center}
+
+% The suggested total operating budget is $8360.
+% This figure comes from having approximately 55 on-floor members with $80 per semester dues (totaling $8800) minus 5% set aside for Accumulated.
+
+Dues collected from on-floor members are to be distributed into directorship budgets as shown in the above table.
+Money allocated for Accumulated or collected from off-floor members is deposited into the CSH Account and saved.
+
+\asubsection{Expenditure Approval}
+All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
+Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
+A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+\\* \\*
+If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
+A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+\\*\\*
+For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
+This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+\\* \\*
+If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+This amount is to be directly subtracted from the general CSH account.
+\\* \\*
+Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
+
+% HOUSING
+\asection{Housing}
+
+\asubsection{Housing Status}
+All Alumni, Active, and Introductory Members have a housing status.
+This status indicates their right to priority housing on the floor.
+Alumni Members in good standing keep the housing status they had as Active Members.
+Alumni Members in bad standing have Off-Floor status.
+\asubsubsection{On-Floor Status}
+Members with On-Floor status are eligible to live on the floor.
+To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
+The Evaluations Director will then bring them up for vote at the next meeting.
+\asubsubsection{Off-Floor Status}
+Members with Off-Floor status do not have the right to live on the floor.
+They still have access to all other privileges associated with their membership, and may still accumulate Housing Priority Points.
+
+\asubsection{Housing Priority System}
+The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
+The member with top priority is the member with on-floor status and the most Housing Priority Points.
+Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
+Each Active Member who passes the Membership Evaluation is granted two (2) Housing Priority Points.
+\\* \\*
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
+\asubsubsection{Single Room Assignments}
+When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
+In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
+If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
+This process continues until a member selects to move into the single room.
+Once in a single room, a House member retains the assignment until voluntarily giving it up.
+It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
+\asubsubsection{Double Rooms as Single rooms}
+During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
+It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
+This only applies if there is a totally vacant room.
 
@@
 
-% ARTICLE VIII - ADHERENCE TO UNIVERSITY POLICIES
+% Article VIII - MODIFICATIONS TO THE CONSTITUTION
+\asubsection{Non-Semantic Changes}
+There are two methods for non-semantic change to the Constitution.
+A Maintainer may approve any proposed change that does not affect the meaning of the document.
+Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
+A quorum of fifty percent of the Total Number of Possible Votes is required for passage.
+
+\asubsection{Semantic Changes}
+Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
+Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
+The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
+The ballots are collected for a minimum of a forty-eight hour period.
+A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
+A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
+The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
+There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
+A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
+
+% ARTICLE IX - ADHERENCE TO UNIVERSITY POLICIES
 \article{ADHERENCE TO UNIVERSITY POLICIES}

### 2024-03-05 constitution.tex
Rebase off of current master branch (#96)
Co-authored-by: Sam Cordry <samcodry@gmail.com>

@@
 % Defined this way so that (for example) each member in a dual directorship is each considered to be a voting member on E-Board.
-Ad Hoc directorships are created on an as-needed basis.
-They are generally very task oriented and are chaired by a House member.
 A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
@@
 
-\asubsubsection{Responsibilities of Ad Hoc Directorships}
-\begin{enumerate}
-	\item Ad Hoc Directorships are responsible for the task for which they were created
-	\item Any responsibilities budgets or finances for the Ad Hoc Directorship are placed upon the assigned director
-\end{enumerate}
-
 \asubsection{Closed Executive Board}
@@
 
-\asubsubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
+\asubsubsection{Qualifications to be the House Secretary}
 \begin{enumerate}
@@
 Each different nomination must be a separate entry on the election ballot.
-Non-voting E-Board positions (i.e. Ad Hoc Directors) are not restricted to single or dual directorship.
 
@@
 
-\asubsection{Selection of Ad Hoc Directors}
-\begin{enumerate}
-	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board.
-  An Executive Board Vote is taken to determine whether directorship status is granted.
-	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
-\end{enumerate}
-
 \asubsection{Selection of the House Secretary}
@@
 If the vote passes, the Executive Board may discuss and make a new ruling by another Executive Board Vote.
+
+\asection{Ad Hoc Directorships}
+Ad Hoc Directorships are created by the Executive Board on an as-needed basis.
+They are generally task-oriented and are chaired by a House member(s).
+Ad Hoc Directors are responsible for the task for which they were created.
+Additionally, any responsibilities, budgets, or finances for the Ad Hoc Directorship are placed upon the assigned director(s).
+Candidates for being Ad Hoc Directors must be Active Members.
+% This is implied, but Ad Hoc Directorships are not intended to be restricted to single or dual directorship rules.
+
+\asubsection{Selection of Ad Hoc Directors}
+\begin{enumerate}
+	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board.
+	An Executive Board Vote is taken to determine whether directorship status is granted.
+	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
+\end{enumerate}
 

### 2024-03-05 constitution.tex
Merge #132 (Resolves #127 Condense 5.D.1.B)
Co-authored-by: Sam Cordry <samcodry@gmail.com>

@@
 The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
-During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
-Dues for off-floor members are to be collected during this period as well by the Financial Director.
-For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
-Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
+During the dues collection period, dues for both semesters for all Active Members are collected through the member's RIT bill.
+Dues for any Alumni Member in good standing are to be collected when intention to pay is expressed to the Financial Director.
 \asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}

### 2024-03-06 constitution.tex
Merge #157 (Combine 5.E.1 and 5.E.2)
Co-authored-by: Sam Cordry <samcodry@gmail.com>

@@
 \asubsection{Qualifications}
-\asubsubsection{Qualifications to be the Chair, Evals Director}
+\asubsubsection{Qualifications to be the Chair, Evals Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
 \begin{enumerate}
 	\item Candidates must be Active Members during the term of office
-	\item Candidates must reside on floor during the term of office
 	\item Candidates must have at least one full semester of House membership as an Active Member
 	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
-\end{enumerate}
-\asubsubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
-\begin{enumerate}
-	\item Candidates must be Active Members during the term of office
-	\item Candidates must have at least one full semester of House membership as an Active Member
-	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
+  \item Candidates for Chairperson or Evals Director must reside on floor during the term of office
 \end{enumerate}

### 2024-03-26 constitution.tex
added one sentence to clarify membership status during conditional (#164)
136 removing dry notes (#163)
* ,

moved contents of the 'note' and 'additional note'

* removed\added \hfill\break for a newline command

* tried to fix the extraneous skill issues that I had

* skill issues again

* theoretically everything should be okay now, I nuked my const.tex file with the master one then made the changes I was supposed to make moving the contents of note and additional note

---------

Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>

@@
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+\hfill\break\hfill\break
+Most membership privileges do not initiate until successful completion of the introductory process.
+This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
+The member does, however, have the right to use Computer Science House's facilities.
+The member is not required to pay dues during the Introductory Process.
+\\* \\*
+No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+
+% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
 
@@
 \end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
-The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Introductory Process.
-\\* \\*
-Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
-
-% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
 \asubsubsubsection{Selection Process for Incoming RIT Students}
@@
 \end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
-The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Introductory Process.
-\\* \\*
-Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
 
@@
 Each conditional consists of a set of additional requirements a deadline for completing them.
+Members who are given a conditional have their evaluation decision deferred, and therefore maintain their current membership status until the conditional is resolved.
 When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.

### 2024-04-07 constitution.tex
added the requested points about chair responsbilities (#162)
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>
[Mega PR] Fixed many of the existing issues (#216)
* Started working on mega pr

* First pass of the document

* second pass

* 3rd pass

* Made changes based on reviews from jeremy and ian

* Made changes discussed at meeting yesterday, and also made remaining changes from reviews

* oops i forgor a thing

* oops i forgor a thing v2

* Made requested changes

* made the table 4 columns because I felt like it

* Fixed all the issues :TM:

* non semantic code

--- 2024-03-06 constitution.tex
@@
 
-% Reference example:
-%Test reference \ref{House Objectives} House Objectives.
-
 \begin{document}
@@
 
-% ARTICLE I - INTRODUCTION
+% ARTICLE I - ABBREVIATIONS
+\article{Abbreviations and Definitions}
+
+\subsection{Abbreviations}
+% Formatted as abbreviation  full term
+\begin{tabular}{ l  l  l l l l}
+	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
+	CSH     & \textit{Computer Science House} & OpComm        & \textit{Operational Communications}   \\
+	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
+	Eval(s) & \textit{Evaluation(s)}          & R\&D          & \textit{Research and Development}     \\
+	History & \textit{House History}          & ResLife       & \textit{Residence Life}               \\
+	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
+	Intro   & \textit{Introductory}                                                                   \\
+\end{tabular}
+
+\subsection{Definitions}
+
+% Formatted as term | definition
+\begin{tabular}{l l}
+	Technical Seminar          & \textit{Seminar relating to computing or electronics}                                     \\
+	Standard Operating Session & \textit{RIT's fall and spring semesters, excluding institute breaks and final exam weeks} \\
+	Total Expenditure          & \textit{funds drawn for a specific event, project, piece of equipment, or service}
+\end{tabular}
+
+% ARTICLE II - INTRODUCTION
 \article{Introduction}
@@
 \asection{Derivation of Authority}
-The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Campus Life and the Department of Residence Life.
+CSH shall recognize that it receives its right to function as a Special Interest House from the Center for Campus Life and the Department of Residence Life.
 
 \asection{House Objectives}
-The objectives of Computer Science House are:
+The objectives of CSH are:
 \begin{enumerate}
@@
 
-\article{Abbreviations and Definitions}
-Many of the commonly used abbreviations will be listed here, and the abbreviations will be used throughout the rest of the document.
-
-\begin{enumerate}
-	\item Chairperson - Chair
-	\item Evaluations - Evals
-	\item Research and Development - R\&D
-	\item House Improvements - IMPs
-	\item Operational Communications - OpComm
-	\item House History - History
-	\item Public Relations - PR
-	\item Socials - Social
-	\item Financials - Financial
-	\item Executive Board - E-Board
-	\item Root Type Person - RTP
-	\item Constitutional Maintainer - Maintainer
-	\item Introductory - Intro
-	\item Department of Residence Life - ResLife
-\end{enumerate}
-
-% ARTICLE II - CONSTITUTIONAL STRUCTURE
-\article{Constitutional Structure}
+% ARTICLE 3 - CONSTITUTIONAL STRUCTURE
+\article{Constitutional Structure and Amendment}
 
 \asection{Constitution}
-The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.
-
-\asection{Standard Operating Session}
-The Standard Operating Session for Computer Science House is during the Fall and Spring semesters.
-The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
-Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.
-
-% ARTICLE IV - MEMBERSHIP
+The CSH Constitution is written and maintained by members and defines the major aspects, goals, and governing structure of CSH.
+\\*\\
+Unless explicitly stated otherwise, the requirements and expectations defined in the Constitution are for the Standard Operating Session.
+
+\subsection{Modifiying the Constitution}
+\asubsection{Non-Semantic Changes}
+There are two methods for non-semantic change to the Constitution.
+A Maintainer may approve any proposed change that does not affect the meaning of the document.
+Alternatively, the change may be presented at a House Meeting for discussion followed by an Immediate One-Half Vote with fifty percent quorum.
+
+\asubsection{Semantic Changes}
+Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
+Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in during the week.
+The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
+The ballots are collected for a minimum of a forty-eight hour period.
+A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
+A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
+The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.
+
+% ARTICLE 4 - MEMBERSHIP
 \article{Membership}
-There are five major types of membership available to Computer Science House.
-Each carries different qualifications, expectations, and privileges.
-When describing the different memberships available, the following terms are used:
+There are five types of membership available to CSH.
+When describing membership types, the following terms are used:
 \begin{description}
-	\item[Qualifications:] What qualifications an applicant needs to apply
+	\item[Qualifications:] What criteria an applicant needs to be eligible for membership
 	\item[Selection:] The process by which an applicant gains membership
-	\item[Expectations:] The duties and responsibilities of House members
-	\item[Privileges:] The benefits offered to House members
+	\item[Expectations:] The duties and responsibilities associated with CSH membership
+	\item[Privileges:] The benefits offered to members
 	\item[Evaluations:] The process by which a member is reviewed and assessed
-	\item[Leave of Absence:] The process by which a member may leave House for a period of time
-	\item[Resignations:] The process by which a member terminates House membership
-	\item[Term:] The length of time the membership lasts
+	\item[Leave of Absence:] The process by which a member may leave CSH during an RIT Leave of Absence
+	\item[Resignations:] The process by which a member terminates CSH membership
+	\item[Term:] The duration of the membership
 \end{description}
@@
 \asubsection{Introductory Membership Qualifications}
-Intro Membership is open to all RIT students.
+Intro Membership is open to all students currently enrolled at RIT.
 
 \asubsection{Introductory Membership Selection}
-Applicants notify the House of their interest in membership by submitting an application to the Evals Director.
-They must then undergo the selection process as defined in \ref{Selection Processes}.
-
-\asubsubsection{Selection Processes}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-
-% Current RIT students is defined as students who have attended RIT for at least 1 full semester
-\asubsubsubsection{Selection Process for Current RIT Students}
-\begin{enumerate}
-	\item The applicant submits an application to the Evaluations Director for review.
-	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
-	\item The application materials are then reviewed at an Evaluations meeting.
-	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
-\end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
-The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Introductory Process.
-\\* \\*
-Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+Applicants notify the Evals Director of their interest in membership by submitting an application.
+They then undergo the selection process as defined below.
+
+\asubsubsection{Selection Process for Current RIT Students}
+\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item The applicant submits an application to the Evals Director for review.
+	\item The applicant participates in an informal interview with three current Active, Alumni, or Honorary Members.
+	\item The application materials are reviewed at an Evals meeting.
+	      Then an Immediate Relative Majority Vote of attending members is held on whether or not to accept the person as an Intro Member.
+\end{enumerate}
 
 % Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
-\asubsubsubsection{Selection Process for Incoming RIT Students}
-\begin{enumerate}
-	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
-		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
-        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
-            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
-            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
-\end{enumerate}
-Note: Most membership privileges do not initiate until successful completion of the introductory process.
-This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
-The member does, however, have the right to use Computer Science House's facilities.
-The member is not required to pay dues during the Introductory Process.
-\\* \\*
-Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.
+\asubsubsection{Selection Process for Incoming RIT Students}
+\begin{enumerate}
+	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
+	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
+	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
+	      A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor.
+	      The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
+\end{enumerate}
 
 \asubsection{Introductory Membership Expectations}
-Intro members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.
+Intro Members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.
+Intro Members are not required to pay membership dues.
 
 \asubsection{Introductory Membership Privileges}
-Intro members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.
+Most membership privileges do not initiate until successful completion of the Intro Process.
+This means that until the member has passed the Intro Eval, the member does not have the right to vote on CSH issues and does not count towards quorum.
+The member does, however, have the privilege to use CSH's facilities.
 
 \asubsection{Introductory Membership Evaluations}
-\asubsection{The Introductory Process}
-The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
-\asubsection{The Evaluation Period}
-The Process will occur either once or twice per semester, and will last for six (6) weeks.
-The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
-The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
-If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
-If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
-If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
-\asubsection{The Introductory Packet}
-Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
-\begin{itemize}
-	\item Alumni members
-	\item Honorary members
-	\item Advisory members
-\end{itemize}
-At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
+The Intro Process allows Intro Members to learn about CSH and demonstrate their interest in becoming Active Members.
+During this period, Intro Members will meet members, learn CSH history, and be evaluated for Active Membership by Active Members.
+
+% fix numbers to be only text
+\asubsubsection{The Evaluation Period}
+The Intro Process will occur either once or twice per semester, and will last for six weeks.
+The process will be initiated by the Evals Director during either the first and second week of each semester. E-Board may approve an extension to the Intro Process by an E-Board Vote.
+If an Intro Process is extended, the Intro Eval shall occur at the termination of the extended process, which may be outside of the period defined in \ref{Introductory Evaluation}.
+If deemed necessary by the Evals Director or by an E-Board Vote, the second Intro Process must begin within nine days of the first process ending.
+If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the process.
+
+\asubsubsection{The Introductory Packet}
+Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active Members who have passed a Membership Eval, all On-Floor Intro and Active Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
+At the discretion of the Evals Director or as the result of an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.
+
 \asubsubsection{Expectations of an Introductory Member}
-Before the end of the Process, an Introductory Member is expected to:
-\begin{itemize}
-\item Attend all House meetings during the process
-\item Complete the Introductory Packet
-\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
-\item Attend at least one House social event during the process
-\item Attend at least two seminars relating to computing or electronics
-\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
-\end{itemize}
+\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use numbers
+Before the end of the Intro Process, an Intro Member is expected to:
+\begin{enumerate}
+	\item Attend all House Meetings during the Intro Process
+	\item Complete the Intro Packet
+	\item Attend at least one directorship meeting for each week of the process
+	\item Attend at least one CSH social event during the process
+	\item Attend at least two Technical Seminars during the process
+\end{enumerate}
 
 \asubsubsection{Introductory Evaluation}
-The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
-It occurs at the conclusion of the final week of the Process.
+The Intro Eval is the process by which Active Members choose which Intro Members to extend an offer of Active Membership.
+It occurs at the end of the final week of the Intro Process.
 
 \asubsubsubsection{Voting}
-On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
-A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
-In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
+On a member by member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
+An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
+For an Active Member to be eligible to vote during the Intro Eval they must meet the requirements outlined in \ref{Expectations of Voting Members}.
 Neither absentee nor proxy votes are allowed.
-House may choose any of the Outcomes for each member.
+Intro Members may be offered any of the outcomes listed in \ref{Outcomes}
 
@@
 \begin{enumerate}
-	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
-	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
-	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
-		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
-		Each conditional consists of a set of additional requirements and a deadline for completing them.
-		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
-		A conditional member who does not meet these additional requirements forfeits membership.
+	\item Intro Members may be offered Active Membership provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of attending members.
+	\item If an Intro Member fails to meet the requirements, their membership will be revoked.
+	\item An Intro Member may be given a conditional to complete as a means of making up for missing requirements.
+	      A conditional may be proposed by any member present at the Intro Eval, and if it is approved by the Evals Director, is then voted on by the attending members.
 \end{enumerate}
@@
 \asubsection{Introductory Membership Leave of Absence}
-After completion of the Intro Packet, an Intro member may request a leave of absence through the process described in \ref{Leave of Absence}.
+An Intro Member may request a Leave of Absence through the process described in \ref{Leave of Absence}.
 
 \asubsection{Introductory Membership Resignations}
-Intro members may resign by submitting the request for termination of membership to the Chair or Evals Director in writing before the completion of the intro process.
+Intro Members may resign by submitting the request for termination of membership to the Chair or the Evals Director in writing before the completion of the Intro Process.
+
 \asubsection{Introductory Membership Term}
-Intro membership shall last until the end of the Intro Process, at which time active membership is granted or membership is revoked.
+Intro Membership shall last until the end of the Intro Process, at which time Active Membership is granted or membership is revoked.
 
@@
 \asubsection{Active Membership Qualifications}
-Active Membership is open to all students currently enrolled at RIT who have passed the Intro Evals and their most recent Membership Evals.
+Active Membership is open to all students currently enrolled at RIT who have passed the Intro Eval and their most recent Membership Eval.
 
 \asubsection{Active Membership Selection}
-
-Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
+Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director.
 They will retain their previous Housing Status if applicable.
 \\*\\*
-Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate.
-The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent Quorum at the next House meeting.
-
-If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
+Any Alumni Member in bad standing, as described in \ref{Alumni Membership Selection}, may become an Active Member by notifying the Evals Director of their intent to participate.
+The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent quorum at the next House Meeting.
+If the vote passes the Alumni is reinstated as an Active Member with Off-Floor Status effective immediately.
 
 \asubsection{Active Membership Expectations}
-Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
-Active voting members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
-
-\asubsubsection{Expectations of House Members}
-Active members are required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Executive Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
+Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
+Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
+
+\asubsubsection{Expectations of Active Members}
+Active Members are required to pay dues as stated in \ref{Collection of Dues}, attend all House Meetings and E-Board candidate speeches, and attend at least fifteen of the directorship meetings for each semester in which they are an Active Member.
+They are also expected to sign a copy of the Membership Agreement.
 \\* \\*
-Active members must participate significantly in at least one major project during the academic year.
-Members are required to submit a description for this major project to the Executive Board for approval.
-As an option to this requirement, members may instead assist on a large number of House activities and projects.
+Active Members must participate in at least one major project during the academic year.
+Members are required to submit a description for this major project to E-Board for approval.
+As an alternative to this requirement, members may instead assist on a large number of CSH activities and projects.
 However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
-This participation will be evaluated by the Executive Board.
+This participation will be evaluated by E-Board.
 
@@
 Active Members receive the privilege to:
-\begin{itemize}
-	\item Vote on all issues brought before the House
-	\item Reside on the House
-	\item Hold an E-Board office on the House
-	\item Use Computer Science House facilities
-	\item Attend Computer Science House functions
-	\item Receive priority for available housing on the House when returning from cooperative education
-	\item Guaranteed housing in compliance with ResLife policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
-\end{itemize}
+\begin{enumerate}
+	\item Vote on CSH issues
+	\item Hold a position on E-Board
+	\item Use CSH facilities
+	\item Receive priority for on-floor housing, or apply for On-Floor Status
+\end{enumerate}
 
 \asubsubsection{Expectations of Voting Members}
-The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
-Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
-\begin{itemize}
-\item Attend all House meetings during the process
-\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
-\item Attend at least one House social event during the process
-\item Attend at least two seminars relating to computing or electronics
-\end{itemize}
+\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
+
+The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
+Any of these requirements may be waived by the Evals Director or an E-Board Vote.
+\begin{enumerate}
+	\item Attend all House Meetings during the Intro Process
+	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
+	\item Attend at least one CSH social event during the Intro Process
+	\item Attend at least two Technical Seminars during the Intro Process
+\end{enumerate}
+
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
+Active Members are evaluated annually through the Eval Process as described in \ref{Evaluations Processes}.
 
 % ACTIVE MEMBERSHIP EVALUATIONS
-
 \asubsubsection{Evaluations Processes}
-During the academic year, a House member is evaluated by the Membership Evaluation.
-The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-Semi-Annual Evaluations Meetings are open only to current Active Members.
-All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
+During the academic year, an Active Member is evaluated by the Membership Eval.
+The Membership Eval is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
+These meetings are open only to Active Members.
+All Active Members are expected to attend the these Evals meetings.
 \\* \\*
-At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
-It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
+At the beginning of any Eval Process listed herein, the Evals Director must read the sections of the CSH Constitution used during the respective Eval Process.
+It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.
+
 \asubsubsubsection{Membership Evaluation}
-The Membership Evaluation process occurs once per academic year.
-It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
+The Membership Eval occurs once per academic year.
+It is performed as part of the Eval Process that takes place during the spring semester to comply with RIT Housing deadlines.
+
 \asubsubsubsubsection{Voting}
-Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
-All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
-The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
-Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
-These requirements must be completed before the Membership Evaluation occurs.
-A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
+Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
+All Active Members who have not recieved an exemption from E-Board prior to the Membership Eval will be evaluated on a member by member basis by Active Members.
+The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
+Exceptions to the requirements may be made, as attending members may choose any of the outcomes for each member, even if the member being evaluated has not completed all of their requirements.
+These requirements must be completed before the Membership Eval occurs.
+A Secret Immediate Relative Majority vote with two-thirds quorum is required for the evaluation to be valid.
 Neither absentee nor proxy votes are allowed.
@@
 \asubsubsubsubsection{Outcomes}
-Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
+Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
 \\* \\*
-If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
-If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
-In either case, the member forfeits their ability to be included on the following year’s roster.
+If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
+If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.
+In either case, the member forfeits their ability to participate as an Active Member in the following year.
 \\* \\*
 A member may be given a conditional to complete as a means of making up for missing requirements.
-A conditional may be proposed by any member present at the Evaluation.
-If the conditional is approved by the Evaluations Director, it is then voted on by House.
+A conditional may be proposed by any member present at the Eval.
+If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
 Each conditional consists of a set of additional requirements a deadline for completing them.
-When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
-A conditional member who does not meet these additional requirements will have failed the evaluation.
+Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
+When the deadline expires, the conditional will be brought before E-Board, who will assess its completeness.
+A conditional member who does not meet these additional requirements will have failed the Eval.
+
 \asubsubsubsection{Appeals Process}
-If a member disagrees with the outcome of any evaluation, (e.g.
-is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
 \\* \\*
-If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
+If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.
 
 \asubsection{Active Membership Leave of Absence}
-An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+
+An Active Member may at any time request a Leave of Absence using the process described in \ref{Leave of Absence}.
 For the duration of an absence, a member:
-\begin{itemize}
+\begin{enumerate}
 	\item Forfeits their right to vote
@@
 	\item Will not be required to attend House Meeting
-\end{itemize}
+\end{enumerate}
 
 \asubsection{Active Membership Resignations}
-An Active member may resign by submitting, in writing, the reason for resignation to the Chair or Evals Director.
-Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
+An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
+Instead of forfeiting membership, Active Members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
@@
 \asubsection{Alumni Membership Qualifications}
-Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evals and departed for reasons other than revocation of House Membership.
+Alumni Membership is open to all former Active Members who passed at least one Membership Eval and departed for reasons other than revocation of membership.
 
 \asubsection{Alumni Membership Selection}
-Active members who depart house (i.e. resign) after passing the current operating session's Membership Evals are considered to be Alumni in good standing.
+Active Members who resign from CSH after passing the current operating session's Membership Eval are considered to be Alumni in good standing.
 \\*\\*
-Active members who depart house without passing the current operating session's Membership Evals are considered to be Alumni in bad standing.
-This may be appealed to E-Board in order to pursue a different outcome.
+Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
+This may be appealed to E-Board in order to pursue a different outcome, as described in \ref{Appeals}.
 
@@
 \asubsection{Alumni Membership Privileges}
-Alumni Members shall receive the right to:
-\begin{itemize}
-	\item Use Computer Science House facilities
-	\item Attend Computer Science House functions
-\end{itemize}
+Alumni Members have the privilege to use CSH facilities and attend CSH functions.
 
 \asubsection{Alumni Membership Evaluations}
-Alumni Members are not subject to any evaluation.
+Alumni Members are not subject to any Evals.
 
@@
 \asection{Honorary and Advisory Memberships}
+
 \asubsection{Honorary Membership Qualifications}
-Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
+Honorary Membership is open to a person whom CSH feels has contributed great personal effort to CSH and is deserving of recognition.
+
 \asubsection{Advisory Membership Qualifications}
-Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
+Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.
+
 \asubsection{Honorary and Advisory Membership Selection}
 \begin{enumerate}
-	\item A House Member submits to the Evals Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
+	\item A CSH Member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
 The nomination must specify the type of membership the nominee is nominated for.
 	\item The Evals Director performs preliminary research on the candidate and presents the findings.
-	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
-		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.
-
-	\item The nomination is presented at a House Meeting for discussion and a Two-Thirds vote, as defined in \ref{Two-Thirds}.
-		Ballots are distributed and voting must remain open for a minimum of forty-eight hour period.
+	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
+	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
+	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
 	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
-    \item Candidates selected for Advisory Membership are notified of their acceptance as House Advisors and asked to accept or decline
-        the selection.
-\end{enumerate}
+	\item Candidates selected for Advisory Membership are notified of their acceptance as CSH Advisors and asked to accept or decline the selection.
+\end{enumerate}
+
 \asubsection{Honorary Membership Expectations}
-Honorary Members are encouraged to remain in contact with the House.
+There are no expectations associated with the Honarary Membership status.
+
 \asubsection{Advisory Membership Expectations}
-Advisors are encouraged to offer advice and assistance to the House in any capacity the Advisor is able to help.
-Advisors are also encouraged to meet House members and occasionally attend House activities.
+There are no expectations associated with the Advisory Membership status.
+
 \asubsection{Honorary and Advisory Membership Privileges}
-Honorary and Advisory Members may advise in all issues brought before the House, use Computer Science House facilities, and attend Computer Science House functions.
+Honorary and Advisory Members may advise in CSH issues, use CSH facilities, and attend CSH functions.
+
 \asubsection{Honorary and Advisory Membership Evaluations}
-Honorary and Advisory Members are not subject to formal evaluations.
+Honorary and Advisory Members are not subject to any Evals.
+
 \asubsection{Honorary and Advisory Membership Resignations}
-
 An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chair.
 The resignation will be read at the following House Meeting and become effective at that time.
+
 \asubsection{Honorary and Advisory Membership Term}
@@
 \asection{Leave of Absence}
-A Leave of Absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
 In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence, located at \url{https://www.rit.edu/policies/d021}.
-Additionally, the member should notify the Evaluations Director of their Leave, at which point they become exempt from all House requirements until they return.
+Additionally, the member should notify the Evals Director of their Leave, at which point they become exempt from all CSH requirements until they return.
 
 % ARTICLE V - OFFICERS OF THE HOUSE
-\article{Officers of the House}
+\article{Computer Science House Officers}
+
 \asection{Executive Board}
-The Executive Board is the main governing body of the House.
-
-Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
+E-Board is the main governing body of CSH.
+Its purpose is to provide leadership and direction for CSH, to oversee the day-to-day operations of CSH, and to initiate and organize programs and projects for CSH.
 \\*\\*
-There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
-A voting E-Board member is considered to be any person with a non-zero vote on E-Board.
+There is one permanent directorship for each major aspect of the government of CSH and each one is chaired by an E-Board Member.
+A Voting E-Board Member is considered to be any E-Board Member with a non-zero vote.
 % Defined this way so that (for example) each member in a dual directorship is each considered to be a voting member on E-Board.
-Ad Hoc directorships are created on an as-needed basis.
-They are generally very task oriented and are chaired by a House member.
-A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
-Any large expenditures or large effect decisions must be brought before the entire House.
 
 \asubsection{Responsibilities}
-
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\asubsubsection{Responsibilities of E-Board}
-
-\begin{enumerate}
-	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
-	\item To meet, as an E-Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
-	\item To report pertinent information to House members at the following House Meeting
+
+\asubsubsection{Responsibilities of the Executive Board}
+\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH
+	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
+	\item To report pertinent information to members at the following House Meeting
 	\item To maintain records of the goals defined by each previous E-Board
 	\item To act as a Judicial Board as defined in \ref{Judicial}
-	\item To review major projects, as defined in \ref{Expectations of House Members}
+	\item To review major projects, as defined in \ref{Expectations of Active Members}
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
-	\item To respect the privacy of House Members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
-	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
-	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
-		The constitution should remain up to date with current practices.
-\end{enumerate}
-
-\asubsection{Responsibilities of the Chair}
+	\item To respect the privacy of members confiding in E-Board, barring situations related to sexual assault or endangerment of oneself or others
+	\item To publish a document at the end of each semester to all members stating CSH's accomplishments of that semester
+	      %\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}.
+	      %The constitution should remain up to date with current practices.
+\end{enumerate}
+
+\asubsubsection{Responsibilities of the Chairperson}
 \begin{enumerate}
@@
 	\item To exercise general supervision over the operations of E-Board
-	\item To exercise general supervision over regular House activities
+	\item To exercise general supervision over regular CSH activities
 	\item To act as a liaison to the academic and administrative departments at RIT
-	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
-	\item To cast tie-breaking vote in a split decision in an E-Board vote
+	\item To represent CSH publicly
+	\item To coordinate collaboration between CSH and companies in the industry
+	\item To cast tie-breaking vote in a split decision in an E-Board Vote
 \end{enumerate}
@@
 \begin{enumerate}
-	\item To preside over Evals Meetings
 	\item To exercise general supervision over Evals operations
-	\item To oversee the screening, interviewing, and acceptance or rejection of prospective House members
-	\item To oversee the Membership Evals of Active Members
+	\item To oversee the screening, interviewing, and acceptance or rejection of prospective members
 	\item To collaborate with the ResLife Advisor to determine room change selection and any changes of membership residency
-	\item To act as a part of a Judicial Board as defined in \ref{Judicial}
-	\item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\asubsubsection{Responsibilities of the Social Director(s)}
-\begin{enumerate}
-	\item To preside over Social Meetings in which House members are encouraged to bring ideas for social events
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
+\asubsubsection{Responsibilities of the Socials Director(s)}
+\begin{enumerate}
 	\item To exercise general supervision over Social operations
-	\item To oversee the organization, initiation, and execution of House social activities
-  \item To ensure that there is a variety of events for House members to participate in throughout the academic year
-  \item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\asubsection{Responsibilities of the PR Director}
-\begin{enumerate}
-	\item To preside over PR Directorship Meetings
-	\item To operate House social media accounts intended to represent House as a whole
-	\item To oversee the organization, initiation, and execution of House philanthropic events
-	\item To preserve and improve the public image of House
-	\item To collaborate with other E-Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
-    \item To oversee the preparation of House for Open Houses, tours, and special events
+	\item To oversee the organization and execution of CSH social activities
+	\item To ensure that there is a variety of events for members to participate in throughout the academic year
 	\item To vote on issues presented to E-Board
@@
 
+\asubsubsection{Responsibilities of the Public Relations Director}
+\begin{enumerate}
+	\item To operate CSH social media accounts intended to represent CSH as a whole
+	\item To oversee the organization and execution of CSH philanthropic events
+	\item To preserve and improve the public image of CSH
+	\item To collaborate with other E-Board members to organize, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
+	\item To oversee the preparation of CSH for open houses, tours, and special events
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
 \asubsubsection{Responsibilities of the Financial Director}
 \begin{enumerate}
-	\item To preside over Financial Meetings in which House members are encouraged to bring ideas for fund-raising activities
 	\item To supervise financial administrators and transactions involving house projects
-	\item To maintain financial and inventory records of House capital and assets
-	\item To plan and enforce a House budget
-	\item To oversee House finances and generation of House funds
-	\item To publish a semesterly House financial statement
-	\item To supervise the collection of semesterly House dues
+	\item To maintain financial and inventory records of CSH capital and assets
+	\item To plan and enforce a CSH budget
+	\item To oversee CSH finances and generation of CSH funds
+	\item To publish a semesterly CSH financial statement
+	\item To supervise the collection of semesterly dues
 	\item To oversee the planning and execution of fundraising events
-	\item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\subsubsection{Responsibilities of the R\&D Director}
-\begin{enumerate}
-	\item To preside over R\&D Meetings in which House members are encouraged to bring ideas for projects
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
+\asubsubsection{Responsibilities of the Research and Development Director(s)}
+\begin{enumerate}
 	\item To exercise general supervision over R\&D operations
-	\item To oversee the planning, organization and construction of technical projects for the House's benefit
-	\item To strive to fulfill the House's need for technical equipment
-	\item To provide seminars and tutorials to educate House members in technical areas
-	\item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\asubsection{Responsibilities of the IMPs Director}
-\begin{enumerate}
-	\item To preside over IMPs Meetings
+	\item To oversee the planning, organization, and construction of technical projects for the CSH's benefit
+	\item To strive to fulfill the CSH's need for technical equipment
+	\item To organize and support Technical Seminars
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
+\asubsubsection{Responsibilities of the House Improvements Director}
+\begin{enumerate}
 	\item To exercise general supervision over the IMPs operations
-	\item To oversee the organization and construction of physical improvements to the House
-	\item To oversee the general maintenance of the appearance of the House
-	\item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\asubsection{Responsibilities of the OpComm Director}
+	\item To oversee the organization and construction of physical improvements to CSH
+	\item To oversee the general maintenance of the appearance of CSH
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
+\asubsubsection{Responsibilities of the Operational Communications Director}
 \begin{enumerate}
 	\item To represent the RTPs at E-Board Meetings and at House Meetings
-	\item To report the status of the House computer systems and network to E-Board and House members
+	\item To report the status of the house systems, services, and networks
 	\item To facilitate communications with RIT Information and Technology Services
@@
 
-\asubsection{Responsibilities of the History Director}
-\begin{enumerate}
-	\item To preside over History Meetings
+\asubsubsection{Responsibilities of the History Director}
+\begin{enumerate}
 	\item To exercise general supervision over the History operations
@@
 	\item To oversee the production and distribution of a semi-annual newsletter
-	\item To oversee the creation of a yearbook outlining House events for the year
-	\item To vote on issues presented to the Executive Board
-\end{enumerate}
-
-\asubsubsection{Responsibilities of the House Secretary}
+	\item To vote on issues presented to E-Board
+\end{enumerate}
+
+\asubsubsection{Responsibilities of the Secretary}
 \begin{enumerate}
@@
 	\item To oversee the maintenance of E-Board records and documents
-	\item To provide administrative assistance to E-Board
-	\item To record all votes cast during House Meetings and Open E-Board Meetings
+	\item To record all votes held and their outcomes during House Meetings and open E-Board Meetings
 \end{enumerate}
@@
 	\item Ad Hoc Directorships are responsible for the task for which they were created
-	\item Any responsibilities budgets or finances for the Ad Hoc Directorship are placed upon the assigned director
+	\item Any responsibilities, budgets, or finances for the Ad Hoc Directorship are placed upon the assigned director
 \end{enumerate}
@@
 \asubsection{Closed Executive Board}
-Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
-A closed Executive Board meeting may be called at any time by any member of the Executive Board.
-However, the Chairperson and at least two-thirds of the Voting Members of the Executive Board must be present for the meeting to be called.
+Closed E-Board Meetings are open only to the Chair, Voting Members of E-Board, and those with the express permission of the aforementioned members.
+A closed E-Board meeting may be called at any time by any member of E-Board.
+However, the Chair and at least two-thirds of the Voting Members of E-Board must be present for the meeting to be called.
 
 \asubsection{Qualifications}
-\asubsubsection{Qualifications to be the Chair, Evals Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
-\begin{enumerate}
-	\item Candidates must be Active Members during the term of office
-	\item Candidates must have at least one full semester of House membership as an Active Member
-	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
-  \item Candidates for Chairperson or Evals Director must reside on floor during the term of office
-\end{enumerate}
-\asubsubsection{Qualifications to be the Operational Communications Director}
-\begin{enumerate}
-	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
-	\item Candidates must be a current Active Member.
-	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
-\end{enumerate}
-
-\asubsubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
-\begin{enumerate}
-\item Candidates must be Active Members
+
+\asubsubsection{Qualifications for Chairperson, Evaluations Director, Social Director, Financial Director, Research and Development Director(s), House Improvements Director, History Director, Public Relations Director}
+\begin{enumerate}
+	\item Candidates must be Active Members during the term of office.
+	\item Candidates must have at least one full semester of membership as an Active Member.
+	\item Elected or selected candidates may not hold two simultaneous voting E-Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
+	\item Candidates for Chair or Evals Director must reside on floor during the term of office.
+\end{enumerate}
+
+\asubsubsection{Qualifications for Operational Communications Director}
+\begin{enumerate}
+	\item Candidates must be an RTP and an Active Member.
+	\item An RTP cannot be the director if they currently hold any other elected E-Board position. % Consider that opcomm is also an exception before using this wording elsewhere
+\end{enumerate}
+
+\asubsubsection{Qualifications for Secretary or Ad Hoc Director}
+\begin{enumerate}
+	\item Candidates must be Active Members.
 \end{enumerate}
@@
 \begin{enumerate}
-  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
+	\item CSH may choose to waive the following subset of the qualifications for E-Board positions, as defined under \ref{Qualifications}, for all candidates:
 	      \begin{enumerate}
 		      \item Candidates must reside on floor during the term of office.
-      \item Candidates must have at least one full semester of House membership as an Active Member.
-      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
-    \end{enumerate}
-  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
-  \item A Three-Quarters Immediate Vote with three-quarters Quorum is then taken to determine whether the proposed waiver shall take effect.
-  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
-  \item Waivers always apply to all Candidates for the Executive Board position.
+		      \item Candidates must have at least one full semester of membership as an Active Member.
+		      \item Social and R\&D are the only voting E-Board positions that allow for dual directorship.
+	      \end{enumerate}
+	\item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and qualification is being voted upon, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
+	\item A Three-Quarters Immediate Vote with three-quarters quorum is then taken to determine whether the proposed waiver shall take effect.
+	\item Each vote to waive a qualification must only apply to a single qualification for a single E-Board position.
+	\item Waivers always apply to all candidates for the E-Board position.
 \end{enumerate}
@@
 \asubsection{Selection}
-\asubsubsection{Dual Directorship}
-Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
-
-If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
-If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative.
+
+\asubsubsection{Dual Directors}
+Social and R\&D are the only voting E-Board positions that allow for dual directors.
+
+If two candidates elect to run as dual directors, their names are placed together on a single line of the election ballot.
+If they are also nominated as a single directorship or as dual directors with another member, their votes are not cumulative.
 Each different nomination must be a separate entry on the election ballot.
-Non-voting E-Board positions (i.e. Ad Hoc Directors) are not restricted to single or dual directorship.
-
-The following special cases cover the operation of a dual directorship:
-\begin{itemize}
-	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
-		The vacated office is then handled like any other vacated office; see \ref{E-Board Resignations}.
-	\item During an official E-Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
+Ad Hoc Directors are not restricted to single or dual directors.
+
+The following special cases cover the operation of dual directors:
+\begin{enumerate}
+	\item If one of the members in a dual directorship resigns, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
+	      The vacated office is then handled like any other vacated office, as referenced in \ref{Executive Board Resignations}.
+	\item During an official E-Board Vote, each dual director's vote counts for one half of a vote in the tallying of votes.
 	      The members of the dual directorship need not vote the same way in a vote.
-	\item A member of a dual directorship may not hold any other Executive Board position.
-	\item When attendance requirements call for the dual directorship position to be present, both directorship members must be present to fulfill the requirements.
-	\item Dual directorships must have both members present for to count towards Quorum in an Executive Board Vote.
-\end{itemize}
-
-\subsubsection{Selection of the Chair, Evals Director, Social Director(s), Financial Director, IMPs Director, History Director,  R\&D Director(s), PR Director}
-\begin{enumerate}
-	\item The opening of the E-Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
-		Any House member may nominate any member or pair of members where appropriate for a Directorship.
+	      This cannot be used to give a vote to a position that would not otherwise have one in an E-Board Vote.
+	\item A member of a dual directorship may not hold any other Voting E-Board position or the position of Chair.
+	      When attendance requirements call for the dual directorship position to be present, at least one of the dual directors must be present to fulfill the requirements.
+\end{enumerate}
+
+\asubsubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, History Director,  Research and Development Director(s), Public Relations Director}
+\begin{enumerate}
+	\item The opening of the E-Board position(s) is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
+	      Any member may nominate any member, or pair of members where appropriate, for a directorship.
 	\item The candidates will be notified of their nomination.
@@
 	      A list of all nominees who have accepted their nominations will be posted shortly thereafter.
-	\item The date and time of candidate speeches will be announced by a member of E-Board at least five (5) days prior to the event. 
-		All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of House Members}.
+	\item The date and time of candidate speeches will be announced by a member of E-Board at least five days prior to the event.
+	      All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of Active Members}.
 	      If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evals Director, who will record the reason with the absence.
-	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.
+	\item Each candidate will be given an equal amount of time to present their platform of candidacy to the attending members.
 	\item Ballots will then be distributed for a Balloted Vote \ref{Balloted Vote} and voting will be open for a minimum of a forty-eight hour period.
@@
 	      In addition, an area will be provided to indicate a write-in selection of a candidate.
-	\item At the end of the voting period, the Chairperson will terminate voting.
+	\item At the end of the voting period, the Chair will terminate voting.
 	\item The winners are determined via the process described in \ref{Ranked Choice}.
-		A fifty-percent Quorum is required for the election to be official.
+	      A fifty-percent quorum is required for the election to be official.
 	      All winners are notified of their election.
 	      If the position is currently vacant, the winner immediately assumes office.
-		If not, the winner will assume office at the end of the current term (\ref{Term}).
+	      If not, the winner will assume office at the end of the current term, as defined in \ref{Term}.
 	      Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Ranked Choice}.
@@
 
-\asubsection{Selection of the OpComm Director}
+\asubsection{Selection of the Operational Communications Director}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
+
 \begin{enumerate}
@@
 	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
-	\item The candidate is presented to the Executive Board for approval.
-		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
-		An Executive Board Vote is taken to determine whether the candidate is selected for the position.
+	\item The candidate is presented to E-Board for approval.
+	      This E-Board Meeting is closed to the E-Board Members, RTPs, and members with explicit invitation from E-Board.
+	\item All Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
+	      An E-Board Vote is taken to determine whether the candidate is selected for the position.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board.
-  An Executive Board Vote is taken to determine whether directorship status is granted.
-	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
-\end{enumerate}
-
-\asubsection{Selection of the House Secretary}
-E-Board may choose to select a current voting E-Board member, or to select any interested Active member, as House Secretary.
+	\item When a group of members feels an Ad Hoc Directorship is necessary, they present their plans to E-Board.
+	      An E-Board Vote is taken to determine whether directorship status is granted.
+	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budget, and membership considerations are defined.
+\end{enumerate}
+
+\asubsection{Selection of the Secretary}
+E-Board may select any interested Active Member as Secretary.
 The selection process can be an informal appointment, or follow an election process similar to other voting E-Board positions.
 
-\asection{E-Board Resignations}
-An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
-
-The resignation will be read at the following House Meeting and become effective at that time.
-The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
-Following a resignation, the Selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
-To postpone such a Selection, the Chairperson may chair an Immediate Relative Majority Vote \ref{Immediate Vote} \ref{Relative Majority} during a House Meeting prior to the beginning of the Selection process to delay the Selection process by a specified amount of time.
+\asection{Executive Board Resignations}
+An E-Board Member may resign from their E-Board position by submitting in writing the reason for resignation to the Chair.
+The E-Board resignation will be read at the following House Meeting and become effective at that time.
+The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
+Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
+To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.
 
 \asection{Appointment of an Interim Director}
-The duties and responsibilities of a vacated office are assumed by the Chair or by an Active member that is appointed at the Chair's discretion until the new member takes office.
+The duties and responsibilities of a vacated office are assumed by an Active Member that is appointed at the Chair's discretion until the new director takes office.
+% It is often the Chair that assumes the responsibilities of that position
 The vote of a vacated E-Board position shall be cast as an abstention in all E-Board matters where this vote is required to be cast.
@@
 \begin{enumerate}
-	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
-	\item The impeachment petition is then presented at an Executive Board Meeting.
-		The member(s) initiating the petition present their case to the Executive Board.
-		The Executive Board then questions the accused member of the allegations.
-	\item An Executive Board Vote is taken on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
-		If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed.
-		This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
+	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current members equaling or exceeding one-third the number of Eligible Votes, as defined in \ref{Eligible Votes}.
+	\item The impeachment petition is then presented at an E-Board Meeting.
+	      The member(s) initiating the petition present their case to E-Board.
+	      E-Board then questions the accused member of the allegations.
+	\item An E-Board Vote is taken on the impeachment petition, with all Voting E-Board Members present except the accused member who must be absent and whose vote counts as an Abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
+	      If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
+	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
 	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
-	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
-		Votes shall be collected and counted for a Two-Thirds Balloted Vote described in \ref{Balloted Vote}.
-	\item A two-thirds Quorum is necessary for the vote to be official.
+	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
+	      Votes shall be collected and counted for a Two-Thirds Balloted Vote, as described in \ref{Balloted Vote}.
+	\item A two-thirds quorum is necessary for the vote to be official.
 	      If the resolution passes, the accused officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
 	      If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
-		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Executive Board Resignations}.
-	\item House Secretary can be impeached according to the above process, or may be dismissed by an Executive Board Vote.
+	      A new selection and interim duty fulfillment procedure is followed similar to that of a resignation, as described in \ref{Executive Board Resignations}.
+	\item The Secretary can be impeached according to the above process, or may be dismissed by an E-Board Vote.
 \end{enumerate}
@@
 \begin{enumerate}
-\item The Election Process for the following year's E-Board members shall begin in the middle of Spring semester.
+	\item The election process for the following year's E-Board members shall begin in the middle of spring semester.
 	\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
@@
 \asection{Appeals}
-Decisions made by the Executive Board may be appealed and overturned.
-To initiate an appeal, a member must have the support of three voting members of the Executive Board, or a petition with the signatures of one-third of Active Members.
-After the appeal is presented, an Executive Board Vote is taken to determine whether or not to overturn and reevaluate the decision.
-If the vote passes, the Executive Board may discuss and make a new ruling by another Executive Board Vote.
-
-\asection{Maintainers}
-
-\asubsection{Maintainer Qualifications}
+To initiate an appeal, a member must have the support of three Voting E-Board Members, or a petition with the signatures of one-third of Active Members.
+After the appeal is presented, an E-Board Vote is taken to determine whether or not to overturn and reevaluate the decision.
+If the vote passes, E-Board may discuss and make a new ruling by another E-Board Vote.
+
+\asection{Constitutional Maintainers}
+
+\asubsection{Constitutional Maintainer Qualifications}
 Maintainers must be Active or Alumni Members.
 
-\asubsection{Maintainer Expectations}
+\asubsection{Constitutional Maintainer Expectations}
 Maintainers are expected to:
-\begin{itemize}
+\begin{enumerate}
 	\item Be knowledgeable about the Constitution
@@
 	\item Keep a public record of changes to the Constitution
-\end{itemize}
-Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.
-
-\asubsection{Maintainer Term}
-Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
-A Maintainer may resign at any time by notifying the current Executive Board and Maintainer group.
-If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.
-
-\asubsection{Maintainer Selection}
-Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration.
-The Executive Board may choose to approve or reject the nomination by Simple Majority vote with a quorum of seventy-five percent of the Total Number of Possible Votes.
+\end{enumerate}
+Failure to meet any of these expectations is grounds for revocation of Maintainer status by E-Board.
+
+\asubsection{Constitutional Maintainer Term}
+Maintainer status lasts until it is resigned, or until it is revoked by an E-Board Vote.
+A Maintainer may resign at any time by notifying the current E-Board and Maintainer group.
+If a Maintainer no longer satisfies \ref{Constitutional Maintainer Qualifications}, they lose Maintainer status.
+
+\asubsection{Constitutional Maintainer Selection}
+Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
+E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent of the Eligible Votes.
 
 \asection{Root Type Persons}
-The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
-It is a self-governing committee making decisions by a simple majority vote.
-Membership is composed of all Root Type Persons.
+The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
+It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
+Membership is composed of all RTPs.
 
@@
 \begin{enumerate}
-	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
+	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
 	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
-	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
-		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
-	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
-		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
+	\item A list of all nominees who have accepted is presented to E-Board for approval.
+	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
+	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
 \end{enumerate}
@@
 \asubsubsection{Qualifications of a Root Type Person}
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
-	\item Candidates may be granted an exemption by current Root Type Persons.
-		Such an exemption may be withdrawn at any time by the current Root Type Persons.
-	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
-		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
-	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
-\end{enumerate}
+Candidates must be Active Members.
+
+\asubsubsection{Prior Root Type Persons}
+Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
+Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
+The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.
 
 \asubsubsection{Creation of Accounts}
-Root Type Persons have the authority to manage user accounts for House systems.
-Before introductory, active, or alumni members may receive an account they must:
-\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
-\begin{enumerate}
-	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
-	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
-\end{enumerate}
-Accounts for honorary and advisory members may be created at the discretion of the Root Type Persons.
+RTPs have the authority to manage user accounts for CSH systems.
+Before a member may receive an account they must:
+\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
+\begin{enumerate}
+	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of CSH and RIT facilities.
+	\item Obtain greater than or equal to 60\% of required signatures, excluding those of On-Floor Members who have not passed a Membership Eval, in the Intro Packet or successfully complete Intro Eval.
+	\item Sign a copy of the Membership Agreement
+\end{enumerate}
+Accounts for Honorary and Advisory Members may be created at the discretion of the RTPs.
 
 \asubsubsection{Code of Conduct}
-The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
+The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for CSH accounts.
 \\* \\*
@@
 Members may sign a more recent revision of the Code of Conduct to update their agreement.
+
 \asubsubsubsection{Changes}
+\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
 The following process is used for making changes to the Code of Conduct document.
 \begin{enumerate}
-	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
+	\item An RTP drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
 	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
-	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
+	\item The final proposal is presented at the next House Meeting and ballots are distributed for a One-Half Balloted House Vote with fifty percent quorum, as described in \ref{Balloted Vote}.
+	\item Any RTP may make any non-semantic change to the Code of Conduct with the approval of two other RTPs.
 \end{enumerate}
@@
 \asection{Financial Operations of the House}
+
 \asubsection{Amount of House Dues}
-The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
-\asubsection{Collection of House Dues}
-The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
-During the dues collection period, dues for both semesters for all Active Members are collected through the member's RIT bill.
-Dues for any Alumni Member in good standing are to be collected when intention to pay is expressed to the Financial Director.
+The amount of dues for Active Members will be eighty dollars per academic semester.
+
+\asubsection{Collection of Dues}
+The collection period of house dues will be decided in conjunction with the Center for ResLife and Housing Operations.
+During the dues collection period, dues for both semesters are collected through the member’s RIT bill.
+Dues for any Alumni in good standing are to be collected when intention to pay is expressed to the Financial Director.
+
 \asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
-If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
-If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
-If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
-If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
-If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
-In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues.
-Additional time and reduction of dues may both be given to a member in an appropriate situation.
-All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
+If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
+The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
+If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
+If appealed, E-Board may provide an extension and/or reduction to the member.
+If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
+All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
 After this date, dues collection is suspended until the start of the next academic year.
@@
 		\hline
-Directorship Name & Percentage of Dues \\
+		Directorship & Percentage of Dues
+		\\ \hline
 		\hline
-\hline
-Operational Communications & 20\% \\
-\hline
-Evaluations & 5\% \\
-\hline
-House History & 10\% \\
-\hline
-House Improvements & 15\% \\
-\hline
-Research and Development & 20\% \\
-\hline
-Social & 20\% \\
-\hline
-Public Relations & 5\% \\
-\hline
-Accumulated & 5\% \\
-\hline
+		OpComm       & 20\%
+		\\ \hline
+		R\&D         & 20\%
+		\\ \hline
+		Social       & 20\%
+		\\ \hline
+		IMPs         & 15\%
+		\\ \hline
+		History      & 10\%
+		\\ \hline
+		Evals        & 5\%
+		\\ \hline
+		PR           & 5\%
+		\\ \hline
+		Accumulated  & 5\%
+		\\ \hline
 	\end{tabular}
@@
 % This figure comes from having approximately 55 on-floor members with $80 per semester dues (totaling $8800) minus 5% set aside for Accumulated.
-
 Dues collected from on-floor members are to be distributed into directorship budgets as shown in the above table.
-Money allocated for Accumulated or collected from off-floor members is deposited into the CSH Account and saved.
+Money allocated for Accumulated or collected from off-floor members is deposited into the CSH account and saved.
 
 \asubsection{Expenditure Approval}
-All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
-Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
-A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
+All CSH expenditures must be approved by the Financial Director and the director whose budget is going to be used for the expenditure.
+Single expenditures may not exceed seventy-five dollars and Total Expenditures may not exceed one-hundred dollars.
 \\* \\*
-If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
-At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
-A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
+If the above amounts are to be exceeded, the expenditure must be approved by an Immediate One-Half Vote at a House Meeting before the funds may be appropriated.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars, but not to exceed three-hundred dollars.
+A Two-Thirds Immediate Vote with twenty-five percent quorum is required to approve the purchase.
 \\*\\*
-For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
-This proposal includes the project budget, inventory of required resources, and a timeline for completion.
+For expenditures exceeding \$300 in total funding, a spending presentation must be presented to at a House Meeting.
+This presentation includes the funds required for the expenditure, inventory of required resources, and, if applicable, a timeline for completion.
 \\* \\*
-If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
+If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
 This amount is to be directly subtracted from the general CSH account.
-\\* \\*
-Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
-
 % HOUSING
@@
 \asubsection{Housing Status}
-All Alumni, Active, and Introductory Members have a housing status.
-This status indicates their right to priority housing on the floor.
+All Alumni, Active, and Intro Members have a Housing Status.
+This status indicates their privilege of priority housing on the floor.
 Alumni Members in good standing keep the housing status they had as Active Members.
-Alumni Members in bad standing have Off-Floor status.
+Alumni Members in bad standing have Off-Floor Status.
+
 \asubsubsection{On-Floor Status}
-Members with On-Floor status are eligible to live on the floor.
-To be granted On-Floor status, members may notify the Evaluations Director that they would like to come up for a vote.
-The Evaluations Director will then bring them up for vote at the next meeting.
+Members with On-Floor Status are eligible to live on the floor.
+To be granted On-Floor Status, members may notify the Evals Director that they would like to come up for a vote.
+The Evals Director will then bring them up for vote at the next Evals Meeting.
+
 \asubsubsection{Off-Floor Status}
-Members with Off-Floor status do not have the right to live on the floor.
+Members with Off-Floor Status do not have the right to live on the floor.
 They still have access to all other privileges associated with their membership, and may still accumulate Housing Priority Points.
@@
 \asubsection{Housing Priority System}
-The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
-The member with top priority is the member with on-floor status and the most Housing Priority Points.
-Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation.
-Each Active Member who passes the Membership Evaluation is granted two (2) Housing Priority Points.
-\\* \\*
-In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
-\asubsubsection{Single Room Assignments}
-When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
-In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
-If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
-This process continues until a member selects to move into the single room.
-Once in a single room, a House member retains the assignment until voluntarily giving it up.
-It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
-\asubsubsection{Double Rooms as Single rooms}
-During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
-It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
-This only applies if there is a totally vacant room.
+The Housing Priority System is a means for determining the priority a member has in a housing issue or the assignment of available housing.
+The member with top priority is the member with On-Floor Status and the most Housing Priority Points.
+Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval. Each Active Member who passes the Membership Eval is granted two Housing Priority Points.
 
@@
 \article{Voting}
-This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
+This section outlines the different types of votes and ballots used to make decisions and defines relevant terminology.
 
 \asection{Definitions}
+
 \asubsection{Eligible Votes}
-The number of Active members eligible to vote on the issue.
+The number of Active Members eligible to vote on the issue.
+
 \asubsection{Votes Cast}
-The number of ballots cast in a vote, excluding Abstentions.
+The number of ballots cast in a vote, excluding abstentions.
 
 \asubsection{Quorum}
-The minimum Votes Cast for vote to be considered valid.
-Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention.
-A Quorum is expressed as a fraction or percentage of Eligible Votes (rounded up to the nearest vote) unless otherwise specified in the text of the vote.
+The minimum number of votes that must be cast for the vote to be considered valid.
+Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an abstention.
+A quorum is expressed as a fraction or percentage of Eligible Votes, rounded up to the nearest vote, unless otherwise specified in the text of the vote.
+
 \asubsection{Proxy Vote}
@@
 Proxy Votes must be documented in writing and signed by the absent member.
-The count of all Proxy Vote must be recorded and announced in all votes.
+The count of all Proxy Votes must be recorded and announced in all votes.
 
 \asubsection{Abstention}
-An Abstention is a neutral vote that counts towards the Quorum but not towards determining the outcome of a vote.
+An abstention is a neutral vote that counts towards the quorum but not towards determining the outcome of a vote.
 A means to abstain must always be provided in a vote.
+
 \asubsection{Vote Counters}
@@
 \asection{Voting Procedures}
+
 \asubsection{Balloted Vote}
+
 \asubsubsection{Method of Vote}
 Votes are cast on ballots that provide a means to indicate every possible option in the vote.
+
 \asubsubsection{Voting Period}
-For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
-For any other type of vote, the voting period must be at least twenty-four (24) hours.
+For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight hours in length.
+For any other type of vote, the voting period must be at least twenty-four hours.
 The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
 
-The voting period opens once ballots are distributed to each House member eligible to cast a vote.
+The voting period opens once ballots are distributed to each member eligible to cast a vote.
 At the end of the voting period, the Chair of the Vote collects the ballots, closing the voting period.
@@
 The chairing member will count the number of members casting their immediate vote for that possibility.
-Any members that count towards Quorum that do not explicitly cast a vote will have their vote counted as an Abstention.
+Any members that count towards quorum that do not explicitly cast a vote will have their vote counted as an abstention.
+
 \asubsubsection{Voting Period}
 An Immediate Vote lasts as long as it takes for all votes to be tallied.
+
 \asubsubsection{Secret Immediate Vote}
 An Immediate Vote in which votes are kept anonymous.
+
 \asubsubsection{Executive Board Vote}
-In an Executive Board Vote, only Voting Members of the Executive Board are eligible to vote.
-Unless otherwise specified, Executive Board votes are Immediate Relative Majority votes with a fifty percent Quorum.
+In an E-Board Vote, only Voting E-Board Members are eligible to vote.
+Unless otherwise specified, E-Board votes are Immediate Relative Majority Votes with a fifty percent quorum.
 
@@
 Approval Criteria are the rules that determine whether an option in a vote has passed.
+
 \asubsection{Relative Majority}
-In a Relative Majority vote, an option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
+In a Relative Majority Vote, an option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
+
 \asubsection{Fractional}
-In a Fractional vote, an option in the vote passes if the number of votes cast for that option exceeds a specified fraction of the Votes Cast, rounded up to the nearest vote.
-The fraction is specified in the text describing the vote (eg, "Two-Thirds Vote").
+In a Fractional Vote, an option in the vote passes if the number of votes cast for that option exceeds a specified fraction of the Votes Cast, rounded up to the nearest vote.
+The fraction is specified in the text describing the vote, for example, "Two-Thirds Vote".
+
 \asubsection{Ranked Choice}
-In a Ranked Choice vote, voters rank the options by placing a '1' by their first choice, a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of options.
+In a Ranked Choice Vote, voters rank the options by placing a '1' by their first choice, a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of options.
 
@@
 If only one option may pass, then the vote must be recast or tabled at the discretion of the Chair of the Vote.
-In the event of a tie in an Executive Board Vote, the Chairperson may cast the tie-breaking vote.
+In the event of a tie in an E-Board Vote, the Chair may cast the tie-breaking vote.
 
@@
 \article{Judicial}
-The Executive Board may approve a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
+E-Board may approve a request from a member for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among members, or a House interest needs resolution.
+
 \asection{Formation of a Judicial Board}
-A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board.
-If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of an Executive Board Vote of the remaining members.
+A Judicial Board is made up of the Chair, the Evals Director, and an additional Voting E-Board Member.
+If the Chair or the Evals Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another Voting E-Board Member by means of an E-Board Vote of the remaining members.
 
@@
 The Judicial Board may present an official ruling following the Judicial Investigation.
-This ruling may be appealed in the same manner as an E-Board decision \ref{Appeals}.
-
-% Article VIII - MODIFICATIONS TO THE CONSTITUTION
-\asubsection{Non-Semantic Changes}
-There are two methods for non-semantic change to the Constitution.
-A Maintainer may approve any proposed change that does not affect the meaning of the document.
-Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
-A quorum of fifty percent of the Total Number of Possible Votes is required for passage.
-
-\asubsection{Semantic Changes}
-Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
-Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
-The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
-The ballots are collected for a minimum of a forty-eight hour period.
-A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
-A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
-The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
-There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
-A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
+This ruling may be appealed in the same manner as an E-Board decision, as defined in \ref{Appeals}.
 
@@
 conduct which creates a substantial risk of physical injury to such other person or a third person and thereby
-causes such injury. Hazing in the first degree is a class A misdemeanor.
+causes such injury.
+Hazing in the first degree is a class A misdemeanor.
 

### 2024-04-07 constitution.tex
Clarify Resignation of Chair (#57)
* Rebase off of current master branch

* Generalize process

---------

Co-authored-by: Sam Cordry <samcordry@gmail.com>
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>

@@
 \asection{Executive Board Resignations}
-An E-Board Member may resign from their E-Board position by submitting in writing the reason for resignation to the Chair.
+An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
 The E-Board resignation will be read at the following House Meeting and become effective at that time.
@@
 To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.
+
+\asection{Selection of an Acting Chairperson}
+If there is not an acting Chair during a process where one is required, then the following line of succession is used to determine which director becomes the acting Chair until a new Chair is elected.
+\begin{enumerate}
+	\item[1.] Evals Director
+	\item[2.] Financials Director
+	\item[3.] Voting E-Board Member chosen by an E-Board Vote
+\end{enumerate}
 

### 2024-04-08 constitution.tex
Fix subsection-related organization errors (#219)
Co-authored-by: Sam Cordry <samcodry@gmail.com>

--- 2024-04-07 constitution.tex
@@
 
-\asubsection{Selection of the Operational Communications Director}
+\asubsubsection{Selection of the Operational Communications Director}
 \renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
@@
 
-\asubsection{Selection of Ad Hoc Directors}
+\asubsubsection{Selection of Ad Hoc Directors}
 \begin{enumerate}
@@
 
-\asubsection{Selection of the Secretary}
+\asubsubsection{Selection of the Secretary}
 E-Board may select any interested Active Member as Secretary.
@@
 
-\asection{Executive Board Resignations}
-An E-Board Member may resign from their E-Board position by submitting in writing the reason for resignation to the Chair.
+\asubsection{Executive Board Resignations}
+An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
 The E-Board resignation will be read at the following House Meeting and become effective at that time.
@@
 
-\asection{Appointment of an Interim Director}
+\asubsection{Selection of an Acting Chairperson}
+If there is not an acting Chair during a process where one is required, then the following line of succession is used to determine which director becomes the acting Chair until a new Chair is elected.
+\begin{enumerate}
+	\item[1.] Evals Director
+	\item[2.] Financials Director
+	\item[3.] Voting E-Board Member chosen by an E-Board Vote
+\end{enumerate}
+
+\asubsection{Appointment of an Interim Director}
 The duties and responsibilities of a vacated office are assumed by an Active Member that is appointed at the Chair's discretion until the new director takes office.
@@
 
-\asubsection{Impeachment}
+\asubsubsection{Impeachment}
 \begin{enumerate}
@@
 
-\asubsection{Term}
+\asubsubsection{Term}
 \begin{enumerate}
@@
 
-\asection{Appeals}
+\asubsection{Appeals}
 To initiate an appeal, a member must have the support of three Voting E-Board Members, or a petition with the signatures of one-third of Active Members.

### 2024-04-08 constitution.tex
Update constitution.tex (#220)

@@
 	Standard Operating Session & \textit{RIT's fall and spring semesters, excluding institute breaks and final exam weeks} \\
-	Total Expenditure          & \textit{funds drawn for a specific event, project, piece of equipment, or service}
+	Total Expenditure          & \textit{Funds drawn for a specific event, project, piece of equipment, or service}
 \end{tabular}
@@
 	\item To enhance the education experience of its members
-	\item To offer students educational programming with an emphasis in computers
+	\item To offer students educational programming with an emphasis on computers
 	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
@@
 
-\subsection{Modifiying the Constitution}
+\subsection{Modifying the Constitution}
 \asubsection{Non-Semantic Changes}
@@
 Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
-Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in during the week.
+Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
 The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
@@
 The Intro Process will occur either once or twice per semester, and will last for six weeks.
-The process will be initiated by the Evals Director during either the first and second week of each semester. E-Board may approve an extension to the Intro Process by an E-Board Vote.
+The process will be initiated by the Evals Director during either the first or second week of each semester. E-Board may approve an extension to the Intro Process by an E-Board Vote.
 If an Intro Process is extended, the Intro Eval shall occur at the termination of the extended process, which may be outside of the period defined in \ref{Introductory Evaluation}.
@@
 \asubsubsubsection{Voting}
-On a member by member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
+On a member-by-member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
 An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
@@
 These meetings are open only to Active Members.
-All Active Members are expected to attend the these Evals meetings.
+All Active Members are expected to attend these Evals meetings.
 \\* \\*
@@
 Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
-All Active Members who have not recieved an exemption from E-Board prior to the Membership Eval will be evaluated on a member by member basis by Active Members.
+All Active Members who have not received an exemption from E-Board prior to the Membership Eval will be evaluated on a member-by-member basis by Active Members.
 The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
@@
 If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
-Each conditional consists of a set of additional requirements a deadline for completing them.
+Each conditional consists of a set of additional requirements and a deadline for completing them.
 Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
@@
 \asubsection{Honorary Membership Expectations}
-There are no expectations associated with the Honarary Membership status.
+There are no expectations associated with the Honorary Membership status.
 
@@
 	\item To coordinate collaboration between CSH and companies in the industry
-	\item To cast tie-breaking vote in a split decision in an E-Board Vote
+	\item To cast the tie-breaking vote in a split decision in an E-Board Vote
 \end{enumerate}
@@
 	\item To preserve and improve the public image of CSH
-	\item To collaborate with other E-Board members to organize, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
+	\item To collaborate with other E-Board members to organize, execute, and advertise any events that are intended to be attended by persons who have never been Active Members
 	\item To oversee the preparation of CSH for open houses, tours, and special events
@@
 	\item The candidates will be notified of their nomination.
-	      Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	      Each candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
 	      A list of all nominees who have accepted their nominations will be posted shortly thereafter.
@@
 	      If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
-	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
+	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
 	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
@@
 \\*\\*
-For expenditures exceeding \$300 in total funding, a spending presentation must be presented to at a House Meeting.
+For expenditures exceeding \$300 in total funding, a spending presentation must be presented at a House Meeting.
 This presentation includes the funds required for the expenditure, inventory of required resources, and, if applicable, a timeline for completion.
 \\* \\*
-If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
+If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at a House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
 This amount is to be directly subtracted from the general CSH account.
@@
 A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
-If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.
+If the call for Batch Vote passes, the subset may then be voted on; otherwise, the docket remains unchanged.
 

### 2024-04-15 constitution.tex
Fix ordering in budget allocation table (#221)
Update constitution.tex (#222)
Small fixes for grammar, formatting, and organization (#223)

@@
 
-% ARTICLE 3 - CONSTITUTIONAL STRUCTURE
+% ARTICLE III - CONSTITUTIONAL STRUCTURE
 \article{Constitutional Structure and Amendment}
@@
 Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
-The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
+The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
 The ballots are collected for a minimum of a forty-eight hour period.
@@
 
-% ARTICLE 4 - MEMBERSHIP
+% ARTICLE IV - MEMBERSHIP
 \article{Membership}
@@
 \asubsection{Introductory Membership Expectations}
-Intro Members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.
+Intro Members are expected to meet all the requirements of the Intro Process described in \ref{Expectations of an Introductory Member}.
 Intro Members are not required to pay membership dues.
@@
 \asubsubsubsection{Voting}
-On a member-by-member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
+On a member-by-member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements described in \ref{Expectations of an Introductory Member}.
 An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
@@
 Neither absentee nor proxy votes are allowed.
-Intro Members may be offered any of the outcomes listed in \ref{Outcomes}
+Intro Members may be offered any of the outcomes listed in \ref{Outcomes}.
 
@@
 \asubsection{Introductory Membership Resignations}
-Intro Members may resign by submitting the request for termination of membership to the Chair or the Evals Director in writing before the completion of the Intro Process.
+Intro Members may resign by submitting a request for termination of membership to the Chair or the Evals Director in writing before the completion of the Intro Process.
 
@@
 The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent quorum at the next House Meeting.
-If the vote passes the Alumni is reinstated as an Active Member with Off-Floor Status effective immediately.
+If the vote passes, the Alumni is reinstated as an Active Member with Off-Floor Status effective immediately.
 
@@
 \asubsection{Active Membership Evaluations}
-Active Members are evaluated annually through the Eval Process as described in \ref{Evaluations Processes}.
+Active Members are evaluated annually through the Eval Process described below.
 
 % ACTIVE MEMBERSHIP EVALUATIONS
-\asubsubsection{Evaluations Processes}
-During the academic year, an Active Member is evaluated by the Membership Eval.
-The Membership Eval is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
-These meetings are open only to Active Members.
-All Active Members are expected to attend these Evals meetings.
-\\* \\*
-At the beginning of any Eval Process listed herein, the Evals Director must read the sections of the CSH Constitution used during the respective Eval Process.
-It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.
-
-\asubsubsubsection{Membership Evaluation}
-The Membership Eval occurs once per academic year.
-It is performed as part of the Eval Process that takes place during the spring semester to comply with RIT Housing deadlines.
-
-\asubsubsubsubsection{Voting}
+\asubsubsection{Membership Evaluation}
+The Membership Eval occurs once per academic year, where Active Members are evaluated.
+It is performed as part of the Eval Process that takes place during the spring semester to comply with the RIT Housing deadlines.
+The Membership Eval is responsible for determining individuals who will have the option to continue Active Membership in the following academic year.
+This meeting is open only to Active Members.
+All Active Members are expected to attend this meeting.
+
+\asubsubsubsection{Voting}
 Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
@@
 
-\asubsubsubsubsection{Outcomes}
+\asubsubsubsection{Outcomes}
 Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
@@
 
-\asubsubsubsection{Appeals Process}
-If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
-\\* \\*
-If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.
-
 \asubsection{Active Membership Leave of Absence}
@@
 An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
-Instead of forfeiting membership, Active Members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
+Instead of forfeiting membership, Active Members who resign may elect to become Alumni as described in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.
@@
 Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
-This may be appealed to E-Board in order to pursue a different outcome, as described in \ref{Appeals}.
+This may be appealed to E-Board in order to pursue a different outcome, described in \ref{Appeals}.
 
@@
 \begin{enumerate}
-	\item A CSH Member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
+	\item A CSH member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership.
 The nomination must specify the type of membership the nominee is nominated for.
@@
 A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
-In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence, located at \url{https://www.rit.edu/policies/d021}.
-Additionally, the member should notify the Evals Director of their Leave, at which point they become exempt from all CSH requirements until they return.
+In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence located at \url{https://www.rit.edu/policies/d021}.
+Additionally, the member should notify the Evals Director of their Leave of Absence, at which point they become exempt from all CSH requirements until they return.
 
@@
 \begin{enumerate}
-	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH
+	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH, if they are a Voting Member
 	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
@@
 	\item To act as a Judicial Board as defined in \ref{Judicial}
-	\item To review major projects, as defined in \ref{Expectations of Active Members}
+	\item To review major projects as defined in \ref{Expectations of Active Members}
 	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
@@
 \asubsubsection{Dual Directors}
-Social and R\&D are the only voting E-Board positions that allow for dual directors.
+Social and R\&D are the only Voting E-Board positions that allow for dual directors.
 
@@
 	\item If one of the members in a dual directorship resigns, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
-	      The vacated office is then handled like any other vacated office, as referenced in \ref{Executive Board Resignations}.
+	      The vacated office is then handled like any other vacated office in accordance with \ref{Executive Board Resignations}.
 	\item During an official E-Board Vote, each dual director's vote counts for one half of a vote in the tallying of votes.
@@
 E-Board may select any interested Active Member as Secretary.
-The selection process can be an informal appointment, or follow an election process similar to other voting E-Board positions.
+The selection process can be an informal appointment, or follow an election process similar to other Voting E-Board positions.
 
@@
 The E-Board resignation will be read at the following House Meeting and become effective at that time.
-The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
-Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
+The office will become vacant and the selection process for a new director, as described in \ref{Appointment of an Interim Director}, will begin at that time.
+The selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
 To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.
@@
 
-% ARTICLE III - GENERAL OPERATIONS OF THE HOUSE
+% ARTICLE VI - GENERAL OPERATIONS OF THE HOUSE
 \article{General Operations of the House}
 
-% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
 \asection{Financial Operations of the House}
@@
 		\\ \hline
+		Social       & 20\%
+		\\ \hline
 		R\&D         & 20\%
-		\\ \hline
-		Social       & 20\%
 		\\ \hline
@@
 The member with top priority is the member with On-Floor Status and the most Housing Priority Points.
-Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval. Each Active Member who passes the Membership Eval is granted two Housing Priority Points.
-
-% ARTICLE VI - VOTING
+Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval.
+Each Active Member who passes the Membership Eval is granted two Housing Priority Points.
+
+\asection{Evaluations Processes}
+At the beginning of any Eval Process, the Evals Director must read the sections of the CSH Constitution regarding the relevant Eval Process.
+It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.
+
+\asubsection{Appeals Process}
+If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+\\* \\*
+If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.
+
+% ARTICLE VII - VOTING
 \article{Voting}
@@
 
-% ARTICLE VII - JUDICIAL
+% ARTICLE VIII - JUDICIAL
 \article{Judicial}
@@
 
-\asubsection{RIT Hazing Policy (RIT Student Conduct Process; IV. RIT Code of Conduct; 14. Hazing/Failure to Report
-	Hazing)}
+\asubsection{RIT Hazing Policy (RIT Student Conduct Process; IV. RIT Code of Conduct; 14. Hazing/Failure to Report Hazing)}
 Hazing/Failure to Report Hazing.
@@
 \asubsubsection{§ 120.16 Hazing in the first degree.}
-A person is guilty of hazing in the first degree when, in the course of
-another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in
-conduct which creates a substantial risk of physical injury to such other person or a third person and thereby
-causes such injury.
+A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
 Hazing in the first degree is a class A misdemeanor.

### 2024-04-22 constitution.tex
I removed the two lines that are illegal (#224)
Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>
300 i deleted socials in the table of abbreviations (#225)
* I removed the two lines that are illegal

* I think I deleted Socials when I put the table together but also I'm blaming Ella

---------

Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>

@@
 	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
-	Intro   & \textit{Introductory}                                                                   \\
+	Intro   & \textit{Introductory}           & Social        & \textit{Socials}                      \\                                  \\
 \end{tabular}
@@
 	\item Candidates must be Active Members during the term of office.
-	\item Candidates must have at least one full semester of membership as an Active Member.
 	\item Elected or selected candidates may not hold two simultaneous voting E-Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
@@
 		      \item Candidates must reside on floor during the term of office.
-		      \item Candidates must have at least one full semester of membership as an Active Member.
 		      \item Social and R\&D are the only voting E-Board positions that allow for dual directorship.

### 2024-04-25 constitution.tex
226 small wording changes (#226)
* I removed the two lines that are illegal

* I think I deleted Socials when I put the table together but also I'm blaming Ella

* Changed 6.A.2.A to reduce wording, changed wording in some section that allowed everyone to be removed from the org by appeal

---------

Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>

@@
 \asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
-If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
-The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
-If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
-If appealed, E-Board may provide an extension and/or reduction to the member.
+Members may appeal their situation to the Financial Director or E-board in the case that the member is dissatisfied with the Financial Director's decision.
+The Financial Director, or E-board, then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
+\\*\\*
 If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
@@
 \asubsection{Appeals Process}
-If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
+If a member disagrees with the outcome of any non-passing Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
 \\* \\*

### 2024-04-28 constitution.tex
Revert Leave of Absence (#228)
* Add Leave of Absence back in

* Remove E-Board leave of absence loophole

@@
 \asection{Leave of Absence}
-A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
-In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence located at \url{https://www.rit.edu/policies/d021}.
-Additionally, the member should notify the Evals Director of their Leave of Absence, at which point they become exempt from all CSH requirements until they return.
+A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+CSH recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
+House will also help reacclimate any returning member back to the culture of House upon their return.
+Upon approval of a leave of absence request, the Evals Director is notified and the member's leave is applied immediately.
+A member is also allowed to be physically present and also be on a leave of absence.
+
+\asubsection{Leave of Absence Request}
+A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
+The request is then given to a staff member of ResLife, excluding student employees, for approval.
+A leave of absence start date can be backdated.
+At no point does E-Board need to be informed of any details relating to the reason for the leave.
+
+\asubsection{Leave of Absence Duration}
+A leave of absence can be granted for up to the length of one semester.
+
+\asubsection{Leave of Absence Extension}
+A leave of absence can be extended by submitting a new request.
+
+\asubsection{Leave of Absence Return}
+A member may return from a leave of absence whichever they choose to.
+When a member wishes to return, they must in writing notify a staff member of ResLife, excluding student employees, to end their leave of absence.
+
+\asubsection{Modified Evaluations}
+A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
+
+\asubsection{Leave of Absence for Executive Board Member}
+The duties and responsibilities of an E-Board member on leave are assumed using the process defined in \ref{Appointment of an Interim Director} until the member returns from their leave.
+If the member returns before the end of the Standard Operation Session in which they started their leave, they may assume their position and the interim director is removed.
+% someone gets their position back if they come back during the year for which they were elected
+If any point the member's leave is determined by E-Board to be detrimental to be operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.
 

### 2024-08-26 constitution.tex
table of contents numbers now start at correct page number

@@
 \tableofcontents
+\setcounter{page}{4}
 
@@
 All CSH expenditures must be approved by the Financial Director and the director whose budget is going to be used for the expenditure.
-Single expenditures may not exceed seventy-five dollars and Total Expenditures may not exceed one-hundred dollars.
+Single expenditures may not exceed \$75 and Total Expenditures may not exceed \$100.
 \\* \\*
 If the above amounts are to be exceeded, the expenditure must be approved by an Immediate One-Half Vote at a House Meeting before the funds may be appropriated.
-At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars, but not to exceed three-hundred dollars.
+At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding \$100, but not to exceed \$300.
 A Two-Thirds Immediate Vote with twenty-five percent quorum is required to approve the purchase.

### 2024-09-17 constitution.tex
prevent multiple simultaneous memberships
Allow off floor intro members to sign packets

@@
 \asubsubsection{The Introductory Packet}
-Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active Members who have passed a Membership Eval, all On-Floor Intro and Active Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
+Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active and Intro Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
 At the discretion of the Evals Director or as the result of an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.

### 2024-09-22 constitution.tex
add frogperson

--- 2024-08-26 constitution.tex
@@
 
+\asubsubsection{Responsibilities of the Frogperson}
+\begin{enumerate}
+	\item To act as the Shadow Board director pulling the strings of the E-Board behind the scenes.
+\end{enumerate}
+
 \asubsubsection{Responsibilities of the Chairperson}
@@
 \asubsection{Qualifications}
+
+\asubsubsection{Qualifications for Frogperson}
+\begin{enumerate}
+	\item The Frogperson must be selected by the prior Frogperson during a prior Frogperson's resignation.
+	\item In the event the above provision can not be fulfilled, or the position would be unfilled, the Frogperson will be chosen by the Active Member(s) whose birthday is closest to September 10th, 2003.
+	\item House does not select a Frogperson; the position is filled automatically.
+\end{enumerate}
 

### 2024-10-03 constitution.tex
remove the social event requirement from gatekeep
clarify voting members

--- 2024-08-26 constitution.tex
@@
 Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
-Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
+Active Voting Members are eligible to become Voting Members according to the requirements defined in \ref{Qualifications of Voting Members}.
 
@@
 
-\asubsubsection{Expectations of Voting Members}
+\asubsubsection{Qualifications of Voting Members}
 \renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
 
-The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
+For an Active Member to be allowed to vote in an Intro Eval, they must meet the following requirements by the beginning of the Intro Eval.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
@@
 \end{enumerate}
+
+\asubsubsection{Expectations of Voting Members}
+Voting Members are expected to attend and vote at the Intro Eval for which they have qualified.
+If they cannot attend the Intro Eval, they are expected to notify the Evals Director before the Intro Eval.
 

### 2024-10-03 constitution.tex
clarify active member resignations

--- 2024-09-17 constitution.tex
@@
 \asubsubsection{The Introductory Packet}
-Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active and Intro Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
+Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active Members who have passed a Membership Eval, all On-Floor Intro and Active Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
 At the discretion of the Evals Director or as the result of an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.
@@
 An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
-Instead of forfeiting membership, Active Members who resign may elect to become Alumni as described in \ref{Alumni Membership Selection}.
+Instead of forfeiting membership, Active Members who meet the requirements outlined in \ref{Alumni Membership Qualifications} who resign may elect to become Alumni as described in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.

### 2024-10-03 constitution.tex
init commit, redefining subsubsubsections and the like because I don't like them :>

@@
 
+\titleclass{\subsubsubsection}{straight}[\subsection]
+
+\newcounter{subsubsubsection}[subsubsection]
+\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}
+\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered
+
+\titleformat{\subsubsubsection}
+  {\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
+\titlespacing*{\subsubsubsection}
+{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
+
+\makeatletter
+\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
+  {3.25ex \@plus1ex \@minus.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries}}
+\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
+  {3.25ex \@plus1ex \@minus .2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries}}
+\def\toclevel@subsubsubsection{4}
+\def\toclevel@paragraph{5}
+%\def\toclevel@paragraph{6}
+\def\toclevel@subparagraph{6}
+\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
+\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
+\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
+\makeatother
+
+\setcounter{secnumdepth}{7}
+\setcounter{tocdepth}{7}
+
 % Headings
@@
 \begin{document}
+
 % Title
@@
 An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
-Instead of forfeiting membership, Active Members who meet the requirements outlined in \ref{Alumni Membership Qualifications} who resign may elect to become Alumni as described in \ref{Alumni Membership Selection}.
+Instead of forfeiting membership, Active Members who resign may elect to become Alumni as described in \ref{Alumni Membership Selection}.
 The resignation will take effect immediately and an announcement will be made at the following House Meeting.

### 2024-10-04 constitution.tex
prevent the number of eligible votes from changing during the execution of a vote

--- 2024-10-03 constitution.tex
@@
 \asubsection{Introductory Membership Qualifications}
-Intro Membership is open to all students currently enrolled at RIT.
+Intro Membership is open to all students currently enrolled at RIT, excluding all Active and Alumni Members.
 
@@
 The number of Active Members eligible to vote on the issue.
+The number of Eligible Votes is determined when a vote is called and remains fixed throughout the duration of the vote.
 

### 2024-10-07 constitution.tex
jeremy comments

@@
 The number of Active Members eligible to vote on the issue.
-The number of Eligible Votes is determined when a vote is called and remains fixed throughout the duration of the vote.
 

### 2024-10-07 constitution.tex
add explicit mechanisms for housing priority access & automatic NTID access improvement

--- 2024-10-04 constitution.tex
@@
 Each Active Member who passes the Membership Eval is granted two Housing Priority Points.
+Members registered with NTID receive priority over members with equivalent Housing Priority points.
+% NTID students can ONLY choose dorms with doorbells, so this helps ensure that students who need these rooms have access to them.
+Members who require accommodations may be temporarily granted additional Housing Priority Points at the request of RIT Housing or at the discretion of the Evaluations Director. 
+Temporary Housing Priority Points remain in effect until the end of the Standard Operating Session or an earlier date, as specified when granted.
 

### 2024-10-08 constitution.tex
rework with better thoughts

--- 2024-10-04 constitution.tex
@@
 \asubsection{Introductory Membership Qualifications}
-Intro Membership is open to all students currently enrolled at RIT, excluding all Active and Alumni Members.
+Intro Membership is open to all students currently enrolled at RIT.
 
@@
 
-\asubsubsection{Expectations of Voting Members}
+\asubsubsection{Qualifications of Voting Members}
 \renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
 
-The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
+For an Active Member to be allowed to vote in an Intro Eval, they must meet the following requirements by the beginning of the Intro Eval.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
+An Active Member who meets these requirements may opt out of Voting Membership by submitting a request to the Evals Director or E-Board.
 \begin{enumerate}
@@
 	\item Attend at least two Technical Seminars during the Intro Process
+\end{enumerate}
+
+\asubsubsection{Expectations of Voting Members}
+\begin{enumerate}
+	\item Attend and vote at the Intro Eval for which they have qualified.
 \end{enumerate}

### 2025-01-31 constitution.tex
more consistent language
formatting, clarify membership type
fix

--- 2024-10-07 constitution.tex
@@
 	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
-	CSH     & \textit{Computer Science House} & OpComm        & \textit{Operational Communications}   \\
+	CSH     & \textit{Computer Science House} & OpChomm        & \textit{Operational Communications}   \\
 	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
@@
 \begin{enumerate}
-	\item A candidate for the OpComm Directorship shall be chosen by the current RTPs.
+	\item A candidate for the OpChomm Directorship shall be chosen by the current RTPs.
 	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
@@
 \asection{Root Type Persons}
-The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
+The OpChomm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
 It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
@@
 		\hline
-		OpComm       & 20\%
+		OpChomm       & 20\%
 		\\ \hline

### 2025-01-31 constitution.tex
Separated amendments and overrides in the semantic changes section

--- 2024-10-07 constitution.tex
@@
 \asubsection{Semantic Changes}
+\asubsubsection{Amendments}
 Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
@@
 A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
+\asubsubsection{Overrides}
 The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.
@@
 Each Active Member who passes the Membership Eval is granted two Housing Priority Points.
-Members registered with NTID receive priority over members with equivalent Housing Priority points.
-% NTID students can ONLY choose dorms with doorbells, so this helps ensure that students who need these rooms have access to them.
-Members who require accommodations may be temporarily granted additional Housing Priority Points at the request of RIT Housing or at the discretion of the Evaluations Director. 
-Temporary Housing Priority Points remain in effect until the end of the Standard Operating Session or an earlier date, as specified when granted.
 

### 2025-02-03 constitution.tex
Condensed 4.D.4 and 4.D.5

@@
 \asubsection{Semantic Changes}
-\asubsubsection{Amendments}
 Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
@@
 A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
-\asubsubsection{Overrides}
 The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.
@@
 	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
-	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
+	\item If the nomination is presented at a House Meeting for discussion, a Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
 	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
@@
 
-\asubsection{Honorary Membership Expectations}
-There are no expectations associated with the Honorary Membership status.
-
-\asubsection{Advisory Membership Expectations}
-There are no expectations associated with the Advisory Membership status.
+\asubsection{Honorary and Advisory Membership Expectations}
+There are no expectations associated with the Honorary or Advisory Membership status.
 

### 2025-02-04 constitution.tex

@@
 \asubsection{Advisory Membership Qualifications}
-Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.
+Advisory Membership is open to all current members of the RIT professional, academic, or administrative staff.
 
@@
 
-\asubsection{Honorary and Advisory Membership Term}
-Honorary and Advisory Memberships shall last until the member resigns.
+\asubsection{Honorary Membership Term}
+Honorary Membership shall last until the member resigns.
+
+\asubsection{Advisory Membership Term}
+Advisory Membership shall last until the member resigns or is no longer employed by RIT, whichever comes first.
 

### 2025-02-04 constitution.tex
Fix grammar and spelling issues

--- 2025-02-03 constitution.tex
@@
 \asubsection{Leave of Absence Return}
-A member may return from a leave of absence whichever they choose to.
+A member may return from a leave of absence whenever they choose to.
 When a member wishes to return, they must in writing notify a staff member of ResLife, excluding student employees, to end their leave of absence.
@@
 % someone gets their position back if they come back during the year for which they were elected
-If any point the member's leave is determined by E-Board to be detrimental to be operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.
+If any point the member's leave is determined by E-Board to be detrimental to the operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.
 
@@
 	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH, if they are a Voting Member
-	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
+	\item To meet at least once per week during the Standard Operating Session to discuss and report the operations of CSH
 	\item To report pertinent information to members at the following House Meeting
@@
 \asection{Anti-Discrimination Clause}
-This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity and gender expression, religion, age marital state, national origin, disability or veteran status.
+This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity, gender expression, religion, age, marital status, national origin, disability, or veteran status.
 This policy will include but is not limited to, recruiting, membership, organization activities or opportunities to hold or run for club office.

### 2025-02-04 constitution.tex
Fixed additional grammar and phrasing issues for clarity/consistency

@@
 \begin{enumerate}
-	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
+	\item During the spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
 	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
@@
 Members are required to submit a description for this major project to E-Board for approval.
-As an alternative to this requirement, members may instead assist on a large number of CSH activities and projects.
+As an alternative to this requirement, members may instead assist with a large number of CSH activities and projects.
 However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
@@
 Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
-This may be appealed to E-Board in order to pursue a different outcome, described in \ref{Appeals}.
+This may be appealed to E-Board in order to pursue a different outcome, as described in \ref{Appeals}.
 
@@
 \asubsection{Honorary and Advisory Membership Privileges}
-Honorary and Advisory Members may advise in CSH issues, use CSH facilities, and attend CSH functions.
+Honorary and Advisory Members may advise on CSH issues, use CSH facilities, and attend CSH functions.
 
@@
 \asection{Leave of Absence}
-A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
+A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
 CSH recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
@@
 	\item A candidate for the OpComm Directorship shall be chosen by the current RTPs.
-	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
+	\item The candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
 	\item The candidate is presented to E-Board for approval.
@@
 \begin{enumerate}
-	\item The election process for the following year's E-Board members shall begin in the middle of spring semester.
+	\item The election process for the following year's E-Board members shall begin in the middle of the spring semester.
 	\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
@@
 	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
-	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item Each candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
 	\item A list of all nominees who have accepted is presented to E-Board for approval.

### 2025-02-06 constitution.tex

@@
 \asection{Anti-Discrimination Clause}
-This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity, gender expression, religion, age, marital status, national origin, disability, or veteran status.
+This organization shall not discriminate on the basis of sex, race, color, sexual orientation, gender identity and gender expression, religion, age marital state, national origin, disability or veteran status.
 This policy will include but is not limited to, recruiting, membership, organization activities or opportunities to hold or run for club office.

### 2025-03-03 constitution.tex
rtp refactoring

--- 2025-02-04 constitution.tex
@@
 \asubsection{Leave of Absence Return}
-A member may return from a leave of absence whenever they choose to.
+A member may return from a leave of absence whichever they choose to.
 When a member wishes to return, they must in writing notify a staff member of ResLife, excluding student employees, to end their leave of absence.
@@
 % someone gets their position back if they come back during the year for which they were elected
-If any point the member's leave is determined by E-Board to be detrimental to the operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.
+If any point the member's leave is determined by E-Board to be detrimental to be operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.
 
@@
 	\item To hold a weekly meeting specific to their responsibilities and submit notes to CSH, if they are a Voting Member
-	\item To meet at least once per week during the Standard Operating Session to discuss and report the operations of CSH
+	\item To meet at least weekly during the Standard Operating Session to discuss and report the operations of CSH
 	\item To report pertinent information to members at the following House Meeting
@@
 The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
-It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
+It is a committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
 Membership is composed of all RTPs.
@@
 The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.
+
+\asubsubsection{Renewal of a Root Type Person}
+At the conclusion of each academic year, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
+Prior to the vote, the Operational Communications Director shall present a formal statement summarizing each RTP’s contributions and performance. 
+Subsequently, E-Board will conduct an Immediate Relative Majority Vote on each candidate's continuation. 
+RTPs failing to secure the required majority will be mandated to resign their RTP status.
 

### 2025-03-03 constitution.tex
Updates to overall RTP phrasing and word choice

@@
 \asection{Root Type Persons}
-The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
-It is a committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
+Root Type Persons are the members that make up the OpComm Directorship. 
+They are responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems and networks.
+
+\asubsection{OpComm Directorship}
+The OpComm Directorship is a committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
 Membership is composed of all RTPs.
@@
 	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
-	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+	\item If an E-Board Member is a candidate for the office in discussion, the member is absent, and their vote is abstained.
 	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
 \end{enumerate}
+Giving an extension to a previous Active Member is the same as starting a selection process for a new RTP and should also follow this process.
 
 \asubsubsection{Qualifications of a Root Type Person}
-Candidates must be Active Members.
+Candidates must be Active Members or previous Active Members who are given an extension by the RTPs.
 
 \asubsubsection{Prior Root Type Persons}
-Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
-Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
+Prior RTPs are any members who were previously an RTP and are not currently on an extension given by the RTPs.
+Prior RTPs are not guaranteed access to any elevated permissions to any systems or networks, including but not limited to the RTP LDAP role, Vault, or the root password.
 The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.
@@
 At the conclusion of each academic year, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
-Prior to the vote, the Operational Communications Director shall present a formal statement summarizing each RTP’s contributions and performance. 
-Subsequently, E-Board will conduct an Immediate Relative Majority Vote on each candidate's continuation. 
-RTPs failing to secure the required majority will be mandated to resign their RTP status.
+During the second to last E-Board Meeting of the semester, the Operational Communications Director shall present a formal statement summarizing the contributions and performance of each RTP. 
+After each statement, an E-Board Vote will be conducted to determine each candidate's continuation. 
+If the vote does not pass, that member will become a Prior RTP.
 
@@
 RTPs have the authority to manage user accounts for CSH systems.
-Before a member may receive an account they must:
+Before a member may receive an account, they must:
 \renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of CSH and RIT facilities.
-	\item Obtain greater than or equal to 60\% of required signatures, excluding those of On-Floor Members who have not passed a Membership Eval, in the Intro Packet or successfully complete Intro Eval.
+	\item Obtain greater than or equal to 60\% of required signatures, excluding those of On-Floor Members who have not passed a Membership Eval, in the Intro Packet, or successfully complete Intro Eval.
 	\item Sign a copy of the Membership Agreement

### 2025-03-04 constitution.tex
v0.3

@@
 \asubsubsection{Renewal of a Root Type Person}
-At the conclusion of each academic year, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
-During the second to last E-Board Meeting of the semester, the Operational Communications Director shall present a formal statement summarizing the contributions and performance of each RTP. 
-After each statement, an E-Board Vote will be conducted to determine each candidate's continuation. 
-If the vote does not pass, that member will become a Prior RTP.
+At the conclusion of each standard operating session, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
+During the second to last E-Board Meeting of the semester, the OpComm Director shall present a formal statement summarizing the contributions and performance of each RTP. 
+After each statement, an E-Board Vote, as described in \ref{Executive Board Vote} will be conducted to determine each candidate's continuation. 
+Failure to secure the required majority vote will result in the RTP being required to resign their position.
 

### 2025-03-30 constitution.tex
Changed "a __ hour period" to "__ hours" for improved readability

--- 2025-03-03 constitution.tex
@@
 The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
-The ballots are collected for a minimum of a forty-eight hour period.
+The ballots are collected for a minimum of forty-eight hours.
 A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
@@
 	\item If the nomination is presented at a House Meeting for discussion, a Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
-	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
+	      Ballots are distributed and voting must remain open for a minimum of forty-eight hours.
 	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
@@
 \begin{enumerate}
-	\item The opening of the E-Board position(s) is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
+	\item The opening of the E-Board position(s) is announced at a House Meeting and nominations for the position are taken for a minimum of seventy-two hours.
 	      Any member may nominate any member, or pair of members where appropriate, for a directorship.
 	\item The candidates will be notified of their nomination.
-	      Each candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
+	      Each candidate is given a minimum of twenty-four hours to accept or decline the nomination.
 	      A list of all nominees who have accepted their nominations will be posted shortly thereafter.
@@
 	\item Each candidate will be given an equal amount of time to present their platform of candidacy to the attending members.
-	\item Ballots will then be distributed for a Balloted Vote \ref{Balloted Vote} and voting will be open for a minimum of a forty-eight hour period.
+	\item Ballots will then be distributed for a Balloted Vote \ref{Balloted Vote} and voting will be open for a minimum of forty-eight hours.
 	      The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
@@
 	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
-	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
+	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of forty-eight hours to determine whether or not the member should be removed from office.
 	      Votes shall be collected and counted for a Two-Thirds Balloted Vote, as described in \ref{Balloted Vote}.
@@
 The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
-It is a committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
+It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
 Membership is composed of all RTPs.
@@
 	\item Nominations are taken from the RTPs meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
-	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
+	\item Each candidate is given a minimum of twenty-four hours to accept or decline the nomination.
 	\item A list of all nominees who have accepted is presented to E-Board for approval.
@@
 The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.
-
-\asubsubsection{Renewal of a Root Type Person}
-At the conclusion of each academic year, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
-Prior to the vote, the Operational Communications Director shall present a formal statement summarizing each RTP’s contributions and performance. 
-Subsequently, E-Board will conduct an Immediate Relative Majority Vote on each candidate's continuation. 
-RTPs failing to secure the required majority will be mandated to resign their RTP status.
 

### 2025-03-31 constitution.tex
Reverted previous change to 5.A.1.A
Added back previously removed co-op clause

--- 2025-03-03 constitution.tex
@@
 
+Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
+Exceptions may be made at the discretion of the Evaluations Director.
 \asubsubsection{Expectations of Voting Members}
@@
 \asection{Root Type Persons}
-Root Type Persons are the members that make up the OpComm Directorship. 
-They are responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems and networks.
-
-\asubsection{OpComm Directorship}
-The OpComm Directorship is a committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
+The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
+It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
 Membership is composed of all RTPs.
@@
 	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
-	\item If an E-Board Member is a candidate for the office in discussion, the member is absent, and their vote is abstained.
+	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
 	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
 \end{enumerate}
-Giving an extension to a previous Active Member is the same as starting a selection process for a new RTP and should also follow this process.
 
 \asubsubsection{Qualifications of a Root Type Person}
-Candidates must be Active Members or previous Active Members who are given an extension by the RTPs.
+Candidates must be Active Members.
 
 \asubsubsection{Prior Root Type Persons}
-Prior RTPs are any members who were previously an RTP and are not currently on an extension given by the RTPs.
-Prior RTPs are not guaranteed access to any elevated permissions to any systems or networks, including but not limited to the RTP LDAP role, Vault, or the root password.
+Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
+Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
 The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.
-
-\asubsubsection{Renewal of a Root Type Person}
-At the conclusion of each academic year, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
-During the second to last E-Board Meeting of the semester, the Operational Communications Director shall present a formal statement summarizing the contributions and performance of each RTP. 
-After each statement, an E-Board Vote will be conducted to determine each candidate's continuation. 
-If the vote does not pass, that member will become a Prior RTP.
 
@@
 RTPs have the authority to manage user accounts for CSH systems.
-Before a member may receive an account, they must:
+Before a member may receive an account they must:
 \renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
@@
 	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of CSH and RIT facilities.
-	\item Obtain greater than or equal to 60\% of required signatures, excluding those of On-Floor Members who have not passed a Membership Eval, in the Intro Packet, or successfully complete Intro Eval.
+	\item Obtain greater than or equal to 60\% of required signatures, excluding those of On-Floor Members who have not passed a Membership Eval, in the Intro Packet or successfully complete Intro Eval.
 	\item Sign a copy of the Membership Agreement
@@
 \asubsection{Eligible Votes}
-The number of Active Members eligible to vote on the issue.
+The number of Active Members eligible to vote on the issue (e.g., not on co-op).
 

### 2025-04-02 constitution.tex
Added spacing between sections

--- 2025-03-04 constitution.tex
@@
 \asubsubsection{Prior Root Type Persons}
-Prior RTPs are any members who were previously an RTP and are not currently on an extension given by the RTPs.
+Prior RTPs are any members who were previously an RTP and are not currently an Active Member or on an extension given by the RTPs.
 Prior RTPs are not guaranteed access to any elevated permissions to any systems or networks, including but not limited to the RTP LDAP role, Vault, or the root password.
@@
 \asubsubsection{Renewal of a Root Type Person}
-At the conclusion of each standard operating session, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
+At the conclusion of each standard operating session, those intending to keep the rights and responsibilities of a current RTP must participate in a renewal process. 
 During the second to last E-Board Meeting of the semester, the OpComm Director shall present a formal statement summarizing the contributions and performance of each RTP. 
-After each statement, an E-Board Vote, as described in \ref{Executive Board Vote} will be conducted to determine each candidate's continuation. 
+After each statement, an E-Board Vote, as described in \ref{Executive Board Vote}, will be conducted to determine each candidate's continuation. 
 Failure to secure the required majority vote will result in the RTP being required to resign their position.

### 2025-05-19 constitution.tex
Updated Section 9.A.2.A and 9.A.2.B in accordance with NY law

--- 2025-03-31 constitution.tex
@@
 
-Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
-Exceptions may be made at the discretion of the Evaluations Director.
 \asubsubsection{Expectations of Voting Members}
@@
 \asubsection{Eligible Votes}
-The number of Active Members eligible to vote on the issue (e.g., not on co-op).
+The number of Active Members eligible to vote on the issue.
 
@@
 \asubsubsection{§ 120.16 Hazing in the first degree.}
-A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
+A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
 Hazing in the first degree is a class A misdemeanor.
@@
 \asubsubsection{§ 120.17 Hazing in the second degree.}
-A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person.
+A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person.
 Hazing in the second degree is a violation.

### 2025-05-19 constitution.tex
remove interview mentions from 4.A.2.B

--- 2025-03-31 constitution.tex
@@
 	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
-	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
+	      The Selections Committee reviews applications in accordance with the process prescribed by ResLife.
 	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.

### 2025-05-24 constitution.tex
updated amendment so that it includes any change to article 9, in accordance with RIT policy or NY law can be treated as a nonsemantic change
voting member clarifications

@@
 	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
-	      The Selections Committee reviews applications in accordance with the process prescribed by ResLife.
+	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
 	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
@@
 
-The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
+The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
 \begin{enumerate}
-	\item Attend all House Meetings during the Intro Process
-	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
-	\item Attend at least one CSH social event during the Intro Process
-	\item Attend at least two Technical Seminars during the Intro Process
+	\item Attend at least six House Meetings
+	\item Attend at least six directorship meetings
+	\item Attend at least one CSH social event
+	\item Attend at least two Technical Seminars
 \end{enumerate}
@@
 Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
-E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent of the Eligible Votes.
+E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent.
 
@@
 \asubsection{Eligible Votes}
-The number of Active Members eligible to vote on the issue.
+The number of Active Members who are eligible to vote on the issue.
+Following the first Intro Eval of the academic year, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
+Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
 

### 2025-06-09 constitution.tex

--- 2025-05-19 constitution.tex
@@
 A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
+\asubsubsection{Compliance with RIT Policy and New York State Law}
+Any change made to Article  \ref{ADHERENCE TO UNIVERSITY POLICIES} which is made due to an update in NY law or RIT policy may be treated as a Non-Semantic change.
+
 \asubsubsection{Overrides}
@@
 The number of Active Members eligible to vote on the issue.
+The eligible voters for a vote are determined and fixed when the Voting Period begins.
 

### 2025-06-09 constitution.tex

@@
 Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
-Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
+Active Members are eligible to become Voting Members if they meet the requirements defined in \ref{Qualifications of Voting Members}.
 
@@
 
-\asubsubsection{Expectations of Voting Members}
+\asubsubsection{Qualifications of Voting Members}
 \renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
 
-The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
+For an Active Member to be allowed to vote in an Intro Eval, they must meet the following requirements by the beginning of the Intro Eval.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote. 
+An Active Member who meets these requirements may opt out of Voting Membership by submitting a request to the Evals Director or E-Board.
 \begin{enumerate}
@@
 The number of Active Members eligible to vote on the issue.
-The eligible voters for a vote are determined and fixed when the Voting Period begins.
 

### 2025-08-30 constitution.tex
change eligible votes to be semesterly

--- 2025-06-09 constitution.tex
@@
 A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
-\asubsubsection{Compliance with RIT Policy and New York State Law}
-Any change made to Article  \ref{ADHERENCE TO UNIVERSITY POLICIES} which is made due to an update in NY law or RIT policy may be treated as a Non-Semantic change.
-
 \asubsubsection{Overrides}
@@
 \asubsection{Eligible Votes}
-The number of Active Members eligible to vote on the issue.
-The eligible voters for a vote are determined and fixed when the Voting Period begins.
+The number of Active Members who are eligible to vote on the issue.
+Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
+Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
 
@@
 \asubsubsection{§ 120.16 Hazing in the first degree.}
-A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
+A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
 Hazing in the first degree is a class A misdemeanor.
@@
 \asubsubsection{§ 120.17 Hazing in the second degree.}
-A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person.
+A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person.
 Hazing in the second degree is a violation.

### 2025-09-10 constitution.tex

--- 2025-06-09 constitution.tex
@@
 Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
-Active Members are eligible to become Voting Members if they meet the requirements defined in \ref{Qualifications of Voting Members}.
+Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
 
@@
 
-\asubsubsection{Qualifications of Voting Members}
+\asubsubsection{Expectations of Voting Members}
 \renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
 
-For an Active Member to be allowed to vote in an Intro Eval, they must meet the following requirements by the beginning of the Intro Eval.
+The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
-An Active Member who meets these requirements may opt out of Voting Membership by submitting a request to the Evals Director or E-Board.
 \begin{enumerate}
@@
 	\item Attend at least two Technical Seminars during the Intro Process
-\end{enumerate}
-
-\asubsubsection{Expectations of Voting Members}
-\begin{enumerate}
-	\item Attend and vote at the Intro Eval for which they have qualified.
 \end{enumerate}

### 2025-09-10 constitution.tex

@@
 \asubsection{Eligible Votes}
-The number of Active Members eligible to vote on the issue.
+The number of Active Members who are eligible to vote on the issue.
+Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
+Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
 

### 2025-09-21 constitution.tex
removed mention of co-op from Eligible Votes

--- 2025-08-30 constitution.tex
@@
 
+Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
+Exceptions may be made at the discretion of the Evaluations Director.
+
 \asubsubsection{Expectations of Voting Members}
@@
 
-The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
+The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
 \begin{enumerate}
-	\item Attend at least six House Meetings
-	\item Attend at least six directorship meetings
-	\item Attend at least one CSH social event
-	\item Attend at least two Technical Seminars
+	\item Attend all House Meetings during the Intro Process
+	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
+	\item Attend at least one CSH social event during the Intro Process
+	\item Attend at least two Technical Seminars during the Intro Process
 \end{enumerate}
@@
 Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
-E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent.
+E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent of the Eligible Votes.
 
@@
 \asubsection{Eligible Votes}
-The number of Active Members who are eligible to vote on the issue.
-Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
-Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
+The number of Active Members eligible to vote on the issue.
 

### 2025-09-22 constitution.tex
Added in the Squatters Rights Clause

@@
 \end{enumerate}
-
-Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
-Exceptions may be made at the discretion of the Evaluations Director.
 
@@
 	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
-	\item If the nomination is presented at a House Meeting for discussion, a Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
+	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
 	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
@@
 
-\asubsection{Honorary and Advisory Membership Expectations}
-There are no expectations associated with the Honorary or Advisory Membership status.
+\asubsection{Honorary Membership Expectations}
+There are no expectations associated with the Honorary Membership status.
+
+\asubsection{Advisory Membership Expectations}
+There are no expectations associated with the Advisory Membership status.
 
@@
 Each Active Member who passes the Membership Eval is granted two Housing Priority Points. 
+Members registered with NTID receive priority over members with equivalent Housing Priority points.
+% NTID students can ONLY choose dorms with doorbells, so this helps ensure that students who need these rooms have access to them.
+Members who require accommodations may be temporarily granted additional Housing Priority Points at the request of RIT Housing or at the discretion of the Evaluations Director. 
+Temporary Housing Priority Points remain in effect until the end of the Standard Operating Session or an earlier date, as specified when granted.
+Additionally, members are granted 0.5 Temporary Housing Priority Points for the duration of time that they are assigned to the room they currently live in.
 

### 2025-10-06 constitution.tex
correct voting member expectations

@@
 
-\titleclass{\subsubsubsection}{straight}[\subsection]
-
-\newcounter{subsubsubsection}[subsubsection]
-\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}
-\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered
-
-\titleformat{\subsubsubsection}
-  {\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
-\titlespacing*{\subsubsubsection}
-{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
-
-\makeatletter
-\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
-  {3.25ex \@plus1ex \@minus.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries}}
-\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
-  {3.25ex \@plus1ex \@minus .2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries}}
-\def\toclevel@subsubsubsection{4}
-\def\toclevel@paragraph{5}
-%\def\toclevel@paragraph{6}
-\def\toclevel@subparagraph{6}
-\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
-\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
-\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
-\makeatother
-
-\setcounter{secnumdepth}{7}
-\setcounter{tocdepth}{7}
-
 % Headings
@@
 \begin{document}
-
 % Title
@@
 \begin{enumerate}
-	\item Attend at least six House Meetings
+	\item Attend all House Meetings
 	\item Attend at least six directorship meetings

### 2025-10-27 constitution.tex
Remove Social Event Requirements
Removed CSH Social Event requirement from both Intro Member and Voting Member expectations.
Semesterly Gatekeep

@@
 
-The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
+The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic semester.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
 \begin{enumerate}
-	\item Attend all House Meetings
+	\item Attend at least six House Meetings
 	\item Attend at least six directorship meetings

### 2025-11-05 constitution.tex
attendance at house meeting

--- 2025-10-06 constitution.tex
@@
 \begin{enumerate}
-	\item Attend all House Meetings
+	\item Attend at least six House Meetings
 	\item Attend at least six directorship meetings
@@
 The nomination must specify the type of membership the nominee is nominated for.
-	\item The Evals Director performs preliminary research on the candidate and presents the findings.
-	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
+	\item The Evals Director performs preliminary research on the candidate and presents the findings to Eboard for discussion.
+	\item If E-Board decides through an E-board Vote not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
 	\item If the nomination is presented at a House Meeting for discussion, a Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.

### 2025-11-06 constitution.tex
Ensure vote counts dont change during the eval

--- 2025-11-05 constitution.tex
@@
 \\* \\*
-If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
+If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediaely upon completion of the Membership Eval
 If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.

### 2025-11-06 constitution.tex
removed redundant word

--- 2025-11-05 constitution.tex
@@
 \\* \\*
-If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
+If a member fails and has never passed a Membership Eval in the past, their membership will be revoked upon completion of the Membership Eval
 If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.

### 2025-11-06 constitution.tex

--- 2025-11-05 constitution.tex
@@
 	\item Attend at least one directorship meeting for each week of the process
-	\item Attend at least one CSH social event during the process
 	\item Attend at least two Technical Seminars during the process
@@
 	\item Attend at least six directorship meetings
-	\item Attend at least one CSH social event
 	\item Attend at least two Technical Seminars

### 2025-11-18 constitution.tex

@@
 The nomination must specify the type of membership the nominee is nominated for.
-	\item The Evals Director performs preliminary research on the candidate and presents the findings to Eboard for discussion.
+	\item The Evals Director performs preliminary research on the candidate and presents the findings to E-Board for discussion.
 	\item If E-Board decides through an E-board Vote not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.

### 2025-11-18 constitution.tex

@@
 
-Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
-Exceptions may be made at the discretion of the Evaluations Director.
-
 \asubsubsection{Expectations of Voting Members}

### 2025-11-20 constitution.tex

--- 2025-11-18 constitution.tex
@@
 \asection{Root Type Persons}
-The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
-It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
+Root Type Persons are the members that make up the OpComm Directorship. 
+They are responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems and networks.
+
+\asubsection{OpComm Directorship}
+The OpComm Directorship is a committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
 Membership is composed of all RTPs.
@@
 	      This E-Board Meeting is closed to E-Board Members, RTPs, and members with explicit invitation from E-Board.
-	\item If an E-Board Member is a candidate for the office in discussion, the member is absent and their vote is abstained.
+	\item If an E-Board Member is a candidate for the office in discussion, the member is absent, and their vote is abstained.
 	      An E-Board Vote, as described in \ref{Executive Board Vote}, is taken to determine whether the nominations of the RTP(s) are accepted.
 \end{enumerate}
+Giving an extension to a previous Active Member is the same as starting a selection process for a new RTP and should also follow this process.
 
 \asubsubsection{Qualifications of a Root Type Person}
-Candidates must be Active Members.
+Candidates must be Active Members or previous Active Members who are given an extension by the RTPs.
 
 \asubsubsection{Prior Root Type Persons}
-Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
-Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
+Prior RTPs are any members who were previously an RTP and are not currently an Active Member or on an extension given by the RTPs.
+Prior RTPs are not guaranteed access to any elevated permissions to any systems or networks, including but not limited to the RTP LDAP role, Vault, or the root password.
 The current RTPs may draft rules and regulations specifying the rights and privileges of Prior RTPs.
+
+\asubsubsection{Renewal of a Root Type Person}
+At the conclusion of each standard operating session, those intending to keep the rights and responsibilities of a current RTP must participate in a renewal process. 
+During the second to last E-Board Meeting of the semester, the OpComm Director shall present a formal statement summarizing the contributions and performance of each RTP. 
+After each statement, an E-Board Vote, as described in \ref{Executive Board Vote}, will be conducted to determine each candidate's continuation. 
+Failure to secure the required majority vote will result in the RTP being required to resign their position.
 

### 2025-11-22 constitution.tex
dual chair bad

--- 2025-11-20 constitution.tex
@@
 \asubsection{Advisory Membership Qualifications}
-Advisory Membership is open to all current members of the RIT professional, academic, or administrative staff.
+Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.
 
@@
 
-\asubsection{Honorary Membership Term}
-Honorary Membership shall last until the member resigns.
-
-\asubsection{Advisory Membership Term}
-Advisory Membership shall last until the member resigns or is no longer employed by RIT, whichever comes first.
+\asubsection{Honorary and Advisory Membership Term}
+Honorary and Advisory Memberships shall last until the member resigns.
 
@@
 		      \item Candidates must reside on floor during the term of office.
-		      \item Social and R\&D are the only voting E-Board positions that allow for dual directorship.
+		      \item Social and R\&D are the only E-Board positions that allow for dual directorship.
 	      \end{enumerate}
@@
 \asubsubsection{Dual Directors}
-Social and R\&D are the only Voting E-Board positions that allow for dual directors.
+Social and R\&D are the only E-Board positions that allow for dual directors.
 

### 2025-12-02 constitution.tex

--- 2025-11-20 constitution.tex
@@
 
-The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
+The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic semester.
 Any of these requirements may be waived by the Evals Director or an E-Board Vote.
@@
 \asubsection{Eligible Votes}
-The number of Active Members who are eligible to vote on the issue.
+The number of Active Members eligible to vote on the issue.
+The eligible voters for a vote are determined and fixed when the Voting Period begins.
 Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.

### 2025-12-22 constitution.tex

@@
 Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
-Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
+Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.
 
@@
 \asubsection{Eligible Votes}
-The number of Active Members eligible to vote on the issue.
-The eligible voters for a vote are determined and fixed when the Voting Period begins.
+The number of Active Members who are eligible to vote on the issue.
 Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
